### 2020-03-24 tex/gitlinks.tex

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/cfda45841cf4235e82cf705ab27251bd783bdf8c/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/cfda45841cf4235e82cf705ab27251bd783bdf8c/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/cfda45841cf4235e82cf705ab27251bd783bdf8c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

### 2020-03-24 tex/ms.tex

% !TeX root = ./ms.tex
\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}

% Bibliography stuff
\bibliographystyle{aasjournal}

% Begin!
\begin{document}

% Title
\title{Title here}

% Author list
\author{Fran Bartoli\'c}
\email{fbartolic@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%

\begin{abstract} 
Abstract here.
%
\href{https://github.com/rodluger/starrynight}{\color{linkcolor}\faGithub}
\end{abstract}

%
\section{Introduction}
%
Intro here \citep{Luger2019}.
Here's an equation with a proof:
%
\begin{proof}{dummy}
    \label{eq:dummy}
    1 + 1 = 2.
\end{proof}
The proof is a Jupyter notebook with a formal derivation of the solution,
an informal justification, a numerical validation, or whatever you want it
to be.
%
And here's a figure with a link:
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/dummy.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:dummy}
    }
    \end{centering}
\end{figure}

% Bibliography
\bibliography{bib}

\end{document}

### 2020-04-21 paper/gitlinks.tex
Added abstract and sections for the paper

\newcommand{\codelink}[1]{\href{https://github.com/fbartolic/volcano/blob/c5ab3bfe105a70f2b0b6059d49a00231b3c60efb/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/fbartolic/volcano/blob/c5ab3bfe105a70f2b0b6059d49a00231b3c60efb/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/fbartolic/volcano/blob/c5ab3bfe105a70f2b0b6059d49a00231b3c60efb/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/fbartolic/volcano/_build}{#1}}

### 2020-04-21 paper/gen_links.py

@@ -1,0 +1,27 @@
+from __future__ import print_function
+import subprocess
+import os
+
+# Generate the github links
+hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1]
+slug = os.getenv("TRAVIS_REPO_SLUG", "fbartolic/volcano")
+with open("gitlinks.tex", "w") as f:
+    print(
+        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\cilink}[1]{\href{https://dev.azure.com/%s/_build}{#1}}" % (slug),
+        file=f,
+    )

### 2020-04-21 paper/paper.tex
Added abstract and sections for the paper

% !TeX root = ./ms.tex
\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}

% Bibliography stuff
\bibliographystyle{aasjournal}

% Begin!
\begin{document}

% Title
\title{Inferring a time dependent map of Io's surface with occultation mapping.}

% Author list
\author{Fran Bartoli\'c}
\email{fbartolic@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
\affil{Centre for Exoplanet Science, SUPA, School of Physics and Astronomy, University of St. Andrews, St. Andrews, UK}
\author{Rodrigo Luger}
\author{Daniel Foreman-Mackey}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%

\begin{abstract} 
Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanos varying in intensity on different timescales. 
Although the surface of Io has been resolved from both space and ground, to constrain the long term variability it is necessary to use ground based observations taken during occultations by Jupiter and other moons with a time baseline spanning decades.
These infrared light curves encode information %on both the time variability and the two dimensional features on the surface of the moon.
on the two dimensional time variable features on the surface of the moon.
Whereas previous occultation studies focused mostly on studying the variability of individual volcanos, we build a single probabilistic model for a collection of light curves in order to infer a single time dependent map of Io.
    It uses the code Starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which can model occultations in both emitted and reflected light and also enables efficient inference with Hamiltonian Monte Carlo.
The output of the model is a time dependent map of Io's surface with realistic uncertainties.
We use this map to study the time variability of prominent hotspots and the global heatflow over a timescale of decades. The methods we develop to map Io are directly applicable to the mapping of exoplanet surfaces. 
We discuss this application towards the end of the paper.
    \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
\end{abstract}

%
\section{Introduction}
\section{The model}
% Describe the model for inferring a time variable map.
\section{The inverse problem}
% Talk about analytic posteriors with bilinear solve in the simplest case and inference with PyMC3
\subsection{Priors}
\section{The information content of a light curve}
\subsection{Size of the nullspace}
% Plots of the fractional size of the nullspace as a function of map degree for static maps.
\subsection{Recovering a static map}
% Fit a simulated dataset and test predictions from the previous subsection
\section{Fitting a simulated dataset}
% Using ephemeris from real datasets we generate a simulated map consisting of multiple stochastically varying hot spots. Discuss inference with optimizers and sampling with HMC. 
% What can we recover? What breaks the model?
\section{Results from IRTF observations}
\subsection{The dataset}
% Describe the dataset
\subsection{The global map}
% Global properties of the inferred map.
\subsection{Variability of known hotspots}
% Plot inferred intensities of known hotspots as function of time, reference previous work.
\section{Relevance to mapping surfaces of exoplanets}
% I think this should be either a short section describing how all of the formalism developed 
% previously can be easily applied to future exoplanet observations with JWST etc. or we can go
% into more details and simulate a JWST observation of a warm jupiter (super earth?) with some 
% time variable features on its surface.

%Intro here \citep{Luger2019}.
% Here's an equation with a proof:
%
%\begin{proof}{dummy}
%    \label{eq:dummy}
%    1 + 1 = 2.
%\end{proof}
%The proof is a Jupyter notebook with a formal derivation of the solution,
%an informal justification, a numerical validation, or whatever you want it
%to be.
%%
%And here's a figure with a link:
%%
%\begin{figure}[h!]
%    \begin{centering}
%    \includegraphics[width=0.5\linewidth]{figures/dummy.pdf}
%    \oscaption{pretty_function}{%
%        This is a plot of a pretty function. And at the end of this
%        caption is a symbol with a link to the \emph{exact} script
%        that generated it, hosted on \textsf{GitHub}.
%        \label{fig:dummy}
%    }
%    \end{centering}
%\end{figure}
%
 Bibliography
\bibliography{bib}
\end{document}

### 2020-04-23 volcano/time_dependent_solver.py
Added GP prior on the coefficient matrix. Implemented support for sparse matrices

@@ -2,8 +2,10 @@ import numpy as np
 from scipy.sparse import block_diag as sparse_block_diag
 from scipy.linalg import block_diag as dense_block_diag
 from scipy.linalg import cho_factor, cho_solve
+import celerite
 import theano
 import theano.tensor as tt
+import theano.sparse as ts
 from tqdm import tqdm
 from volcano.optimizers import Adam, NAdam
 
@@ -29,15 +31,20 @@ class TimeDependentMapSolver(object):
         K (int, optional): The number of basis maps used to represent the
             map for any given light curve. By definition K << L where L
             is the total number of light curves. Defaults to 3.
-        p_mu (float or ndarray, optional): Prior mean on  the spherical
-            harmonic coefficients of the basis maps p=vec(P).
-            Defaults to 0.
-        p_sig (float or ndarray, optional): Prior standard deviation on
-            p Defaults to 0.01.
-        q_mu (float or ndarray, optional): Prior mean on the coefficient
-            vector q = vec(Q). Defaults to zero.
-        q_sig (float, optional): Prior standard deviation on q. 
-            Defaults to 1.
+        t_grid (ndarray, optional): Grid of size L on which the GP is to be
+            evaluated.
+        P_mu (float or ndarray, optional): Prior mean on the spherical
+            harmonic coefficients of the basis maps of shape (N, K)  where N
+            is the nr. of coefficients and K is the number of basis maps.
+        P_sig (float or ndarray, optional): Prior standard deviation on
+            P. 
+        Q_mu (float or ndarray, optional): Prior mean on the coefficient
+            matrix of shape (K, L) where K is the number of basis maps and L
+            is the number of light curves.
+        Q_sig (ndarray, optional): Prior standard deviation for the GP on the
+            coefficient matrix. This is needs to be an array of size K.
+        Q_rho (float, optional): Prior lenghtscale for the GP on the
+            coefficient matrix. This is needs to be an array of size K. 
     """
 
     def __init__(
@@ -46,19 +53,22 @@ class TimeDependentMapSolver(object):
         ferr_list,
         A_list,
         K=3,
-        p_mu=0.0,
-        p_sig=0.01,
-        q_mu=0.0,
[…]

### 2020-06-07 paper/paper.tex
Rewrote abstract. Wrote draft introduction.

@@
 % Title
-\title{Inferring a time dependent map of Io's surface with occultation mapping.}
+%\title{Inferring a time dependent map of Io's surface from occultations and phase curves.}
+\title{Time-variable surface mapping of exoplanets: an application to Io}
 
@@
 \begin{abstract} 
-Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanos varying in intensity on different timescales. 
-Although the surface of Io has been resolved from both space and ground, to constrain the long term variability it is necessary to use ground based observations taken during occultations by Jupiter and other moons with a time baseline spanning decades.
-These infrared light curves encode information %on both the time variability and the two dimensional features on the surface of the moon.
-on the two dimensional time variable features on the surface of the moon.
-Whereas previous occultation studies focused mostly on studying the variability of individual volcanos, we build a single probabilistic model for a collection of light curves in order to infer a single time dependent map of Io.
-    It uses the code Starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which can model occultations in both emitted and reflected light and also enables efficient inference with Hamiltonian Monte Carlo.
-The output of the model is a time dependent map of Io's surface with realistic uncertainties.
-We use this map to study the time variability of prominent hotspots and the global heatflow over a timescale of decades.
-The methods we develop to map Io are directly applicable to the mapping of exoplanet surfaces.
-We discuss this application towards the end of the paper.
-    \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales. 
+Existing photometric observations in the near infrared taken during occultations by Jupiter and Galilean moons encode a wealth of information about its surface. 
+As such, Io is an ideal testbed for models of time-variable exoplanet surfaces. 
+We build a single probabilistic model of Io's surface using Nonnegative Matrix Factorization to infer one map per light curve.
+The model is built on top of the code Starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which can compute occultation light curves and phase curves in both emitted and reflected light.
+It also enables efficient inference with gradient based samplers.
+We use the inferred map to study the time variability of prominent volcanoes over a timescale of decades.
+While we mostly focus on Io, the lessons we learn are directly applicable to mapping exoplanets. 
+We discuss this application towards the end of the paper.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+
 \end{abstract}
@@
 \section{Introduction}
-\section{The model}
-% Describe the model for inferring a time variable map.
+The surface of Jupiter's moon Io is littered with hundreds of volcanoes appearing as bright spots in the near infrared and varying in intensity on timescales of days to decades.
+The volcanic activity is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale_melting_1979}.
+Io is a perfect analogue of an extremely volcanically active exoplanet.
+Such rocky exoplanets, often dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because the photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future \citep{kaltenegger_detecting_2010,henning_highly_2018,oza_sodium_2019}.
+Studying volcanism on both Io and exoplanets is scientifically valuable because it provides a window into the properties of early Earth and it informs theories of planet formation.
+
+Existing exoplanet detections with potential volcanism include CoRoT-7b \citep{barnes_corot-7b_2010}, the first discovered rocky exoplanet with likely significant tidal heating; 55 Cancri e, whose longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory_variability_2016,demory_map_2016,hammond_linking_2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova_magma_2017,dobos_tidal_2019}; and many others.
+Not all exoplanets will have Io-like volcanism, some will have magma oceans due to their proximity to the star or volcanism caused by nuclear decay similar to early Earth volcanism.
+
+Io has been observed extensively using both space and ground observatories.
+High resolution images of Io's surface were taken by space missions such as Voyager \citep{smith_jupiter_1979}, Galileo \citep{belton_galileos_1996} and Juno \citep{mura_infrared_2020}.
+It has also been resolved from the ground in the near infrared using disk resolved imaging
+\citep{howell_infrared_1985,simonelli_disk-resolved_1986,spencer_discovery_1990} and adaptive optics observations \citep{marchis_adaptive_2000,marchis_keck_2005,de_kleer_spatial_2016}.
+Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter starting with \cite{spencer_discovery_1990}.
+Occultations by Jupiter occur twice every orbit lasting ~1.7 days and mutual occultations with Europa, Ganymede or Callisto happen every ~6 years when Earth pasess through the orbital plane of Galilean satellites.
+The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow ("in eclipse") while mutual occultations are almost always observed in sunlight because mutual occultations while Io is in eclipse are extraordinarily rare.
+Only the brightest volcanoes are visible over the reflected light background when Io is illuminated by the Sun\citep{veeder_ios_1994,de_kleer_spatial_2016}.
+
+Both kinds of occultations have been used to study volcanic activity on the surface.
+\cite{spencer_io_1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
+\cite{rathbun_loki_2002, rathbun_loki_2006,rathbun_ground-based_2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots finding evidence of periodicity in Loki's eruptions and established the transient nature of the volcanoes (only Loki is persistently active).
+By studying an occultation of Io by Europa, \cite{de_kleer_multi-phase_2017} mapped the Loki region to a precision of about 2 kilometers.
+In addition to observations of occultations in near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot_mutual_1974,saquet_phemu15_2018,morgado_astrometry_2016} with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
+
+None of the studies of occultations in the infrared attempted to infer a two-dimensional map of Io's surface. 
+The light curves are usually fit independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface.
+Strong priors on the locations of individual volcanoes are assumed based on maps from space mission observations.
+In this work, we build a fully probabilistic model in order to infer a time-dependent two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infra red.
+The model is built on top of the recently developed code Starry \citep[][Luger et al. 2020 in prep]{luger_starry_2019} which 
+enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
+Starry can compute phase curves and occultations in both emitted light (for modeling the isotropic volcanic emission from Io's surface) and reflected light (for mapping albedo variations).
+Instead of fitting one map per occultation light curve, we reduce the dimensionality of the problem using matrix factorization, assuming a fixed map for a given light curve which is a linear combination of $K$ basis maps.
+We use priors on the map features which ensure the maps are physical and prevent overfitting of the data.
+The model is interpretable, each of the basis maps roughly corresponds to a single spot on the surface, and the coefficients multiplying the basis maps encode information on the time variability.
+
+Our goals for this paper are to both improve on past studies of Io using occultation light curves and to construct a flexible model directly applicable to future efforts on inferring time-dependent maps of variable features on exoplanet surfaces such as volcanoes, magma oceans or clouds.
+The fact that we have lots of prior information on what the surface of Io should look like enables us to test our model in a realistic setting, testing sensitivity to chosen priors, data quality, the orbital parameters and different kinds of surface features.
+
+The paper is organized as follows.
+In \S\ref{sec:data} we describe the IRTF light curves of occultations by Jupiter which we use to infer maps. 
+In \S\ref{sec:model} we discuss the generative model for the data for the case of a static map, and a dynamic map modeled using a matrix factorization approach and we write down the relevant likelihood functions.
+In \S\ref{sec:inverse_problem} we focus on the question of how to do Bayesian inference given the forward model specifications defined in \S\ref{sec:model}. 
+We discuss and test different priors on map features, the information content of light curves and fitting the models using variational inference (VI) methods and Hamiltonian Monte Carlo (HMC).
+We present results on simulated data.
+\S\ref{sec:results} shows the results on real data.
+In particular, the inferred dynamic map, the  different component maps and accompanying coefficients, the uncertainties of the maps, sensitivity to different choices of priors, comparison of inferred locations and intensities of spots to known values from the literature.
+Finally, in \S\ref{sec:exoplanets} we discuss applications of the model to future exoplanet obervations and test the model predictions on simulated JWST observations of a volcanic Super-Earth.
+
+\section{Data}
+\label{sec:data}
+\section{Model}
+\label{sec:model}
+% Discuss starry, pixels vs. schmixels vs. harmonics, forward model for static map, NMF model for dynamic map
+\subsection{Orbital parameters}
+\label{ssec:orbital_parameters}
+% Talk about JPL horizons, uncertainties on parameters, geometry of occultations etc.
+
 \section{The inverse problem}
-% Talk about analytic posteriors with bilinear solve in the simplest case and inference with PyMC3
-\subsection{Priors}
-\section{The information content of a light curve}
-\subsection{Size of the nullspace}
-% Plots of the fractional size of the nullspace as a function of map degree for static maps.
-\subsection{Recovering a static map}
-% Fit a simulated dataset and test predictions from the previous subsection
-\section{Fitting a simulated dataset}
-% Using ephemeris from real datasets we generate a simulated map consisting of multiple stochastically varying hot spots. Discuss inference with optimizers and sampling with HMC. 
-% What can we recover? What breaks the model?
-\section{Results from IRTF observations}
-\subsection{The dataset}
-% Describe the dataset
-\subsection{The global map}
-% Global properties of the inferred map.
+\label{sec:inverse_problem}
+% bulk of the results in the paper
+\subsection{The information content of a light curve}
+% information in different kinds of occultations/phase curves, reflected light vs. emitted light, posterior shrinkage etc.
+
+\label{ssec:information_content}
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/information_content.pdf}
+    \oscaption{InformationContent}{%
+        This is a plot of a pretty function. And at the end of this
+        caption is a symbol with a link to the \emph{exact} script
+        that generated it, hosted on \textsf{GitHub}.
+        \label{fig:information_content}
+    }
+    \end{centering}
+\end{figure}
+
+\subsection{Fitting a static map}
+\label{ssec:static_map}
+% Priors for static maps, sparsity, positivity, plot of map inference with simulated data and different kinds of priors. Inference with MAP, VI, HMC.
+
+\subsection{Fitting a dynamic map}
+\label{ssec:dynamic_map}
+% Priors for NMF. Optimization vs. bayesian approach to NMF. Results on simulated data. Comparison of results to matrix factorization without the positivity constraint and clever priors.
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Individual events}
+\label{ssec:individual}
+% Fits of individual events. In particular, those light curves that were analyzed in previous papers.
+
+\subsection{The time-variable map}
+\label{ssec:time_variable_map}
+%
+
 \subsection{Variability of known hotspots}
+\label{ssec:variability_hotspots}
 % Plot inferred intensities of known hotspots as function of time, reference previous work.
-\section{Relevance to mapping surfaces of exoplanets}
-% I think this should be either a short section describing how all of the formalism developed 
-% previously can be easily applied to future exoplanet observations with JWST etc. or we can go
-% into more details and simulate a JWST observation of a warm jupiter (super earth?) with some 
-% time variable features on its surface.
 
-%Intro here \citep{Luger2019}.
-% Here's an equation with a proof:
-%
-%\begin{proof}{dummy}
-%    \label{eq:dummy}
-%    1 + 1 = 2.
-%\end{proof}
-%The proof is a Jupyter notebook with a formal derivation of the solution,
-%an informal justification, a numerical validation, or whatever you want it
-%to be.
-%%
-%And here's a figure with a link:
-%%
-%\begin{figure}[h!]
-%    \begin{centering}
-%    \includegraphics[width=0.5\linewidth]{figures/dummy.pdf}
-%    \oscaption{pretty_function}{%
-%        This is a plot of a pretty function. And at the end of this
-%        caption is a symbol with a link to the \emph{exact} script
-%        that generated it, hosted on \textsf{GitHub}.
-%        \label{fig:dummy}
-%    }
-%    \end{centering}
-%\end{figure}
-%
- Bibliography
+\section{Mapping volcanic exoplanets}
+\label{sec:exoplanets}
+% Application to exoplanets. Fitting mock JWST observations.
+
+% Bibliography
 \bibliography{bib}

### 2020-06-07 volcano/time_variable_map.py

@@ -46,24 +46,6 @@ class TimeDependentMapSolver(object):
             coefficient matrix. This is needs to be an array of size K.
         Q_rho_gp (float, optional): Prior lenghtscale for the GP on the
             coefficient matrix. This is needs to be an array of size K. 
-        sp_alpha (ndarray, optional): Alpha parameter of the beta distribution
-            in cos(lat) for the Starry Process. Array of size K.
-        sp_beta (ndarray, optional): Beta parameter of the beta distribution
-            in cos(lat) for the Starry Process. Array of size K. 
-        sp_P0_sig (ndarray, optional): Standard deviation of the Y_00
-            coefficient for each of the K basis maps. This needs to be specified
-            separately because the Starry Process asigns a very small value for
-            these coefficients. 
-        sp_ln_size_mu (ndarray, optional): Log of the spot size distribution
-            mean. Array of size K.
-        sp_ln_size_sig (ndarray, optional): Log of the spot size distribution
-            standard deviation. Array of size K.
-        sp_ln_amp_mu (ndarray, optional): Log of the spot amplitude distribution
-            mean. Array of size K.
-        sp_ln_amp_sig (ndarray, optional): Log of the spot amplitude distribution
-            standard deviation. Array of size K.
-        sp_sign (ndarray, optional): Sign of the spot amplitude. Positive is a
-            dark spot. Array of size K.
     """
 
     def __init__(
@@ -79,14 +61,6 @@ class TimeDependentMapSolver(object):
         Q_sig=None,
         Q_sig_gp=None,
         Q_rho_gp=None,
-        sp_alpha=None,
-        sp_beta=None,
-        sp_P0_sig=None,
-        sp_ln_size_mu=None,
-        sp_ln_size_sig=None,
-        sp_ln_amp_mu=None,
-        sp_ln_amp_sig=None,
-        sp_sign=None,
     ):
 
         # Data
@@ -112,16 +86,6 @@ class TimeDependentMapSolver(object):
         self.Q_rho_gp = Q_rho_gp
         self._q_CInv = None
         self._p_CInv = None
-
-        # Starry Process parameters
-        self._sp_alpha = sp_alpha
-        self._sp_beta = sp_beta
-        self._sp_P0_sig = sp_P0_sig
-        self._sp_ln_size_mu = sp_ln_size_mu
-        self._sp_ln_size_sig = sp_ln_size_sig
-        self._sp_ln_amp_mu = sp_ln_amp_mu
-        self._sp_ln_amp_sig = sp_ln_amp_sig
[…]

### 2020-06-07 paper/figures/notebook_setup.py
Rewrote abstract. Wrote draft introduction.

@@ -1,0 +1,31 @@
+# Pretty figures
+get_ipython().magic('config InlineBackend.figure_format = "retina"')
+
+
+import matplotlib
+import matplotlib.pyplot as plt
+import warnings
+
+
+# Disable annoying font warnings
+matplotlib.font_manager._log.setLevel(50)
+
+
+# Disable theano deprecation warnings
+warnings.filterwarnings("ignore", category=DeprecationWarning)
+warnings.filterwarnings("ignore", category=FutureWarning)
+warnings.filterwarnings("ignore", category=UserWarning, module="theano")
+
+
+# Style
+plt.style.use("default")
+plt.rcParams["savefig.dpi"] = 100
+plt.rcParams["figure.dpi"] = 100
+plt.rcParams["figure.figsize"] = (12, 4)
+plt.rcParams["font.size"] = 14
+plt.rcParams["text.usetex"] = False
+plt.rcParams["font.family"] = "sans-serif"
+plt.rcParams["font.sans-serif"] = ["Liberation Sans"]
+plt.rcParams["font.cursive"] = ["Liberation Sans"]
+plt.rcParams["mathtext.fontset"] = "cm"
+plt.rcParams["mathtext.fallback_to_cm"] = True

### 2020-06-07 tex/gen_links.py

@@ -1,27 +1,0 @@
-from __future__ import print_function
-import subprocess
-import os
-
-# Generate the github links
-hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1]
-slug = os.getenv("TRAVIS_REPO_SLUG", "fbartolic/volcano")
-with open("gitlinks.tex", "w") as f:
-    print(
-        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}"
-        % (slug, hash),
-        file=f,
-    )
-    print(
-        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}"
-        % (slug, hash),
-        file=f,
-    )
-    print(
-        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
-        % (slug, hash),
-        file=f,
-    )
-    print(
-        r"\newcommand{\cilink}[1]{\href{https://dev.azure.com/%s/_build}{#1}}" % (slug),
-        file=f,
-    )

### 2020-06-07 volcano/tests/test_time_dependent_solver.py

@@ -1,42 +1,0 @@
-import numpy as np
-from scipy.sparse import block_diag as sparse_block_diag
-from scipy.linalg import block_diag as dense_block_diag
-from scipy.linalg import cho_factor, cho_solve
-import theano
-import theano.tensor as tt
-
-# sys.path.append("../../volcano")
-# from optimizers import Adam, NAdam
-# from time_dependent_solver import TimeDependentMapSolver
-
-from volcano.optimizers import Adam, NAdam
-from volcano.time_dependent_solver import TimeDependentMapSolver
-
-np.random.seed(42)
-
-# Create some mock data
-L = 45
-N = 81
-K = 4
-npts = np.random.randint(500, size=L)
-f_list = [np.random.rand(n) for n in npts]
-ferr_list = [1e-2 * np.ones_like(f_list[i]) for i in range(L)]
-A_list = [np.random.rand(n, N) for n in npts]
-solver = TimeDependentMapSolver(f_list, ferr_list, A_list, K)
-
-
-def test_bilinear_form():
-
-    P = np.random.rand(solver.N, solver.K)
-    Q = np.random.rand(solver.K, solver.L)
-    Y = P @ Q
-
-    Qp = solver.get_Qp(Q)
-    Pp = solver.get_Pp(P)
-
-    f1 = solver.A @ Y.T.flatten()
-    f2 = solver.A @ Qp @ P.T.flatten()
-    f3 = solver.A @ Pp @ Q.T.flatten()
-
-    assert np.allclose(f1, f2)
-    assert np.allclose(f2, f3)

### 2020-06-09 paper/gen_links.py
Fixing paper build

@@ -7,17 +7,17 @@ hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1
 slug = os.getenv("TRAVIS_REPO_SLUG", "fbartolic/volcano")
 with open("gitlinks.tex", "w") as f:
     print(
-        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}"
+        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/paper/figures/#1.py}{\codeicon}\,\,}"
         % (slug, hash),
         file=f,
     )
     print(
-        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}"
+        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/paper/figures/#1.gif}{\animicon}\,\,}"
         % (slug, hash),
         file=f,
     )
     print(
-        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
+        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/paper/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
         % (slug, hash),
         file=f,
     )

### 2020-06-16 paper/paper.tex
Added some figures, sarted writing the data section.

@@
-% !TeX root = ./ms.tex
+% !TeX root = ./paper.tex
 \documentclass[modern]{aastex62}
@@
 \section{Introduction}
+%% ADD PARAGRAPH REVIEWING PREVIOUS LITERATURE ON MAPPING EXOPLANETS, MENTION JWST AND LUVOIR
+%% MAYBE EVEN IN THE ABSTRACT
 The surface of Jupiter's moon Io is littered with hundreds of volcanoes appearing as bright spots in the near infrared and varying in intensity on timescales of days to decades.
@@
 \label{sec:data}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/irtf_max_flux.pdf}
+    \oscaption{irtf_dataset}{%
+        Maximum flux for each curve taken using NASA's IRTF telescope during an
+        occultation of Io by Jupiter.
+       \label{fig:irtf_max_flux}
+    }
+    \end{centering}
+\end{figure}
+
+The dataset we use to infer maps of Io's surface consists of 112 observations of Io in the near infrared taken from 1996 until 2018 using various instruments at NASA's IRTF observatory.
+Figure~\ref{fig:irtf_max_flux} shows the maximum flux in $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ for each light curve plotted as a function of time which approximately corresponds to the disc integrated flux of Io at the beginning of ingress or the end of egress prior to it being occulted by Jupiter.
+Two features of this plot are apparent.
+First although the observations span decades the cadence is non-uniform with only a few observations taken between 2008 and 2016.
+Second, the baseline brightness is varying stochastically by a large amount and there are several notable events of increased volcanic activity.
+All of the observations were taken while Io was \emph{in eclipse}, meaning that it was in Jupiter's shadow and all of the observed emission from the surface is due to thermal radiation.
+Observations of Io \emph{in sunlight} on the other hand probe both the thermal (volcanic) emission and the surface albedo variations in the near infrared.
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/irtf_sample_lightcurves.pdf}
+    \oscaption{irtf_dataset}{%
+        A selection of sample light curves taken during occultations of Io by Jupiter in our dataset.
+        The step-like morphology of the light curves is due to bright volcanoes on Io's surface coming in or out of view during an occultation.
+        These light curves thus visibly encode information about the features on the surface.
+        \label{fig:irtf_sample_lightcurves}
+    }
+    \end{centering}
+\end{figure}
+
+In Figure~\ref{fig:irtf_sample_lightcurves} we display a random subset of all the light curves
+in the dataset.
+All occultations last for $\sim4$ min and the cadence for each light varies but it on the order of a second.
+It follows that over the course of a single exposure Jupiter's limb move by about 15km which provides a lower bound for the size of the features on the surface that we can reliably estimate.
+The shapes of light curves strongly deviate from the smooth variability one would expect assuming a homogeneous distribution of thermal emission on the surface.
+Especially prominent are light curves with clear step-like features which are present when bright spots come in or out of view during the course of an occultation.
+The fact that these features are so clearly visible means that even individual light curves encode a wealth of information about the surface.
+
+The photometric quality varies from year to year because multiple instruments were used over the years.
+An additional issue is that estimated errorbars aren't provided.
+As with all ground based photometry, the observations are influenced by atmospheric variability which induces correlated noise in the light curves.
+Because of this the flux isn't always monotonically increasing or decreasing as one would expect.
+All of these issues need to be accounted for in the final model.
+
 \section{Model}
@@
 \label{ssec:orbital_parameters}
+To model the occultations, first we need to know the trajectory of Jupiter relative to Io for any given time.
+To compute the trajectory we use  \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner_planetary_2014}.
+The quantities given by the Horizons database needed to uniquely define the relative trajectory
+of Jupiter and the orientation of Io with respect to the observer on Earth are given in Table~\ref{tab:horizons}.
+JPL Horizons interface provides $(\alpha,\delta)$ coordinates of both objects and the
+central longitude and latitude
+
 % Talk about JPL horizons, uncertainties on parameters, geometry of occultations etc.
@@
 \subsection{The information content of a light curve}
+\label{ssec:information_content}
 % information in different kinds of occultations/phase curves, reflected light vs. emitted light, posterior shrinkage etc.
 
-\label{ssec:information_content}
 \begin{figure}[h!]
@@
 
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/single_event_fit.pdf}
+    \oscaption{single_event_fit}{%
+        This is a plot of a pretty function. And at the end of this
+        caption is a symbol with a link to the \emph{exact} script
+        that generated it, hosted on \textsf{GitHub}.
+        \label{fig:single_event_fit}
+    }
+    \end{centering}
+\end{figure}
+
 \subsection{The time-variable map}

### 2020-06-20 paper/paper.tex
Added a section on the forward model.

@@
 We build a single probabilistic model of Io's surface using Nonnegative Matrix Factorization to infer one map per light curve.
-The model is built on top of the code Starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which can compute occultation light curves and phase curves in both emitted and reflected light.
+The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which can compute occultation light curves and phase curves in both emitted and reflected light.
 It also enables efficient inference with gradient based samplers.
@@
 In this work, we build a fully probabilistic model in order to infer a time-dependent two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infra red.
-The model is built on top of the recently developed code Starry \citep[][Luger et al. 2020 in prep]{luger_starry_2019} which
+The model is built on top of the recently developed code starry \citep[][Luger et al. 2020 in prep]{luger_starry_2019} which
 enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
-Starry can compute phase curves and occultations in both emitted light (for modeling the isotropic volcanic emission from Io's surface) and reflected light (for mapping albedo variations).
+starry can compute phase curves and occultations in both emitted light (for modeling the isotropic volcanic emission from Io's surface) and reflected light (for mapping albedo variations).
 Instead of fitting one map per occultation light curve, we reduce the dimensionality of the problem using matrix factorization, assuming a fixed map for a given light curve which is a linear combination of $K$ basis maps.
@@
 \label{ssec:orbital_parameters}
-To model the occultations, first we need to know the trajectory of Jupiter relative to Io for any given time.
-To compute the trajectory we use  \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner_planetary_2014}.
-The quantities given by the Horizons database needed to uniquely define the relative trajectory
-of Jupiter and the orientation of Io with respect to the observer on Earth are given in Table~\ref{tab:horizons}.
-JPL Horizons interface provides $(\alpha,\delta)$ coordinates of both objects and the
-central longitude and latitude
+To model the occultations we need to know the projected separation between Jupiter and Io and the orientation of Io at any given time.
+We use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner_planetary_2014} for this purpose.
+Specifically, we use the Right Ascension and Declination, the angular (equatorial) diameter (\textsf{Ang-diam}), the visibility flag indicating whether Io is occulted or not and whether it is in partial or total eclipse (\textsf{Ang-sep/v}), the longitude and latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}), the sub-solar point longitude and latitude which specify the direction pointing towards the Sun on Io's surface (\textsf{Sl-lon}, \textsf{Sl-lat}), the distance from Io to the Sun (\textsf{r}) and
+the counterclockwise angle between the Celestial North Pole unit vector projected onto the plane of the sky and the Io's north pole (\textsf{NP.ang}).
+All longitudes are positive to the west.
+\textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 second so we interpolate all values such that we can evaluate them for arbitrary times.
 
-% Talk about JPL horizons, uncertainties on parameters, geometry of occultations etc.
+The coordinate system in \textsf{starry} is defined to be right handed such that the $\hat{z}$
+axis points towards the observer and the $\hat{x}$ axis points to the right on the plane of the sky.
+The radius of the occulted sphere is fixed to 1 and the orientation is specified by three angles,
+the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the North Pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the North Pole is aligned with the $\hat{y}$ axis and the phase angle \textsf{theta} rotates the sphere around the $\hat{y}$ axis in the eastward direction.
+We have $\mathrm{obl}=\textsf{NP.ang}$, $\mathrm{inc}=90^\circ-\textsf{Ob-lat}$ and
+$\mathrm{theta}=\textsf{Ob-lon}$.
+The occultor position relative to the occulted object is given by
+\begin{align}
+    \mathrm{xo}/\gamma&=-\Delta\alpha\,\cos\delta\\
+    \mathrm{yo}/\gamma&=\Delta\delta\\
+    \mathrm{zo}/\gamma&=1
+\end{align}
+where $\Delta\alpha$ are the $\Delta\delta$ differences in Right Ascension and Declination respectively relative to the occulted object and $\gamma$ is the angular radius of the occulted sphere.
+If the occulted object is illuminated by the Sun then we also need to specify the coordinates of the light source which are given by
+\begin{align}
+    \mathrm{xs}&=r\cos\theta\sin\phi\\
+    \mathrm{ys}&=r\sin\theta\\
+    \mathrm{zs}&=r\cos\theta\cos\phi
+\end{align}
+where $\theta$ is obtained by subtracting \textsf{Ob-lat} from \textsf{Sl-lat} and similarly $\phi$ is obtained by subtracting \textsf{Ob-lon} from \textsf{Sl-lon}.
+$r$ is equal to the heliocentric distance of the occulted object \textsf{r}.
+
+\subsection{Static map model}
+\label{ssec:static}
+Given the geometry of on occultation event at an arbitrary time, computing the predicted flux with \textsf{starry} is straightforward.
+\textsf{starry} computes the integrated flux of an unocculted or an occulted sphere analytically assuming that the surface map can be expanded in terms of spherical harmonics $Y_{lm}(\theta,\phi)$ up to a certain \emph{degree} $l$.
+The map is thus defined by a vector of spherical harmonic coefficients $\mathbf{y}$ multiplying the spherical harmonic basis $\tilde{\mathbf{y}}(x, y)=\left(Y_{0,0} Y_{1,-1} Y_{1,0} Y_{1,1} Y_{2,-2} Y_{2,-1} Y_{2,0} Y_{2,1} Y_{2,2} \cdots\right)^{\top}$ and the total number of coefficients is $(l+1)^2$.
+In addition to computing \emph{thermal} phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations when the sphere is illuminated by a distant light source \citep[Luger et al.
+2020 in prep][]{} which is complicated by the presence of the terminator line.
+In the case of a reflected light map, the coefficient vector $\mathbf{y}$ represents spherical albedo in a given wavelength range.
+Most importantly, conditional on the parameters specifying the geometry of the occultations being fixed, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
+This is achieved by representing all rotations, changes of basis and integrals with complicated boundaries needed to compute the flux as linear transformations.
+Since a sequence of linear mappings is also linear, the predicted flux can be written as
+\begin{equation}
+    \mathbf{f}=\mathbf{A}\,\mathbf{y}
+\end{equation}
+where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and optionally the direction of the illumination source and $\mathbf{A}$ is the design
+matrix of shape $(T, N)$ (with $N=(l+1)^2$) which encodes information all operations needed to compute the integrated flux.
+If the geometry isn't known precisely then the matrix $\mathbf{A}$ is not fixed and the model is no longer linear.
+
+The characteristic angular scale of features that can be represented with a given map is set by the degree of the map and it is approximately equal to $\frac{180^\circ}{l}$.
+State of the art inferences involving phase curves and secondary eclipses of exoplanets are able to constrain features of order $l=1$ (inferring a bright spot on single hemisphere) but for Io we need to fit much higher order maps because the typical scale of volcanic spots is on the order of tens of kilometers (a few degrees).
+\textsf{starry} can handle computations with maps up to $l\approx 20$ before numerical instabilities kick in (TODO: make this statement more precise).
+
+Although \textsf{starry} is built around the idea of expending surface features in a spherical harmonic basis, this is not the ideal basis for doing inference because it makes it difficult to ensure positivity of the maps.
+Ideally we would like to fit all models in the \emph{pixel basis} where ensuring positivity is trivial but still do all computations in the $Y_{lm}$ basis where everything is analytic and fast.
+We obtain the pixels by constructing a discrete grid on the surface of the sphere using an equal area Molleweide projection.
+To ensure that the intensity is positive everywhere on the surface we also need to have more pixels than spherical harmonics (by a factor of a few).
+The mapping $\mathbf{P}$ from the spherical harmonic basis to the pixel basis is linear operator and it is straightforward to compute.
+Unfortunately, because the number of pixels is greater than the number of $Y_{lm}$ coefficients, the matrix $\mathbf{P}$ is not square and is therefore not invertible.
+We can still compute Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ which is obtained by solving the linear system $\mathbf{P}\,\mathbf{y}=\mathbf{p}$ where $\mathbf{p}$ is the vector of all pixels comprising a map.
+The model is also linear in the pixels:
+\begin{equation}
+    \mathbf{f}=\mathbf{A}\,\mathbf{P}^\dagger\,\mathbf{p}
+    \label{eq:linear_model_pix}
+\end{equation}
+In what follows, we will assume that we work in the pixel basis and compute all fluxes in the $Y_{lm}$ basis where the model is exact.
+We will discuss the validity of this approach in detail in Section~\ref{sec:inverse_problem}.
+
+\subsection{Nonnegative Matrix Factorization}
+\label{ssec:nmf}
+In the case when we cannot assume a static map, the situation is considerably more complicated.
+In principle, the surface map is different for each \emph{data point}.
+Of course, fitting one map per data point is intractable so we might instead fit a single map per light curve, generated by Eq.~\ref{eq:linear_model_pix}.
+Even then, we would need to fit on the order of 1k parameters!
+This is both becuse the number of spherical coefficients scales as $(l+1)^2$ and because when fitting in pixel space we need many more pixels than spherical harmonics to ensure positivity.
+Although fitting a model of such high dimensionality for a single IRTF light curve of high signal to noise ratio is tractable thanks to exact gradients provided by autodifferentiation in \textsf{starry}, we don't want to do that for a hundred or so separate light curves.
+Such a model would be very difficult to fit and it would require strong regularization between successive maps in time.
+It also wouldn't directly provide much physical insight into the volcanic activity, we would have to conduct a separate analysis on the inferred maps to constrain the time variability of the volcanoes.
+Instead, we need an approach which reduces the dimensionality of the problem.
+One way of accomplishing that is to expand the spherical harmonic coefficients (or pixels) in a Taylor series in time about a certain point.
+This is the approach \cite{luger_tess_2019} took to model a map of Earth's albedo in reflected light from stray Earthshine in the aperture of the TESS space telescope.
+This issue with this approach and similar series expansions such as the Fourier series is that with the very long baseline of IRTF data and the observations being scattered throughout the years sporadically, it is unclear which point should be the origin of the expansion.
+More importantly, there likely doesn't exist a well defined global time-averaged map of Io so requiring too much smoothness between successive maps wouldn't work.
+Another way of reducing the dimensionality of the problem would be a parametric approach where where we place a few spots on the sphere and then fit only for the locations and intensities of each spot.
+This is assuming that we know a priori that the surface features are spot like and roughly how many we should expect.
+While such a strong assumption might work for studying individual spots in the context of Io, it certainly isn't justified for exoplanets.
+In Section~\ref{sec:inverse_problem} we do assume stronger priors on the locations of and shapes of surface features to better constrain the variability of individual volcanoes, but we still fit for pixels, at least in principle allowing the data to override our assumptions.
+
+The approach approach opted for is to treat the problem of inferring a single map per light curve as a probabilistic matrix factorization problem.
+The idea is to assume that a map for any given light curve can be expressed as a linear combination of $K$ "basis maps".
+Consider $L$ lightcurves, the model for the $l$-th light curve is
+\begin{equation}
+    \mathbf{f}_l=\mathbf{A}_l\,\mathbf{P}^\dagger\,\mathbf{p}_l
+\end{equation}
+We can stack the column vectors $\mathbf{p}_l$ into a matrix $\mathbf{Y}$ of shape $(N_p, L)$ where $N_p$ is the number of pixels for each light curve.
+We then assume that the $\mathbf{Y}$ can be decomposed into a product of two matrices $\mathbf{B}$ and $\mathbf{Q}$ as
+\begin{equation}
+    \mathbb{Y}=\mathbf{B}\,\mathbf{Q}
+    \label{eq:nmf}
+\end{equation}
+where $\mathbf{B}$ has shape $(N_p, K)$ and $\mathbf{Q}$ has shape $(K, L)$.
+The model for all light curves can be written as
+\begin{equation}
+    \mathbb{f}=\mathbb{A}\,\mathrm{vec}(\mathbf{\mathbb{Y}})
+    \label{eq:model_all_lcs}
+\end{equation}
+Where $\mathbf{f}$ is a tall column vector consisting of predictions for all light curves stacked together, $\mathbb{A}$ is a block diagonal matrix with matrices $\mathbf{A}_l\,\mathbf{P}^\dagger$ on the diagonal for $l=1\dots, L$ and the $\mathrm{vec}$ operator stacks the columns of $\mathbb{Y}$ into a tall vector.
+The model is \emph{bilinear} which means that is linear in the matrices $\mathbb{B}$ and $\mathbf{Q}$ separately.
+The interpretation of Equation~\ref{eq:nmf} is simple, each of the $K$ columns of $\mathbf{B}$ represents pixels of a basis map and the columns of $\mathbf{Q}$ determine how those maps add together to produce a final map for the $l$-th light curve.
+Ideally, we want the basis maps to be physically meaningful and the coefficients encode the time variability.
+A nice feature of this model is that there is no requirement that successive maps are smoothly varying between different light curves.
+
+The matrix factorization problem as written in Equation~\ref{eq:nmf} is highly degenerate and practically intractable a probabilistic framework with a small dataset.
+Since each of the columns of $\mathbf{B}$ are pixels representing emitted light or albedo, we can substantially reduce the ambiguity in the decomposition by requiring that both matrices are strictly positive.
+This matrix factorization problem is known as \emph{Nonnegative Matrix Factorization} (NMF) \citep{paatero_positive_1994,lee_algorithms_2001} and it has a rich history across many different fields.
+It is commonly used for decomposing physical signals in the spectral or the time domain.
+Even though NMF is more tractable than unconstrained matrix factorization, it is still an NP hard problem \citep{vavasis_complexity_2009} and it requires additional constraints or priors to be tractable.
+Simultaneously transforming $\mathbf{B}\leftarrow \mathbf{B}\,\mathbf{S}^{-1}$ and
+$\mathbf{Q}\leftarrow \,\mathbf{S}\mathbf{Q}$ with a nonsingular matrix $\mathbf{S}$ doesn't change the value of the objective function.
+The objective function is also invariant to a simultaneous permutation of the columns of $\mathbf{B}$ and rows of $\mathbf{Q}$ and rescaling either of the two matrices by a scalar.
+Nevertheless, getting around these degeneracies in practice is possible, especially when we have a lot of prior knowledge on the problem.
+For a recent review article with a detalied analysis of these degeneracies and common algorithms, see \cite{fu_nonnegative_2019}.
+
+Broadly speaking, there are two approaches to fitting NMF models, the constrained optimization approach and the probabilistic approach.
+In the optimization approach we optimize $\mathbb{Y}$ in a least-squares sense under a set of constraints on either one or both of the matrices \citep[see][for recent examples from the astronomical literature]{acosta-pulido_new_2017, melchior_scarlet_2018,ren_non-negative_2018,ren_using_2020}.
+The probabilistic approach introduces priors and the inference is usually done with variational inference.
+In this work we opt for the probabilistic approach because we care about the uncertanties on the map features a lot.
+
+One difference between most applications of NMF in the literature and NMF within the context of infering surface maps from 1D light curves is that
+in the majority of the work in the literature \citep[except][]{kawahara_global_2020} the matrix $\mathbb{Y}$ is assumed to be directly observed  up to a simple noise term.
+In our case the problem is considerably more challenging because we observe the light curves
+$\mathbb{A}\,\mathrm{vec}(\mathbf{\mathbb{Y}})$ instead of $\mathbb{Y}$ directly, a process in which some information is lost because, depending on the geometry of the occultations, certain combinations of spherical harmonic coefficients will be in the nullspace.
+\cite{kawahara_global_2020} are using NMF to model phase variations in directly imaged exoplanets with the goal of simultaneously inferring a surface map and a spectral decomposition of the map into several components, a case in which the
+matrix which is to be decomposed is also unobserved.
+Although we don't attempt to solve the problem of spectrally decomposing the maps, our approach is directly applicable to that problem as well. (TODO: should I add more details here?)
+One could also imagine inferring a multi spectral component and time dependent map by solving two NMF problems simultaneously.
+We leave this application for future work.
+
+\subsection{The likelihood}
+\label{ssec:likelihood}
+Given Eq.~\ref{eq:nmf} we can write down the likelihood for our data and in Section~\ref{sec:inverse_problem} we dicuss in detail the priors which make the problems of inferring static and dynamic maps tractable.
+Assuming a Gaussian noise process for the data with a dense covariance matrix, the (log) likelihood is
+\begin{equation}
+    \ln\mathcal{L}=-\frac{1}{2}\left[\mathbb{f}_\mathrm{obs}-(\mathbb{f} + \mathbb{b})\right]^{\top} \boldsymbol{\Sigma}^{-1}\left[\mathbb{f}_\mathrm{obs}-(\mathbb{f} + \mathbb{b})\right]
+\end{equation}
+where $\mathbb{f}_\mathrm{obs}$ is the vector of stacked observed light curves, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbb{b}$ is a fixed flux offset per light curve accounting for stray flux not attributed to Io (mostly due to Jupiter).
+We model the data covariance with a Gaussian Process using the fast Celerite method\citep{foreman-mackey_fast_2017} as implemented in the \textsf{exoplanet} package (TODO: cite) to capute correlations imposed by the seeing plus an additional white noise term which is different for each light curve.
+The IRTF data isn't provided with any uncertainties so we estimate the uncertainties by filtering the data with the Savitzky Golay filter as implemented in \textsf{SciPy} (TODO: CITE) and estimating the variance of the residuals.
+We assume identical errors for all data points in a given light curve but allow for a rescaling factor when fitting the model.
+In the next section, we add priors to this likelihood and fit the model on simulated data using optimization and Variational Inference (VI).
+
+%TODO: mention that A depends on the geometry and that we fit for some of those parameters.
 
@@
 
+\section{Conclusions}
+\label{sec:conclusions}
+
 % Bibliography

### 2020-08-31 paper/figures/pixels_vs_harmonics.py
Adding new figures.

@@ -1,135 +1,67 @@
-#!/usr/bin/env python
-import os
-import pickle as pkl
-import sys
-
-import matplotlib.gridspec as gridspec
 import numpy as np
-import pymc3 as pm
-import starry
+from matplotlib import pyplot as plt
+
 import theano
 import theano.tensor as tt
-from matplotlib import colors
-from matplotlib import pyplot as plt
-from matplotlib.ticker import FormatStrFormatter
-from volcano.utils import *
-
+import pymc3 as pm
+import starry
 import exoplanet as xo
+
+from matplotlib import colors
+import matplotlib.gridspec as gridspec
+from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+
+from volcano.utils import *
 
 np.random.seed(42)
 starry.config.lazy = True
 
-# Load data
-directory = "../../data/irtf_processed/"
-lcs = []
-
-for file in os.listdir(directory):
-    with open(os.path.join(directory, file), "rb") as handle:
-        lcs.append(pkl.load(handle))
-
-# Select a single light curve
-idx = 29
-lc = lcs[idx]
-
-f_obs = lc["flux"].value
-f_err = lc["flux_err"].value
+# Set up mock map
+def get_S(ydeg, sigma=0.1):
+    l = np.concatenate([np.repeat(l, 2 * l + 1) for l in range(ydeg + 1)])
+    s = np.exp(-0.5 * l * (l + 1) * sigma ** 2)
+    S = np.diag(s)
+    return S
 
 
-# Get ephemeris
-eph_io = get_body_ephemeris(
-    lc.time, body_id="501", step="1m", return_orientation=True
+xo_sim = np.linspace(37.15, 39.43, 120)
+yo_sim = np.linspace(-8.284, -8.27, 120)
+ro = 39.1
+
+ydeg_true = 30
+map_true = starry.Map(ydeg_true)
+map_true.add_spot(
+    amp=2.0, sigma=1e-03, lat=13.0, lon=360 - 308.8, relative=False
 )
-eph_jup = get_body_ephemeris(
-    lc.time, body_id="599", step="1m", return_orientation=True
-)
+map_true.amp = 20
 
+# Smooth the true map
[…]

### 2020-08-31 paper/figures/irtf_ingress_egress.py
Adding new figures.

@@ -1,0 +1,413 @@
+import numpy as np
+from matplotlib import pyplot as plt
+import tifffile
+
+import theano
+import theano.tensor as tt
+import pymc3 as pm
+import starry
+import exoplanet as xo
+from astropy import units as u
+from astropy.table import Table
+from astropy.timeseries import TimeSeries
+
+from matplotlib import colors
+import matplotlib.gridspec as gridspec
+from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+
+from volcano.utils import *
+
+np.random.seed(42)
+starry.config.lazy = True
+
+
+# Load light curves
+lc_in_n = np.load("irtf_ingress.npy")
+lc_eg_n = np.load("irtf_egress.npy")
+
+lc_in = TimeSeries(
+    time=Time(lc_in_n[:, 0], format="mjd"),
+    data=Table(
+        lc_in_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
+    ),
+)
+lc_eg = TimeSeries(
+    time=Time(lc_eg_n[:, 0], format="mjd"),
+    data=Table(
+        lc_eg_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
+    ),
+)
+
+
+# Compute ephemeris
+eph_list_io = []
+eph_list_jup = []
+
+for lc in (lc_in, lc_eg):
+    times = lc.time
+
+    eph_io = get_body_ephemeris(
+        times, body_id="501", step="1m", return_orientation=True
+    )
+    eph_jup = get_body_ephemeris(
+        times, body_id="599", step="1m", return_orientation=True
+    )
+
+    eph_list_io.append(eph_io)
+    eph_list_jup.append(eph_jup)
+
+eph_io_in = eph_list_io[0]
+eph_jup_in = eph_list_jup[0]
+eph_io_eg = eph_list_io[1]
+eph_jup_eg = eph_list_jup[1]
+
+t_in = (lc_in.time.mjd - lc_in.time.mjd[0]) * 24 * 60
+t_eg = (lc_eg.time.mjd - lc_eg.time.mjd[0]) * 24 * 60
+
+f_obs_in = lc_in["flux"].value
+f_err_in = lc_in["flux_err"].value
+f_obs_eg = lc_eg["flux"].value
[…]

### 2020-08-31 paper/figures/simulated_ingress_egress.py

@@ -1,0 +1,309 @@
+import numpy as np
+from matplotlib import pyplot as plt
+
+import theano
+import theano.tensor as tt
+import pymc3 as pm
+import starry
+import exoplanet as xo
+from scipy import optimize
+
+from matplotlib import colors
+import matplotlib.gridspec as gridspec
+from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+
+from volcano.utils import *
+
+np.random.seed(42)
+starry.config.lazy = True
+
+
+def get_S(ydeg, sigma=0.1):
+    l = np.concatenate([np.repeat(l, 2 * l + 1) for l in range(ydeg + 1)])
+    s = np.exp(-0.5 * l * (l + 1) * sigma ** 2)
+    S = np.diag(s)
+    return S
+
+
+xo_eg = np.linspace(37.15, 39.43, 150)
+yo_eg = np.linspace(-8.284, -8.27, 150)
+
+xo_in = np.linspace(-39.5, -37.3, 150)
+yo_in = np.linspace(-7.714, -7.726, 150)
+
+xo_com = np.concatenate([xo_in, xo_eg])
+yo_com = np.concatenate([yo_in, yo_eg])
+
+ro = 39.1
+
+ydeg_true = 25
+map_true = starry.Map(ydeg_true)
+spot_lon = 360 - 308.8
+spot_lat = 13.0
+map_true.add_spot(
+    amp=2.0, sigma=1e-03, lat=spot_lat, lon=spot_lon, relative=False
+)
+map_true.amp = 20
+
+# Smooth the true map
+S_true = get_S(ydeg_true, 0.1)
+x = (map_true.amp * map_true.y).eval()
+x_smooth = (S_true @ x[:, None]).reshape(-1)
+map_true[:, :] = x_smooth / x_smooth[0]
+map_true.amp = x_smooth[0]
+
+
+# Generate mock ingress and egress light curves
+f_true_in = map_true.flux(ro=ro, xo=xo_in, yo=yo_in).eval()
+f_true_eg = map_true.flux(ro=ro, xo=xo_eg, yo=yo_eg).eval()
+
+f_err = 0.46
+
+f_obs_in = f_true_in + np.random.normal(0, f_err, len(f_true_in))
+f_obs_eg = f_true_eg + np.random.normal(0, f_err, len(f_true_eg))
[…]

### 2020-08-31 paper/paper.tex
paper update

@@
 \label{sec:model}
-% Discuss starry, pixels vs. schmixels vs. harmonics, forward model for static map, NMF model for dynamic map
 \subsection{Orbital parameters}
@@
 
+\subsection{Effective radius of Jupiter}
+
 \subsection{Static map model}
@@
     \mathbf{f}=\mathbf{A}\,\mathbf{y}
+    \label{eq:linear_model}
 \end{equation}
@@
 
-Although \textsf{starry} is built around the idea of expending surface features in a spherical harmonic basis, this is not the ideal basis for doing inference because it makes it difficult to ensure positivity of the maps.
-Ideally we would like to fit all models in the \emph{pixel basis} where ensuring positivity is trivial but still do all computations in the $Y_{lm}$ basis where everything is analytic and fast.
-We obtain the pixels by constructing a discrete grid on the surface of the sphere using an equal area Molleweide projection.
-To ensure that the intensity is positive everywhere on the surface we also need to have more pixels than spherical harmonics (by a factor of a few).
-The mapping $\mathbf{P}$ from the spherical harmonic basis to the pixel basis is linear operator and it is straightforward to compute.
-Unfortunately, because the number of pixels is greater than the number of $Y_{lm}$ coefficients, the matrix $\mathbf{P}$ is not square and is therefore not invertible.
-We can still compute Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ which is obtained by solving the linear system $\mathbf{P}\,\mathbf{y}=\mathbf{p}$ where $\mathbf{p}$ is the vector of all pixels comprising a map.
-The model is also linear in the pixels:
+Although \textsf{starry} is built around the idea of expanding surface features in a spherical harmonic basis, this is not the ideal basis for doing inference because it makes it difficult to ensure that the intensity is positive everywhere on the map.
+In order to circumvent this limitation of the spherical harmonic basis, we fit all models in a \emph{pixel basis} instead where ensuring positivity amounts to putting a positive prior on the pixels but still do all computations in the $Y_{lm}$ basis where all integrals are analytic and can be computed efficiently.
+We obtain the pixels by constructing a discrete grid on the surface of the sphere using an equal area Molleweide projection
+and to ensure that the intensity is positive everywhere on the surface we need to have more pixels than spherical harmonics (by a factor of a few).
+Given a vector of spherical harmonic coefficients we can switch to the pixel basis with a linear operator $\mathbf{P}$ which is straightforward to compute.
+The inverse transform is less straightforward because the number of pixels is greater than the number of $Y_{lm}$ coefficients so the matrix $\mathbf{P}$ is not square and is therefore not invertible.
+Although we can't invert this matrix we can still compute the Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ which is obtained by solving the linear system $\mathbf{P}\,\mathbf{y}=\mathbf{p}$ where $\mathbf{p}$ is the vector of all pixels comprising a map.
+The flux can then be computed as a linear operation on the pixels: 
 \begin{equation}
-    \mathbf{f}=\mathbf{A}\,\mathbf{P}^\dagger\,\mathbf{p}
+    \mathbf{f}=\mathbf{A}\,\mathbf{P}^\dagger\,\mathbf{p}'
     \label{eq:linear_model_pix}
 \end{equation}
+where the pixels $\mathbf{p}'$ are close to $\mathbf{p}$ in a least-squares sense.
 In what follows, we will assume that we work in the pixel basis and compute all fluxes in the $Y_{lm}$ basis where the model is exact.
@@
 \begin{equation}
-    \mathbf{f}_l=\mathbf{A}_l\,\mathbf{P}^\dagger\,\mathbf{p}_l
+    \mathbf{f}_l=\mathbf{A}_l\,\mathbf{P}^\dagger\,\mathbf{p}_l'
 \end{equation}
@@
 Where $\mathbf{f}$ is a tall column vector consisting of predictions for all light curves stacked together, $\mathbb{A}$ is a block diagonal matrix with matrices $\mathbf{A}_l\,\mathbf{P}^\dagger$ on the diagonal for $l=1\dots, L$ and the $\mathrm{vec}$ operator stacks the columns of $\mathbb{Y}$ into a tall vector.
-The model is \emph{bilinear} which means that is linear in the matrices $\mathbb{B}$ and $\mathbf{Q}$ separately.
+The model is \emph{bilinear} which means that is linear in the matrices $\mathbf{B}$ and $\mathbf{Q}$ separately.
 The interpretation of Equation~\ref{eq:nmf} is simple, each of the $K$ columns of $\mathbf{B}$ represents pixels of a basis map and the columns of $\mathbf{Q}$ determine how those maps add together to produce a final map for the $l$-th light curve.
+For this reason we call $\mathbf{B}$ the \emph{basis matrix} and the matrix $\mathbf{Q}$ the \emph{encoding matrix}.
 Ideally, we want the basis maps to be physically meaningful and the coefficients encode the time variability.
@@
 
-Broadly speaking, there are two approaches to fitting NMF models, the constrained optimization approach and the probabilistic approach.
-In the optimization approach we optimize $\mathbb{Y}$ in a least-squares sense under a set of constraints on either one or both of the matrices \citep[see][for recent examples from the astronomical literature]{acosta-pulido_new_2017, melchior_scarlet_2018,ren_non-negative_2018,ren_using_2020}.
-The probabilistic approach introduces priors and the inference is usually done with variational inference.
-In this work we opt for the probabilistic approach because we care about the uncertanties on the map features a lot.
+Broadly, there are two approaches to fitting NMF models, the constrained optimization approach and the probabilistic approach.
+In the optimization approach we optimize $\mathbb{Y}$ in a least-squares sense under a set of constraints on either one or both of the matrices \citep[see][for recent examples from the astronomical literature]{acosta-pulido_new_2017, melchior_scarlet_2018,ren_non-negative_2018,ren_using_2020} with the goal of obtaining a point estimate for the two matrices.
+The probabilistic approach introduces priors and the inference is usually done with variational inference in order to obtain an approximate posterior distribution over the matrices.
+In this work we opt for the probabilistic approach because we care about the uncertainties on the map features a lot.
 
-One difference between most applications of NMF in the literature and NMF within the context of infering surface maps from 1D light curves is that
+One difference between most applications of NMF in the literature and NMF within the context of inferring surface maps from 1D light curves is that
 in the majority of the work in the literature \citep[except][]{kawahara_global_2020} the matrix $\mathbb{Y}$ is assumed to be directly observed  up to a simple noise term.
@@
 \label{sec:inverse_problem}
+Having defined the forward models in the previous section, in this section we focus on choosing priors, doing inference and testing the models on simulated data.
+We compute the information content of different kinds of occultation and phase light curves and , we test the differences between fitting in the $Y_{lm}$ basis vs.
+fitting in the pixel basis, prior choices for pixel maps and priors for NMF.
+To fit the models, we use  variational inference and Hamiltonian Monte Carlo.
+
 % bulk of the results in the paper
@@
 \label{ssec:information_content}
-% information in different kinds of occultations/phase curves, reflected light vs. emitted light, posterior shrinkage etc.
+The mapping problem is famously ill posed.
+In other words, certain linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Eq.~\ref{eq:linear_model}.
+This means that even if we had noiseless observations, certain features would still be impossible to recover.
+To recover surface features from observed flux integrated over the disc of the object we need
+to have some mechanism which breaks the various degeneracies.
+For phase curves in emitted light, we can only recover longitudinal variations in intensity.
+Occultations are a lot better thanks to the limb of the occultor sweeping across the surface of the occulted sphere.
+Even better are grazing occultations with an occultor of a small diameter sweeping across the disc at different latitudes and therefore breaking the latitudinal degeneracies. 
+Observing phase curves and occultations in reflected light improves the model even more because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
+2020 in prep]{luger_starry_2019}.
+In some cases for reflected light observations (phase curves of an inclined planet for example) there is no nullspace at all at low degrees of the map.
 
+To compute how much information can in principle be obtained by observing occultations of Io by Jupiter and other moons or phase curves we need to compute some measure of how much does observing Io at certain times reduce our prior uncertainty on the map features.
+Given that the model for a static map (Eq.~\ref{eq:linear_model}) is linear, under Gaussian priors with covariance $\boldsymbol{\Lambda}$ on the spherical harmonic coefficients and a Gaussian likelihood, the posterior is analytic and the mean is given by
+\begin{equation}
+    \widehat{\mathbf{y}}=\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}\left(\mathbf{A}^{\top} \boldsymbol{\Sigma}_{\mathbf{f}}^{-1} \mathbf{f}+\boldsymbol{\Lambda}_{\mathbf{y}}^{-1} \boldsymbol{\mu}_{\mathbf{y}}\right)
+\end{equation}
+where the posterior covariance matrix $\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}$ is 
+\begin{equation}
+\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}=\left( \mathbf{A}^{\top} \boldsymbol{\Sigma}_{\mathbf{f}}^{-1} \mathbf{A} +\boldsymbol{\Lambda}_{\mathbf{y}}^{-1}\right)^{-1}
+\end{equation}
+The posterior covariance matrix depends on the design matrix $\mathbf{A}$, the prior covariance  $\boldsymbol{\Lambda}$ and the data covariance $\boldsymbol{\Sigma}_{\mathbf{f}}$.
+We first compute the design matrices using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
+
+We take the ephemeris data  from \textsf{JPL HORIZONS} and assume that it is known exactly, we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse.
+This is because we are interested in constraining the volcanic emission rather than the albedo.
+Given the fixed design matrices, we can compute the variance reduction of the posterior relative to the prior known as \emph{posterior shrinkage}, defined as
+\begin{equation}
+    1-\frac{\sigma^2_\mathrm{post}}{\sigma^2_\mathrm{prior}}
+\end{equation}
+where $\sigma^2_\mathrm{prior}$ is the prior and $\sigma^2_\mathrm{post}$ is the posterior variance for a given parameter.
+To compute this quantity for each spherical harmonic coefficient in $\mathbf{y}$ we divide the diagonal elements of matrices $\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}$ and $\boldsymbol{\Lambda}$, divide them, and average over all $m$-modes.
+We need to assume some variance for the Gaussian prior on the $Y_{l,m}$ coefficients so we choose a broad prior $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$.
+Although the posterior shrinkage depends on this prior the main results do not change for a different choice of the prior.
+The result is plotted in Fig.~\ref{fig:information_content}.
 \begin{figure}[h!]
@@
     \includegraphics[width=0.5\linewidth]{figures/information_content.pdf}
-    \oscaption{InformationContent}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
+    \oscaption{InformationContent}{
+        The plot shows the information content of different kinds of observations of Io as a function of spherical harmonic degree (angular scale of surface features).
+        On the y axis is posterior shrinkage (the variance ratio between the prior and the posterior distribution) for each spherical harmonic coefficient at a given degree $l$ on the x axis, averaged across all $m$ modes.
+        Posterior shrinkage of 1 represent maximum information gain in updating from the prior to the posterior while a shrinkage of 0 represents no information gain. 
+        We compute the posterior variance for different kinds of mock observations of Io over
+        the course of a single year: phase curves (blue), occultations by Jupiter (orange), combined phase curves and occultations by Jupiter (green) and occulltations of Io by other Galilean moons (red lines).
+        Solid lines represent observations at SNR=100 while dashed lines represent observations at SNR=10.
         \label{fig:information_content}
@@
 \end{figure}
+The plot shows posterior shrinkage for phase curve observations (blue lines), occultations by Jupiter (orange), the previous two combined (green) and mutual occultations by other Galilean moons (red).
+Solid lines correspond to SNR=100 while dashed lines correspond to SNR=10 where the signal is defined as the min-max difference of the predicted flux.
+
+        It is clear that observations of mutual occultations of Io (red lines) are by far the most informative and most useful for constraining surface features.
+The posterior shrinkage is near unity at all angular scales $l$ up to $l=18$ owing to degeneracy breaking features of these occcultations.
+        Occultations by Jupiter (orange lines) are far less informative because we only see one side of Io during an occultation (hence the kink in the curve at $l=1$) and the position of Jupiter's limb on the surface of Io does not vary significantly so latitudinal features are only weakly constrained.
+        The posterior shrinkage is exactly zero for phase curves at all odd degrees above $l=2$ because phase curves for objects rotating about an axis perpendicular to the line of sight encode zero information on these coefficients because they are in the nullspace.
+Although observations of mutual occultations most easily break the degeneracies, they only occur every 6 years and more importantly they almost never occur while Io is in eclipse.
+This means that only the brightest volcanoes will be visible above the reflected light background emission due to the Sun.
+Figure~\ref{fig:information_content} does not reflect this fact.
+When modeling the observations taken while Io is in sunlight, we have to take into account the reflected light component.
+Although \textsf{starry} supports computing occultations and phase curves in reflected light, we only fit in eclipse observations in this work.
 
@@
 \label{ssec:static_map}
-% Priors for static maps, sparsity, positivity, plot of map inference with simulated data and different kinds of priors. Inference with MAP, VI, HMC.
+In this section we test inference with the static map model defined in Section~\ref{ssec:static} on both simulated and real data.
+First we use \textsf{starry} to generate one simulated light curve of an occultation of Io by Jupiter with an $l=30$ map containing a single bright hot spot.
+We take ephemeris parameters (assumed to be fixed) from a real occultation and assume an observational cadence and noise similar to IRTF light curves.
+We use this dataset to test the difference between fitting a map in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the pixel basis (Eq.~\ref{eq:linear_model_pix}).
+We fit two models for the Maximum A Posteriori (MAP) estimate of the parameters using the
+\textsf{BFGS} algorithm as implemented in \textsf{scipy.optimize.minimize} in the \textsf{scipy} package (CITE) and the exact gradients of the model with respect to all parameters provided by \textsf{Theano}.
+
+In the first model we place a Gaussian prior on $Y_{lm}$ coefficients with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$ and optimize for the values of the coefficients. 
+In the second model we fit for pixels $\mathbf{p}'$ with a positive prior  in order to ensure (approximate) positivity of the inferred maps.
+To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the pixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each step in the inference algorithm.
+As the end product of the inference we do not store the interim pixels $\mathbf{p}'$ but rather the spherical harmonic coefficients. 
+To distinguish between the pixels $\mathbf{p}'$ which are defined on a fixed grid in (latitude,longitude) and the pixels $\mathbf{p}=\mathbf{P}\,\mathbf{y}$ which can be computed on an arbitrary grid conditional on knowing $\mathbf{y}$, we call the former \emph{schmixels}.
+Although the priors on schmixels $\mathbf{p}'$ are strictly positive, because of the approximate mapping to spherical harmonics the pixels $\mathbf{p}$ won't completely respect the prior and there will be still be some regions of the map with negative intensity.
+
+The justification for this somewhat convoluted procedure is shown in Fig.~\ref{fig:pixels_vs_harmonics}.
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/pixels_vs_harmonics.pdf}
+    \oscaption{pixels_vs_harmonics}{%
+        Inferred Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a mock light curve (third panel) which was generated from a simulated $l=30$ map consisting of a single bright spot (top panel).
+        The left portion of the figure shows a map inferred using a model in which we directly fit for spherical harmonic coefficients with a Gaussian prior on the coefficients.
+        The right portion shows a map inferred from a model in which an Exponential prior is placed on the pixels defined on a fixed latitude-longitude grid which are converted to spherical harmonic coefficients at every step of the inference process.
+        The pixels are only used as a tool to impose positivity and sparsity (via the Exponential prior) on the map intensity but the final inferred map (second panel on the right) and the predicted flux (orange lines) are generated from a map defined by a set of spherical harmonic coefficients.
+Both models fit the data reasonably well but the inferred maps are widely different. 
+As a result of the sparse prior, the model whose prior is specified in pixel space results in a considerably simpler map with a single bright features where all the other regions of the map are pushed towards zero intensity.
+Both maps show significant ringing effects due to the finite order of the spherical harmonic expansion. 
+        The precise location of the true spot is not recovered for either of the two models
+        which is not surprising because a single light curve is not sufficient to break the degeneracies.
+        \label{fig:pixels_vs_harmonics}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/pixels_hist.pdf}
+    \oscaption{pixels_hist}{%
+        Cumulative distribution of pixels in the true map and the inferred maps shown in Fig.~\ref{fig:pixels_vs_harmonics}.
+        The pixels were obtained by dotting a pixel transform matrix $\mathbf{P}$ into the spherical coefficient vector $\mathbf{y}$ of each map.
+        The top panel shows the distribution of pixels for the model in which we fit for the spherical harmonic coefficients with a Gaussian prior (orange). 
+        The distribution of pixels in the true map is shown in blue.
+        The bottom panel shows the pixels for a second model (right panel of Fig.~\ref{fig:pixels_vs_harmonics}) in which we fit for interim pixels which we call schmixels (green) instead of the spherical harmonic coefficients although the coefficients are still used to compute the flux and to compute the final pixel distribution (orange).
+        The true map pixels are almost all positive (as they should be) except for a small tail due to truncation of the spherical harmonic expansion.
+        The distribution of inferred pixels in the spherical harmonic model looks nothing like the truth and there is a significant left tail corresponding to negative values of map intensity which is due to the ringing artefacts which aren't sufficiently suppressed by the Gaussian prior.
+        The distribution of schmixels (interim pixels used to enforce positivity of the map)       follows the exponential prior and is strictly positive by definition. 
+        The distribution of corresponding pixels is not identical to that of schmixels because the mapping $\mathbf{P}$ from spherical harmonics to pixels is not invertible.
+        However, the resulting distribution is closer the truth with a smaller left tail.
+        \label{fig:pixels_hist}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/smoothing_kernel.pdf}
+    \oscaption{smoothing_kernel}{%
+        This is a plot of a pretty function. And at the end of this
+        caption is a symbol with a link to the \emph{exact} script
+        that generated it, hosted on \textsf{GitHub}.
+        \label{fig:smoothing_kernel}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/ingress_egress_simulated.pdf}
+    \oscaption{ingress_egress_simulated}{%
+        This is a plot of a pretty function. And at the end of this
+        caption is a symbol with a link to the \emph{exact} script
+        that generated it, hosted on \textsf{GitHub}.
+        \label{fig:ingress_egress_simulated}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress.pdf}
+    \oscaption{irtf_ingress_egress}{%
+        This is a plot of a pretty function. And at the end of this
+        caption is a symbol with a link to the \emph{exact} script
+        that generated it, hosted on \textsf{GitHub}.
+        \label{fig:irtf_ingress_egress}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=.5\linewidth]{figures/irtf_ingress_egress_loki.pdf}
+    \oscaption{irtf_ingress_egress_loki}{%
+        This is a plot of a pretty function. And at the end of this
+        caption is a symbol with a link to the \emph{exact} script
+        that generated it, hosted on \textsf{GitHub}.
+        \label{fig:irtf_ingress_egress_loki}
+    }
+    \end{centering}
+\end{figure}
 
@@
 % Fits of individual events. In particular, those light curves that were analyzed in previous papers.
-
-\begin{figure}[h!]
-    \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/single_event_fit.pdf}
-    \oscaption{single_event_fit}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
-        \label{fig:single_event_fit}
-    }
-    \end{centering}
-\end{figure}
 

### 2020-08-31 paper/figures/smoothing_kernel.py
trying to fix build on azure

@@ -1,86 +1,86 @@
-import numpy as np
-import starry
-from matplotlib import pyplot as plt
-
-np.random.seed(42)
-starry.config.lazy = False
-
-
-def get_S(ydeg, sigma=0.1):
-    l = np.concatenate([np.repeat(l, 2 * l + 1) for l in range(ydeg + 1)])
-    s = np.exp(-0.5 * l * (l + 1) * sigma ** 2)
-    S = np.diag(s)
-    return S
-
-
-# Dummy featureless map
-map0 = starry.Map(ydeg=1)
-map0.show()
-
-# Compute the intensity along the equator
-# Remove the baseline intensity and normalize it
-lon = np.linspace(-90, 90, 300)
-baseline = 1.0 / np.pi
-
-# Compute the intensity of a normalized gaussian
-# in cos(longitude) with the same standard deviation
-coslon = np.cos(lon * np.pi / 180)
-spot_ang_dim = 5 * np.pi / 180
-spot_sigma = 1 - np.cos(spot_ang_dim / 2)
-I_gaussian = np.exp(-((coslon - 1) ** 2) / (2 * spot_sigma ** 2))
-
-degs = [10, 15, 20]
-
-Is = np.zeros((3, len(degs), 300))
-smoothing_sigmas = np.array([0.0, 0.1, 0.2])
-
-
-def get_map(deg, sig_smooth, sig_size):
-    if sig_smooth == 0:
-        map = starry.Map(deg)
-        map.add_spot(amp=2.0, sigma=sig_size, lat=0.0, lon=0, relative=False)
-        map.amp = 20
-    else:
-        map = starry.Map(deg)
-        map.add_spot(amp=2.0, sigma=sig_size, lat=0.0, lon=0, relative=False)
-        map.amp = 20
-        S = get_S(deg, sig_smooth)
-        x = map.amp * map.y
-        x_smooth = (S @ x[:, None]).reshape(-1)
-        map[:, :] = x_smooth / x_smooth[0]
-        map.amp = x_smooth[0]
-
-    return map
-
-
-for j in range(len(smoothing_sigmas)):
-    for l in range(len(degs)):
-        map = get_map(degs[l], smoothing_sigmas[j], spot_sigma)
-        I = (map.intensity(lon=lon) - baseline) / (
-            map.intensity(lon=0) - baseline
-        )
-        Is[j, l] = I
-
[…]

### 2020-09-18 paper/paper.tex
trying to fix build on azure
More details on smoothing

@@
 To model the occultations we need to know the projected separation between Jupiter and Io and the orientation of Io at any given time.
-We use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner_planetary_2014} for this purpose.
+We use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner_planetary_2014} which are accurate to a few kilometers on Io's surface.
 Specifically, we use the Right Ascension and Declination, the angular (equatorial) diameter (\textsf{Ang-diam}), the visibility flag indicating whether Io is occulted or not and whether it is in partial or total eclipse (\textsf{Ang-sep/v}), the longitude and latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}), the sub-solar point longitude and latitude which specify the direction pointing towards the Sun on Io's surface (\textsf{Sl-lon}, \textsf{Sl-lat}), the distance from Io to the Sun (\textsf{r}) and
@@
 \subsection{Effective radius of Jupiter}
+Although the sky position of Jupiter relative to Io is known to a precision of a few kilometers, several complications arise when attempting to compute Jupiter's radius.
+First, Jupiter is not spherical and its equatorial radius is larger than the polar radius by thousands of kilometers. 
+Because \textsf{starry} does not support occultations by non-spherical occultors we 
+assume that Jupiter is locally spherical at the point of an occultation and estimate an effective radius from measurements of Jupiter's shape which are based on Voyager radio occultation measurements \citep{lindal1981}.
+These data come in the form of a plot of effective radius  as a function of planetocentric latitude at a fixed pressure of 100 mbar \citep[Fig.~7 in ][]{lindal1981}.
+When computing the occultation latitude we ignore the variation in effective radius along Jupiter's limb projected on Io's surface and instead fix Jupiter's latitude to the value corresponding to the center of Io's disc.
+
+The second complication is that Jupiter is gaseous which means that it does not have a well defined boundary.
+In principle, we should compute an effective radius of Jupiter at different locations (pressure) in the atmosphere and model an occultation of Io by a fuzzy occultor.
+Although this can be done with Starry, it is not necessary because the characteristic scale height of Jupiter is around 27 km (CITE) which is below the uncertainty of our inferred maps.
+Instead, we follow \cite{spencer1990} and compute the effective radius of Jupiter at about 2.2 mbar, this is the pressure (and the associated effective radius) at which during an occultation a bright source on the surface of Io fades by 50\% due to differential refraction.
+
+Since the effective radius information is provided only at a fixed pressure of 100 mbar, 
+to adjust those values for a lower pressure of 2.2 mbar, we assume an exponential pressure profile $P=P_0\, e^{-\Delta r/H}$ where $H$ is the scale height and $\Delta r$ is the height difference between the two pressure levels.
+It follows that to convert the shape profile at 100 mbar to 2.2 mbar we need to add the factor
+$-H\ln(2.2/100)$ which is assumed to be constant in the $\pm 21$ deg latitude range in which the occultations occur.
+Besides refractive absorption there is a also a slight additional methane molecular absorption which \cite{spencer1990} estimate to be equal to around 12\% in their filter, 
+we choose to ignore this because it is far below the resolution of our maps.
+
+Finally, we have to account for the fact that the light from Io is getting significantly bent at the point of half reflective intensity in Jupiter's atmosphere 
+which results in a smaller shadow of Jupiter on the surface of Io then would be the case if the light didn't get bent.
+It is zero at the beginning of the disappearance of a hot spot when there is no refraction, increasing to one scale height $H$ at the half intensity point and then increasing further to a large value when Io disappears behind Jupiter's limb.
+We ignore the variation in the bending and adopt a fixed value of one scale height for this effect which we subtract from the value of the effective radius.
+
+In summary, to compute an effective radius of Jupiter for a given occultation of Io we first have to compute the latitude at which the occultation is occurring, use a modified shape profile from \cite{lindal1981} to get an effective radius and finally subtract one scale height due to light bending.
+There are substantial uncertainties in each of these steps, most notably the shape profile data are quite old and it is not clear that the structure of Jupiter's atmosphere stayed the same since 1980s.
+The shape profile also depends on the wind velocity structure and temperature which we ignore.
+In addition to uncertainties about the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
+We digitizing this figure by reading off the data points "by eye" and then interpolating them using cubic spline interpolation.
+Finally we add the pressure conversion factor and subtract one scale height due to light bending.
+
+Throughout this paper the highest resolution maps we fit to the data are of order $l=25$ which corresponds to a characteristic length scale of around 230 km on the surface of Io.
+Quantifying the uncertainty in each of these steps is beyond the scope of this paper but we are confident that the errors in the radius estimate are below the typical resolution of our inferred maps. 
+We provide justification for this assumption in section~\ref{ssec:static_map} where we infer the location of Loki and it ends up matching well with the high resolution geological map of Io.
 
@@
         Posterior shrinkage of 1 represent maximum information gain in updating from the prior to the posterior while a shrinkage of 0 represents no information gain. 
-        We compute the posterior variance for different kinds of mock observations of Io over
+        We compute the posterior variance for different kinds of simulated observations of Io over
         the course of a single year: phase curves (blue), occultations by Jupiter (orange), combined phase curves and occultations by Jupiter (green) and occulltations of Io by other Galilean moons (red lines).
@@
     \oscaption{pixels_vs_harmonics}{%
-        Inferred Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a mock light curve (third panel) which was generated from a simulated $l=30$ map consisting of a single bright spot (top panel).
+        Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (third panel) which generated from an $l=30$ map consisting of a single bright spot (top panel).
         The left portion of the figure shows a map inferred using a model in which we directly fit for spherical harmonic coefficients with a Gaussian prior on the coefficients.
@@
 
+To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:pixels_vs_harmonics} we choose to apply a spatial smoothing filter to the spherical harmonics.
+Mathematically, the filtering operation is a convolution between the map and some kernel function $B(\theta,\phi)$.
+The simplest choice for the kernel function is a Gaussian distribution given by
+\begin{equation}
+    B(\theta)=\frac{1}{\sqrt{2 \pi \sigma_s^{2}}}\exp \left(-\theta^{2} / 2 \sigma_s^{2}\right)
+\end{equation}
+where $\sigma_s$ sets the characteristic scale of the smoothing.
+This function can be expended in terms of spherical harmonics as
+\begin{equation}
+B(\theta)=\sum_{l=0}^{\infty}\left(\frac{2 l+1}{4 \pi}\right) B_{l} P_{l}(\cos \theta)
+\end{equation}
+where $B_l$ are the spherical harmonic coefficients and $P_l$ are the associated Legendre polynomials.
+They depend only on $l$ because the kernel function is azimuthally symmetric so all nonzero $m$ modes vanish.
+For $\sigma_s\ll 1$ $B_l$ can be approximated as \citep{seon2007}
+\begin{equation}
+    B_l\approx \exp\left[-\frac{1}{2}l(l+1)\sigma_s^2\right]
+\end{equation}
+The Gaussian filter results in an exponential cutoff for scales smaller than $l\sim \sigma_s^{-1}$.
+
 \begin{figure}[h!]
@@
     \oscaption{smoothing_kernel}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
+       Normalized intensity of a spherical harmonic expansion of 
+        a Gaussian spot placed at zero degrees latitude and longitude.
+        The expansion is in the quantity $\cos\Delta\theta$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere, it is set to 5 degrees.
+        The three insets show the spot profile at different strengths of the smoothing kernel
+        where the leftmost spot has no smoothing ($\sigma_s=0$) and the rightmost spot is strongly smoothed. 
+        The lines of different colors correspond to spot expansions up to certain order and the black line is the expansion at infinite order.
+        The purpose of smoothing is to taper the higher order spherical harmonic coefficients.
+        No smoothing results in significant "rings" where the intensity goes negative, even at high order.
+        High levels of smoothing reduce the ringing but increase the spot size and eliminate differences between expansions above a certain order.
                 \label{fig:smoothing_kernel}
@@
     \oscaption{ingress_egress_simulated}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
+        Maximum A Posteriori (MAP) estimate of an $l=25$ map (right panel from the top) produced by fitting a pair of light curves simulated from the true map which is shown on the left.
+        The simulated light curves are shown in the third panel from the top, an ingress light curve on the left and an egress light curve on the right.
+        The small circles above each of the light curves show the progression of the occultation over the inferred map.
+        The precise location of the true spot is not recovered for either of the two models
+        which is not surprising because a single light curve is not sufficient to break the degeneracies.
         \label{fig:ingress_egress_simulated}

### 2020-09-18 paper/figures/smoothing_kernel.py

@@ -34,6 +34,7 @@ degs = [10, 15, 20]
 Is = np.zeros((3, len(degs), 300))
 smoothing_sigmas = np.array([0.0, 0.1, 0.2])
 
+
 def get_map(deg, sig_smooth, sig_size):
     if sig_smooth == 0:
         map = starry.Map(deg)
@@ -70,7 +71,7 @@ for i in range(len(smoothing_sigmas)):
             lon, Is[i, l], alpha=0.8, color=f"C{l}", label=f"$l = {degs[l]}$"
         )
     ax[i].plot(lon, I_gaussian, "k-", alpha=0.8, label="exact")
-    ax[i].set_title(r"$\tau={}$".format(smoothing_sigmas[i]))
+    ax[i].set_title(r"$\sigma_s={}$".format(smoothing_sigmas[i]))
 
 for a in ax.flatten():
     a.set_xticks(np.arange(-60, 90, 30))

### 2020-09-19 paper/figures/smoothing_kernel.py
adding minor ticks

@@ -1,6 +1,7 @@
 import numpy as np
 import starry
 from matplotlib import pyplot as plt
+from matplotlib.ticker import AutoMinorLocator
 
 np.random.seed(42)
 starry.config.lazy = False
@@ -76,6 +77,8 @@ for i in range(len(smoothing_sigmas)):
 for a in ax.flatten():
     a.set_xticks(np.arange(-60, 90, 30))
     a.set_xlim(-60, 60)
+    a.xaxis.set_minor_locator(AutoMinorLocator())
+    a.yaxis.set_minor_locator(AutoMinorLocator())
 #     a.grid()
 
 ax[-1].legend(loc=4, prop={"size": 12})

### 2020-09-25 paper/figures/pixels_vs_harmonics.py
Added new plot. Removing histograms.

@@ -30,13 +30,15 @@ ro = 39.1
 
 ydeg_true = 30
 map_true = starry.Map(ydeg_true)
+spot_ang_dim = 5 * np.pi / 180
+spot_sigma = 1 - np.cos(spot_ang_dim / 2)
 map_true.add_spot(
-    amp=2.0, sigma=1e-03, lat=13.0, lon=360 - 308.8, relative=False
+    amp=1.0, sigma=spot_sigma, lat=13.0, lon=360 - 309, relative=False
 )
-map_true.amp = 20
 
 # Smooth the true map
-S_true = get_S(ydeg_true, 0.07)
+sigma_s = 2 / ydeg_true
+S_true = get_S(ydeg_true, sigma_s)
 x = (map_true.amp * map_true.y).eval()
 x_smooth = (S_true @ x[:, None]).reshape(-1)
 map_true[:, :] = x_smooth / x_smooth[0]
@@ -44,7 +46,7 @@ map_true.amp = x_smooth[0]
 
 # Generate mock light curve
 f_true = map_true.flux(ro=ro, xo=xo_sim, yo=yo_sim).eval()
-f_err = 0.5
+f_err = 0.02 * np.max(f_true)
 f_obs = f_true + np.random.normal(0, f_err, len(f_true))
 
 # Ylm model
@@ -63,7 +65,7 @@ ncoeff = (ydeg_inf + 1) ** 2
 with pm.Model() as model_ylm:
     map = starry.Map(ydeg_inf)
 
-    cov = (3e-02) ** 2 * np.eye(ncoeff - 1)
+    cov = (1e-01) ** 2 * np.eye(ncoeff - 1)
     y1 = pm.MvNormal(
         "y1",
         np.zeros(ncoeff - 1),
@@ -91,11 +93,37 @@ with pm.Model() as model_ylm:
 with model_ylm:
     soln_ylm = xo.optimize(options=dict(maxiter=99999))
 
-# Pixel model
-with pm.Model() as model_pix:
+
+# Compute the standard deviation of pixels in the Ylm model
+with pm.Model() as model_prior:
+    map = starry.Map(ydeg_inf)
+    cov = (1e-01) ** 2 * np.eye(ncoeff - 1)
+    y1 = pm.MvNormal(
+        "y1",
+        np.zeros(ncoeff - 1),
+        cov,
+        shape=(ncoeff - 1,),
+        testval=1e-03 * np.random.rand(ncoeff - 1),
+    )
[…]

### 2020-09-25 paper/figures/schmixels_to_pixels.py
Adding figure on schmixel to pixel mapping.

@@ -1,0 +1,201 @@
+import numpy as np
+import theano.tensor as tt
+import pymc3 as pm
+import starry
+from starry._plotting import (
+    get_moll_latitude_lines,
+    get_moll_longitude_lines,
+)
+
+from matplotlib import pyplot as plt
+from matplotlib import colors
+from scipy import optimize
+
+np.random.seed(42)
+starry.config.lazy = True
+
+ydeg = 20
+map = starry.Map(ydeg)
+lat, lon, Y2P, P2Y, Dx, Dy = map.get_pixel_transforms(oversample=4)
+npix = Y2P.shape[0]
+
+std_p = 1.62
+
+with pm.Model() as model:
+    p = pm.Exponential("p", 1 / std_p, shape=(npix,))
+    x = tt.dot(P2Y, p)
+    pm.Deterministic("x", x)
+    p_back = tt.dot(Y2P, x)
+    pm.Deterministic("p_back", p_back)
+
+    trace_pp = pm.sample_prior_predictive(10)
+
+
+# Convert lat, lon to x,y coordinates in Mollewiede projection
+def lon_lat_to_mollweide(lon, lat):
+    lat *= np.pi / 180
+    lon *= np.pi / 180
+
+    f = lambda x: 2 * x + np.sin(2 * x) - np.pi * np.sin(lat)
+    theta = optimize.newton(f, 0.3)
+
+    x = 2 * np.sqrt(2) / np.pi * lon * np.cos(theta)
+    y = np.sqrt(2) * np.sin(theta)
+
+    return x, y
+
+
+x_mol = np.zeros(npix)
+y_mol = np.zeros(npix)
+
+for idx, (lo, la) in enumerate(zip(lon, lat)):
+    x_, y_ = lon_lat_to_mollweide(lo, la)
+    x_mol[idx] = x_
+    y_mol[idx] = y_
+
+
+def plot_grid_lines(ax, alpha=0.6):
+    """
+    Code from https://github.com/rodluger/starry/blob/0546b4e445f6570b9a1cf6e33068e01a96ecf20f/starry/maps.py.
+    """
+    ax.axis("off")
+    ax.set_xlim(-2 * np.sqrt(2) - 0.2, 2 * np.sqrt(2) + 0.2)
+    ax.set_ylim(-np.sqrt(2) - 0.2, np.sqrt(2) + 0.2)
+
+    borders = []
[…]

### 2020-09-25 paper/paper.tex
Even more paragraphs

@@
 Although \textsf{starry} is built around the idea of expanding surface features in a spherical harmonic basis, this is not the ideal basis for doing inference because it makes it difficult to ensure that the intensity is positive everywhere on the map.
-In order to circumvent this limitation of the spherical harmonic basis, we fit all models in a \emph{pixel basis} instead where ensuring positivity amounts to putting a positive prior on the pixels but still do all computations in the $Y_{lm}$ basis where all integrals are analytic and can be computed efficiently.
-We obtain the pixels by constructing a discrete grid on the surface of the sphere using an equal area Molleweide projection
-and to ensure that the intensity is positive everywhere on the surface we need to have more pixels than spherical harmonics (by a factor of a few).
-Given a vector of spherical harmonic coefficients we can switch to the pixel basis with a linear operator $\mathbf{P}$ which is straightforward to compute.
-The inverse transform is less straightforward because the number of pixels is greater than the number of $Y_{lm}$ coefficients so the matrix $\mathbf{P}$ is not square and is therefore not invertible.
-Although we can't invert this matrix we can still compute the Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ which is obtained by solving the linear system $\mathbf{P}\,\mathbf{y}=\mathbf{p}$ where $\mathbf{p}$ is the vector of all pixels comprising a map.
+The positivity constraint is important not only because we want to avoid having unphysical regions on inferred maps but because it also imposes a strong constraint on the map which reduces the complexity of the inference problem.
+There is no analytic way to determine weather a given spherical harmonic map $\mathbf{y}$ is positive-valued everywhere on the sphere. 
+The only way of circumventing this problem that we are aware of is to evaluate the intensity on a (sufficiently fine) discrete grid of \emph{pixels} $\mathbf{p}$ on the sphere and then either fit for $\mathbf{y}$ while rejecting inference steps where any of the pixels $\mathbf{p}$ end up being negative, or we can treat the pixels as model parameters but still compute the actual light curve model in the $Y_{lm}$ basis where everything is fast.
+We opt for the latter approach because it is much easier to implement.
+There exists a linear operator $\mathbf{P}$ which maps $\mathbf{y}$ it to pixels:
+\begin{equation}
+    \mathbf{p}=\mathbf{P}\,\mathbf{y}
+\end{equation}
+Each row of $\mathbf{P}$ contains values of each of spherical harmonic coefficients at a point on the grid. 
+To construct the grid we use an equal area Molleweide projection so that we don't end up with more pixels in some areas of the sphere than others.
+The grid needs to be fine enough to ensure positivity over most of the sphere, we find that we need to have more pixels than spherical harmonics by a factor of at least 4.
+Although we can't invert $\mathbf{P}$ to obtain the inverse transform we can still compute the Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$ where $\mathbf{I}$ is the identity matrix.
+The solution is given by
+\begin{equation}
+\mathbf{P}^\dagger=\left(\mathbf{P}^{\top} \mathbf{P}+\lambda \mathbf{I}\right)^{-1} \mathbf{P}^{\top}
+\end{equation}
+where $\lambda$ is a small regularization parameter and $\mathbf{I}$ is the identity matrix.
+We then have 
+\begin{equation}
+    \mathbf{y}'=\mathbf{P}^\dagger\mathbf{p}'
+\end{equation}
+Both matrices can be easily pre-computed with \textsf{starry} before doing inference.
+
 The flux can then be computed as a linear operation on the pixels: 
@@
 \end{equation}
-where the pixels $\mathbf{p}'$ are close to $\mathbf{p}$ in a least-squares sense.
-In what follows, we will assume that we work in the pixel basis and compute all fluxes in the $Y_{lm}$ basis where the model is exact.
-We will discuss the validity of this approach in detail in Section~\ref{sec:inverse_problem}.
+We use the symbol $\mathbf{p}'$ to denote pixels which are mapped to spherical harmonic coefficients using $\mathbf{P}^\dagger$ and $\mathbf{p}$ for those generated from $\mathbf{y}$ using $\mathbf{P}$.
+In the rest of the paper we call the former kind pixels \emph{schmixels}.
+In Section~\ref{ssec:schmixels_vs_harmonics} we test differences between fitting a model for spherical harmonic coefficients vs. fitting for schmixels.
 
@@
 
-\subsection{Fitting a static map}
-\label{ssec:static_map}
-In this section we test inference with the static map model defined in Section~\ref{ssec:static} on both simulated and real data.
-First we use \textsf{starry} to generate one simulated light curve of an occultation of Io by Jupiter with an $l=30$ map containing a single bright hot spot.
-We take ephemeris parameters (assumed to be fixed) from a real occultation and assume an observational cadence and noise similar to IRTF light curves.
-We use this dataset to test the difference between fitting a map in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the pixel basis (Eq.~\ref{eq:linear_model_pix}).
-We fit two models for the Maximum A Posteriori (MAP) estimate of the parameters using the
-\textsf{BFGS} algorithm as implemented in \textsf{scipy.optimize.minimize} in the \textsf{scipy} package (CITE) and the exact gradients of the model with respect to all parameters provided by \textsf{Theano}.
+\subsection{Schmixels vs. spherical harmonics}
+\label{ssec:schmixels_vs_harmonics}
+To test inference with the static map model defined in Section~\ref{ssec:static} 
+we use \textsf{starry} to generate a single simulated light curve of an occultation of Io by Jupiter from an $l=30$ map.
+The simulated map consists of a spherical harmonic expansion of a bright spot with a Gaussian profile which we add using the built in \textsf{add\_spot} function in \textsf{starry}.
+The expansion is in the quantity $\cos(\Delta\theta)$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere. 
+We place the spot at 13 degrees latitude and 51 degrees East longitude, set the diameter of the spot ($2\Delta\theta$) to 5 degrees and the amplitude to 55\% of the total luminosity of a spotless map.
+We take ephemeris parameters (assumed to be fixed) from a real occultation and assume an observational cadence of 1s and errorbars equal to 2\% of the total flux, similar to high quality IRTF light curves.
+We use this dataset to test the difference between fitting a model in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the schmixel basis (Eq.~\ref{eq:linear_model_pix})
+by fitting for an $l=20$ map.
 
-In the first model we place a Gaussian prior on $Y_{lm}$ coefficients with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$ and optimize for the values of the coefficients. 
-In the second model we fit for pixels $\mathbf{p}'$ with a positive prior  in order to ensure (approximate) positivity of the inferred maps.
-To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the pixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each step in the inference algorithm.
-As the end product of the inference we do not store the interim pixels $\mathbf{p}'$ but rather the spherical harmonic coefficients. 
-To distinguish between the pixels $\mathbf{p}'$ which are defined on a fixed grid in (latitude,longitude) and the pixels $\mathbf{p}=\mathbf{P}\,\mathbf{y}$ which can be computed on an arbitrary grid conditional on knowing $\mathbf{y}$, we call the former \emph{schmixels}.
-Although the priors on schmixels $\mathbf{p}'$ are strictly positive, because of the approximate mapping to spherical harmonics the pixels $\mathbf{p}$ won't completely respect the prior and there will be still be some regions of the map with negative intensity.
+In the first case we place a Gaussian prior on $Y_{lm}$ coefficients with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$ and optimize for the values of the coefficients.
+In the second case we fit for schmixel $\mathbf{p}'$ evaluated on a fixed (latitude, longitude) grid with two sets of positive priors, a Half Gaussian prior with zero mean and an Exponential prior.
+To ensure we have a grid of high enough resolution we use 4 times as many schmixels as spherical harmonic coefficients.
 
-The justification for this somewhat convoluted procedure is shown in Fig.~\ref{fig:pixels_vs_harmonics}.
+To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the schmixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each evaluation of the posterior.
+As the end product of the inference we do not use the schmixels $\mathbf{p}'$ but rather the spherical harmonic coefficients $\mathbf{y}=\mathbf{P}^\dagger\mathbf{p}'$ generated from the schmixels.
+The coefficents $\mathbf{y}$ can then be used to evaluate the map on a pixelated grid of arbitrary resolution via the matrix $\mathbf{P}$. 
+Although the priors on schmixels $\mathbf{p}'$ are strictly positive, the pixels $\mathbf{P}\,\mathbf{y}$ don't completely respect those priors because some information is lost in going from schmixels to spherical harmonics  and there will still be some regions of the map with negative intensity.
+To visualize the effect of the transformation from schmixels to spherical harmonics, in Figure~\ref{fig:schmixels_to_pixels} we plot a single draw of schmixels from an Exponential prior (left), convert them to spherical harmonics (middle) and then generate another pixelated map from the spherical harmonics on a grid of the same size as the schmixel grid.
+The middle map is visibly smoother than the prior map and based on the histograms shown in black, it seems that the effective prior is closer to a Gaussian than an Exponential.
+There is also minimal leakage into negative values.
 
@@
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/pixels_vs_harmonics.pdf}
-    \oscaption{pixels_vs_harmonics}{%
-        Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (third panel) which generated from an $l=30$ map consisting of a single bright spot (top panel).
-        The left portion of the figure shows a map inferred using a model in which we directly fit for spherical harmonic coefficients with a Gaussian prior on the coefficients.
-        The right portion shows a map inferred from a model in which an Exponential prior is placed on the pixels defined on a fixed latitude-longitude grid which are converted to spherical harmonic coefficients at every step of the inference process.
-        The pixels are only used as a tool to impose positivity and sparsity (via the Exponential prior) on the map intensity but the final inferred map (second panel on the right) and the predicted flux (orange lines) are generated from a map defined by a set of spherical harmonic coefficients.
-Both models fit the data reasonably well but the inferred maps are widely different. 
-As a result of the sparse prior, the model whose prior is specified in pixel space results in a considerably simpler map with a single bright features where all the other regions of the map are pushed towards zero intensity.
-Both maps show significant ringing effects due to the finite order of the spherical harmonic expansion. 
-        The precise location of the true spot is not recovered for either of the two models
-        which is not surprising because a single light curve is not sufficient to break the degeneracies.
-        \label{fig:pixels_vs_harmonics}
+    \includegraphics[width=1.\linewidth]{figures/schmixels_to_pixels.pdf}
+    \oscaption{schmixels_to_pixels}{%
+        Mapping from a pixelated map in which we set our priors (left) to the spherical harmonic basis which we use to compute the model (middle) and then back to pixels (right).
+        The mapping from spherical harmonics to pixels is exact but the reverse is not true
+        so to differentiate between pixels mapped to spherical harmonics and pixels constructed from spherical harmonics we call the former "schmixels".
+        Since there are many more schmixels than there are spherical harmonics coefficients 
+       the map drawn from an Exponential prior on the left can only be approximately represented in the $Y_{lm}$ basis and the effective prior on pixels ends up looking more like a Gaussian with a heavier right tail than an Exponential.
+  \label{fig:schmixels_to_pixels}
     }
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/pixels_hist.pdf}
-    \oscaption{pixels_hist}{%
-        Cumulative distribution of pixels in the true map and the inferred maps shown in Fig.~\ref{fig:pixels_vs_harmonics}.
-        The pixels were obtained by dotting a pixel transform matrix $\mathbf{P}$ into the spherical coefficient vector $\mathbf{y}$ of each map.
-        The top panel shows the distribution of pixels for the model in which we fit for the spherical harmonic coefficients with a Gaussian prior (orange). 
-        The distribution of pixels in the true map is shown in blue.
-        The bottom panel shows the pixels for a second model (right panel of Fig.~\ref{fig:pixels_vs_harmonics}) in which we fit for interim pixels which we call schmixels (green) instead of the spherical harmonic coefficients although the coefficients are still used to compute the flux and to compute the final pixel distribution (orange).
-        The true map pixels are almost all positive (as they should be) except for a small tail due to truncation of the spherical harmonic expansion.
-        The distribution of inferred pixels in the spherical harmonic model looks nothing like the truth and there is a significant left tail corresponding to negative values of map intensity which is due to the ringing artefacts which aren't sufficiently suppressed by the Gaussian prior.
-        The distribution of schmixels (interim pixels used to enforce positivity of the map)       follows the exponential prior and is strictly positive by definition. 
-        The distribution of corresponding pixels is not identical to that of schmixels because the mapping $\mathbf{P}$ from spherical harmonics to pixels is not invertible.
-        However, the resulting distribution is closer the truth with a smaller left tail.
-        \label{fig:pixels_hist}
+    \includegraphics[width=1.\linewidth]{figures/pixels_vs_harmonics.pdf}
+    \oscaption{schmixels_vs_harmonics}{%
+        Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (bottom) which was generated from an $l=30$ map consisting of a single bright spot (top).
+        The small circles beneath each inferred map show the progression of the occultation.
+        The map on the left corresponds to a model in which we directly fit for spherical harmonic coefficients $\mathbf{y}$ with a Gaussian prior.
+        The map in the middle comes from a model in which we instead fit for schmixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
+        The map on the right is the same as the middle one except we use an Exponential prior.
+        The scale parameter of the Half Gaussian and the Exponential prior is set to a value which approximates the scale of Gaussian prior on $\mathbf{y}$ to ensure fair comparison between the solutions.
+        While all models fit the data reasonably well, the ones in which we fit for schmixels result in more plausible and sparse maps.
+The location of the true spot is not recovered correctly because a single light curve does not contain enough information to break the degeneracy in position along the limb of the occultor.
+        \label{fig:schmixels_vs_harmonics}
     }
@@
 
-To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:pixels_vs_harmonics} we choose to apply a spatial smoothing filter to the spherical harmonics.
+To ensure that the difference in the inferred maps is not in part due to a difference in the scale of the priors, we take 10000 prior samples of the $y$ in the spherical harmonic model, compute the standard deviation and use that as the scale parameter of the Half Gaussian and the Exponential prior.
+We fit all models for the Maximum A Posteriori (MAP) estimate of the parameters using the
+\textsf{BFGS} algorithm as implemented in \textsf{scipy.optimize.minimize} in the \textsf{scipy} package (CITE) and the exact gradients of the model with respect to all parameters provided by \textsf{Theano}.
+The results are shown in Figure~\ref{fig:schmixels_vs_harmonics}.
+The top subplot shows the true map with a localized bright spot and the 
+inferred maps are shown in the second row from the top together with the progression of the occultation (miniature maps). 
+Bottom subplots show the simulated light curves, the predicted flux from the model and the normalized residuals.
+The difference between the inferred maps is substantial despite the fact that the predicted flux is similar in all three cases.
+
+The inferred map from the spherical harmonic model (left) has near zero intensity on the observer facing side of Io except for a bright arc tracing the projected limb of Jupiter at the location of the true spot.
+The flux on the unobserved side of Io is nearly uniform and significantly higher than the flux on the observer facing side which results in an unrealistic transition between the bright and the dark region at $\pm 90$ degrees longitude.
+A very clear "ringing" pattern is visible in the with high intensity peaks and low (in some regions negative) intensity troughs.
+These features are a consequence of the finite order spherical harmonic expansion of the map and we could in principle get rid of them by fitting a higher order map but at $l=20$ we are already pushing the limits of what \textsf{starry} can do.
+Besides avoiding unphysical negative intensities, ringing is undesirable because we want to avoid situations in which the model uses the rings to explain the data instead of just placing a spot directly.
+For example, we find that for some fits at low $l$, the model would place a bright spot on the unobserved side of Io in order to produce a ringing artefact on the observed side to explain an increase or decrease in brightness in the light curve.
+This is happening to a lesser extent in the shown map where a small spot is visible at the right edge of the observed hemisphere in order to amplify the visible bright arc through ringing.
+
+The schmixel model with Half Gaussian priors produces a more sensible map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
+The map from a model with an Exponential prior on the schmixels provides the best fit.
+It is the sparsest of the three maps, having a single bright spot at the center of the projected limb of Jupiter at the location of the true spot with extended tails along the limb.
+In principle, the sparsity is a consequence of the Exponential prior which has significant probability mass near zero, meaning that it pushes most schmixels towards zero intensity, and a heavy tail towards large intensities.
+It favors parse maps with near zero intensity everywhere except for a few high intensity regions which is exactly the kind of prior information we want to assume for Io because we expect spot like features on its surface.
+In practice, as shown in Figure~\ref{fig:schmixels_to_pixels}, the Exponential prior 
+implies a more Gaussian like prior in spherical harmonic space and yet it still gives noticeably different looking map than a Gaussian (NOT CONVINCING).
+
+%Figure~\ref{fig:pixels_hist} shows the cumulative distributions of pixels and schmixels corresponding to the three inferred maps shown in Figure~\ref{fig:schmixels_vs_harmonics}, shown in the same order as the inferred maps.
+%The plot on the left shows the distribution of pixels in the true map (blue line) 
+%and the inferred pixels $\mathbf{P}\,\mathbf{y}$ (orange).
+%The true distribution rapidly increases towards unity because the majority of pixels have near zero intensity. 
+%There is a very small tail towards negative values which is due to the fact that we generate the true map at $l=30$ and even at that resolution there is still some ringing present leading to negative intensities.
+%The inferred distribution has a very different shape with approximately 20\% of pixels having negative values and a much more gradual increase towards unity.
+%
+%The second subplot shows the distribution of both pixels (orange) and schmixels (green) corresponding to the model with Half Gaussian priors on the schmixels.
+%The distribution of pixels and schmixels in this case is nearly identical meaning that the approximate mapping $\mathbf{P}^\dagger$ is good enough.
+%In the case of an Exponential prior on schmixels (right) the shape of the schmixel and pixel distributions is similar to the Gaussian prior solution except for a small discrepancy between the two distributions.
+%The schmixel distribution has no mass at negative values (by definition), but the inferred pixel distribution has a very small negative tail.
+%The discrepancy is likely due to the fact that the Exponential prior favors more concentrated regions of high intensity which induce more ringing artefacts with some negative pixels.
+%
+%\begin{figure}[h!]
+%    \begin{centering}
+%        \includegraphics[width=\linewidth]{figures/pixels_hist.pdf}
+%    \oscaption{pixels_hist}{%
+%        Cumulative distribution of pixels in the true map and the and schmixels/pixels of inferred maps shown in Fig.~\ref{fig:schmixels_vs_harmonics}.
+%        The distribution of pixels in the inferred map from the $Y_{lm}$ model (left) is very different from the truth and it has a significant left tail towards negative values.
+%        On the other hand, the distribution of pixels in the schmixel model (middle and right) is much closer to the truth and it has a negligible fraction of negative intensities.
+%        The distribution of pixels closely follows the distribution of schmixels for both choices of priors on schmixels. 
+%        \label{fig:pixels_hist}
+%    }
+%    \end{centering}
+%\end{figure}
+
+\subsection{Smoothing out spurious features}
+\label{ssec:spurious_features}
+To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:schmixels_vs_harmonics}, we choose to apply a spatial smoothing filter to the spherical harmonics.
 Mathematically, the filtering operation is a convolution between the map and some kernel function $B(\theta,\phi)$.
-The simplest choice for the kernel function is a Gaussian distribution given by
+Assuming both the map and the kernel function are expanded in terms of spherical harmonics, the convolution operation is simply a multiplication between the two sets of spherical harmonic coefficients.
+We choose a simple azimuthally symmetric Gaussian kernel function given by
 \begin{equation}
@@
 \begin{equation}
-B(\theta)=\sum_{l=0}^{\infty}\left(\frac{2 l+1}{4 \pi}\right) B_{l} P_{l}(\cos \theta)
+    B(\theta)=\sum_{l=0}^{\infty}\left(\frac{2 l+1}{4 \pi}\right) B_{l} \,\mathcal{P}_{l}(\cos \theta)
 \end{equation}
-where $B_l$ are the spherical harmonic coefficients and $P_l$ are the associated Legendre polynomials.
-They depend only on $l$ because the kernel function is azimuthally symmetric so all nonzero $m$ modes vanish.
-For $\sigma_s\ll 1$ $B_l$ can be approximated as \citep{seon2007}
+where $B_l$ are the spherical harmonic coefficients and $\mathcal{P}_l$ are the associated Legendre polynomials.
+They depend only on $l$ because all nonzero $m$ modes vanish due to azimuthal symmetry.
+For $\sigma_s\ll 1$ $B_l$ can be approximated as \citep{seon2007,white1995}
 \begin{equation}
-    B_l\approx \exp\left[-\frac{1}{2}l(l+1)\sigma_s^2\right]
+    B_l\simeq \exp\left[-\frac{1}{2}l(l+1)\sigma_s^2\right]
 \end{equation}
 The Gaussian filter results in an exponential cutoff for scales smaller than $l\sim \sigma_s^{-1}$.
+
+In Figure~\ref{fig:smoothing_kernel} we show the effect of (Gaussian) smoothing on a spherical harmonic expansion of a spot with a Gaussian intensity profile.
+The expansion is in the quantity $\cos\Delta\theta$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere.
+We place the spot at zero degrees latitude and longitude and set the size of the spot $\Delta\theta$ to 5 degrees.
+All three subplots show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
+The leftmost subplot shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
+The middle subplot shows an intermediate level of smoothing where $\sigma_s=0.1$, meaning that all features on scales above $l\approx 10$ are exponentially suppressed.
+In this case the negative ringing is a lot less visible albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
+This is most apparent in the rightmost subplot where $\sigma_s=0.2$. 
+Although there is practically no ringing, expansions at $l=10$, $l=15$ and $l=20$ look almost the same because all coefficients above $l=5$ are significantly suppressed.
 
@@
 
+Thus, there is a trade-off between smoothing and resolution of the maps. 
+In principle we can always get rid of ringing by fitting sufficiently high order maps.
+In practice, computing the analytic integrals computed by \textsf{starry} becomes computationally unstable above $l\approx 25$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
+
+\subsection{Fitting simulated ingress/egress light curves}
+In Figure~\ref{fig:ingress_egress_simulated} we test a model with the smoothing filter 
+by simulating data as in Figure~\ref{fig:schmixels_vs_harmonics}, except this time we simulate two light curves, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
+
 \begin{figure}[h!]
@@
 
+\subsection{Fitting IRTF ingress/egress light curves}
 \begin{figure}[h!]
@@
     \oscaption{irtf_ingress_egress}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
+Maximum A Posteriori (MAP) estimate of two $l=25$ maps produced by simultaneously fitting two IRTF light curves of an occultation of Io by Jupiter.
+The light curve on the left corresponds to an ingress of Io 
+        while the one on the right
+        fitting a pair of light curves simulated from the true map which is shown on the left.
+        The simulated light curves are shown in the third panel from the top, an ingress light curve on the left and an egress light curve on the right.
+        The small circles above each of the light curves show the progression of the occultation over the inferred map.
+        The precise location of the true spot is not recovered for either of the two models
+        which is not surprising because a single light curve is not sufficient to break the degeneracies.
         \label{fig:irtf_ingress_egress}

### 2020-09-26 paper/figures/irtf_ingress_egress.py
Adding geological map.

@@ -38,7 +38,6 @@ lc_eg = TimeSeries(
     ),
 )
 
-
 # Compute ephemeris
 eph_list_io = []
 eph_list_jup = []
@@ -101,7 +100,6 @@ xo_eg, yo_eg, ro_eg = get_pos_rot(eph_io_eg, eph_jup_eg)
 theta_in = eph_io_in["theta"].value
 theta_eg = eph_io_eg["theta"].value
 
-
 # Fit single map model with different map amplitudes for ingress and egress
 ydeg_inf = 25
 map = starry.Map(ydeg_inf)
@@ -132,12 +130,12 @@ with pm.Model() as model:
     map = starry.Map(ydeg_inf)
 
     p = pm.Exponential(
-        "p", 1 / 20.0, shape=(npix,), testval=0.1 * np.random.rand(npix)
+        "p", 1 / 10.0, shape=(npix,), testval=0.1 * np.random.rand(npix)
     )
     x = tt.dot(P2Y, p)
 
     # Run the smoothing filter
-    S = get_S(ydeg_inf, 0.07)
+    S = get_S(ydeg_inf, 2 / ydeg_inf)
     x_s = tt.dot(S, x[:, None]).flatten()
 
     map.amp = x_s[0]
@@ -354,32 +352,35 @@ for ax in (ax_lc, ax_res):
     ax[1].plot((-d, +d), (-d, +d), **kwargs)
 
 #  Ticks
-for a in ax_lc:
-    a.set_xticklabels([])
-    a.grid()
-    a.set_yticks(np.arange(0, 60, 10))
-    a.set_ylim(-2, 52)
-
 for a in (ax_lc[0], ax_res[0]):
     a.set_xticks(np.arange(0, 4.5, 0.5))
-    a.set_xlim(left=-0.2)
     a.xaxis.set_minor_locator(AutoMinorLocator())
     a.yaxis.set_minor_locator(AutoMinorLocator())
 
 for a in (ax_lc[1], ax_res[1]):
     a.set_xticks(np.arange(0, 6.0, 0.5))
-    a.set_xlim(left=-0.2)
     a.xaxis.set_minor_locator(AutoMinorLocator())
+    a.yaxis.set_ticklabels([])
+    a.yaxis.set_ticklabels([])
+    a.set_ylabel("")
+    a.set_ylabel("")
+
+for a in ax_lc:
+    a.set_ylim(-2, 52)
+    a.set_xticklabels([])
[…]

### 2020-09-27 paper/figures/irtf_ingress_egress.py
Fixing resolution of all maps.

@@ -243,9 +243,9 @@ gs2 = fig.add_gridspec(
 # Maps
 ax_map_in = fig.add_subplot(gs0[0, :nim])
 ax_map_eg = fig.add_subplot(gs0[0, nim:])
-map.show(ax=ax_map_in, projection="molleweide", colorbar=False, norm=cmap_norm)
+map.show(ax=ax_map_in, projection="molleweide", colorbar=False, norm=cmap_norm, res=resol)
 map_eg.show(
-    ax=ax_map_eg, projection="molleweide", colorbar=True, norm=cmap_norm
+    ax=ax_map_eg, projection="molleweide", colorbar=True, norm=cmap_norm, res=resol
 )
 ax_map_in.set_title("Inferred map\n ingress")
 ax_map_eg.set_title("Inferred map\n egress")
@@ -395,7 +395,7 @@ shifted_map = np.roll(combined_mosaic, int(11445 / 2), axis=1)
 
 fig, ax = plt.subplots(figsize=(8, 4))
 map.show(
-    projection="rectangular", ax=ax, colorbar=False,
+    projection="rectangular", ax=ax, colorbar=False, res=resol
 )
 
 ax.imshow(shifted_map, extent=(-180, 180, -90, 90), alpha=0.7, cmap="gray")

### 2020-09-27 paper/figures/pixels_vs_harmonics.py

@@ -195,6 +195,7 @@ def plot_everything(
         ax=ax_map,
         colorbar=show_cbar,
         norm=colors.Normalize(vmin=-0.5, vmax=20),
+        res=resol,
     )
     ax_map.axis("off")
 
@@ -335,6 +336,7 @@ map_true.show(
     ax=ax_true_map,
     projection="molleweide",
     colorbar=True,
+    res=resol
     #    norm=colors.Normalize(vmin=-0.5),
 )
 ax_true_map.axis("off")
@@ -401,7 +403,6 @@ plot_everything(
     res_pix_exp,
     show_cbar=True,
 )
-
 
 for a in ax_lc[1:] + ax_res[1:]:
     a.yaxis.set_ticklabels([])

### 2020-09-27 paper/figures/schmixels_to_pixels.py

@@ -123,6 +123,7 @@ im1 = ax[0, 0].scatter(
 )
 
 #  Plot Ylm map
+resol = 150
 map = starry.Map(ydeg)
 map.amp = x_sample[0]
 map[1:, :] = x_sample[1:] / map.amp
@@ -130,6 +131,7 @@ map.show(
     ax=ax[0, 1],
     projection="molleweide",
     norm=colors.Normalize(vmin=0, vmax=vmax),
+    res=resol,
 )
 
 

### 2020-09-27 paper/figures/simulated_ingress_egress.py

@@ -38,29 +38,32 @@ ro = 39.1
 
 ydeg_true = 25
 map_true = starry.Map(ydeg_true)
-spot_lon = 360 - 308.8
+spot_lon = 360 - 309
 spot_lat = 13.0
+spot_ang_dim = 5 * np.pi / 180
+spot_sigma = 1 - np.cos(spot_ang_dim / 2)
 map_true.add_spot(
-    amp=2.0, sigma=1e-03, lat=spot_lat, lon=spot_lon, relative=False
+    amp=1.0, sigma=spot_sigma, lat=spot_lat, lon=spot_lon, relative=False
 )
 map_true.amp = 20
 
 # Smooth the true map
-S_true = get_S(ydeg_true, 0.1)
+sigma_s = 2 / ydeg_true
+S_true = get_S(ydeg_true, sigma_s)
 x = (map_true.amp * map_true.y).eval()
 x_smooth = (S_true @ x[:, None]).reshape(-1)
 map_true[:, :] = x_smooth / x_smooth[0]
 map_true.amp = x_smooth[0]
 
-
 # Generate mock ingress and egress light curves
 f_true_in = map_true.flux(ro=ro, xo=xo_in, yo=yo_in).eval()
 f_true_eg = map_true.flux(ro=ro, xo=xo_eg, yo=yo_eg).eval()
 
-f_err = 0.46
+f_err_in = 0.02 * np.max(f_true_in)
+f_err_eg = 0.02 * np.max(f_true_eg)
 
-f_obs_in = f_true_in + np.random.normal(0, f_err, len(f_true_in))
-f_obs_eg = f_true_eg + np.random.normal(0, f_err, len(f_true_eg))
+f_obs_in = f_true_in + np.random.normal(0, f_err_in, len(f_true_in))
+f_obs_eg = f_true_eg + np.random.normal(0, f_err_eg, len(f_true_eg))
 f_obs = np.concatenate([f_obs_in, f_obs_eg])
 
 
@@ -84,7 +87,7 @@ with pm.Model() as model:
     x = tt.dot(P2Y, p)
 
     # Run the smoothing filter
-    S = get_S(ydeg_inf, 0.1)
+    S = get_S(ydeg_inf, 2/ydeg_inf)
     x_s = tt.dot(S, x[:, None]).flatten()
 
     map.amp = x_s[0]
@@ -111,7 +114,18 @@ with pm.Model() as model:
     pm.Deterministic("flux_eg_dense", flux_eg_dense)
[…]

### 2020-10-08 paper/paper.tex
Updating abstract

@@
 Existing photometric observations in the near infrared taken during occultations by Jupiter and Galilean moons encode a wealth of information about its surface.
-As such, Io is an ideal testbed for models of time-variable exoplanet surfaces.
-We build a single probabilistic model of Io's surface using Nonnegative Matrix Factorization to infer one map per light curve.
-The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which can compute occultation light curves and phase curves in both emitted and reflected light.
-It also enables efficient inference with gradient based samplers.
+Io is thus an ideal testbed for models of time-variable exoplanet surfaces.
+We built a generative model of Io's surface for each observation using Nonnegative Matrix Factorization.
+The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic computation of occultation light curves, phase curves in both emitted and reflected light and also computes exact gradients with respect to all input parameters.
 We use the inferred map to study the time variability of prominent volcanoes over a timescale of decades.
-While we mostly focus on Io, the lessons we learn are directly applicable to mapping exoplanets.
+While we mostly focus on Io, the models are directly applicable to mapping exoplanets.
 We discuss this application towards the end of the paper.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
@@
 by fitting for an $l=20$ map.
+Since we are only fitting a single light curve, the inferred maps will be strongly prior dominated.
 
@@
 
-The schmixel model with Half Gaussian priors produces a more sensible map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
-The map from a model with an Exponential prior on the schmixels provides the best fit.
-It is the sparsest of the three maps, having a single bright spot at the center of the projected limb of Jupiter at the location of the true spot with extended tails along the limb.
-In principle, the sparsity is a consequence of the Exponential prior which has significant probability mass near zero, meaning that it pushes most schmixels towards zero intensity, and a heavy tail towards large intensities.
-It favors parse maps with near zero intensity everywhere except for a few high intensity regions which is exactly the kind of prior information we want to assume for Io because we expect spot like features on its surface.
-In practice, as shown in Figure~\ref{fig:schmixels_to_pixels}, the Exponential prior 
-implies a more Gaussian like prior in spherical harmonic space and yet it still gives noticeably different looking map than a Gaussian (NOT CONVINCING).
-
-%Figure~\ref{fig:pixels_hist} shows the cumulative distributions of pixels and schmixels corresponding to the three inferred maps shown in Figure~\ref{fig:schmixels_vs_harmonics}, shown in the same order as the inferred maps.
-%The plot on the left shows the distribution of pixels in the true map (blue line) 
-%and the inferred pixels $\mathbf{P}\,\mathbf{y}$ (orange).
-%The true distribution rapidly increases towards unity because the majority of pixels have near zero intensity. 
-%There is a very small tail towards negative values which is due to the fact that we generate the true map at $l=30$ and even at that resolution there is still some ringing present leading to negative intensities.
-%The inferred distribution has a very different shape with approximately 20\% of pixels having negative values and a much more gradual increase towards unity.
-%
-%The second subplot shows the distribution of both pixels (orange) and schmixels (green) corresponding to the model with Half Gaussian priors on the schmixels.
-%The distribution of pixels and schmixels in this case is nearly identical meaning that the approximate mapping $\mathbf{P}^\dagger$ is good enough.
-%In the case of an Exponential prior on schmixels (right) the shape of the schmixel and pixel distributions is similar to the Gaussian prior solution except for a small discrepancy between the two distributions.
-%The schmixel distribution has no mass at negative values (by definition), but the inferred pixel distribution has a very small negative tail.
-%The discrepancy is likely due to the fact that the Exponential prior favors more concentrated regions of high intensity which induce more ringing artefacts with some negative pixels.
-%
-%\begin{figure}[h!]
-%    \begin{centering}
-%        \includegraphics[width=\linewidth]{figures/pixels_hist.pdf}
-%    \oscaption{pixels_hist}{%
-%        Cumulative distribution of pixels in the true map and the and schmixels/pixels of inferred maps shown in Fig.~\ref{fig:schmixels_vs_harmonics}.
-%        The distribution of pixels in the inferred map from the $Y_{lm}$ model (left) is very different from the truth and it has a significant left tail towards negative values.
-%        On the other hand, the distribution of pixels in the schmixel model (middle and right) is much closer to the truth and it has a negligible fraction of negative intensities.
-%        The distribution of pixels closely follows the distribution of schmixels for both choices of priors on schmixels. 
-%        \label{fig:pixels_hist}
-%    }
-%    \end{centering}
-%\end{figure}
+The schmixel model with Half Gaussian priors produces a simpler map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
+Finally, the Exponential prior on schmixels results in a map with the most spot like feature but it also has noticeable ringing.
+This is somewhat surprising because based on Figure~\ref{fig:schmixels_to_pixels}, we wouldn't expect much difference between the Half Gaussian and the Exponential priors.
+It seems that the heavier tail of the Exponential is nevertheless able to induce a sparser solution.
+In the next section, we tackle the issue of ringing artefacts.
 
@@
 \label{ssec:spurious_features}
-To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:schmixels_vs_harmonics}, we choose to apply a spatial smoothing filter to the spherical harmonics.
+To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:schmixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonics.
 Mathematically, the filtering operation is a convolution between the map and some kernel function $B(\theta,\phi)$.
@@
 where $\sigma_s$ sets the characteristic scale of the smoothing.
-This function can be expended in terms of spherical harmonics as
+This function can be expanded in terms of spherical harmonics as
 \begin{equation}
@@
 \end{equation}
-The Gaussian filter results in an exponential cutoff for scales smaller than $l\sim \sigma_s^{-1}$.
+The effect of this filter is to exponentially suppress features on scales smaller than $l\sim \sigma_s^{-1}$.
 
-In Figure~\ref{fig:smoothing_kernel} we show the effect of (Gaussian) smoothing on a spherical harmonic expansion of a spot with a Gaussian intensity profile.
-The expansion is in the quantity $\cos\Delta\theta$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere.
+Figure~\ref{fig:smoothing_kernel} shows the effect of (Gaussian) smoothing on a spherical harmonic expansion of a spot with a Gaussian intensity profile.
 We place the spot at zero degrees latitude and longitude and set the size of the spot $\Delta\theta$ to 5 degrees.
 All three subplots show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
-The leftmost subplot shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
+The subplot on the left shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
 The middle subplot shows an intermediate level of smoothing where $\sigma_s=0.1$, meaning that all features on scales above $l\approx 10$ are exponentially suppressed.
-In this case the negative ringing is a lot less visible albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
-This is most apparent in the rightmost subplot where $\sigma_s=0.2$. 
-Although there is practically no ringing, expansions at $l=10$, $l=15$ and $l=20$ look almost the same because all coefficients above $l=5$ are significantly suppressed.
+The negative ringing is a lot less visible albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
+For $\sigma_s=0.2$ (right) there is practically no ringing, but the expansions at $l=10$, $l=15$ and $l=20$ result in the spot of the same size because all coefficients above $l=5$ are significantly suppressed.
 
@@
         a Gaussian spot placed at zero degrees latitude and longitude.
-        The expansion is in the quantity $\cos\Delta\theta$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere, it is set to 5 degrees.
-        The three insets show the spot profile at different strengths of the smoothing kernel
-        where the leftmost spot has no smoothing ($\sigma_s=0$) and the rightmost spot is strongly smoothed. 
-        The lines of different colors correspond to spot expansions up to certain order and the black line is the expansion at infinite order.
-        The purpose of smoothing is to taper the higher order spherical harmonic coefficients.
-        No smoothing results in significant "rings" where the intensity goes negative, even at high order.
-        High levels of smoothing reduce the ringing but increase the spot size and eliminate differences between expansions above a certain order.
+        The expansion is in the quantity $\cos\Delta\theta$ where $\Delta\theta=5^\circ$.
+        The three plots show the spot profile for increasing values of the smoothing parameter 
+    $\sigma_s=0$. 
+        The colored lines correspond to spot expansions up to a certain order and the black line is the exact expansion.
+        The purpose of smoothing is to taper higher order spherical harmonic coefficients in order to suppress ringing artefacts which result in negative intensities.
+        It is apparent that no smoothing results in significant ringing, high levels of smoothing suppress the ringing completely but as a result they increase the spot size and eliminate differences between expansions above a certain order.
+        Intermediate levels of smoothing provide a compromise beteween the two extremes.
                \label{fig:smoothing_kernel}
@@
 
-Thus, there is a trade-off between smoothing and resolution of the maps. 
+Thus, there is a trade-off between smoothing and being able to resolve smaller scale features
+in the maps. 
 In principle we can always get rid of ringing by fitting sufficiently high order maps.
 In practice, computing the analytic integrals computed by \textsf{starry} becomes computationally unstable above $l\approx 25$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
+We find that setting $\sigma_s=2/l$ where $l$ is the order of expansion of the map provides the best results .
 
 \subsection{Fitting simulated ingress/egress light curves}
-In Figure~\ref{fig:ingress_egress_simulated} we test a model with the smoothing filter 
-by simulating data as in Figure~\ref{fig:schmixels_vs_harmonics}, except this time we simulate two light curves, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
+In this section we test a model which includes the smoothing filter. 
+We use the same map to generate the data as in Figure~\ref{fig:schmixels_vs_harmonics} except this time we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
+We generate the light curves from an $l=25$ map and fit a map of the same order. 
+We apply a Gaussian smoothing filter to both the simulated map and the map we fit to the data and set the smoothing parameter to $\sigma_s=2/l=2/25$. 
+We use an Exponential prior on the schmixels and set the scale parameter to 10.
+The results are shown in Figure~\ref{fig:ingress_egress_simulated}.
 
@@
     \oscaption{ingress_egress_simulated}{%
-        Maximum A Posteriori (MAP) estimate of an $l=25$ map (right panel from the top) produced by fitting a pair of light curves simulated from the true map which is shown on the left.
-        The simulated light curves are shown in the third panel from the top, an ingress light curve on the left and an egress light curve on the right.
-        The small circles above each of the light curves show the progression of the occultation over the inferred map.
-        The precise location of the true spot is not recovered for either of the two models
-        which is not surprising because a single light curve is not sufficient to break the degeneracies.
+Maximum A Posteriori (MAP) estimate of an $l=25$ map (right) produced by fitting a pair of simulated ingress and egress occultation light curves (bottom) which were generated from a $l=25$ map consisting of a single bright spot (left).
+       A Gaussian smoothing filter is applied to reduce the ringing artefacts.
+       Small circles beneath each inferred map show the progression of the occultation.
+        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:schmixels_vs_harmonics}.
         \label{fig:ingress_egress_simulated}
@@
 
+The inferred map looks significantly better than the one in Figure~\ref{fig:schmixels_vs_harmonics}. 
+With two occultation light curves the model is able to break the degeneracy in the location of the spot and thanks to the smoothing filter there is almost no visible ringing around the spot in the inferred map.
+Some residuals in the data are still present (WHY).
+In the next section, we fit a pair of light curves from the IRTF dataset described in Section~\ref{sec:data}.
+
 \subsection{Fitting IRTF ingress/egress light curves}
+
 \begin{figure}[h!]
@@
     \oscaption{irtf_ingress_egress}{%
-Maximum A Posteriori (MAP) estimate of two $l=25$ maps produced by simultaneously fitting two IRTF light curves of an occultation of Io by Jupiter.
-The light curve on the left corresponds to an ingress of Io 
-        while the one on the right
-        fitting a pair of light curves simulated from the true map which is shown on the left.
-        The simulated light curves are shown in the third panel from the top, an ingress light curve on the left and an egress light curve on the right.
-        The small circles above each of the light curves show the progression of the occultation over the inferred map.
-        The precise location of the true spot is not recovered for either of the two models
-        which is not surprising because a single light curve is not sufficient to break the degeneracies.
+        Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
+       The small circles beneath each inferred map show the progression of the occultation.
+        Both light curves are assumed to be generated from the same map except for a difference in the overall amplitude.
+        We allow for multiplicative rescaling of the error bars and an additive flux offset for each light curve.
+        The model places a single bright spot to explain most of the variance in the data.
+        The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
         \label{fig:irtf_ingress_egress}
@@
     \oscaption{irtf_ingress_egress_loki}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
+        Hot spot from the inferred maps shown in Figure~\ref{fig:irtf_ingress_egress} overlaid on top of the U.S. Geological Survey's map of the surface of Io (CITE) which was
+        constructed from Galileo observations.
+        The location of the hot spots matches the location of Loki Patera, the largest active volcano on the surface of Io. 
         \label{fig:irtf_ingress_egress_loki}

### 2020-10-08 paper/paper.tex
minor changes to abstract

@@
 We built a generative model of Io's surface for each observation using Nonnegative Matrix Factorization.
-The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic computation of occultation light curves, phase curves in both emitted and reflected light and also computes exact gradients with respect to all input parameters.
+The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic computation of occultation light curves, phase curves in both emitted and reflected light and exact gradients with respect to all input parameters.
 We use the inferred map to study the time variability of prominent volcanoes over a timescale of decades.
-While we mostly focus on Io, the models are directly applicable to mapping exoplanets.
+While we mostly focus on Io, our models are directly applicable to mapping exoplanets.
 We discuss this application towards the end of the paper.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}

### 2020-10-10 paper/paper.tex
Renaming schmixels -> sphixels

@@
 We use the symbol $\mathbf{p}'$ to denote pixels which are mapped to spherical harmonic coefficients using $\mathbf{P}^\dagger$ and $\mathbf{p}$ for those generated from $\mathbf{y}$ using $\mathbf{P}$.
-In the rest of the paper we call the former kind pixels \emph{schmixels}.
-In Section~\ref{ssec:schmixels_vs_harmonics} we test differences between fitting a model for spherical harmonic coefficients vs. fitting for schmixels.
+In the rest of the paper we call the former kind pixels \emph{sphixels}.
+In Section~\ref{ssec:sphixels_vs_harmonics} we test differences between fitting a model for spherical harmonic coefficients vs. fitting for sphixels.
 
@@
 
-\subsection{Schmixels vs. spherical harmonics}
-\label{ssec:schmixels_vs_harmonics}
+\subsection{Sphixels vs. spherical harmonics}
+\label{ssec:sphixels_vs_harmonics}
 To test inference with the static map model defined in Section~\ref{ssec:static} 
@@
 We take ephemeris parameters (assumed to be fixed) from a real occultation and assume an observational cadence of 1s and errorbars equal to 2\% of the total flux, similar to high quality IRTF light curves.
-We use this dataset to test the difference between fitting a model in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the schmixel basis (Eq.~\ref{eq:linear_model_pix})
+We use this dataset to test the difference between fitting a model in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the sphixel basis (Eq.~\ref{eq:linear_model_pix})
 by fitting for an $l=20$ map.
@@
 In the first case we place a Gaussian prior on $Y_{lm}$ coefficients with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$ and optimize for the values of the coefficients.
-In the second case we fit for schmixel $\mathbf{p}'$ evaluated on a fixed (latitude, longitude) grid with two sets of positive priors, a Half Gaussian prior with zero mean and an Exponential prior.
-To ensure we have a grid of high enough resolution we use 4 times as many schmixels as spherical harmonic coefficients.
+In the second case we fit for sphixel $\mathbf{p}'$ evaluated on a fixed (latitude, longitude) grid with two sets of positive priors, a Half Gaussian prior with zero mean and an Exponential prior.
+To ensure we have a grid of high enough resolution we use 4 times as many sphixels as spherical harmonic coefficients.
 
-To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the schmixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each evaluation of the posterior.
-As the end product of the inference we do not use the schmixels $\mathbf{p}'$ but rather the spherical harmonic coefficients $\mathbf{y}=\mathbf{P}^\dagger\mathbf{p}'$ generated from the schmixels.
+To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the sphixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each evaluation of the posterior.
+As the end product of the inference we do not use the sphixels $\mathbf{p}'$ but rather the spherical harmonic coefficients $\mathbf{y}=\mathbf{P}^\dagger\mathbf{p}'$ generated from the sphixels.
 The coefficents $\mathbf{y}$ can then be used to evaluate the map on a pixelated grid of arbitrary resolution via the matrix $\mathbf{P}$. 
-Although the priors on schmixels $\mathbf{p}'$ are strictly positive, the pixels $\mathbf{P}\,\mathbf{y}$ don't completely respect those priors because some information is lost in going from schmixels to spherical harmonics  and there will still be some regions of the map with negative intensity.
-To visualize the effect of the transformation from schmixels to spherical harmonics, in Figure~\ref{fig:schmixels_to_pixels} we plot a single draw of schmixels from an Exponential prior (left), convert them to spherical harmonics (middle) and then generate another pixelated map from the spherical harmonics on a grid of the same size as the schmixel grid.
+Although the priors on sphixels $\mathbf{p}'$ are strictly positive, the pixels $\mathbf{P}\,\mathbf{y}$ don't completely respect those priors because some information is lost in going from sphixels to spherical harmonics  and there will still be some regions of the map with negative intensity.
+To visualize the effect of the transformation from sphixels to spherical harmonics, in Figure~\ref{fig:sphixels_to_pixels} we plot a single draw of sphixels from an Exponential prior (left), convert them to spherical harmonics (middle) and then generate another pixelated map from the spherical harmonics on a grid of the same size as the sphixel grid.
 The middle map is visibly smoother than the prior map and based on the histograms shown in black, it seems that the effective prior is closer to a Gaussian than an Exponential.
@@
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/schmixels_to_pixels.pdf}
-    \oscaption{schmixels_to_pixels}{%
+    \includegraphics[width=1.\linewidth]{figures/sphixels_to_pixels.pdf}
+    \oscaption{sphixels_to_pixels}{%
         Mapping from a pixelated map in which we set our priors (left) to the spherical harmonic basis which we use to compute the model (middle) and then back to pixels (right).
         The mapping from spherical harmonics to pixels is exact but the reverse is not true
-        so to differentiate between pixels mapped to spherical harmonics and pixels constructed from spherical harmonics we call the former "schmixels".
-        Since there are many more schmixels than there are spherical harmonics coefficients 
+        so to differentiate between pixels mapped to spherical harmonics and pixels constructed from spherical harmonics we call the former "sphixels".
+        Since there are many more sphixels than there are spherical harmonics coefficients 
        the map drawn from an Exponential prior on the left can only be approximately represented in the $Y_{lm}$ basis and the effective prior on pixels ends up looking more like a Gaussian with a heavier right tail than an Exponential.
-  \label{fig:schmixels_to_pixels}
+  \label{fig:sphixels_to_pixels}
     }
@@
     \includegraphics[width=1.\linewidth]{figures/pixels_vs_harmonics.pdf}
-    \oscaption{schmixels_vs_harmonics}{%
+    \oscaption{sphixels_vs_harmonics}{%
         Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (bottom) which was generated from an $l=30$ map consisting of a single bright spot (top).
@@
         The map on the left corresponds to a model in which we directly fit for spherical harmonic coefficients $\mathbf{y}$ with a Gaussian prior.
-        The map in the middle comes from a model in which we instead fit for schmixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
+        The map in the middle comes from a model in which we instead fit for sphixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
         The map on the right is the same as the middle one except we use an Exponential prior.
         The scale parameter of the Half Gaussian and the Exponential prior is set to a value which approximates the scale of Gaussian prior on $\mathbf{y}$ to ensure fair comparison between the solutions.
-        While all models fit the data reasonably well, the ones in which we fit for schmixels result in more plausible and sparse maps.
+        While all models fit the data reasonably well, the ones in which we fit for sphixels result in more plausible and sparse maps.
 The location of the true spot is not recovered correctly because a single light curve does not contain enough information to break the degeneracy in position along the limb of the occultor.
-        \label{fig:schmixels_vs_harmonics}
+        \label{fig:sphixels_vs_harmonics}
     }
@@
 \textsf{BFGS} algorithm as implemented in \textsf{scipy.optimize.minimize} in the \textsf{scipy} package (CITE) and the exact gradients of the model with respect to all parameters provided by \textsf{Theano}.
-The results are shown in Figure~\ref{fig:schmixels_vs_harmonics}.
+The results are shown in Figure~\ref{fig:sphixels_vs_harmonics}.
 The top subplot shows the true map with a localized bright spot and the 
@@
 
-The schmixel model with Half Gaussian priors produces a simpler map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
-Finally, the Exponential prior on schmixels results in a map with the most spot like feature but it also has noticeable ringing.
-This is somewhat surprising because based on Figure~\ref{fig:schmixels_to_pixels}, we wouldn't expect much difference between the Half Gaussian and the Exponential priors.
+The sphixel model with Half Gaussian priors produces a simpler map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
+Finally, the Exponential prior on sphixels results in a map with the most spot like feature but it also has noticeable ringing.
+This is somewhat surprising because based on Figure~\ref{fig:sphixels_to_pixels}, we wouldn't expect much difference between the Half Gaussian and the Exponential priors.
 It seems that the heavier tail of the Exponential is nevertheless able to induce a sparser solution.
@@
 \label{ssec:spurious_features}
-To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:schmixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonics.
+To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:sphixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonics.
 Mathematically, the filtering operation is a convolution between the map and some kernel function $B(\theta,\phi)$.
@@
 In this section we test a model which includes the smoothing filter. 
-We use the same map to generate the data as in Figure~\ref{fig:schmixels_vs_harmonics} except this time we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
+We use the same map to generate the data as in Figure~\ref{fig:sphixels_vs_harmonics} except this time we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
 We generate the light curves from an $l=25$ map and fit a map of the same order. 
 We apply a Gaussian smoothing filter to both the simulated map and the map we fit to the data and set the smoothing parameter to $\sigma_s=2/l=2/25$. 
-We use an Exponential prior on the schmixels and set the scale parameter to 10.
+We use an Exponential prior on the sphixels and set the scale parameter to 10.
 The results are shown in Figure~\ref{fig:ingress_egress_simulated}.
@@
        Small circles beneath each inferred map show the progression of the occultation.
-        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:schmixels_vs_harmonics}.
+        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:sphixels_vs_harmonics}.
         \label{fig:ingress_egress_simulated}
@@
 
-The inferred map looks significantly better than the one in Figure~\ref{fig:schmixels_vs_harmonics}. 
+The inferred map looks significantly better than the one in Figure~\ref{fig:sphixels_vs_harmonics}. 
 With two occultation light curves the model is able to break the degeneracy in the location of the spot and thanks to the smoothing filter there is almost no visible ringing around the spot in the inferred map.

### 2020-10-10 paper/figures/pixels_vs_harmonics.py

@@ -400,8 +400,8 @@ fig.text(0.5, 0.05, "Occultor x-position [Io radii]", ha="center")
 ax_map[0].set_title(
     "Gaussian prior on $\mathrm{Y}_{lm}$\n coefficients", pad=20
 )
-ax_map[1].set_title("Positive Gaussian\n prior on schmixels", pad=20)
-ax_map[2].set_title("Exponential\n prior on schmixels", pad=20)
+ax_map[1].set_title("Positive Gaussian\n prior on sphixels", pad=20)
+ax_map[2].set_title("Exponential\n prior on sphixels", pad=20)
 
 #  Ticks
 for a in ax_lc:

### 2020-12-28 volcano/utils.py
Added method for plotting median maps in pixel space.

@@ -5,6 +5,10 @@ from astropy.timeseries import TimeSeries
 from astroquery.jplhorizons import Horizons
 from scipy.interpolate import interp1d
 
+import starry
+
+starry.config.lazy = False
+
 
 def get_body_ephemeris(
     times, body_id="501", step="1m", return_orientation=True
@@ -156,7 +160,7 @@ def get_body_ephemeris(
     epochs = {"start": start, "stop": end, "step": step}
     obj = Horizons(id=body_id, epochs=epochs, id_type="id")
 
-    eph = obj.ephemerides(quantities="1,13, 20", extra_precision=True)
+    eph = obj.ephemerides(quantities="1,13,20", extra_precision=True)
     times_jpl = Time(eph["datetime_jd"], format="jd")
 
     # Store all data in a TimeSeries object
@@ -527,19 +531,63 @@ def get_smoothing_filter(ydeg, sigma=0.1):
     filter controls the strength of the smoothing. Features on angular scales
     smaller than ~ 1/sigma are strongly suppressed.
 
-    Parameters
-    ----------
-    ydeg : int
-        Degree of the map.
-    sigma : float, optional
-        Standard deviation of the Gaussian filter, by default 0.1
+    Args:
+        ydeg (int): Degree of the map.
+        sigma (float, optional): Standard deviation of the Gaussian filter.
+            Defaults to 0.1.
 
-    Returns
-    -------
-    ndarray
-        Diagonal matrix of shape (ncoeff, ncoeff) where ncoeff = (l + 1)^2.
+    Returns:
+        ndarray: Diagonal matrix of shape (ncoeff, ncoeff) where ncoeff = (l + 1)^2.
     """
     l = np.concatenate([np.repeat(l, 2 * l + 1) for l in range(ydeg + 1)])
     s = np.exp(-0.5 * l * (l + 1) * sigma ** 2)
     S = np.diag(s)
     return S
+
+
+def get_median_map(
+    ydeg,
+    samples_ylm,
+    projection="Mollweide",
+    inc=90,
+    theta=0.0,
+    nsamples=15,
+    resol=300,
+):
+    """
+    Given a set of samples from a posterior distribution over the spherical
+    harmonic coefficients, the function computes a median map in pixel space.
+
+    Args:
+        ydeg (int): Degree of the map.
+        samples_ylm (list): List of (amplitude weighted) Ylm samples.
+        projection (str, optional): Map projection. Defaults to "Mollweide".
[…]

### 2020-12-28 paper/figures/irtf_ingress_egress_fit.py
Adding horseshoe prior for irtf fits. Added another pair of IRTF light curves from 2017.

@@ -1,0 +1,288 @@
+import numpy as np
+import pickle as pkl
+
+import starry
+import jax.numpy as jnp
+from jax import random, jit, vmap, lax
+import numpyro
+import numpyro.distributions as dist
+from numpyro.diagnostics import print_summary
+from numpyro.infer import *
+
+import celerite2.jax
+from celerite2.jax import terms as jax_terms
+from celerite2 import terms, GaussianProcess
+from exoplanet.distributions import estimate_inverse_gamma_parameters
+
+from astropy import units as u
+from astropy.table import Table
+from astropy.timeseries import TimeSeries
+
+from volcano.utils import *
+
+np.random.seed(42)
+starry.config.lazy = False
+numpyro.enable_x64()
+
+
+def fit_model(ydeg_inf, lc_in_numpy, lc_eg_numpy):
+    lc_in = TimeSeries(
+        time=Time(lc_in_numpy[:, 0], format="mjd"),
+        data=Table(
+            lc_in_numpy[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
+        ),
+    )
+    lc_eg = TimeSeries(
+        time=Time(lc_eg_numpy[:, 0], format="mjd"),
+        data=Table(
+            lc_eg_numpy[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
+        ),
+    )
+
+    # Compute ephemeris
+    eph_list_io = []
+    eph_list_jup = []
+
+    for lc in (lc_in, lc_eg):
+        times = lc.time
+
+        eph_io = get_body_ephemeris(
+            times, body_id="501", step="1m", return_orientation=True
+        )
+        eph_jup = get_body_ephemeris(
+            times, body_id="599", step="1m", return_orientation=True
+        )
+
+        eph_list_io.append(eph_io)
+        eph_list_jup.append(eph_jup)
+
+    eph_io_in = eph_list_io[0]
+    eph_jup_in = eph_list_jup[0]
+    eph_io_eg = eph_list_io[1]
+    eph_jup_eg = eph_list_jup[1]
+
+    t_in = (lc_in.time.mjd - lc_in.time.mjd[0]) * 24 * 60
+    t_eg = (lc_eg.time.mjd - lc_eg.time.mjd[0]) * 24 * 60
+
[…]

### 2020-12-28 paper/figures/irtf_ingress_egress_plots.py

@@ -1,0 +1,459 @@
+import numpy as np
+from matplotlib import pyplot as plt
+from PIL import Image
+import pickle as pkl
+
+import starry
+import celerite2.jax
+from celerite2.jax import terms as jax_terms
+from celerite2 import terms, GaussianProcess
+from exoplanet.distributions import estimate_inverse_gamma_parameters
+
+from astropy import units as u
+from astropy.table import Table
+from astropy.time import Time
+from astropy.timeseries import TimeSeries
+
+from matplotlib import colors
+import matplotlib.gridspec as gridspec
+from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+
+from volcano.utils import *
+
+np.random.seed(42)
+starry.config.lazy = False
+
+
+def get_pos_rot(eph_io, eph_jup, method=""):
+    # Get occultor position
+    obl = eph_io["obl"]
+    inc = np.mean(eph_jup["inc"])
+    theta = np.array(eph_io["theta"])
+
+    xo_unrot, yo_unrot, zo, ro = get_occultor_position_and_radius(
+        eph_io, eph_jup, occultor_is_jupiter=True, method=method
+    )
+
+    # Rotate to coordinate system where the obliquity of Io is 0
+    theta_rot = -obl.to(u.rad)
+    xo_rot, yo_rot = rotate_vectors(xo_unrot, yo_unrot, theta_rot)
+
+    return xo_rot, yo_rot, ro
+
+
+def make_plots(
+    lc_in_n,
+    lc_eg_n,
+    samples,
+    yticks,
+    ylim,
+    xticks_in,
+    xticks_eg,
+    res_yticks,
+    cmap_norm=colors.Normalize(vmin=0.0, vmax=1500),
+):
+    lc_in = TimeSeries(
+        time=Time(lc_in_n[:, 0], format="mjd"),
+        data=Table(
+            lc_in_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
+        ),
+    )
+    lc_eg = TimeSeries(
+        time=Time(lc_eg_n[:, 0], format="mjd"),
+        data=Table(
+            lc_eg_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
+        ),
+    )
+
+    #  Compute epheremis
+    eph_list_io = []
+    eph_list_jup = []
+
[…]

### 2020-12-28 paper/figures/simulated_ingress_egress.py

@@ -17,7 +17,7 @@ from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
 from volcano.utils import *
 
 np.random.seed(42)
-starry.config.lazy = True
+starry.config.lazy = False
 numpyro.enable_x64()
 
 xo_eg = np.linspace(37.15, 39.43, 150)
@@ -48,14 +48,14 @@ map_true.amp = 20
 # Smooth the true map
 sigma_s = 2 / ydeg_true
 S_true = get_smoothing_filter(ydeg_true, sigma_s)
-x = (map_true.amp * map_true.y).eval()
+x = map_true.amp * map_true.y
 xsmooth = (S_true @ x[:, None]).reshape(-1)
 map_true[:, :] = xsmooth / xsmooth[0]
 map_true.amp = xsmooth[0]
 
 # Generate mock ingress and egress light curves
-f_true_in = map_true.flux(ro=ro, xo=xo_in, yo=yo_in, theta=theta_in).eval()
-f_true_eg = map_true.flux(ro=ro, xo=xo_eg, yo=yo_eg, theta=theta_eg).eval()
+f_true_in = map_true.flux(ro=ro, xo=xo_in, yo=yo_in, theta=theta_in)
+f_true_eg = map_true.flux(ro=ro, xo=xo_eg, yo=yo_eg, theta=theta_eg)
 
 # S/N = 50
 f_err_in_50 = np.max(np.concatenate([f_true_in, f_true_eg])) / 50
@@ -88,21 +88,13 @@ yo_eg_dense = np.linspace(yo_eg[0], yo_eg[-1], 200)
 
 # Compute design matrix
 map = starry.Map(ydeg_inf)
-A_in = jnp.array(
-    map.design_matrix(xo=xo_in, yo=yo_in, ro=ro, theta=theta_in).eval()
-)
-A_eg = jnp.array(
-    map.design_matrix(xo=xo_eg, yo=yo_eg, ro=ro, theta=theta_eg).eval()
-)
+A_in = jnp.array(map.design_matrix(xo=xo_in, yo=yo_in, ro=ro, theta=theta_in))
+A_eg = jnp.array(map.design_matrix(xo=xo_eg, yo=yo_eg, ro=ro, theta=theta_eg))
 A_in_dense = jnp.array(
-    map.design_matrix(
-        xo=xo_in_dense, yo=yo_in_dense, ro=ro, theta=theta_in
-    ).eval()
[…]

### 2020-12-28 paper/figures/sphixels_to_pixels.py

@@ -195,9 +195,9 @@ for a in (ax[1, 0], ax[1, 2]):
 
 ax[1, 1].axis("off")
 
-ax[0, 0].set_title("Schmixels\n(draw from prior)")
+ax[0, 0].set_title("Sphixels\n(draw from prior)")
 ax[0, 1].set_title("Spherical\nharmonics")
 ax[0, 2].set_title("Pixels")
 
 # Save
-fig.savefig("schmixels_to_pixels.pdf", bbox_inches="tight", dpi=500)
+fig.savefig("sphixels_to_pixels.pdf", bbox_inches="tight", dpi=500)

### 2020-12-28 paper/figures/irtf_ingress_egress.py
deleting unnecessary files

@@ -1,412 +1,0 @@
-import numpy as np
-from matplotlib import pyplot as plt
-from PIL import Image
-
-import theano
-import theano.tensor as tt
-import pymc3 as pm
-import starry
-import exoplanet as xo
-from astropy import units as u
-from astropy.table import Table
-from astropy.timeseries import TimeSeries
-
-from matplotlib import colors
-import matplotlib.gridspec as gridspec
-from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
-
-from volcano.utils import *
-
-np.random.seed(42)
-starry.config.lazy = True
-
-# Load light curves
-lc_in_n = np.load("irtf_ingress.npy")
-lc_eg_n = np.load("irtf_egress.npy")
-
-lc_in = TimeSeries(
-    time=Time(lc_in_n[:, 0], format="mjd"),
-    data=Table(
-        lc_in_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
-    ),
-)
-lc_eg = TimeSeries(
-    time=Time(lc_eg_n[:, 0], format="mjd"),
-    data=Table(
-        lc_eg_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
-    ),
-)
-
-# Compute ephemeris
-eph_list_io = []
-eph_list_jup = []
-
-for lc in (lc_in, lc_eg):
-    times = lc.time
-
-    eph_io = get_body_ephemeris(
-        times, body_id="501", step="1m", return_orientation=True
-    )
-    eph_jup = get_body_ephemeris(
-        times, body_id="599", step="1m", return_orientation=True
-    )
-
-    eph_list_io.append(eph_io)
-    eph_list_jup.append(eph_jup)
-
-eph_io_in = eph_list_io[0]
-eph_jup_in = eph_list_jup[0]
-eph_io_eg = eph_list_io[1]
-eph_jup_eg = eph_list_jup[1]
-
-t_in = (lc_in.time.mjd - lc_in.time.mjd[0]) * 24 * 60
-t_eg = (lc_eg.time.mjd - lc_eg.time.mjd[0]) * 24 * 60
-
-f_obs_in = lc_in["flux"].value
-f_err_in = lc_in["flux_err"].value
[…]

### 2020-12-28 paper/paper.tex
Reformatting the paper with the split into paper 1/2 in mind.

@@
 % Title
-%\title{Inferring a time dependent map of Io's surface from occultations and phase curves.}
-\title{Time-variable surface mapping of exoplanets: an application to Io}
+\title{Occultation mapping of Io's surface in the near-infrared I: Inferring static maps}
 
@@
 Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
-Existing photometric observations in the near infrared taken during occultations by Jupiter and Galilean moons encode a wealth of information about its surface.
-Io is thus an ideal testbed for models of time-variable exoplanet surfaces.
-We built a generative model of Io's surface for each observation using Nonnegative Matrix Factorization.
-The model is built on top of the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic computation of occultation light curves, phase curves in both emitted and reflected light and exact gradients with respect to all input parameters.
-We use the inferred map to study the time variability of prominent volcanoes over a timescale of decades.
-While we mostly focus on Io, our models are directly applicable to mapping exoplanets.
-We discuss this application towards the end of the paper.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
-
+Existing photometric observations in the near infrared taken during occultations by Jupiter and other Galilean moons encode a wealth of information about its surface.
+These data are ideal for testing methods for inferring surface features of occulted bodies from time series observations.
+We built a generative model of Io's surface using the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic and differentiable computation of occultation light curves in emitted and reflected light.
+    Our (fully Bayesian) model is able to recover known bright features on the surface of Io with only two light curves and without any assumptions on where the features are located or how many there are.
+    This work is a first step towards constructing a model for time-variable surface features. 
+    Although we do not present new findings about Io in this work, the methods we have developed are directly applicable to the problem of mapping stars and exoplanets.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 \section{Introduction}
-%% ADD PARAGRAPH REVIEWING PREVIOUS LITERATURE ON MAPPING EXOPLANETS, MENTION JWST AND LUVOIR
-%% MAYBE EVEN IN THE ABSTRACT
-The surface of Jupiter's moon Io is littered with hundreds of volcanoes appearing as bright spots in the near infrared and varying in intensity on timescales of days to decades.
-The volcanic activity is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale_melting_1979}.
-Io is a perfect analogue of an extremely volcanically active exoplanet.
-Such rocky exoplanets, often dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because the photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future \citep{kaltenegger_detecting_2010,henning_highly_2018,oza_sodium_2019}.
-Studying volcanism on both Io and exoplanets is scientifically valuable because it provides a window into the properties of early Earth and it informs theories of planet formation.
+The surface of Jupiter's moon Io is littered with hundreds of volcanoes which appear as bright spots in the near infrared and in intensity on timescales ranging from days to decades.
+The volcanic activity is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
+Because of its extreme volcanic activity, Io is in many ways an analogue of a volcanically active exoplanet.
+Volcanic exoplanets, often dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019}.
+Studying extreme volcanism on both Io and exoplanets is scientifically valuable because it provides a window into the properties of the early Earth and it informs theories of planet formation.
 
-Existing exoplanet detections with potential volcanism include CoRoT-7b \citep{barnes_corot-7b_2010}, the first discovered rocky exoplanet with likely significant tidal heating; 55 Cancri e, whose longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory_variability_2016,demory_map_2016,hammond_linking_2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova_magma_2017,dobos_tidal_2019}; and many others.
+Existing exoplanet detections with potential volcanism include CoRoT-7b \citep{barnes2010}, the first rock exoplanet to have been discovered and one which likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016a,hammond2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019} and many others.
 Not all exoplanets will have Io-like volcanism, some will have magma oceans due to their proximity to the star or volcanism caused by nuclear decay similar to early Earth volcanism.
@@
 Io has been observed extensively using both space and ground observatories.
-High resolution images of Io's surface were taken by space missions such as Voyager \citep{smith_jupiter_1979}, Galileo \citep{belton_galileos_1996} and Juno \citep{mura_infrared_2020}.
+High resolution images of Io's surface were taken by space missions such as Voyager \citep{smith1979}, Galileo \citep{belton1996} and Juno \citep{mura2020}.
 It has also been resolved from the ground in the near infrared using disk resolved imaging
-\citep{howell_infrared_1985,simonelli_disk-resolved_1986,spencer_discovery_1990} and adaptive optics observations \citep{marchis_adaptive_2000,marchis_keck_2005,de_kleer_spatial_2016}.
-Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter starting with \cite{spencer_discovery_1990}.
+\citep{howell1985,simonelli1986,spencer1990} and adaptive optics observations \citep{marchis2000,marchis2005,dekleer2016}.
+Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter starting with \cite{spencer1990}.
 Occultations by Jupiter occur twice every orbit lasting ~1.7 days and mutual occultations with Europa, Ganymede or Callisto happen every ~6 years when Earth pasess through the orbital plane of Galilean satellites.
 The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow ("in eclipse") while mutual occultations are almost always observed in sunlight because mutual occultations while Io is in eclipse are extraordinarily rare.
-Only the brightest volcanoes are visible over the reflected light background when Io is illuminated by the Sun\citep{veeder_ios_1994,de_kleer_spatial_2016}.
+Only the brightest volcanoes are visible over the reflected light background when Io is illuminated by the Sun\citep{veeder1994,dekleer2016a}.
 
 Both kinds of occultations have been used to study volcanic activity on the surface.
-\cite{spencer_io_1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
-\cite{rathbun_loki_2002, rathbun_loki_2006,rathbun_ground-based_2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots finding evidence of periodicity in Loki's eruptions and established the transient nature of the volcanoes (only Loki is persistently active).
-By studying an occultation of Io by Europa, \cite{de_kleer_multi-phase_2017} mapped the Loki region to a precision of about 2 kilometers.
-In addition to observations of occultations in near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot_mutual_1974,saquet_phemu15_2018,morgado_astrometry_2016} with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
+\cite{spencer1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
+\cite{rathbun2002, rathbun2006,rathbun2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots finding evidence of periodicity in Loki's eruptions and established the transient nature of the volcanoes (only Loki is persistently active).
+By studying an occultation of Io by Europa, \cite{dekleer2017} mapped the Loki region to a precision of about 2 kilometers.
+In addition to observations of occultations in near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot1974,saquet2018,morgado2016a} for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
 
@@
 Strong priors on the locations of individual volcanoes are assumed based on maps from space mission observations.
-In this work, we build a fully probabilistic model in order to infer a time-dependent two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infra red.
-The model is built on top of the recently developed code starry \citep[][Luger et al. 2020 in prep]{luger_starry_2019} which
-enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
-starry can compute phase curves and occultations in both emitted light (for modeling the isotropic volcanic emission from Io's surface) and reflected light (for mapping albedo variations).
-Instead of fitting one map per occultation light curve, we reduce the dimensionality of the problem using matrix factorization, assuming a fixed map for a given light curve which is a linear combination of $K$ basis maps.
-We use priors on the map features which ensure the maps are physical and prevent overfitting of the data.
-The model is interpretable, each of the basis maps roughly corresponds to a single spot on the surface, and the coefficients multiplying the basis maps encode information on the time variability.
+In this work, we build a fully probabilistic model in order to infer a two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infra red.
+We assume that the map generating a given set of light curves is static (up to an overall amplitude) so we are restricted to modeling the surface during a timespan when the surface emission hasn't changed drastically.
+In a subsequent paper we build on the model we have developed here and generalize to a case where the surface is time-variable.
 
-Our goals for this paper are to both improve on past studies of Io using occultation light curves and to construct a flexible model directly applicable to future efforts on inferring time-dependent maps of variable features on exoplanet surfaces such as volcanoes, magma oceans or clouds.
-The fact that we have lots of prior information on what the surface of Io should look like enables us to test our model in a realistic setting, testing sensitivity to chosen priors, data quality, the orbital parameters and different kinds of surface features.
+The model is built on top of the recently developed code starry \citep[][Luger et al.
+2020 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
+Starry can compute phase curves and occultations in both emitted light (for modeling the isotropic thermal emission from Io's surface) and reflected light (for mapping albedo variations).
+It is many orders of magnitude faster and more accurate than pixel based codes and it computes exact gradients with respect to all parameters through automatic differentiation.
+Starry also comes with extensive tools for visualizing spherical harmonic maps and simulating data.
+
+Our goal for this paper is to develop a general model for mapping surfaces of occulted bodies with sparse high contrast features and to test it on a real world dataset. 
+Because we have lots of prior information on what the surface of Io should look like, we can compare our inferences to known features on its surface and we can test the sensitivity of the inferred maps to different choices of priors and noise models.
+The work should also be of interest to the Io research community as it presents a very different approach to modeling Io occultations without having to make strong assumptions on the locations of the hot spots.
 
@@
 In \S\ref{sec:data} we describe the IRTF light curves of occultations by Jupiter which we use to infer maps.
-In \S\ref{sec:model} we discuss the generative model for the data for the case of a static map, and a dynamic map modeled using a matrix factorization approach and we write down the relevant likelihood functions.
+In \S\ref{sec:model} we discuss the generative model for the data and we write down the relevant likelihood functions.
 In \S\ref{sec:inverse_problem} we focus on the question of how to do Bayesian inference given the forward model specifications defined in \S\ref{sec:model}.
-We discuss and test different priors on map features, the information content of light curves and fitting the models using variational inference (VI) methods and Hamiltonian Monte Carlo (HMC).
-We present results on simulated data.
-\S\ref{sec:results} shows the results on real data.
+We discuss and test different priors on map features, the information content of light curves and fitting the modelsusing Hamiltonian Monte Carlo (HMC). 
+We show results on simulated data.
+\S\ref{sec:results} shows the results on real IRTF data for two pairs of light curves (closely spaced in time)
 In particular, the inferred dynamic map, the  different component maps and accompanying coefficients, the uncertainties of the maps, sensitivity to different choices of priors, comparison of inferred locations and intensities of spots to known values from the literature.
@@
 To model the occultations we need to know the projected separation between Jupiter and Io and the orientation of Io at any given time.
-We use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner_planetary_2014} which are accurate to a few kilometers on Io's surface.
+We use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner2014} which are accurate to a few kilometers on Io's surface.
 Specifically, we use the Right Ascension and Declination, the angular (equatorial) diameter (\textsf{Ang-diam}), the visibility flag indicating whether Io is occulted or not and whether it is in partial or total eclipse (\textsf{Ang-sep/v}), the longitude and latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}), the sub-solar point longitude and latitude which specify the direction pointing towards the Sun on Io's surface (\textsf{Sl-lon}, \textsf{Sl-lat}), the distance from Io to the Sun (\textsf{r}) and
@@
 
-\subsection{Nonnegative Matrix Factorization}
-\label{ssec:nmf}
-In the case when we cannot assume a static map, the situation is considerably more complicated.
-In principle, the surface map is different for each \emph{data point}.
-Of course, fitting one map per data point is intractable so we might instead fit a single map per light curve, generated by Eq.~\ref{eq:linear_model_pix}.
-Even then, we would need to fit on the order of 1k parameters!
-This is both becuse the number of spherical coefficients scales as $(l+1)^2$ and because when fitting in pixel space we need many more pixels than spherical harmonics to ensure positivity.
-Although fitting a model of such high dimensionality for a single IRTF light curve of high signal to noise ratio is tractable thanks to exact gradients provided by autodifferentiation in \textsf{starry}, we don't want to do that for a hundred or so separate light curves.
-Such a model would be very difficult to fit and it would require strong regularization between successive maps in time.
-It also wouldn't directly provide much physical insight into the volcanic activity, we would have to conduct a separate analysis on the inferred maps to constrain the time variability of the volcanoes.
-Instead, we need an approach which reduces the dimensionality of the problem.
-One way of accomplishing that is to expand the spherical harmonic coefficients (or pixels) in a Taylor series in time about a certain point.
-This is the approach \cite{luger_tess_2019} took to model a map of Earth's albedo in reflected light from stray Earthshine in the aperture of the TESS space telescope.
-This issue with this approach and similar series expansions such as the Fourier series is that with the very long baseline of IRTF data and the observations being scattered throughout the years sporadically, it is unclear which point should be the origin of the expansion.
-More importantly, there likely doesn't exist a well defined global time-averaged map of Io so requiring too much smoothness between successive maps wouldn't work.
-Another way of reducing the dimensionality of the problem would be a parametric approach where where we place a few spots on the sphere and then fit only for the locations and intensities of each spot.
-This is assuming that we know a priori that the surface features are spot like and roughly how many we should expect.
-While such a strong assumption might work for studying individual spots in the context of Io, it certainly isn't justified for exoplanets.
-In Section~\ref{sec:inverse_problem} we do assume stronger priors on the locations of and shapes of surface features to better constrain the variability of individual volcanoes, but we still fit for pixels, at least in principle allowing the data to override our assumptions.
-
-The approach approach opted for is to treat the problem of inferring a single map per light curve as a probabilistic matrix factorization problem.
-The idea is to assume that a map for any given light curve can be expressed as a linear combination of $K$ "basis maps".
-Consider $L$ lightcurves, the model for the $l$-th light curve is
-\begin{equation}
-    \mathbf{f}_l=\mathbf{A}_l\,\mathbf{P}^\dagger\,\mathbf{p}_l'
-\end{equation}
-We can stack the column vectors $\mathbf{p}_l$ into a matrix $\mathbf{Y}$ of shape $(N_p, L)$ where $N_p$ is the number of pixels for each light curve.
-We then assume that the $\mathbf{Y}$ can be decomposed into a product of two matrices $\mathbf{B}$ and $\mathbf{Q}$ as
-\begin{equation}
-    \mathbb{Y}=\mathbf{B}\,\mathbf{Q}
-    \label{eq:nmf}
-\end{equation}
-where $\mathbf{B}$ has shape $(N_p, K)$ and $\mathbf{Q}$ has shape $(K, L)$.
-The model for all light curves can be written as
-\begin{equation}
-    \mathbb{f}=\mathbb{A}\,\mathrm{vec}(\mathbf{\mathbb{Y}})
-    \label{eq:model_all_lcs}
-\end{equation}
-Where $\mathbf{f}$ is a tall column vector consisting of predictions for all light curves stacked together, $\mathbb{A}$ is a block diagonal matrix with matrices $\mathbf{A}_l\,\mathbf{P}^\dagger$ on the diagonal for $l=1\dots, L$ and the $\mathrm{vec}$ operator stacks the columns of $\mathbb{Y}$ into a tall vector.
-The model is \emph{bilinear} which means that is linear in the matrices $\mathbf{B}$ and $\mathbf{Q}$ separately.
-The interpretation of Equation~\ref{eq:nmf} is simple, each of the $K$ columns of $\mathbf{B}$ represents pixels of a basis map and the columns of $\mathbf{Q}$ determine how those maps add together to produce a final map for the $l$-th light curve.
-For this reason we call $\mathbf{B}$ the \emph{basis matrix} and the matrix $\mathbf{Q}$ the \emph{encoding matrix}.
-Ideally, we want the basis maps to be physically meaningful and the coefficients encode the time variability.
-A nice feature of this model is that there is no requirement that successive maps are smoothly varying between different light curves.
-
-The matrix factorization problem as written in Equation~\ref{eq:nmf} is highly degenerate and practically intractable a probabilistic framework with a small dataset.
-Since each of the columns of $\mathbf{B}$ are pixels representing emitted light or albedo, we can substantially reduce the ambiguity in the decomposition by requiring that both matrices are strictly positive.
-This matrix factorization problem is known as \emph{Nonnegative Matrix Factorization} (NMF) \citep{paatero_positive_1994,lee_algorithms_2001} and it has a rich history across many different fields.
-It is commonly used for decomposing physical signals in the spectral or the time domain.
-Even though NMF is more tractable than unconstrained matrix factorization, it is still an NP hard problem \citep{vavasis_complexity_2009} and it requires additional constraints or priors to be tractable.
-Simultaneously transforming $\mathbf{B}\leftarrow \mathbf{B}\,\mathbf{S}^{-1}$ and
-$\mathbf{Q}\leftarrow \,\mathbf{S}\mathbf{Q}$ with a nonsingular matrix $\mathbf{S}$ doesn't change the value of the objective function.
-The objective function is also invariant to a simultaneous permutation of the columns of $\mathbf{B}$ and rows of $\mathbf{Q}$ and rescaling either of the two matrices by a scalar.
-Nevertheless, getting around these degeneracies in practice is possible, especially when we have a lot of prior knowledge on the problem.
-For a recent review article with a detalied analysis of these degeneracies and common algorithms, see \cite{fu_nonnegative_2019}.
-
-Broadly, there are two approaches to fitting NMF models, the constrained optimization approach and the probabilistic approach.
-In the optimization approach we optimize $\mathbb{Y}$ in a least-squares sense under a set of constraints on either one or both of the matrices \citep[see][for recent examples from the astronomical literature]{acosta-pulido_new_2017, melchior_scarlet_2018,ren_non-negative_2018,ren_using_2020} with the goal of obtaining a point estimate for the two matrices.
-The probabilistic approach introduces priors and the inference is usually done with variational inference in order to obtain an approximate posterior distribution over the matrices.
-In this work we opt for the probabilistic approach because we care about the uncertainties on the map features a lot.
-
-One difference between most applications of NMF in the literature and NMF within the context of inferring surface maps from 1D light curves is that
-in the majority of the work in the literature \citep[except][]{kawahara_global_2020} the matrix $\mathbb{Y}$ is assumed to be directly observed  up to a simple noise term.
-In our case the problem is considerably more challenging because we observe the light curves
-$\mathbb{A}\,\mathrm{vec}(\mathbf{\mathbb{Y}})$ instead of $\mathbb{Y}$ directly, a process in which some information is lost because, depending on the geometry of the occultations, certain combinations of spherical harmonic coefficients will be in the nullspace.
-\cite{kawahara_global_2020} are using NMF to model phase variations in directly imaged exoplanets with the goal of simultaneously inferring a surface map and a spectral decomposition of the map into several components, a case in which the
-matrix which is to be decomposed is also unobserved.
-Although we don't attempt to solve the problem of spectrally decomposing the maps, our approach is directly applicable to that problem as well. (TODO: should I add more details here?)
-One could also imagine inferring a multi spectral component and time dependent map by solving two NMF problems simultaneously.
-We leave this application for future work.
-
 \subsection{The likelihood}
@@
 where $\mathbb{f}_\mathrm{obs}$ is the vector of stacked observed light curves, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbb{b}$ is a fixed flux offset per light curve accounting for stray flux not attributed to Io (mostly due to Jupiter).
-We model the data covariance with a Gaussian Process using the fast Celerite method\citep{foreman-mackey_fast_2017} as implemented in the \textsf{exoplanet} package (TODO: cite) to capute correlations imposed by the seeing plus an additional white noise term which is different for each light curve.
+We model the data covariance with a Gaussian Process using the fast Celerite method\citep{foreman-mackey2017} as implemented in the \textsf{exoplanet} package (TODO: cite) to capute correlations imposed by the seeing plus an additional white noise term which is different for each light curve.
 The IRTF data isn't provided with any uncertainties so we estimate the uncertainties by filtering the data with the Savitzky Golay filter as implemented in \textsf{SciPy} (TODO: CITE) and estimating the variance of the residuals.
@@
 Observing phase curves and occultations in reflected light improves the model even more because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
-2020 in prep]{luger_starry_2019}.
+2020 in prep]{luger2019a}.
 In some cases for reflected light observations (phase curves of an inclined planet for example) there is no nullspace at all at low degrees of the map.
@@
     \oscaption{InformationContent}{
-        The plot shows the information content of different kinds of observations of Io as a function of spherical harmonic degree (angular scale of surface features).
+        The information content of different kinds of observations of Io as a function of spherical harmonic degree (angular scale of surface features).
         On the y axis is posterior shrinkage (the variance ratio between the prior and the posterior distribution) for each spherical harmonic coefficient at a given degree $l$ on the x axis, averaged across all $m$ modes.
@@
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/ingress_egress_simulated.pdf}
-    \oscaption{ingress_egress_simulated}{%
+    \includegraphics[width=1.\linewidth]{figures/ingress_egress_sim_snr_50.pdf}
+    \oscaption{ingress_egress_sim_snr_50}{%
 Maximum A Posteriori (MAP) estimate of an $l=25$ map (right) produced by fitting a pair of simulated ingress and egress occultation light curves (bottom) which were generated from a $l=25$ map consisting of a single bright spot (left).
@@
         The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:sphixels_vs_harmonics}.
-        \label{fig:ingress_egress_simulated}
+        \label{fig:ingress_egress_sim_snr_50}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=1.\linewidth]{figures/ingress_egress_sim_snr_10.pdf}
+    \oscaption{ingress_egress_sim_snr_10}{%
+Maximum A Posteriori (MAP) estimate of an $l=25$ map (right) produced by fitting a pair of simulated ingress and egress occultation light curves (bottom) which were generated from a $l=25$ map consisting of a single bright spot (left).
+       A Gaussian smoothing filter is applied to reduce the ringing artefacts.
+       Small circles beneath each inferred map show the progression of the occultation.
+        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:sphixels_vs_harmonics}.
+        \label{fig:ingress_egress_sim_snr_10}
     }
@@
 Some residuals in the data are still present (WHY).
-In the next section, we fit a pair of light curves from the IRTF dataset described in Section~\ref{sec:data}.
 
-\subsection{Fitting IRTF ingress/egress light curves}
+\section{Results}
+\label{sec:results}
 
@@
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress.pdf}
-    \oscaption{irtf_ingress_egress}{%
+    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress_1998.pdf}
+    \oscaption{irtf_ingress_egress_1998}{%
         Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
@@
         The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
-        \label{fig:irtf_ingress_egress}
+        \label{fig:irtf_ingress_egress_1998}
     }
@@
     \begin{centering}
-    \includegraphics[width=.5\linewidth]{figures/irtf_ingress_egress_loki.pdf}
+    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress_2017.pdf}
+    \oscaption{irtf_ingress_egress_2017}{%
+        Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
+       The small circles beneath each inferred map show the progression of the occultation.
+        Both light curves are assumed to be generated from the same map except for a difference in the overall amplitude.
+        We allow for multiplicative rescaling of the error bars and an additive flux offset for each light curve.
+        The model places a single bright spot to explain most of the variance in the data.
+        The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
+        \label{fig:irtf_ingress_egress_2017}
+    }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=.5\linewidth]{figures/irtf_spot_overlay_1998.pdf}
     \oscaption{irtf_ingress_egress_loki}{%
@@
 
-\subsection{Fitting a dynamic map}
-\label{ssec:dynamic_map}
-% Priors for NMF. Optimization vs. bayesian approach to NMF. Results on simulated data. Comparison of results to matrix factorization without the positivity constraint and clever priors.
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Individual events}
-\label{ssec:individual}
-% Fits of individual events. In particular, those light curves that were analyzed in previous papers.
-
-\subsection{The time-variable map}
-\label{ssec:time_variable_map}
-%
-
-\subsection{Variability of known hotspots}
-\label{ssec:variability_hotspots}
-% Plot inferred intensities of known hotspots as function of time, reference previous work.
-
-\section{Mapping volcanic exoplanets}
-\label{sec:exoplanets}
-% Application to exoplanets. Fitting mock JWST observations.
-
 \section{Conclusions}
@@
 \bibliography{bib}
+
 \end{document}

### 2020-12-28 paper/figures/irtf_ingress_egress_plots.py
fixing wrong file names

@@ -409,8 +409,8 @@ def make_plots(
     fig.savefig(f"irtf_spot_overlay_{year}.pdf", bbox_inches="tight", dpi=500)
 
 # Plots for the the 1998 pair of light curves
-lc_in_numpy = np.load("irtf_ingress.npy")
-lc_eg_numpy = np.load("irtf_egress.npy")
+lc_in_numpy = np.load("irtf_1998_ingress.npy")
+lc_eg_numpy = np.load("irtf_1998_egress.npy")
 
 yticks = np.arange(0, 60, 10)
 ylim = (-2, 52)
@@ -434,8 +434,8 @@ make_plots(
 )
 
 # Plots for the 2017 pair of light curves
-lc_in_numpy2 = np.load("irtf_ingress2.npy")
-lc_eg_numpy2 = np.load("irtf_egress2.npy")
+lc_in_numpy2 = np.load("irtf_2017_ingress.npy")
+lc_eg_numpy2 = np.load("irtf_2017_egress.npy")
 
 with open("irtf_2017_samples.pkl", "rb") as handle:
     samples2 = pkl.load(handle)

### 2020-12-29 data/process_irtf_lightcurves.py
added script which processes the raw data

@@ -1,0 +1,134 @@
+import numpy as np
+import os
+import xml.etree.ElementTree as ET
+import sys
+import pickle as pkl
+
+from astropy import units as u
+from astropy.time import Time
+from astropy.timeseries import TimeSeries
+from astropy.table import vstack
+from astropy.table import Table
+from astropy.stats import sigma_clip, mad_std
+
+from scipy.signal import savgol_filter
+
+np.random.seed(42)
+
+
+def get_data_from_xml(path):
+    tree = ET.parse(path)
+    root = tree.getroot()
+
+    namespaces = {"pds": "http://pds.nasa.gov/pds4/pds/v1"}
+
+    description = root.findall(".//pds:description", namespaces=namespaces)[
+        0
+    ].text
+    start_date = root.findall(".//pds:start_date_time", namespaces=namespaces)[
+        0
+    ].text
+    end_date = root.findall(".//pds:stop_date_time", namespaces=namespaces)[
+        0
+    ].text
+    instrument = root.findall(
+        ".//pds:Observing_System_Component", namespaces=namespaces
+    )[0][0].text
+    facility = root.findall(
+        ".//pds:Observing_System_Component", namespaces=namespaces
+    )[1][0].text
+
+    dic = {
+        "description": description,
+        "start_date": start_date,
+        "end_date": end_date,
+        "instrument": instrument,
+        "facility": facility,
+    }
+    return dic
+
+
+directory = "irtf_raw"
+
+lcs = []
+i = 0
+for filename in os.listdir(directory):
+    if filename.endswith(".xml"):
+        metadata = get_data_from_xml(os.path.join(directory, filename))
+        data = np.genfromtxt(
+            os.path.join(directory, filename[:-4] + "tab.txt")
+        )
+
+        # Remove the zeros at the beginning of some files
+        mask = data[:, 0] == 0
+        data = data[~mask]
+
+        start_time = Time(
+            metadata["start_date"][:-1], format="isot", scale="utc"
+        ).to_value("mjd", "long")
+        times = start_time + data[:, 0] / 24.0
+        times = Time(times, format="mjd")
+
+        # Convert to astropy.TimeSeries
+        ts = TimeSeries(time=times)
+        ts["flux"] = data[:, 2] * u.GW / u.um / u.sr
[…]

### 2020-12-30 paper/figures/irtf_ingress_egress_fit.py
minor

@@ -25,20 +25,7 @@ starry.config.lazy = False
 numpyro.enable_x64()
 
 
-def fit_model(ydeg_inf, lc_in_numpy, lc_eg_numpy):
-    lc_in = TimeSeries(
-        time=Time(lc_in_numpy[:, 0], format="mjd"),
-        data=Table(
-            lc_in_numpy[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
-        ),
-    )
-    lc_eg = TimeSeries(
-        time=Time(lc_eg_numpy[:, 0], format="mjd"),
-        data=Table(
-            lc_eg_numpy[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
-        ),
-    )
-
+def fit_model(ydeg_inf, lc_in, lc_eg):
     # Compute ephemeris
     eph_list_io = []
     eph_list_jup = []
@@ -213,7 +200,7 @@ def fit_model(ydeg_inf, lc_in_numpy, lc_eg_numpy):
         numpyro.deterministic("flux_eg_dense", flux_eg_dense)
 
         # Rescale errorbars
-        ln_K = numpyro.sample("ln_K", dist.HalfNormal(0.1).expand([2]))
+        ln_K = numpyro.sample("ln_K", dist.HalfNormal(0.05).expand([2]))
 
         # GP likelihood
         params = estimate_inverse_gamma_parameters(0.001, t_eg[-1])
@@ -250,7 +237,7 @@ def fit_model(ydeg_inf, lc_in_numpy, lc_eg_numpy):
         "tau_raw": 0.1,
         "c2_raw": 5 ** 2,
         "ln_flux_offset": -2 * np.ones(2),
-        "ln_K": 0.001 * np.ones(2),
+        "ln_K": 1e-05 * np.ones(2),
         "sigma_gp": 0.001 * np.ones(2) * f_err_in[0],
         "rho_gp": 0.15 * np.ones(2),
     }
@@ -270,19 +257,25 @@ def fit_model(ydeg_inf, lc_in_numpy, lc_eg_numpy):
 
 
 # Fit the 1998 pair of light curves
-lc_in_numpy = np.load("irtf_1998_ingress.npy")
-lc_eg_numpy = np.load("irtf_1998_egress.npy")
+with open("../../data/irtf_processed/lc_1998-08-27.pkl", "rb") as handle:
+    lc_in = pkl.load(handle)
 
[…]

### 2020-12-30 paper/figures/irtf_ingress_egress_plots.py

@@ -42,8 +42,8 @@ def get_pos_rot(eph_io, eph_jup, method=""):
 
 
 def make_plots(
-    lc_in_n,
-    lc_eg_n,
+    lc_in,
+    lc_eg,
     samples,
     yticks,
     ylim,
@@ -52,19 +52,6 @@ def make_plots(
     res_yticks,
     cmap_norm=colors.Normalize(vmin=0.0, vmax=1500),
 ):
-    lc_in = TimeSeries(
-        time=Time(lc_in_n[:, 0], format="mjd"),
-        data=Table(
-            lc_in_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
-        ),
-    )
-    lc_eg = TimeSeries(
-        time=Time(lc_eg_n[:, 0], format="mjd"),
-        data=Table(
-            lc_eg_n[:, 1:] * u.GW / u.um / u.sr, names=["flux", "flux_err"]
-        ),
-    )
-
     #  Compute epheremis
     eph_list_io = []
     eph_list_jup = []
@@ -380,7 +367,9 @@ def make_plots(
     ax_res[0].set_ylabel("Residuals\n (norm.)")
 
     year = lc_in.time[0].isot[:4]
-    fig.savefig(f"irtf_ingress_egress_{year}.pdf", bbox_inches="tight", dpi=500)
+    fig.savefig(
+        f"irtf_ingress_egress_{year}.pdf", bbox_inches="tight", dpi=500
+    )
 
     # Plot inferred hot spot on top of Galileo maps
     combined_mosaic = Image.open("Io_SSI_VGR_bw_Equi_Clon180_8bit.tif")
@@ -390,16 +379,17 @@ def make_plots(
 
     median_map_rect_in, std_map_rect_in = get_median_map(
         ydeg_inf, samples["x_in"], projection="Rectangular"
-
     )
     fig, ax = plt.subplots(figsize=(8, 4))
     map.show(
-        image=median_map_rect_in, projection="rectangular",  ax=ax, colorbar=False,
-
+        image=median_map_rect_in,
+        projection="rectangular",
+        ax=ax,
+        colorbar=False,
     )
-    ax.imshow(galileo_map, extent=(-180, 180, -90, 90), alpha=0.7, cmap='gray')
-    ax.set_yticks(np.arange(-15, 60, 15));
[…]

### 2021-01-02 paper/paper.tex
writing...

@@
     \oscaption{irtf_dataset}{%
-        Maximum flux for each curve taken using NASA's IRTF telescope during an
-        occultation of Io by Jupiter.
+        Maximum flux for each IRTF light curve of Io observed during an occultation of Io by Jupiter.
        \label{fig:irtf_max_flux}
@@
 
-The dataset we use to infer maps of Io's surface consists of 112 observations of Io in the near infrared taken from 1996 until 2018 using various instruments at NASA's IRTF observatory.
-Figure~\ref{fig:irtf_max_flux} shows the maximum flux in $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ for each light curve plotted as a function of time which approximately corresponds to the disc integrated flux of Io at the beginning of ingress or the end of egress prior to it being occulted by Jupiter.
-Two features of this plot are apparent.
-First although the observations span decades the cadence is non-uniform with only a few observations taken between 2008 and 2016.
-Second, the baseline brightness is varying stochastically by a large amount and there are several notable events of increased volcanic activity.
+The dataset we use to infer maps of Io's surface consists of 112 observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994} (TODO: WHICH FILTERS), the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} (TODO: DETAILS) and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{johnrayner2016}.
+Although the observations span decades, the cadence is non-uniform, there are only a few observations taken between 2008 and 2016.
 All of the observations were taken while Io was \emph{in eclipse}, meaning that it was in Jupiter's shadow and all of the observed emission from the surface is due to thermal radiation.
 Observations of Io \emph{in sunlight} on the other hand probe both the thermal (volcanic) emission and the surface albedo variations in the near infrared.
+Figure~\ref{fig:irtf_max_flux} shows the maximum flux in units of $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ (TODO: UNDERSTAND THESE UNITS) for each light curve plotted as a function of time.
+This value is approximately equal to the total flux emitted from the Jupiter facing side of Io.
+The baseline brightness is varying stochastically by a large amount and there are several notable events of intense volcanic activity.
 
@@
 in the dataset.
-All occultations last for $\sim4$ min and the cadence for each light varies but it on the order of a second.
-It follows that over the course of a single exposure Jupiter's limb move by about 15km which provides a lower bound for the size of the features on the surface that we can reliably estimate.
-The shapes of light curves strongly deviate from the smooth variability one would expect assuming a homogeneous distribution of thermal emission on the surface.
-Especially prominent are light curves with clear step-like features which are present when bright spots come in or out of view during the course of an occultation.
-The fact that these features are so clearly visible means that even individual light curves encode a wealth of information about the surface.
+All occultations last for $\sim4$ min.
+The exposure cadence for each light curve is around a second with some variation between light curves.
+It follows that over the course of a single exposure Jupiter's limb passes over about 15km on Io's surface which provides a lower bound for the size of the features that we can reliably estimate.
+The shapes of light curves strongly deviate from the smooth variability one would expect assuming uniform thermal surface emission.
+Especially prominent are light curves with clear step-like features which are present when bright localized spots come in or out of view during the course of an occultation.
+The fact that these features are so clearly visible means that even individual light curves encode precise information on the longitudinal position of the spots.
 
-The photometric quality varies from year to year because multiple instruments were used over the years.
-An additional issue is that estimated errorbars aren't provided.
-As with all ground based photometry, the observations are influenced by atmospheric variability which induces correlated noise in the light curves.
-Because of this the flux isn't always monotonically increasing or decreasing as one would expect.
-All of these issues need to be accounted for in the final model.
+The photometric quality of the light curves varies from year to year because multiple instruments were used over the years. 
+As with all ground based photometry, the observations are influenced by atmospheric variability which results in some correlated noise in the light curves and because of this the flux is not always monotonically increasing or decreasing as one would expect.
+The light curves lack errorbars. 
+To estimate the errorbars we do some basic pre-processing on the light curves. 
+We filter each light curve with the Savitzky-Golay filter as implemented in \textsf{SciPy} \citep{virtanen2020} with
+a third order polynomial and a window length equal to 5\% of the number of data points and rounded up to the nearest odd integer. 
+After filtering, we compute the residuals with respect to the filtered model and run iterative sigma-clipping, removing all data points 5 median absolute deviations (MAD) from the median value. 
+Finally, we estimate the errorbars by computing the standard deviation of the sigma clipped residuals.
+This estimate is far from perfect which is why we introducing a rescaling parameter when fitting the model.
 
@@
 \label{ssec:orbital_parameters}
-To model the occultations we need to know the projected separation between Jupiter and Io and the orientation of Io at any given time.
-We use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner2014} which are accurate to a few kilometers on Io's surface.
-Specifically, we use the Right Ascension and Declination, the angular (equatorial) diameter (\textsf{Ang-diam}), the visibility flag indicating whether Io is occulted or not and whether it is in partial or total eclipse (\textsf{Ang-sep/v}), the longitude and latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}), the sub-solar point longitude and latitude which specify the direction pointing towards the Sun on Io's surface (\textsf{Sl-lon}, \textsf{Sl-lat}), the distance from Io to the Sun (\textsf{r}) and
-the counterclockwise angle between the Celestial North Pole unit vector projected onto the plane of the sky and the Io's north pole (\textsf{NP.ang}).
-All longitudes are positive to the west.
-\textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 second so we interpolate all values such that we can evaluate them for arbitrary times.
+To model the occultations we need to know the projected relative position of Jupiter with respect to Io and the orientation of Io at any given time.
+To compute the geometry, we use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner2014} which is accurate to a few kilometers on Io's surface.
+For both Jupiter and Io we need the Right Ascension and Declination and the angular (equatorial) diameter (\textsf{Ang-diam}).
+In addition, we need to fix the orientation of Io we need the longitude and the latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}) and the counterclockwise angle between the Celestial North Pole unit vector projected onto the plane of the sky and the Io's north pole (\textsf{NP.ang}).
+All longitudes are positive  in the direction of West.
+\textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 second so we interpolate all values so that we can evaluate them for arbitrary times.
 
@@
 The radius of the occulted sphere is fixed to 1 and the orientation is specified by three angles,
-the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the North Pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the North Pole is aligned with the $\hat{y}$ axis and the phase angle \textsf{theta} rotates the sphere around the $\hat{y}$ axis in the eastward direction.
+the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the North Pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the North Pole is aligned with the $\hat{y}$ axis and the phase angle \textsf{theta} which rotates the sphere around the $\hat{y}$ axis in the eastward direction.
 We have $\mathrm{obl}=\textsf{NP.ang}$, $\mathrm{inc}=90^\circ-\textsf{Ob-lat}$ and
@@
 \end{align}
-where $\Delta\alpha$ are the $\Delta\delta$ differences in Right Ascension and Declination respectively relative to the occulted object and $\gamma$ is the angular radius of the occulted sphere.
-If the occulted object is illuminated by the Sun then we also need to specify the coordinates of the light source which are given by
-\begin{align}
-    \mathrm{xs}&=r\cos\theta\sin\phi\\
-    \mathrm{ys}&=r\sin\theta\\
-    \mathrm{zs}&=r\cos\theta\cos\phi
-\end{align}
-where $\theta$ is obtained by subtracting \textsf{Ob-lat} from \textsf{Sl-lat} and similarly $\phi$ is obtained by subtracting \textsf{Ob-lon} from \textsf{Sl-lon}.
-$r$ is equal to the heliocentric distance of the occulted object \textsf{r}.
+where $\Delta\alpha$ and $\Delta\delta$ are differences in Right Ascension and Declination respectively relative to the occulted object and $\gamma$ is the angular radius of the occulted sphere.
 
-\subsection{Effective radius of Jupiter}
+\subsection{Jupiter's effective radius}
 Although the sky position of Jupiter relative to Io is known to a precision of a few kilometers, several complications arise when attempting to compute Jupiter's radius.
-First, Jupiter is not spherical and its equatorial radius is larger than the polar radius by thousands of kilometers. 
-Because \textsf{starry} does not support occultations by non-spherical occultors we 
-assume that Jupiter is locally spherical at the point of an occultation and estimate an effective radius from measurements of Jupiter's shape which are based on Voyager radio occultation measurements \citep{lindal1981}.
-These data come in the form of a plot of effective radius  as a function of planetocentric latitude at a fixed pressure of 100 mbar \citep[Fig.~7 in ][]{lindal1981}.
-When computing the occultation latitude we ignore the variation in effective radius along Jupiter's limb projected on Io's surface and instead fix Jupiter's latitude to the value corresponding to the center of Io's disc.
+First, Jupiter is not spherical and its equatorial radius is greater than the polar radius by thousands of kilometers. 
+Because \textsf{starry} does not support occultations by non-spherical occultors and because the effect is negligible at the resolution of our maps, we assume that Jupiter is locally spherical at the point of an occultation.
+We estimate an effective radius from the measurements of Jupiter's shape from Voyager radio occultation data \citep{lindal1981}.
+These data come in the form of a plot of effective radius  as a function of Jupiter's planetocentric latitude at a fixed pressure of 100 mbar \citep[Fig.~7 in ][]{lindal1981}.
+When computing the occultation latitude we fix Jupiter's latitude to the value at the center of Io's disc because 
+the variation of Jupiter's effective radius along Io's disc is negligible.
 
-The second complication is that Jupiter is gaseous which means that it does not have a well defined boundary.
+Second, Jupiter is gaseous so it does not have a well defined boundary.
 In principle, we should compute an effective radius of Jupiter at different locations (pressure) in the atmosphere and model an occultation of Io by a fuzzy occultor.
-Although this can be done with Starry, it is not necessary because the characteristic scale height of Jupiter is around 27 km (CITE) which is below the uncertainty of our inferred maps.
-Instead, we follow \cite{spencer1990} and compute the effective radius of Jupiter at about 2.2 mbar, this is the pressure (and the associated effective radius) at which during an occultation a bright source on the surface of Io fades by 50\% due to differential refraction.
+Although this is possible with Starry, it is unnecessary for our models because the characteristic scale height of Jupiter is around 27 km (CITE) which is below the uncertainty of our inferred maps.
+Instead, we follow the approach in \cite{spencer1990} and compute the effective radius of Jupiter at about 2.2 mbar, the pressure (and the associated effective radius) at which a  bright source on the surface of Io fades by 50\% due to differential refraction during the course of an occultation.
 
-Since the effective radius information is provided only at a fixed pressure of 100 mbar, 
-to adjust those values for a lower pressure of 2.2 mbar, we assume an exponential pressure profile $P=P_0\, e^{-\Delta r/H}$ where $H$ is the scale height and $\Delta r$ is the height difference between the two pressure levels.
+Third, the information on the effective radius in \citep{lindal1981} is provided only at a fixed pressure of 100 mbar.
+To adjust the values for a lower pressure of 2.2 mbar we assume an exponential pressure profile $P=P_0\, e^{-\Delta r/H}$ where $H$ is the scale height and $\Delta r$ is the height difference between the two pressure levels.
 It follows that to convert the shape profile at 100 mbar to 2.2 mbar we need to add the factor
 $-H\ln(2.2/100)$ which is assumed to be constant in the $\pm 21$ deg latitude range in which the occultations occur.
-Besides refractive absorption there is a also a slight additional methane molecular absorption which \cite{spencer1990} estimate to be equal to around 12\% in their filter, 
-we choose to ignore this because it is far below the resolution of our maps.
+In addition to refractive absorption in Jupiter's atmosphere there is a also slight additional molecular absorption due to methane which \cite{spencer1990} estimate to be equal to around 12\% in their filter, we choose to ignore this because it is far below the resolution of our maps.
 
-Finally, we have to account for the fact that the light from Io is getting significantly bent at the point of half reflective intensity in Jupiter's atmosphere 
-which results in a smaller shadow of Jupiter on the surface of Io then would be the case if the light didn't get bent.
+Finally, we have to account for the fact that the light from Io is getting significantly bent at the point of half reflective intensity in Jupiter's atmosphere which results in a smaller shadow of Jupiter on the surface of Io then would be the case for a straight propagation.
 It is zero at the beginning of the disappearance of a hot spot when there is no refraction, increasing to one scale height $H$ at the half intensity point and then increasing further to a large value when Io disappears behind Jupiter's limb.
@@
 
-In summary, to compute an effective radius of Jupiter for a given occultation of Io we first have to compute the latitude at which the occultation is occurring, use a modified shape profile from \cite{lindal1981} to get an effective radius and finally subtract one scale height due to light bending.
-There are substantial uncertainties in each of these steps, most notably the shape profile data are quite old and it is not clear that the structure of Jupiter's atmosphere stayed the same since 1980s.
-The shape profile also depends on the wind velocity structure and temperature which we ignore.
+In summary, to compute an effective radius of Jupiter for a given occultation of Io first we have to compute Jupiter's planetocentric latitude at which Io's disk disappears or reappears behind the limb, then use a modified shape profile from \cite{lindal1981} to get an effective radius and finally we have to subtract one scale height due to light bending.
+There are substantial uncertainties in each of these steps.
+The data about on the shape profile are quite old and it is not known if the structure of Jupiter's atmosphere stayed the same since 1980s. 
+The shape profile also depends on the wind velocity structure and temperature which we do not take into account.
 In addition to uncertainties about the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
-We digitizing this figure by reading off the data points "by eye" and then interpolating them using cubic spline interpolation.
-Finally we add the pressure conversion factor and subtract one scale height due to light bending.
+We digitized the figure by reading off the data points "by eye" and then interpolating them using cubic spline interpolation.
 
 Throughout this paper the highest resolution maps we fit to the data are of order $l=25$ which corresponds to a characteristic length scale of around 230 km on the surface of Io.
-Quantifying the uncertainty in each of these steps is beyond the scope of this paper but we are confident that the errors in the radius estimate are below the typical resolution of our inferred maps. 
-We provide justification for this assumption in section~\ref{ssec:static_map} where we infer the location of Loki and it ends up matching well with the high resolution geological map of Io.
+This is about an order of magnitude larger than the errors introduced in the effective radius estimate above so we are not concerned with substantial errors in our radius estimate.
 
-\subsection{Static map model}
-\label{ssec:static}
+\subsection{Model specification}
+\label{ssec:model_spec}
 Given the geometry of on occultation event at an arbitrary time, computing the predicted flux with \textsf{starry} is straightforward.
 \textsf{starry} computes the integrated flux of an unocculted or an occulted sphere analytically assuming that the surface map can be expanded in terms of spherical harmonics $Y_{lm}(\theta,\phi)$ up to a certain \emph{degree} $l$.
-The map is thus defined by a vector of spherical harmonic coefficients $\mathbf{y}$ multiplying the spherical harmonic basis $\tilde{\mathbf{y}}(x, y)=\left(Y_{0,0} Y_{1,-1} Y_{1,0} Y_{1,1} Y_{2,-2} Y_{2,-1} Y_{2,0} Y_{2,1} Y_{2,2} \cdots\right)^{\top}$ and the total number of coefficients is $(l+1)^2$.
+The map is thus defined by a vector of spherical harmonic coefficients $\mathbf{y}$ which multiplies the spherical harmonic basis $\tilde{\mathbf{y}}(x, y)=\left(Y_{0,0} Y_{1,-1} Y_{1,0} Y_{1,1} Y_{2,-2} Y_{2,-1} Y_{2,0} Y_{2,1} Y_{2,2} \cdots\right)^{\top}$ and the total number of coefficients is $(l+1)^2$.
 In addition to computing \emph{thermal} phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations when the sphere is illuminated by a distant light source \citep[Luger et al.
@@
 In the case of a reflected light map, the coefficient vector $\mathbf{y}$ represents spherical albedo in a given wavelength range.
-Most importantly, conditional on the parameters specifying the geometry of the occultations being fixed, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
-This is achieved by representing all rotations, changes of basis and integrals with complicated boundaries needed to compute the flux as linear transformations.
+We only use data taken while Io was in eclipse shadowed by Jupiter so we do not need to model the reflected light component. 
+If instead we had occultation data or phase curves taken while Io is illuminated by the Sun and if both the thermal component and the reflected sunlight component of observed flux were comparable, it would be necessary to simultaneously fit for two vectors of spherical harmonic coefficients,
+one for the albedo distribution and the other for thermal emission.
+
+Importantly, conditional on the parameters specifying the geometry of the occultations being fixed, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
+\cite{luger2019} achieved this by representing all rotations, changes of basis transformations and integrals with complicated boundaries which are needed to compute the flux as linear transformations.
 Since a sequence of linear mappings is also linear, the predicted flux can be written as
@@
 The characteristic angular scale of features that can be represented with a given map is set by the degree of the map and it is approximately equal to $\frac{180^\circ}{l}$.
-State of the art inferences involving phase curves and secondary eclipses of exoplanets are able to constrain features of order $l=1$ (inferring a bright spot on single hemisphere) but for Io we need to fit much higher order maps because the typical scale of volcanic spots is on the order of tens of kilometers (a few degrees).
-\textsf{starry} can handle computations with maps up to $l\approx 20$ before numerical instabilities kick in (TODO: make this statement more precise).
+For reference, state of the art inferences involving phase curves and secondary eclipses of exoplanets are able to constrain features of order $l=1$ (inferring a bright spot offset from the substellar point) but for Io we need to fit much higher order maps because the typical scale of volcanic spots is on the order of tens of kilometers (a few degrees).
+\textsf{starry} can handle maps up to $l\approx 20$ before numerical instabilities kick in (TODO: make this statement more precise).
 
 Although \textsf{starry} is built around the idea of expanding surface features in a spherical harmonic basis, this is not the ideal basis for doing inference because it makes it difficult to ensure that the intensity is positive everywhere on the map.
-The positivity constraint is important not only because we want to avoid having unphysical regions on inferred maps but because it also imposes a strong constraint on the map which reduces the complexity of the inference problem.
-There is no analytic way to determine weather a given spherical harmonic map $\mathbf{y}$ is positive-valued everywhere on the sphere. 
-The only way of circumventing this problem that we are aware of is to evaluate the intensity on a (sufficiently fine) discrete grid of \emph{pixels} $\mathbf{p}$ on the sphere and then either fit for $\mathbf{y}$ while rejecting inference steps where any of the pixels $\mathbf{p}$ end up being negative, or we can treat the pixels as model parameters but still compute the actual light curve model in the $Y_{lm}$ basis where everything is fast.
+The positivity constraint is important not only because we want to avoid having unphysical regions on inferred maps but also because it imposes a strong constraint on the map which substantially reduces the complexity of the inference problem.
+Unfortunately, there is no analytic way to determine weather a given spherical harmonic map $\mathbf{y}$ is positive-valued everywhere on the sphere.
+
+The are two ways of circumventing this problem that we are aware of.
+The first is to evaluate the intensity on a (sufficiently fine) discrete grid of \emph{pixels} $\mathbf{p}$ on the sphere and then either fit for $\mathbf{y}$ while rejecting steps when fitting the model for which any of the pixels $\mathbf{p}$ end up being negative.
+The second is to treat the pixels as model parameters but still compute the actual light curve model in the $Y_{lm}$ basis where everything is fast. 
 We opt for the latter approach because it is much easier to implement.
-There exists a linear operator $\mathbf{P}$ which maps $\mathbf{y}$ it to pixels:
+The mapping from spherical harmonics $\mathbf{y}$ to pixels $\mathbf{p}$ can be expressed as a linear operator 
+$\mathbf{P}$:
 \begin{equation}
@@
 \end{equation}
-Each row of $\mathbf{P}$ contains values of each of spherical harmonic coefficients at a point on the grid. 
+Each row of $\mathbf{P}$ contains values of each of spherical harmonic coefficients at a given point on the grid. 
 To construct the grid we use an equal area Molleweide projection so that we don't end up with more pixels in some areas of the sphere than others.
-The grid needs to be fine enough to ensure positivity over most of the sphere, we find that we need to have more pixels than spherical harmonics by a factor of at least 4.
-Although we can't invert $\mathbf{P}$ to obtain the inverse transform we can still compute the Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$ where $\mathbf{I}$ is the identity matrix.
+The grid needs to be fine enough to ensure positivity over most of the sphere.
+We find that we need to have more pixels than spherical harmonics by a factor of at least 4.
+This increases the computational cost of the inference somewhat because the number of parameters we have to fit increases fourfold.
+
+Because $\mathbf{P}$ is not a square matrix, we cannot compute its inverse to obtain the inverse transform, however we can still compute the Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$ where $\mathbf{I}$ is the identity matrix.
 The solution is given by
@@
 \end{equation}
-Both matrices can be easily pre-computed with \textsf{starry} before doing inference.
-
-The flux can then be computed as a linear operation on the pixels: 
+Both matrices can easily be pre-computed with \textsf{starry} before doing inference.
+We use the symbol $\mathbf{p}'$ to denote pixels which are mapped to spherical harmonic coefficients using $\mathbf{P}^\dagger$ and $\mathbf{p}$ for those generated from $\mathbf{y}$ using $\mathbf{P}$.
+In the rest of the paper we call the former kind of pixels \emph{sphixels}.
+Setting $\mathbf{A}'\equiv \mathbf{A}\,\mathbf{P}^\dagger$, we see that the flux is also linear in the spixels:
 \begin{equation}
-    \mathbf{f}=\mathbf{A}\,\mathbf{P}^\dagger\,\mathbf{p}'
+    \mathbf{f}=\mathbf{A}'\,\mathbf{p}'
     \label{eq:linear_model_pix}
 \end{equation}
-We use the symbol $\mathbf{p}'$ to denote pixels which are mapped to spherical harmonic coefficients using $\mathbf{P}^\dagger$ and $\mathbf{p}$ for those generated from $\mathbf{y}$ using $\mathbf{P}$.
-In the rest of the paper we call the former kind pixels \emph{sphixels}.
-In Section~\ref{ssec:sphixels_vs_harmonics} we test differences between fitting a model for spherical harmonic coefficients vs. fitting for sphixels.
+
+\begin{figure}[h!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/sphixels_to_pixels.pdf}
+    \oscaption{sphixels_to_pixels}{%
+        Transformation of a pixelated map in which we set our priors (left) to the spherical harmonic basis which we use to compute the model (middle) and then again to pixels.
+        The mapping from spherical harmonics to pixels is exact but the reverse is not true so to differentiate between pixels mapped to spherical harmonics and pixels constructed from spherical harmonics we call the former "sphixels".
+        Since there are many more sphixels than there are spherical harmonics coefficients a sphixel map 
+       drawn from an Exponential prior on the left can only be approximately represented in the $Y_{lm}$ basis and the effective prior on pixels ends up looking more like a skewed Gaussian with a heavy right tail than an Exponential.
+  \label{fig:sphixels_to_pixels}
+    }
+    \end{centering}
+\end{figure}
+
+To visualize the effect of the transformation from sphixels to spherical harmonics, in Figure~\ref{fig:sphixels_to_pixels} we plot a single draw of sphixels $\mathbf{p}'$ from an Exponential prior (left) in the Mollweide projection, map them to spherical harmonics (middle), and then generate another pixelated map from the spherical harmonics on a grid of the same size as the initial sphixel grid.
+The middle map is visibly smoother than the prior map and looking at the histograms (black) the effective prior looks more like a skewed Gaussian with a heavy right tail than an Exponential distribution.
+There is also minimal leakage into negative values of intensity.
+The reason for this is that the pixels $\mathbf{P}\,\mathbf{y}'$ generated from $\mathbf{P}^\dagger\mathbf{p}'$ do not completely respect the Exponential prior because some information is lost in going from sphixels to spherical harmonics.
+Nevertheless, in Section~\ref{ssec:sphixels_vs_harmonics} we find that setting priors on sphixels is a far better solution than using the spherical harmonic coefficients.
 
@@
 \label{ssec:likelihood}
-Given Eq.~\ref{eq:nmf} we can write down the likelihood for our data and in Section~\ref{sec:inverse_problem} we dicuss in detail the priors which make the problems of inferring static and dynamic maps tractable.
-Assuming a Gaussian noise process for the data with a dense covariance matrix, the (log) likelihood is
+Given Eq.~\ref{eq:linear_model_pix} we can write down the likelihood for our data.
+We assume a Gaussian likelihood for the data with a dense covariance matrix generated with from a Gaussian Process.
+To compute the Gaussian process likelihood we use the fast Celerite method \citep{foreman-mackey2017} as implemented in the \textsf{celerite2} package (TODO: cite).
 \begin{equation}
@@
 where $\mathbb{f}_\mathrm{obs}$ is the vector of stacked observed light curves, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbb{b}$ is a fixed flux offset per light curve accounting for stray flux not attributed to Io (mostly due to Jupiter).
-We model the data covariance with a Gaussian Process using the fast Celerite method\citep{foreman-mackey2017} as implemented in the \textsf{exoplanet} package (TODO: cite) to capute correlations imposed by the seeing plus an additional white noise term which is different for each light curve.
-The IRTF data isn't provided with any uncertainties so we estimate the uncertainties by filtering the data with the Savitzky Golay filter as implemented in \textsf{SciPy} (TODO: CITE) and estimating the variance of the residuals.
-We assume identical errors for all data points in a given light curve but allow for a rescaling factor when fitting the model.
-In the next section, we add priors to this likelihood and fit the model on simulated data using optimization and Variational Inference (VI).
-
-%TODO: mention that A depends on the geometry and that we fit for some of those parameters.
+An important assumption here is that a single static map generates all of the light curves, an assumption which is violated if the surface emission changed substantially between observations. 
+For this reason we fit at most two light curves at a time relatively closely spaced in time.
 
@@
 \label{sec:inverse_problem}
-Having defined the forward models in the previous section, in this section we focus on choosing priors, doing inference and testing the models on simulated data.
-We compute the information content of different kinds of occultation and phase light curves and , we test the differences between fitting in the $Y_{lm}$ basis vs.
-fitting in the pixel basis, prior choices for pixel maps and priors for NMF.
-To fit the models, we use  variational inference and Hamiltonian Monte Carlo.
+Having defined the forward model in the previous section, in this section we describe how to solve the inverse problem in a Bayesian setting.
 
-% bulk of the results in the paper
 \subsection{The information content of a light curve}
 \label{ssec:information_content}
-The mapping problem is famously ill posed.
-In other words, certain linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Eq.~\ref{eq:linear_model}.
-This means that even if we had noiseless observations, certain features would still be impossible to recover.
-To recover surface features from observed flux integrated over the disc of the object we need
-to have some mechanism which breaks the various degeneracies.
-For phase curves in emitted light, we can only recover longitudinal variations in intensity.
-Occultations are a lot better thanks to the limb of the occultor sweeping across the surface of the occulted sphere.
-Even better are grazing occultations with an occultor of a small diameter sweeping across the disc at different latitudes and therefore breaking the latitudinal degeneracies. 
+The mapping problem is famously ill posed meaning that specific linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Eq.~\ref{eq:linear_model}.
+This means that even if we had noiseless observations it would still be impossible to recover certain features.
+To recover the greatest information about the surface we need to have some mechanism which breaks the various degeneracies.
+With phase curves only we can recover longitudinal variations in emission.
+Occultations are a lot better because the limb of the occultor sweeps across the surface of the occulted sphere, thereby exposing or blocking light from different points on the surface.
+Best case scenario is having phase curve observations plus a series of occultations by a small occultor at different latitudes and different phases.
 Observing phase curves and occultations in reflected light improves the model even more because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
@@
 
-To compute how much information can in principle be obtained by observing occultations of Io by Jupiter and other moons or phase curves we need to compute some measure of how much does observing Io at certain times reduce our prior uncertainty on the map features.
-Given that the model for a static map (Eq.~\ref{eq:linear_model}) is linear, under Gaussian priors with covariance $\boldsymbol{\Lambda}$ on the spherical harmonic coefficients and a Gaussian likelihood, the posterior is analytic and the mean is given by
+We can reformulate these statements more precisely by computing a measure of information content of the different kinds of observations.
+Given that our model is linear, assuming Gaussian priors on the spherical harmonic coefficients with covariance $\boldsymbol{\Lambda}$ and a Gaussian likelihood, the posterior can be computed analytically and its mean is given by
 \begin{equation}
@@
 The posterior covariance matrix depends on the design matrix $\mathbf{A}$, the prior covariance  $\boldsymbol{\Lambda}$ and the data covariance $\boldsymbol{\Sigma}_{\mathbf{f}}$.
-We first compute the design matrices using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
-
-We take the ephemeris data  from \textsf{JPL HORIZONS} and assume that it is known exactly, we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse.
-This is because we are interested in constraining the volcanic emission rather than the albedo.
-Given the fixed design matrices, we can compute the variance reduction of the posterior relative to the prior known as \emph{posterior shrinkage}, defined as
+We define the information content as the variance reduction of the posterior relative to the prior which is called \emph{posterior shrinkage}.
+It is defined as
 \begin{equation}
@@
 where $\sigma^2_\mathrm{prior}$ is the prior and $\sigma^2_\mathrm{post}$ is the posterior variance for a given parameter.
-To compute this quantity for each spherical harmonic coefficient in $\mathbf{y}$ we divide the diagonal elements of matrices $\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}$ and $\boldsymbol{\Lambda}$, divide them, and average over all $m$-modes.
+For each spherical harmonic coefficient in $\mathbf{y}$ the posterior shrinkage is then the ratio of the diagonal elements of matrices $\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}$ and $\boldsymbol{\Lambda}$.
+In order to compute the posterior shrinkage we first compute the design matrices using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
+We take the ephemeris data from \textsf{JPL HORIZONS} and assume that it is known exactly and we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
 We need to assume some variance for the Gaussian prior on the $Y_{l,m}$ coefficients so we choose a broad prior $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$.
 Although the posterior shrinkage depends on this prior the main results do not change for a different choice of the prior.
-The result is plotted in Fig.~\ref{fig:information_content}.
+
 \begin{figure}[h!]
@@
     \oscaption{InformationContent}{
-        The information content of different kinds of observations of Io as a function of spherical harmonic degree (angular scale of surface features).
-        On the y axis is posterior shrinkage (the variance ratio between the prior and the posterior distribution) for each spherical harmonic coefficient at a given degree $l$ on the x axis, averaged across all $m$ modes.
-        Posterior shrinkage of 1 represent maximum information gain in updating from the prior to the posterior while a shrinkage of 0 represents no information gain. 
-        We compute the posterior variance for different kinds of simulated observations of Io over
-        the course of a single year: phase curves (blue), occultations by Jupiter (orange), combined phase curves and occultations by Jupiter (green) and occulltations of Io by other Galilean moons (red lines).
-        Solid lines represent observations at SNR=100 while dashed lines represent observations at SNR=10.
+        The posterior shrinkage of different kinds of observations of Io as a function of spherical harmonic degree (angular scale), averaged across all $m$ modes.
+    Posterior shrinkage of 1 represent maximum information gain in updating from the prior to the posterior while 0 represents no information gain. 
+    The posterior variance has been computed for different kinds of simulated observations of Io over the course of a single year: phase curves (blue), occultations by Jupiter (orange), combined phase curves and occultations by Jupiter (green) and occulltations of Io by other Galilean moons (red lines).
+        Solid lines are for observations at SNR=100 and dashed are for observations at SNR=10.
         \label{fig:information_content}
@@
 \end{figure}
-The plot shows posterior shrinkage for phase curve observations (blue lines), occultations by Jupiter (orange), the previous two combined (green) and mutual occultations by other Galilean moons (red).
+
+Fig.~\ref{fig:information_content} shows the posterior shrinkage as a function of $l$ (averaged over all $m$ modes) for phase curve observations (blue lines), occultations by Jupiter (orange), the former two combined (green) and mutual occultations by other Galilean moons (red).
 Solid lines correspond to SNR=100 while dashed lines correspond to SNR=10 where the signal is defined as the min-max difference of the predicted flux.
+As expected, the mutual occultations of Io by other moons are by far the most informative with posterior shrinkage near unity at all angular scales up to $l=18$. 
+Occultations by Jupiter are far less informative because we only see one side of Io during an occultation.
+This is also why there is a kink in the curve at $l=1$.
+We also see that the shrinkage is exactly zero for phase curves at all odd degrees above $l=2$ because phase curves for objects rotating about an axis perpendicular to the line of sight encode zero information on these coefficients because they are in the nullspace.
+Although observations of mutual occultations most easily break the degeneracies, they only occur every 6 years and more importantly they almost never occur while Io is in eclipse which means that only the brightest volcanoes will be visible above the reflected light background emission due to the Sun.
+Figure~\ref{fig:information_content} does not reflect this fact.
 
-        It is clear that observations of mutual occultations of Io (red lines) are by far the most informative and most useful for constraining surface features.
-The posterior shrinkage is near unity at all angular scales $l$ up to $l=18$ owing to degeneracy breaking features of these occcultations.
-        Occultations by Jupiter (orange lines) are far less informative because we only see one side of Io during an occultation (hence the kink in the curve at $l=1$) and the position of Jupiter's limb on the surface of Io does not vary significantly so latitudinal features are only weakly constrained.
-        The posterior shrinkage is exactly zero for phase curves at all odd degrees above $l=2$ because phase curves for objects rotating about an axis perpendicular to the line of sight encode zero information on these coefficients because they are in the nullspace.
-Although observations of mutual occultations most easily break the degeneracies, they only occur every 6 years and more importantly they almost never occur while Io is in eclipse.
-This means that only the brightest volcanoes will be visible above the reflected light background emission due to the Sun.
-Figure~\ref{fig:information_content} does not reflect this fact.
-When modeling the observations taken while Io is in sunlight, we have to take into account the reflected light component.
-Although \textsf{starry} supports computing occultations and phase curves in reflected light, we only fit in eclipse observations in this work.
+Although Figure~\ref{fig:information_content} gives us some idea about which kinds of observations are most informative, it doesn't really tell us how well we can constrain very bright spot like features we expect to see on Io.
+To answer this question we have to simulate some data and the inference process.
 
@@
 \label{ssec:sphixels_vs_harmonics}
-To test inference with the static map model defined in Section~\ref{ssec:static} 
-we use \textsf{starry} to generate a single simulated light curve of an occultation of Io by Jupiter from an $l=30$ map.
-The simulated map consists of a spherical harmonic expansion of a bright spot with a Gaussian profile which we add using the built in \textsf{add\_spot} function in \textsf{starry}.
+We use \textsf{starry} to generate a single simulated light curve of an occultation of Io by Jupiter from an $l=30$ map with known coefficients.
+The simulated map consists of a spherical harmonic expansion of a bright spot with a Gaussian profile which we add to a featureless map using the built in \textsf{add\_spot} function in \textsf{starry}.
 The expansion is in the quantity $\cos(\Delta\theta)$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere. 
-We place the spot at 13 degrees latitude and 51 degrees East longitude, set the diameter of the spot ($2\Delta\theta$) to 5 degrees and the amplitude to 55\% of the total luminosity of a spotless map.
-We take ephemeris parameters (assumed to be fixed) from a real occultation and assume an observational cadence of 1s and errorbars equal to 2\% of the total flux, similar to high quality IRTF light curves.
-We use this dataset to test the difference between fitting a model in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the sphixel basis (Eq.~\ref{eq:linear_model_pix})
-by fitting for an $l=20$ map.
-Since we are only fitting a single light curve, the inferred maps will be strongly prior dominated.
+We place the spot at $13^\circ$ N latitude and $51^\circ$ E longitude, we set the diameter of the spot (given by  $2\Delta\theta$) to $5^\circ$ and the amplitude of the spot such that the total \emph{luminosity} (by default equal to 4 in \textsf{starry}) of the map increases by 50\% with the addition of the spot.
+We take ephemeris parameters (assumed to be fixed) from a real occultation of Io and assume an observational cadence of 1s and SNR=50.
+We use this dataset to test the difference between fitting setting a prior in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the sphixel basis (Eq.~\ref{eq:linear_model_pix}) by fitting an $l=20$ map to the dataset.
+Since we are only fitting a single light curve the inferred maps will be strongly prior dominated.
 
 In the first case we place a Gaussian prior on $Y_{lm}$ coefficients with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$ and optimize for the values of the coefficients.
-In the second case we fit for sphixel $\mathbf{p}'$ evaluated on a fixed (latitude, longitude) grid with two sets of positive priors, a Half Gaussian prior with zero mean and an Exponential prior.
-To ensure we have a grid of high enough resolution we use 4 times as many sphixels as spherical harmonic coefficients.
-
+In the second case we fit for sphixels $\mathbf{p}'$ evaluated on a fixed (latitude, longitude) grid with two sets of positive priors, a Half Gaussian prior with zero mean and an Exponential prior.
+We use four times as many sphixels as spherical harmonics.
 To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the sphixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each evaluation of the posterior.
-As the end product of the inference we do not use the sphixels $\mathbf{p}'$ but rather the spherical harmonic coefficients $\mathbf{y}=\mathbf{P}^\dagger\mathbf{p}'$ generated from the sphixels.
-The coefficents $\mathbf{y}$ can then be used to evaluate the map on a pixelated grid of arbitrary resolution via the matrix $\mathbf{P}$. 
-Although the priors on sphixels $\mathbf{p}'$ are strictly positive, the pixels $\mathbf{P}\,\mathbf{y}$ don't completely respect those priors because some information is lost in going from sphixels to spherical harmonics  and there will still be some regions of the map with negative intensity.
-To visualize the effect of the transformation from sphixels to spherical harmonics, in Figure~\ref{fig:sphixels_to_pixels} we plot a single draw of sphixels from an Exponential prior (left), convert them to spherical harmonics (middle) and then generate another pixelated map from the spherical harmonics on a grid of the same size as the sphixel grid.
-The middle map is visibly smoother than the prior map and based on the histograms shown in black, it seems that the effective prior is closer to a Gaussian than an Exponential.
-There is also minimal leakage into negative values.
-
-\begin{figure}[h!]
-    \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/sphixels_to_pixels.pdf}
-    \oscaption{sphixels_to_pixels}{%
-        Mapping from a pixelated map in which we set our priors (left) to the spherical harmonic basis which we use to compute the model (middle) and then back to pixels (right).
-        The mapping from spherical harmonics to pixels is exact but the reverse is not true
-        so to differentiate between pixels mapped to spherical harmonics and pixels constructed from spherical harmonics we call the former "sphixels".
-        Since there are many more sphixels than there are spherical harmonics coefficients 
-       the map drawn from an Exponential prior on the left can only be approximately represented in the $Y_{lm}$ basis and the effective prior on pixels ends up looking more like a Gaussian with a heavier right tail than an Exponential.
-  \label{fig:sphixels_to_pixels}
-    }
-    \end{centering}
-\end{figure}
+As the end product of the inference we do not use the sphixels $\mathbf{p}'$ but rather the spherical harmonic coefficients $\mathbf{y}'=\mathbf{P}^\dagger\mathbf{p}'$ generated from the sphixels.
+The coefficents $\mathbf{y}'$ can then be used to evaluate the map on a pixelated grid of arbitrary resolution via the matrix $\mathbf{P}$.
 
@@
     \oscaption{sphixels_vs_harmonics}{%
-        Maximum A Posteriori (MAP) estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (bottom) which was generated from an $l=30$ map consisting of a single bright spot (top).
+        Median estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (bottom) which had been generated from an $l=30$ map consisting of a single bright spot (top).
         The small circles beneath each inferred map show the progression of the occultation.
         The map on the left corresponds to a model in which we directly fit for spherical harmonic coefficients $\mathbf{y}$ with a Gaussian prior.
-        The map in the middle comes from a model in which we instead fit for sphixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
+        The map in the middle corresponds to a model in which we instead fit for sphixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
         The map on the right is the same as the middle one except we use an Exponential prior.
         The scale parameter of the Half Gaussian and the Exponential prior is set to a value which approximates the scale of Gaussian prior on $\mathbf{y}$ to ensure fair comparison between the solutions.
-        While all models fit the data reasonably well, the ones in which we fit for sphixels result in more plausible and sparse maps.
         The location of the true spot is not recovered correctly because a single light curve does not contain enough information to break the degeneracy in position along the limb of the occultor.
@@
 To ensure that the difference in the inferred maps is not in part due to a difference in the scale of the priors, we take 10000 prior samples of the $y$ in the spherical harmonic model, compute the standard deviation and use that as the scale parameter of the Half Gaussian and the Exponential prior.
-We fit all models for the Maximum A Posteriori (MAP) estimate of the parameters using the
-\textsf{BFGS} algorithm as implemented in \textsf{scipy.optimize.minimize} in the \textsf{scipy} package (CITE) and the exact gradients of the model with respect to all parameters provided by \textsf{Theano}.
+We implement the model in the probabilistic programming language \textsf{numpyro} (CITE) which is built on top of the \textsf{JAX} library and fit it with Hamiltonian Monte Carlo using the No-U-Turn-Sampler (NUTS) (CITE).
+\textsf{JAX} is a \textsf{numpy} like library which supports automatic differentiation, parallelization and GPUs.
+We run the chains until for X tuning steps and Y final steps (TODO: HOW MANY?), monitoring divergences and the R-hat  diagnostic to check for convergence.
+Because these models have many hundreds if not thousands of parameters, it wouldn't be possible to fit them (at least for nontrivial priors) without automatic differentiation.
+
 The results are shown in Figure~\ref{fig:sphixels_vs_harmonics}.
@@
 The difference between the inferred maps is substantial despite the fact that the predicted flux is similar in all three cases.
-
 The inferred map from the spherical harmonic model (left) has near zero intensity on the observer facing side of Io except for a bright arc tracing the projected limb of Jupiter at the location of the true spot.
-The flux on the unobserved side of Io is nearly uniform and significantly higher than the flux on the observer facing side which results in an unrealistic transition between the bright and the dark region at $\pm 90$ degrees longitude.
+The flux on the unobserved side of Io is nearly uniform and significantly higher than the flux on the observer facing side which results in an unrealistic transition between the bright and the dark region at $\pm 90^\circ$ longitude.
 A very clear "ringing" pattern is visible in the with high intensity peaks and low (in some regions negative) intensity troughs.
-These features are a consequence of the finite order spherical harmonic expansion of the map and we could in principle get rid of them by fitting a higher order map but at $l=20$ we are already pushing the limits of what \textsf{starry} can do.
+These features are a consequence of the finite order spherical harmonic expansion of the map and we could in principle get rid of them by fitting a much higher order map but at $l=20$ we are already pushing the limits of what \textsf{starry} can handle.
 Besides avoiding unphysical negative intensities, ringing is undesirable because we want to avoid situations in which the model uses the rings to explain the data instead of just placing a spot directly.
@@
 The sphixel model with Half Gaussian priors produces a simpler map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
-Finally, the Exponential prior on sphixels results in a map with the most spot like feature but it also has noticeable ringing.
-This is somewhat surprising because based on Figure~\ref{fig:sphixels_to_pixels}, we wouldn't expect much difference between the Half Gaussian and the Exponential priors.
+Finally, the Exponential prior on sphixels results in a map with the most spot like feature 
+which is somewhat surprising because based on Figure~\ref{fig:sphixels_to_pixels}, we wouldn't expect much difference between the Half Gaussian and the Exponential priors.
 It seems that the heavier tail of the Exponential is nevertheless able to induce a sparser solution.
-In the next section, we tackle the issue of ringing artefacts.
+The rightmost map also has the most visible ringing artefacts, an issue which we discuss in the following section.
 
@@
 Figure~\ref{fig:smoothing_kernel} shows the effect of (Gaussian) smoothing on a spherical harmonic expansion of a spot with a Gaussian intensity profile.
-We place the spot at zero degrees latitude and longitude and set the size of the spot $\Delta\theta$ to 5 degrees.
+We place the spot at $0^\circ$ latitude and longitude and set the size of the spot $\Delta\theta$ to $5^\circ$.
 All three subplots show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
@@
        Normalized intensity of a spherical harmonic expansion of 
-        a Gaussian spot placed at zero degrees latitude and longitude.
+        a Gaussian spot placed at $0^\circ$ latitude and longitude.
         The expansion is in the quantity $\cos\Delta\theta$ where $\Delta\theta=5^\circ$.
@@
         The purpose of smoothing is to taper higher order spherical harmonic coefficients in order to suppress ringing artefacts which result in negative intensities.
-        It is apparent that no smoothing results in significant ringing, high levels of smoothing suppress the ringing completely but as a result they increase the spot size and eliminate differences between expansions above a certain order.
-        Intermediate levels of smoothing provide a compromise beteween the two extremes.
+        High levels of smoothing suppress the ringing completely but as a result they increase the spot size and eliminate differences between expansions above a certain order.
+        Intermediate levels of smoothing provide a compromise between the two extremes.
                \label{fig:smoothing_kernel}
@@
 
-Thus, there is a trade-off between smoothing and being able to resolve smaller scale features
-in the maps. 
+Thus, there is a trade-off between smoothing and the ability to resolve smaller scale features
+in maps. 
 In principle we can always get rid of ringing by fitting sufficiently high order maps.
 In practice, computing the analytic integrals computed by \textsf{starry} becomes computationally unstable above $l\approx 25$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
-We find that setting $\sigma_s=2/l$ where $l$ is the order of expansion of the map provides the best results .
+We find that setting $\sigma_s=2/l$ where $l$ is the order of expansion of the map  is a good default setting for $\sigma_s$.
 
+\section{Results with simulated data}
+\label{sec:results_sim}
 \subsection{Fitting simulated ingress/egress light curves}
-In this section we test a model which includes the smoothing filter. 
-We use the same map to generate the data as in Figure~\ref{fig:sphixels_vs_harmonics} except this time we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
+In this section we use the same map to generate the data as in Figure~\ref{fig:sphixels_vs_harmonics} except now we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
 We generate the light curves from an $l=25$ map and fit a map of the same order. 
 We apply a Gaussian smoothing filter to both the simulated map and the map we fit to the data and set the smoothing parameter to $\sigma_s=2/l=2/25$.
-We use an Exponential prior on the sphixels and set the scale parameter to 10.
+
+The prior we place on the sphixels is a sparse prior called the Regularized Horseshoe Prior (also known as the "Finnish Horseshoe") (CITE). 
+It is an improvement on the Horseshoe Prior (CITE).
+The horseshoe prior is a prior designed for use in sparse linear regression which is exactly what we are doing.
+The horseshoe prior sets a scale for each of the regression coefficients (sphixels) which is a product of a global scale $\tau$ and a local scale $\lambda_m$.
+It is defined hierarchically as 
+\begin{equation}
+\mathcal{Half}-\mathcal{C} 
+\end{equation}
+\begin{equation}
+\begin{aligned}
+\beta_{m} & \sim \mathcal{N}\left(0, \tau \cdot \lambda_{m}\right) \\
+    \lambda_{m} & \sim \mathcal{Half}-\mathcal{C} (0,1) \\
+    \tau & \sim \mathcal{Half-C} \left(0, \tau_{0}\right)
+\end{aligned}
+\end{equation}
+where $\tau_0$ is a characteristic global scale.
+
+The regularized horseshoe prior is 
+\begin{equation}
+\begin{aligned}
+\beta_{m} & \sim \mathcal{N}\left(0, \tau \cdot \lambda_{m}\right) \\
+\tilde{\lambda}_{m} &=\frac{c \lambda_{m}}{\sqrt{c^{2}+\tau^{2} \lambda_{m}^{2}}} \\
+\lambda_{m} & \sim \mathcal{Half-C}(0,1) \\
+c^{2} & \sim \mathcal{Inv-G}\left(\frac{\nu}{2}, \frac{\nu}{2} s^{2}\right) \\
+\tau & \sim \mathcal{Half-C}\left(0, \tau_{0}\right)
+\end{aligned}
+\end{equation}
+
 The results are shown in Figure~\ref{fig:ingress_egress_simulated}.
-
 \begin{figure}[h!]
@@
 
-\section{Results}
+\subsection{Comparison to a parametric model}
+
+\section{Results with IRTF data}
 \label{sec:results}
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \begin{centering}
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \begin{centering}
@@
 \label{sec:conclusions}
+\clearpage
 

### 2021-01-19 volcano/utils.py
Don't return std map by default

@@ -553,6 +553,7 @@ def get_median_map(
     theta=0.0,
     nsamples=15,
     resol=300,
+    return_std=False,
 ):
     """
     Given a set of samples from a posterior distribution over the spherical
@@ -567,6 +568,8 @@ def get_median_map(
         nsamples (int, optional): Number of samples to use to compute the 
             median. Defaults to 15.
         resol (int, optional): Map resolution. Defaults to 300.
+        return_std(bool, optional): If true, the function returns both the
+        median map and the standard deviation as a tuple. By default False.
 
     Returns:
         ndarray: Pixelated map in the requested projection. Shape (resol, resol).
@@ -590,4 +593,7 @@ def get_median_map(
             im = map.render(theta=theta, res=resol)
         imgs.append(im)
 
-    return np.nanmedian(imgs, axis=0), np.nanstd(imgs, axis=0)
+    if return_std:
+        return np.nanmedian(imgs, axis=0), np.nanstd(imgs, axis=0)
+    else:
+        return np.nanmedian(imgs, axis=0)

### 2021-01-21 paper/figures/irtf_ingress_egress_fit.py
Some tweaks and adjusments to models and plots.

@@ -135,7 +135,7 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
     print("tau0", tau0)
 
     # Other constants for the model
-    slab_scale = 50.0
+    slab_scale = 100.0
     slab_df = 10
 
     def model():
@@ -200,10 +200,13 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
         numpyro.deterministic("flux_eg_dense", flux_eg_dense)
 
         # Rescale errorbars
-        ln_K = numpyro.sample("ln_K", dist.HalfNormal(0.05).expand([2]))
+        K = numpyro.sample("K", dist.Normal(0.85, 0.05).expand([2]))
+        #        K = numpyro.deterministic("K", np.array([1.0, 1.0]))
 
         # GP likelihood
-        params = estimate_inverse_gamma_parameters(0.001, t_eg[-1])
+        params = estimate_inverse_gamma_parameters(
+            np.min(np.diff(t_eg)), t_eg[-1] - t_eg[0]
+        )
         sigma = numpyro.sample(
             "sigma_gp", dist.HalfNormal(0.1 * f_err_in[0]).expand([2])
         )
@@ -211,6 +214,7 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
             "rho_gp",
             dist.InverseGamma(params["alpha"], params["beta"]).expand([2]),
         )
+
         kernel_in = jax_terms.Matern32Term(sigma=sigma[0], rho=rho[0])
         kernel_eg = jax_terms.Matern32Term(sigma=sigma[1], rho=rho[1])
 
@@ -219,16 +223,12 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
 
         # Ingress GP
         gp_in = celerite2.jax.GaussianProcess(kernel_in, mean=flux_in_fun)
-        gp_in.compute(
-            t_in, diag=(jnp.exp(ln_K[0]) * f_err_in) ** 2, check_sorted=False
-        )
+        gp_in.compute(t_in, diag=(K[0] * f_err_in) ** 2, check_sorted=False)
         numpyro.sample("obs_in", gp_in.numpyro_dist(), obs=f_obs_in)
 
         # Egress GP
         gp_eg = celerite2.jax.GaussianProcess(kernel_eg, mean=flux_eg_fun)
-        gp_eg.compute(
[…]

### 2021-01-21 paper/figures/irtf_ingress_egress_plots.py

@@ -93,7 +93,7 @@ def make_plots(
     theta_eg = eph_io_eg["theta"].value
 
     # Fit single map model with different map amplitudes for ingress and egress
-    ydeg_inf = 25
+    ydeg_inf = 20
     map = starry.Map(ydeg_inf)
 
     # Evalute MAP model on denser grid
@@ -108,16 +108,12 @@ def make_plots(
     t_in_dense = np.linspace(t_in[0], t_in[-1], 200)
     t_eg_dense = np.linspace(t_eg[0], t_eg[-1], 200)
 
-    median_map_moll_in, std_map_moll_in = get_median_map(
-        ydeg_inf, samples["x_in"]
-    )
-    median_map_moll_eg, std_map_moll_eg = get_median_map(
-        ydeg_inf, samples["x_eg"]
-    )
-    median_map_in, std_map_in = get_median_map(
+    median_map_moll_in = get_median_map(ydeg_inf, samples["x_in"])
+    median_map_moll_eg = get_median_map(ydeg_inf, samples["x_eg"])
+    median_map_in = get_median_map(
         ydeg_inf, samples["x_in"], projection=None, theta=np.mean(theta_in)
     )
-    median_map_eg, std_map_eg = get_median_map(
+    median_map_eg = get_median_map(
         ydeg_inf, samples["x_eg"], projection=None, theta=np.mean(theta_eg)
     )
 
@@ -137,7 +133,7 @@ def make_plots(
         gp = celerite2.GaussianProcess(
             kernel_in, t=t_in, mean=np.array(samples["flux_in"])[i]
         )
-        gp.compute(t_in, yerr=(np.exp(samples["ln_K"][i][0]) * f_err_in) ** 2)
+        gp.compute(t_in, yerr=(samples["K"][i][0] * f_err_in) ** 2)
         gp_pred_in_dense.append(
             gp.predict(f_obs_in, t=t_in_dense, include_mean=False)
         )
@@ -149,7 +145,7 @@ def make_plots(
         gp = celerite2.GaussianProcess(
             kernel_eg, t=t_eg, mean=np.array(samples["flux_eg"])[i]
         )
-        gp.compute(t_eg, yerr=(np.exp(samples["ln_K"][i][1]) * f_err_eg) ** 2)
[…]

### 2021-01-21 paper/figures/simulated_ingress_egress.py

@@ -33,9 +33,9 @@ theta_in = 350.0
 theta_eg = 10.0
 ro = 39.1
 
-ydeg_true = 25
+ydeg_true = 20
 map_true = starry.Map(ydeg_true)
-spot_ang_dim = 5 * np.pi / 180
+spot_ang_dim = 10 * np.pi / 180
 spot_sigma = 1 - np.cos(spot_ang_dim / 2)
 map_true.add_spot(
     amp=1.0, sigma=spot_sigma, lat=13.0, lon=51.0, relative=False
@@ -70,7 +70,7 @@ f_obs_in_10 = f_true_in + np.random.normal(0, f_err_in_10, len(f_true_in))
 f_obs_eg_10 = f_true_eg + np.random.normal(0, f_err_eg_10, len(f_true_eg))
 
 # Set up model
-ydeg_inf = 25
+ydeg_inf = 20
 map = starry.Map(ydeg_inf)
 lat, lon, Y2P, P2Y, Dx, Dy = map.get_pixel_transforms(oversample=4)
 npix = Y2P.shape[0]
@@ -116,12 +116,12 @@ def model(f_obs_in, f_obs_eg, f_err_in, f_err_eg):
     lamda_raw = numpyro.sample("lamda_raw", dist.HalfCauchy(1.0).expand([D]))
     tau_raw = numpyro.sample("tau_raw", dist.HalfCauchy(1.0))
     c2_raw = numpyro.sample(
-        "c2_raw", dist.InverseGamma(0.5 * slab_df, 0.5 * slab_df)
+        "c2_raw", dist.InverseGamma(0.5 * slab_df, 1.)
     )
 
     # Do the shifting/stretching
     tau = numpyro.deterministic("tau", tau_raw * tau0)
-    c2 = numpyro.deterministic("c2", slab_scale ** 2 * c2_raw)
+    c2 = numpyro.deterministic("c2", 0.5 * slab_df*slab_scale ** 2 * c2_raw)
     lamda_tilde = numpyro.deterministic(
         "lamda_tilde",
         jnp.sqrt(c2) * lamda_raw / jnp.sqrt(c2 + tau ** 2 * lamda_raw ** 2),

### 2021-01-21 paper/paper.tex
More sections and words

@@
 % Begin!
+
 \begin{document}
@@
 \label{ssec:likelihood}
-Given Eq.~\ref{eq:linear_model_pix} we can write down the likelihood for our data.
-We assume a Gaussian likelihood for the data with a dense covariance matrix generated with from a Gaussian Process.
-To compute the Gaussian process likelihood we use the fast Celerite method \citep{foreman-mackey2017} as implemented in the \textsf{celerite2} package (TODO: cite).
+Assuming we have a single light curve with $N$ data points and a map specified with sphixels $\mathbf{p}'$, the (Gaussian) log likelihood is given by
 \begin{equation}
-    \ln\mathcal{L}=-\frac{1}{2}\left[\mathbb{f}_\mathrm{obs}-(\mathbb{f} + \mathbb{b})\right]^{\top} \boldsymbol{\Sigma}^{-1}\left[\mathbb{f}_\mathrm{obs}-(\mathbb{f} + \mathbb{b})\right]
+    \ln\mathcal{L}=-\frac{1}{2}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]^{\top}
+    \boldsymbol{\Sigma}_l^{-1}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]
+    \label{eq:likelihood}
 \end{equation}
-where $\mathbb{f}_\mathrm{obs}$ is the vector of stacked observed light curves, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbb{b}$ is a fixed flux offset per light curve accounting for stray flux not attributed to Io (mostly due to Jupiter).
-An important assumption here is that a single static map generates all of the light curves, an assumption which is violated if the surface emission changed substantially between observations. 
-For this reason we fit at most two light curves at a time relatively closely spaced in time.
+where $\mathbf{f}_\mathrm{obs}$ is the observed light curve, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbf{f}$ is predicted flux given by
+\begin{equation}
+    \mathbf{f}=\mathbf{A}'\,\mathbf{p}' +b\,\mathbf{1}_N
+    \label{eq:flux_model}
+\end{equation}
+where we have added a fixed flux offset parameter for each light curve in order to account for stray flux which cannot be attributed to Io.
+This flux is mostly due to light emitted from Jupiter.
+
+To model the data covariance $\boldsymbol{\Sigma}$ we use use a Gaussian Process and we compute the likelihood using the fast Celerite method \citep{foreman-mackey2017} as implemented in the \textsf{celerite2} package (CITE).
+We use the simple (approximate) Matern 3/2 function which is parametrized by two parameters, a standard deviation parameter $\sigma_\mathrm{GP}$ and a characteristic timescale parameter $\rho_\mathrm{GP}$.
+The kernel is given by 
+\begin{equation}
+    k(\tau)=\sigma_\mathrm{GP}^{2}\left[(1+1 / \epsilon) e^{-(1-\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}(1-1 / \epsilon) e^{-(1+\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}\right]
+\end{equation}
+where $\tau=|t_n-t_m|$ and $\epsilon$ controls the quality of the approximation.
+A single element of the data covariance matrix $\boldsymbol{\Sigma}$ is then 
+\begin{equation}
+    \boldsymbol{\Sigma}_{nm}=(K\sigma_n)^2\delta_{nm} + k(\tau\sigma_\mathrm{GP},\rho_\mathrm{GP})
+\end{equation}
+where $\sigma_n$ is the errorbar for the n-th data point and $K$ is a rescaling factor for the errorbar common to all data points in a single light curve.
+In cases where we fit multiple light curves assume independence and the total log likelihood is the product of individual likelihoods defined in Eq.~\ref{eq:likelihood}.
 
@@
         The map on the left corresponds to a model in which we directly fit for spherical harmonic coefficients $\mathbf{y}$ with a Gaussian prior.
+        Orange lines show posterior samples in data space and the residuals shown at the bottom are computed with respect to the median of those samples.
         The map in the middle corresponds to a model in which we instead fit for sphixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
@@
 
-\section{Results with simulated data}
+\section{Results for simulated data}
 \label{sec:results_sim}
 \subsection{Fitting simulated ingress/egress light curves}
-In this section we use the same map to generate the data as in Figure~\ref{fig:sphixels_vs_harmonics} except now we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
-We generate the light curves from an $l=25$ map and fit a map of the same order. 
-We apply a Gaussian smoothing filter to both the simulated map and the map we fit to the data and set the smoothing parameter to $\sigma_s=2/l=2/25$.
+\label{ssec:fitting_sim_ingress_egress}
+In this section we generalize the simulated example from Section~\ref{ssec:sphixels_vs_harmonics} to include two light curves with 150 data points each.
+The first light curve corresponds to an ingress of Io as it is disappearing behind Jupiter and the second light curve corresponds to the egress when Io reappears. 
+As before we assume that we know the ephemeris exactly.
+The simulated map consists of two spots.
+The first spot is located at $13^\circ$ N latitude and $51^\circ$ E longitude and the second spot is at $-15^\circ$ N latitude and $-40^\circ$ E longitude.
+Both have the same angular diameter of $15^\circ$.
+The amplitude of the bright spot is set to 100\% and the amplitude of the faint spot is to 20\% of the luminosity of the featureless map. 
+We generate the light curves from an $l=20$ map and fit a map of the same order and we apply a Gaussian smoothing filter to both the simulated map and the inferred map with the smoothing parameter set to $\sigma_s=2/l=2/20$.
+We assume that the phase of Io changes linearly between $10^\circ$ W and $10^\circ$ E the beginning of the ingress and the end of the egress.
 
-The prior we place on the sphixels is a sparse prior called the Regularized Horseshoe Prior (also known as the "Finnish Horseshoe") (CITE). 
-It is an improvement on the Horseshoe Prior (CITE).
-The horseshoe prior is a prior designed for use in sparse linear regression which is exactly what we are doing.
-The horseshoe prior sets a scale for each of the regression coefficients (sphixels) which is a product of a global scale $\tau$ and a local scale $\lambda_m$.
+We place a sparse prior on the sphixels called the Regularized Horseshoe prior (also known as the "Finnish Horseshoe") \citep{piironen2017}. 
+This prior is specifically designed for use in Bayesian sparse linear regression. 
+It is an improvement on the Horseshoe prior introduced in \cite{carvalho2010}.
+The idea behind the Horseshoe prior is to set the scale for each regression coefficient (sphixel) to a product of a global scale $\tau$ and a local scale $\lambda_m$ where $m$ indexes all the sphixels.
 It is defined hierarchically as 
 \begin{equation}
-\mathcal{Half}-\mathcal{C} 
+\begin{aligned}
+    &\tau  \sim \mathrm{Half}-\mathcal{C} \left(0, \tau_{0}\right)\\
+    &\lambda_{m}  \sim \mathrm{Half}-\mathcal{C} (0,1) \\
+    &p_{m}  \sim \mathcal{N}\left(0, \tau \lambda_{m}\right) 
+\end{aligned}
+    \label{eq:horseshoe}
 \end{equation}
+where $p_m$ are the sphixels.
+Each local scale parameter is drawn from a unit scale heavy tailed Half Cauchy distribution which allows for very large values of the sphixels.
+The global scale parameter is also a free parameter, drawn from a Half Cauchy distribution with the scale equal to $\tau_0$.
+The Horseshoe prior is closely related to the spike-and-slab prior which is is a mixture between a delta function prior at zero (\emph{spike}) and some other prior elsewhere (\emph{slab}).
+
+The Regularized Horseshoe prior adds another level to Eq.~\ref{eq:horseshoe} to allow fine tuned control of sparsity and to regularize very large values of coefficients in cases where the data is only weakly constraining.
+\cite{piironen2017} show that the Regularized Horseshoe prior can be considered as a continuous counterpart of the spike-and-slab prior with a finite slab width $c$ whereas the Horseshoe prior resembles a spike-and-slab prior with a slab of infinite width.
+The Regularized Horseshoe is defined by
 \begin{equation}
 \begin{aligned}
-\beta_{m} & \sim \mathcal{N}\left(0, \tau \cdot \lambda_{m}\right) \\
-    \lambda_{m} & \sim \mathcal{Half}-\mathcal{C} (0,1) \\
-    \tau & \sim \mathcal{Half-C} \left(0, \tau_{0}\right)
+    &\tau  \sim \mathrm{Half}-\mathcal{C}\left(0, \tau_{0}\right)\\
+    &c^{2}  \sim \mathrm{Inv}-\mathcal{G}\left(\frac{\nu}{2}, \frac{\nu}{2} s^{2}\right) \\
+    &\overline{\lambda}_{m}  \sim \mathrm{Half}-\mathcal{C}(0,1) \\
+    &\lambda_{m} =\frac{c \overline{\lambda}_{m}}{\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{m}^{2}}} \\
+    &p_{m}  \sim \mathcal{N}^+\left(0, \tau \lambda_{m}\right) 
 \end{aligned}
+    \label{eq:reg_horseshoe}
 \end{equation}
-where $\tau_0$ is a characteristic global scale.
+Integrating out the slab scale $c$ implies a marginal $\mathrm{Student}-\mathit{t}\,(\nu,0,s)$ prior for sphixels far from zero.
+When sphixels $p_m$ are close to zero ($\tau^2\overline{\lambda}_m^2\ll c^2$) we have $\lambda_m^2\rightarrow\overline{\lambda}_m^2$ and the prior approaches the original Horseshoe.
+When sphixels are far from zero ($\tau^2\overline{\lambda}_m^2\gg c^2$) then $\lambda_m^2\rightarrow c^2/\tau^2$ and the prior approaches $\mathcal{N}(0, c)$.
 
-The regularized horseshoe prior is 
+For setting the scale parameter $\tau_0$ for the prior on the global scale $\tau$, \cite{piironen2017} suggest the following expression
+\begin{equation}
+    \tau_0=\frac{p_0}{D-p_0}\frac{\sigma}{\sqrt{n}}
+    \label{eq:horseshoe_tau0}
+\end{equation}
+where $p_0$ is our prior guess for the number of significant (sphixels) which are sufficiently far above zero, $D$ is the total number of sphixels, $n$ is the number of data points and $\sigma$ is the standard deviation of the data points (the errobars).
+Thus, we only need to specify $p_0$, the degree of freedom parameter $\nu$ and the slab width $c$.
+
+When using the Regularized Horseshoe prior in a small data regime it is often necessary to use the non-centered parametrization to avoid funnels in the posterior which are often present in hierarchical models.
+The purpose of this reparametrization is to reduce the dependence between the hyperparameters in the posterior.
+To implement the non-centered parametrization we replace priors in Equation~\ref{eq:reg_horseshoe} with zero mean and unit variance priors and rescale them with deterministic transforms as follows
 \begin{equation}
 \begin{aligned}
-\beta_{m} & \sim \mathcal{N}\left(0, \tau \cdot \lambda_{m}\right) \\
-\tilde{\lambda}_{m} &=\frac{c \lambda_{m}}{\sqrt{c^{2}+\tau^{2} \lambda_{m}^{2}}} \\
-\lambda_{m} & \sim \mathcal{Half-C}(0,1) \\
-c^{2} & \sim \mathcal{Inv-G}\left(\frac{\nu}{2}, \frac{\nu}{2} s^{2}\right) \\
-\tau & \sim \mathcal{Half-C}\left(0, \tau_{0}\right)
+    &\overline{\tau} \sim \mathrm{Half}-\mathcal{C}\left(0, 1\right)\\
+    &\overline{c^{2}}  \sim \mathrm{Inv}-\mathcal{G}\left(\frac{\nu}{2}, 1\right) \\
+    &\overline{\lambda}_{m}  \sim \mathrm{Half}-\mathcal{C}(0,1) \\
+    &\overline{p}_{m}  \sim \mathcal{N}^+\left(0, 1\right)\\
+    &\tau=\tau_0\overline{\tau}\\
+    &c^2=\frac{\nu}{2}s^2\,\overline{c^2}\\
+    &\lambda_{m} =\frac{c \overline{\lambda}_{m}}{\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{m}^{2}}} \\
+    &p_m = \tau\lambda_m\,\overline{p}_m
 \end{aligned}
+    \label{eq:reg_horseshoe_noncentered}
 \end{equation}
+We find that without using the non-centered parametrization the sampling is problematic and there are lots of divergences in the gradients of the parameters, with the non-centered parametrization there are no problems with sampling.
 
-The results are shown in Figure~\ref{fig:ingress_egress_simulated}.
+To fully specify the prior, we set $p_0$ to 80\% of the total number of sphixels, $\nu=4$ and $c=10$. 
+We fit the model with NUTS with 500 warm-up steps and 1500 final steps. 
+The results for a light curve with SNR=50 are shown in Fig.~\ref{fig:ingress_egress_sim_snr_50} and the light curve with SNR=10 are shown in Fig.~\ref{fig:ingress_egress_sim_snr_10}.
+For both light curves we recover the locations of the two spots to a high accuracy. 
+The inferred bright spot is nearly indistinguishable from the true spot, the fainter spot is somewhat less well constrained but the error in position for both is at most a few degrees.
+Rinding artefacts are minimal because we of the smoothing filter.
+There are no discernible patterns in the residuals with respect to the median model in data space. 
+We found that with priors other than the Horseshoe class priors the model was not able to capture the first step in the light curve which is due to the fainter spot coming in our out of view, it would only recover the brighter spot.
+In Fig.~\ref{fig:ingress_egress_sim_snr_10} we show the output of the same model except assuming we have data of worse quality with SNR=10. 
+Despite the increased white noise the inferred map does not look substantially different from the one shown in Fig.~\ref{fig:ingress_egress_sim_snr_50}.
+
 \begin{figure}[h!]
@@
     \oscaption{ingress_egress_sim_snr_50}{%
-Maximum A Posteriori (MAP) estimate of an $l=25$ map (right) produced by fitting a pair of simulated ingress and egress occultation light curves (bottom) which were generated from a $l=25$ map consisting of a single bright spot (left).
-       A Gaussian smoothing filter is applied to reduce the ringing artefacts.
-       Small circles beneath each inferred map show the progression of the occultation.
-        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:sphixels_vs_harmonics}.
+        Median estimate of an $l=20$ map (middle panel) inferred by fitting a pair of simulated ingress/egress occultation light curves of Io assuming SNR=50.
+        The simulated map has the same degree as the inferred map and it consists of two hot spots.
+The small circles beneath the inferred map show the progression of the occultation. 
+        Orange lines show posterior samples in data space and the residuals shown at the bottom are computed with respect to the median of those samples.
+With the Regularized Horseshoe prior placed on sphixels, the model is able to recover the locations of both hot spots using only two light curves.
        \label{fig:ingress_egress_sim_snr_50}
@@
     \oscaption{ingress_egress_sim_snr_10}{%
-Maximum A Posteriori (MAP) estimate of an $l=25$ map (right) produced by fitting a pair of simulated ingress and egress occultation light curves (bottom) which were generated from a $l=25$ map consisting of a single bright spot (left).
-       A Gaussian smoothing filter is applied to reduce the ringing artefacts.
-       Small circles beneath each inferred map show the progression of the occultation.
-        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:sphixels_vs_harmonics}.
+        Same as Fig.~\ref{fig:ingress_egress_sim_snr_50} except for light curves with SNR=10.
        \label{fig:ingress_egress_sim_snr_10}
@@
 
-The inferred map looks significantly better than the one in Figure~\ref{fig:sphixels_vs_harmonics}. 
-With two occultation light curves the model is able to break the degeneracy in the location of the spot and thanks to the smoothing filter there is almost no visible ringing around the spot in the inferred map.
-Some residuals in the data are still present (WHY).
+\subsection{Comparison to a parametric model}
+It is instructive to compare the model developed in the previous section to a parametric model in which we assume that the map contains some fixed number of spot and we fit for the positions, amplitudes and the sizes of the spots.
+A parametrized spot model might be useful if we want to fit for a small number of spots and we know what the map should look like.
+To test how the parametrized spot model compares to the model defined in Section~\ref{ssec:fitting_sim_ingress_egress} we fit it to the light curves shown in Figure~\ref{fig:ingress_egress_sim_snr_50}.
+We then fit a model consisting of 5 parameters: the latitude, longitude, amplitude and size of the spot.
+We place uniform priors on the angles and positive Gaussian priors on other parameters.
 
-\subsection{Comparison to a parametric model}
+We find that if the number of modeled spots matches the number of true spots the model easily converges to the true solution. 
+If the number of modeled spots is larger or smaller than the true number the model does not converge due to pathologies in the posterior distribution.
+To summarize, although a parametric approach likely would have been sufficient for modeling the light curves shown in this work, it won't work well when the number is unknown or if the features aren't spots and there is no need to restrict ourselves to a parametric model where the sphixel model gives the same results with fewer assumptions about the surface.
+The computational advantages of the parametric spot model relative to the sphixel model are minimal. 
+Even though the spot model has only 5 parameters per spot and the sphixel model has thousands of parameters, the runtime for the sphixel model is only longer by a factor of a few.
+(TODO: add more details to this section).
 
-\section{Results with IRTF data}
+\section{Results for IRTF data}
 \label{sec:results}
+\subsection{1998 pair of occultations by Jupiter}
+Having demonstrated that our model works well on simulated data, int this section we use it to fit IRTF light curves of actual occultations of Io.
+Out of all the IRTF occultation light curves of Io by Jupiter, we choose two pairs of high quality ingress/egress light curves closely spaced in time so that that we can assume that the surface emission does not change substantially between the ingress and the egress occultation.
+We fit a pair of events from 1998, an ingress occultation observed on the 27th of August and an egress occultation observed on the 29th of November.
+For comparison, we also fit a pair of events from 2017, an ingress occultation observed on the 31st of March and an egress occultation observed on the 11th of May.
+
+We assume the same map for both the ingress and the egress light curve except for  a difference in the overall amplitude.
+The predicted fluxes are then:
+\begin{align}
+    \mathbf{f}_I&=\mathbf{A}_I'\,\mathbf{p}_I' +b_I\,\mathbf{1}_{N_I}\\
+    \mathbf{f}_E&=\mathbf{A}_E'\,\mathbf{p}_E' +b_E\,\mathbf{1}_{N_E}
+\end{align}
+where $\mathbf{f}_I$ is the predicted flux for the ingress light curve and $\mathbf{f}_E$ is the predicted flux for the egress light curve.
+Since we assume that the map is the same for both light curves up to an overall amplitude difference, we have
+\begin{equation}
+    \mathbf{p}'_E=a\,\mathbf{p}'_I
+\end{equation}
+where $a$ is the relative difference in amplitude.
+The log likelihood is the sum of the log likelihoods for individual light curves (Eq.~\ref{eq:likelihood}).
+We list all model parameters and their associated priors in Table~\ref{tab:priors}.
+\begin{table}
+\centering
+\begin{tabular}{l l l}
+    \hline
+Parameter & Description & Prior\\
+ \hline
+    $\tau$ & Global sphixel scale &  \begin{minipage}{0.5\textwidth}  \shortstack[l]{$\mathrm{Half}-\mathcal{C}(0,\tau_0)$, $\tau_0$ defined by Eq.~\ref{eq:horseshoe_tau0} \\with $p_0=0.8D$}\end{minipage}\\
+ $c^2$ & Slab scale squared & $\mathrm{Inv}-\mathcal{G}(2,2s^2)$, $s=10$\\
+    $\overline{\lambda}_m$  & Local sphixel scale & $\mathrm{Half}-\mathcal{C}(0,1)$\\
+    $p_m$ & Sphixels & $\mathcal{N}^+(0, \tau\lambda_m)$, $\lambda_{m} =c \overline{\lambda}_{m}/\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{m}^{2}}$\\
+    $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{Relative change in \\map amplitude}\end{minipage}& $\mathcal{N}(1, 0.1)$\\
+    $b_I$, $b_E$& Flux offset &$\mathcal{N}(0, 4)$\\
+    $K_I$, $K_E$& Errorbar rescaling factor&$\mathcal{N}(1,0.05)$\\
+    $\sigma_{\mathrm{GP},I}$, $\sigma_{\mathrm{GP},E}$ & GP standard deviation&$\mathcal{N}^+(0,0.1\sigma)$\\
+    $\rho_{\mathrm{GP},I}$, $\rho_{\mathrm{GP},E}$ & GP timescale  &  \begin{minipage}{0.5\textwidth}  \ \shortstack[l]{ \\$\mathrm{Inv}-\mathcal{G}(\alpha,\beta)$  with $\alpha$ and $\beta$ defined such that \\ $P(\rho_\mathrm{GP}<\Delta t_\mathrm{min})=P(\rho_\mathrm{GP}>(t_\mathrm{max}-t_\mathrm{min}))=0.01$}\end{minipage}
+\end{tabular}
+\caption{Parameters and priors for the final model. 
+    The subscript $I$ denotes parameters associated with the ingress light curve while the subscript $E$ denotes parameters associated with the egress light curve.
+    $\Delta t_\mathrm{min}$ is the minimum time between two consecutive data points in the ingress (egress) light curve and $(t_\mathrm{max}-t_\mathrm{min})$ is the duration of the ingress (egress) occultation.}
+    \label{tab:priors}
+\end{table}
+One of the more important priors is the prior on the characteristic timescale of the Matern 3/2 kernel for the Gaussian Process. 
+We choose an Inverse Gamma prior for this parameter with the parameters $\alpha$ and $\beta$ chosen such that 1\% of the probability is assigned to timescales smaller than the median spacing between the data points in the light curve  on the left tail of the distribution and 1\% of probability on the right tail is assigned for timescales longer than the duration of the occultation.
+The purpose of this prior is to suppress the timescales for which the data provide much information\footnote{ \url{https://betanalpha.github.io/assets/case_studies/gaussian_processes.html}}.
+
+We run the MCMC for 500 warm-up steps and 2000 final steps, monitoring divergences and R-hat.
+The inferred map for the 1998 pair of events is shown in Figure~\ref{fig:irtf_ingress_egress_1998}.
+Selected inferred parameters parameters are shown in Table~\ref{tab:1998_parameters}. 
+The inferred map has two distinct hot spots, a bright hotspot and a faint hotspot.
+The orange lines in the second subplot from the bottom are posterior samples for the physical model in data space (not including the effects of the GP).
+The bottom panel shows the residuals with respect to the physical model and the posterior GP predictions.
+
+Most of the wiggles in the residuals are either due to surface emission features which were not accounted for by the model or due to atmospheric variability.
+The most notable feature in the residuals is visible at around 3.3 minutes in the ingress light curve and 3.6 minutes in the egress light curve when the bright spot comes in and out of view. 
+This feature is present because our model is limited in resolution so the inferred spot size is not small enough to explain the rapid change in flux seen in the data.
+The GP accounts for all three types of features - the model atmospheric variability, the emission due to surface features which are too faint to be well constrained by the physical model and the limitation of the physical model to capture the true size of the spot.
+Although the GP could easily account for the small dip in both light curves due to the faint hot spot, it does not too that because the physical model provides a better explanation for the data (TODO: formalize this argument).
+Thus there is a trade-off between the explanatory power of the noise model and the physical model.
+
+To obtain the inferred location of the hot spots we optimize for the location of maximum intensity in the spot for each posterior map. 
+The location of the bright hotspot is $16.295_{-0.009}^{0.009}$$^\circ$ N latitude and $53.098_{-0.004}^{0.006}$$^\circ$ E longitude which corresponds to the location of Loki Patera.
+Figure~\ref{fig:irtf_ingress_egress_loki} shows the hotspot overlaid on top overlaid on top of the U.S.
+Geological Survey's map of the surface of Io (CITE) which was constructed from Galileo observations.
+The faint hot spot is at $-11{-0.0}^{0.0}$$^\circ$ N latitude and $323_{-0.0}^{0.0}$$^\circ$ E longitude (TODO: input exact location) which is most likely Kanehekili (TODO: CITE, check if this is true).
 
@@
     \oscaption{irtf_ingress_egress_1998}{%
-        Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
-       The small circles beneath each inferred map show the progression of the occultation.
-        Both light curves are assumed to be generated from the same map except for a difference in the overall amplitude.
-        We allow for multiplicative rescaling of the error bars and an additive flux offset for each light curve.
-        The model places a single bright spot to explain most of the variance in the data.
-        The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
+    Median estimates of two $l=20$ maps (top panel) inferred by fitting a pair of observations of occultations of Io by Jupiter from 1998.  
+        The map and light curve correspond to the ingress event and the ones on the right are the egress event. 
+        The two maps are (by construction) the same except for a difference in the overall amplitude. 
+        The observations were taken using the IRTF telescope in the NIR filter (TODO: which filter).
+The small circles beneath the inferred map show the progression of the occultation. 
+        Orange lines show posterior samples from the physical model (excluding the Gaussian Process).
+        The residuals (bottom) are computed with respect the median prediction from the physical model and the Gaussian Process predictions are shown on the same plot.
+The inferred map shows two hotspots, the bright hot spot is emission due to Loki and the faint hot spot is Kanehekili.
      \label{fig:irtf_ingress_egress_1998}
@@
 
+\begin{table}
+    \centering
+\begin{tabular}{l l l}
+    \hline
+    Parameter & Value & Unit\\
+ \hline
+ $\tau$ &  & \\
+    $c^2$ & &\\
+    $p_m$ & &\\
+    $a$ & &\\
+    $b_I$ & &\\
+    $b_E$ & &\\
+    $K_I$ & & \\
+    $K_E$ & &\\
+    $\sigma_{\mathrm{GP},I}$ && \\
+    $\sigma_{\mathrm{GP},E}$ & &\\
+    $\rho_{\mathrm{GP},I}$ & &\\
+    $\rho_{\mathrm{GP},E}$ &&  
+\end{tabular}
+    \caption{Inferred model parameters for the pair of occultations from 1998.}
+    \label{tab:1998_parameters}
+\end{table}
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=.5\linewidth]{figures/irtf_spot_overlay_1998.pdf}
+    \oscaption{irtf_ingress_egress_loki}{%
+        Zoom in on the bright hot spot from Figure~\ref{fig:irtf_ingress_egress_1998} overlaid on top of the U.S.
+Geological Survey's map of the surface of Io (CITE) which was        constructed from Galileo observations.
+        The location of the hot spots matches the location of Loki Patera, the largest active volcano on the surface of Io. 
+        \label{fig:irtf_ingress_egress_loki}
+    }
+    \end{centering}
+\end{figure}
+
+\subsection{2017 pair of occultations by Jupiter}
+
 \begin{figure}[ht!]
@@
     \oscaption{irtf_ingress_egress_2017}{%
-        Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
-       The small circles beneath each inferred map show the progression of the occultation.
-        Both light curves are assumed to be generated from the same map except for a difference in the overall amplitude.
-        We allow for multiplicative rescaling of the error bars and an additive flux offset for each light curve.
-        The model places a single bright spot to explain most of the variance in the data.
-        The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
                 \label{fig:irtf_ingress_egress_2017}
@@
 
-\begin{figure}[ht!]
-    \begin{centering}
-    \includegraphics[width=.5\linewidth]{figures/irtf_spot_overlay_1998.pdf}
-    \oscaption{irtf_ingress_egress_loki}{%
-        Hot spot from the inferred maps shown in Figure~\ref{fig:irtf_ingress_egress} overlaid on top of the U.S. Geological Survey's map of the surface of Io (CITE) which was
-        constructed from Galileo observations.
-        The location of the hot spots matches the location of Loki Patera, the largest active volcano on the surface of Io. 
-        \label{fig:irtf_ingress_egress_loki}
-    }
-    \end{centering}
-\end{figure}
+\subsection{What happens if we don't include the Gaussian Process?}
 

### 2021-02-06 volcano/utils.py
minor

@@ -431,7 +431,12 @@ def get_occultation_latitude(x_io, y_io, re):
 
 
 def get_occultor_position_and_radius(
-    eph_occulted, eph_occultor, occultor_is_jupiter=False, **kwargs
+    eph_occulted,
+    eph_occultor,
+    occultor_is_jupiter=False,
+    rotate=True,
+    return_occ_lat=False,
+    **kwargs
 ):
     """
     Given the ephemeris of an occulted object and an occultor, the function
@@ -445,20 +450,26 @@ def get_occultor_position_and_radius(
         eph_occulted (astropy.timeseries.TimeSeries): ephemeris of the occulted
             body.
         eph_occultor (astropy.timeseries.TimeSeries): ephemeris of the occultor.
+        occultor_is_jupiter (bool): Set to true if occultor is Jupiter because
+            Jupiter is non-spherical and its radius needs to be estimated in a
+            different way. Defaults to False.
+        rotate (bool): Rotate the position vectors to a frame in which the
+            obliquity of the occultor is zero. Defaults to True.
+        return_occ_lat (bool): Optionally return the occultation latitude if
+            the occultor is Jupiter. Defaults to False.
 
     Returns:
-        list: (xo, yo, zo, ro)
+        list: (xo, yo, ro)
     """
     delta_ra = (eph_occultor["RA"] - eph_occulted["RA"]).to(u.arcsec)
     delta_dec = (eph_occultor["DEC"] - eph_occulted["DEC"]).to(u.arcsec)
 
-    xo_ = (
+    xo = (
         -delta_ra
         * np.cos(eph_occultor["DEC"].to(u.rad))
         / (0.5 * eph_occulted["ang_width"].to(u.arcsec))
-    )
-    yo = delta_dec / (0.5 * eph_occulted["ang_width"].to(u.arcsec))
-    zo = np.ones(len(yo))
+    ).value
+    yo = delta_dec / (0.5 * eph_occulted["ang_width"].to(u.arcsec)).value
 
     if occultor_is_jupiter is False:
         # Convert everything to units where the radius of Io = 1
@@ -473,18 +484,17 @@ def get_occultor_position_and_radius(
         r_io = 1821.3 * u.km  # radius of Io (km)
         jup_dist = eph_occultor["dist"].to(u.km)
 
-        xo_ = (
+        xo = (
             ((-delta_ra * np.cos(eph_occultor["DEC"].to(u.rad)))).to(u.rad)
             * jup_dist
[…]

### 2021-02-08 paper/figures/irtf_dataset.py
minor changes to plots

@@ -1,4 +1,3 @@
-#!/usr/bin/env python
 import os
 import pickle as pkl
 
@@ -6,7 +5,6 @@ import numpy as np
 from astropy.table import vstack
 from matplotlib import pyplot as plt
 from matplotlib.ticker import MaxNLocator
-from volcano.utils import get_body_ephemeris
 
 np.random.seed(42)
 
@@ -32,12 +30,13 @@ max_f = np.array([np.sort(lcs[i]["flux"].value)[-2] for i in range(len(lcs))])
 yr = np.array([lc.time.decimalyear[0] for lc in lcs])
 idx_sorted = np.argsort(yr)
 
-fig, ax = plt.subplots(figsize=(6, 2))
+fig, ax = plt.subplots(figsize=(6, 3))
 ax.plot(yr[idx_sorted], max_f[idx_sorted], "k.", alpha=0.6)
 ax.set_ylabel("Maximum flux\n [GW/um/sr]")
 ax.set_xlabel("Time [years]")
 ax.set_xticks(np.arange(1996, 2024, 4))
 ax.set_yticks(np.arange(0, 250, 50))
+ax.grid()
 plt.savefig("irtf_max_flux.pdf", bbox_inches="tight", dpi=500)
 
 # Plot a few example light curves
@@ -58,5 +57,5 @@ for a, idx in zip(ax.flatten(), idcs):
     a.set_ylim(bottom=0)
 
 fig.text(0.5, 0.01, "Duration [minutes]", ha="center")
-fig.text(0.0, 0.5, "Flux [GW/um/sr]", va="center", rotation="vertical")
+fig.text(-0.03, 0.5, "Flux [GW/um/sr]", va="center", rotation="vertical")
 plt.savefig("irtf_sample_lightcurves.pdf", bbox_inches="tight", dpi=500)

### 2021-02-08 paper/figures/irtf_main_plots.py
Updating plots

@@ -1,6 +1,5 @@
 import numpy as np
 from matplotlib import pyplot as plt
-from PIL import Image
 import pickle as pkl
 
 import starry
@@ -9,36 +8,16 @@ from celerite2.jax import terms as jax_terms
 from celerite2 import terms, GaussianProcess
 from exoplanet.distributions import estimate_inverse_gamma_parameters
 
-from astropy import units as u
-from astropy.table import Table
-from astropy.time import Time
-from astropy.timeseries import TimeSeries
-
 from matplotlib import colors
 import matplotlib.gridspec as gridspec
 from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+from matplotlib.lines import Line2D
+import seaborn as sns
 
 from volcano.utils import *
 
 np.random.seed(42)
 starry.config.lazy = False
-
-
-def get_pos_rot(eph_io, eph_jup, method=""):
-    # Get occultor position
-    obl = eph_io["obl"]
-    inc = np.mean(eph_jup["inc"])
-    theta = np.array(eph_io["theta"])
-
-    xo_unrot, yo_unrot, zo, ro = get_occultor_position_and_radius(
-        eph_io, eph_jup, occultor_is_jupiter=True, method=method
-    )
-
-    # Rotate to coordinate system where the obliquity of Io is 0
-    theta_rot = -obl.to(u.rad)
-    xo_rot, yo_rot = rotate_vectors(xo_unrot, yo_unrot, theta_rot)
-
-    return xo_rot, yo_rot, ro
 
 
 def make_plots(
@@ -50,6 +29,8 @@ def make_plots(
     xticks_in,
     xticks_eg,
     res_yticks,
+    res_ylim,
+    gp=True,
     cmap_norm=colors.Normalize(vmin=0.0, vmax=1500),
 ):
     #  Compute epheremis
@@ -85,8 +66,12 @@ def make_plots(
     f_obs = np.concatenate([f_obs_in, f_obs_eg])
     f_err = np.concatenate([f_err_in, f_err_eg])
 
-    xo_in, yo_in, ro_in = get_pos_rot(eph_io_in, eph_jup_in)
-    xo_eg, yo_eg, ro_eg = get_pos_rot(eph_io_eg, eph_jup_eg)
+    xo_in, yo_in, ro_in = get_occultor_position_and_radius(
+        eph_io_in, eph_jup_in, occultor_is_jupiter=True
+    )
+    xo_eg, yo_eg, ro_eg = get_occultor_position_and_radius(
[…]

### 2021-02-08 paper/figures/irtf_spots_plots.py

@@ -1,0 +1,304 @@
+import numpy as np
+from matplotlib import pyplot as plt
+from PIL import Image
+import pickle as pkl
+
+import starry
+
+from matplotlib import colors
+import matplotlib.gridspec as gridspec
+from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+from matplotlib.lines import Line2D
+
+from scipy.integrate import dblquad
+
+from volcano.utils import get_median_map
+
+np.random.seed(42)
+starry.config.lazy = False
+
+
+def integrand(theta, phi, map):
+    lat = theta * 180 / np.pi - 90
+    lon = phi * 180 / np.pi
+
+    return map.intensity(lat=lat, lon=lon) * np.sin(theta)
+
+
+def get_power_emitted(map, lat_range, lon_range):
+    phi_min = lon_range[0] * np.pi / 180
+    phi_max = lon_range[1] * np.pi / 180
+    theta_min = lat_range[0] * np.pi / 180 + np.pi / 2
+    theta_max = lat_range[1] * np.pi / 180 + np.pi / 2
+
+    res, _ = dblquad(
+        integrand,
+        phi_min,
+        phi_max,
+        lambda x: theta_min,
+        lambda x: theta_max,
+        epsabs=1e-4,
+        epsrel=1e-4,
+        args=(map,),
+    )
+    return res
+
+
+def find_centroid(lats, lons, img, bounds):
+    mask_lat = np.logical_and(lats > bounds[0][0], lats < bounds[0][1])
+    mask_lon = np.logical_and(lons > bounds[1][0], lons < bounds[1][1])
+
+    img_bounded = img[mask_lat][:, mask_lon]
+
+    I_min = np.nanpercentile(img_bounded, [90])
+    mask = img_bounded > I_min
+
+    lon_grid, lat_grid = np.meshgrid(lons[mask_lon], lats[mask_lat])
+    return np.mean(lon_grid[mask]), np.mean(lat_grid[mask])
+
+
+def get_spot_position_and_power(samples, bounds=None, nsamples=100):
+    """
+    For each sample find local maximum to get spot position,
+    then compute emitted power from the spot.
+    """
+    lat_list = []
+    lon_list = []
+    power_list_in = []
+    power_list_eg = []
+
[…]

### 2021-02-08 paper/figures/pixels_vs_harmonics.py

@@ -1,24 +1,11 @@
 import numpy as np
+import os
+import sys
+
 from matplotlib import pyplot as plt
-
-import theano
-import theano.tensor as tt
-import pymc3 as pm
-import starry
-import exoplanet as xo
-
 from matplotlib import colors
 import matplotlib.gridspec as gridspec
 from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
-
-from volcano.utils import *
-
-np.random.seed(42)
-starry.config.lazy = True
-
-import numpy as np
-import os
-import sys
 
 import starry
 import jax.numpy as jnp
@@ -27,16 +14,39 @@ import numpyro
 import numpyro.distributions as dist
 from numpyro.infer import *
 
+from volcano.utils import get_smoothing_filter
+
 numpyro.enable_x64()
-
-from matplotlib import colors
-import matplotlib.gridspec as gridspec
-from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
-
-from volcano.utils import *
 
 np.random.seed(42)
 starry.config.lazy = True
+
+
+def get_median_map(
+    ydeg_inf,
+    samples,
+    projection="Mollweide",
+    inc=90,
+    theta=0.0,
+    nsamples=20,
+    resol=300,
+):
+    imgs = []
+    map = starry.Map(ydeg=ydeg_inf)
+    map.inc = inc
+
+    for n in np.random.randint(0, len(samples), 10):
+        x = samples[n]
+        map.amp = x[0]
+        map[1:, :] = x[1:] / map.amp
+
+        if projection == "Mollweide":
+            im = map.render(projection="Mollweide", res=resol).eval()
+        else:
+            im = map.render(theta=theta, res=resol).eval()
+        imgs.append(im)
+
+    return np.median(imgs, axis=0)
 
 
 # Set up mock map
@@ -92,7 +102,8 @@ A_dense = jnp.array(map.design_matrix(xo=xo_dense, yo=yo_dense, ro=ro).eval())
 
 def model_ylm():
     y1 = numpyro.sample(
-        "y1", dist.Normal(jnp.zeros(ncoeff - 1), 1e-01 * jnp.ones(ncoeff - 1))
+        "y1",
[…]

### 2021-02-08 paper/figures/scripts/irtf_fit.py

@@ -3,20 +3,15 @@ import pickle as pkl
 
 import starry
 import jax.numpy as jnp
-from jax import random, jit, vmap, lax
+from jax import random
 import numpyro
 import numpyro.distributions as dist
-from numpyro.diagnostics import print_summary
 from numpyro.infer import *
 
 import celerite2.jax
 from celerite2.jax import terms as jax_terms
 from celerite2 import terms, GaussianProcess
 from exoplanet.distributions import estimate_inverse_gamma_parameters
-
-from astropy import units as u
-from astropy.table import Table
-from astropy.timeseries import TimeSeries
 
 from volcano.utils import *
 
@@ -59,28 +54,25 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
     f_obs = np.concatenate([f_obs_in, f_obs_eg])
     f_err = np.concatenate([f_err_in, f_err_eg])
 
-    def get_pos_rot(eph_io, eph_jup, method=""):
-        """
-        Get sky position of Io relative to Jupiter rotated such that the
-        obliquity of Jupiter is zero.
-        """
-        # Get occultor position
-        obl = eph_io["obl"]
-        inc = np.mean(eph_jup["inc"])
-        theta = np.array(eph_io["theta"])
+    (xo_in, yo_in, ro_in, occ_lat_in,) = get_occultor_position_and_radius(
+        eph_io_in,
+        eph_jup_in,
+        occultor_is_jupiter=True,
+        rotate=True,
+        return_occ_lat=True,
+    )
+    (xo_eg, yo_eg, ro_eg, occ_lat_eg,) = get_occultor_position_and_radius(
+        eph_io_eg,
+        eph_jup_eg,
+        occultor_is_jupiter=True,
+        rotate=True,
+        return_occ_lat=True,
+    )
 
-        xo_unrot, yo_unrot, zo, ro = get_occultor_position_and_radius(
-            eph_io, eph_jup, occultor_is_jupiter=True, method=method
-        )
-
-        # Rotate to coordinate system where the obliquity of Io is 0
-        theta_rot = -obl.to(u.rad)
-        xo_rot, yo_rot = rotate_vectors(xo_unrot, yo_unrot, theta_rot)
-
-        return xo_rot, yo_rot, ro
-
-    xo_in, yo_in, ro_in = get_pos_rot(eph_io_in, eph_jup_in)
[…]

### 2021-02-08 paper/figures/scripts/irtf_fit_no_GP.py

@@ -1,0 +1,250 @@
+import numpy as np
+import pickle as pkl
+
+import starry
+import jax.numpy as jnp
+from jax import random
+import numpyro
+import numpyro.distributions as dist
+from numpyro.infer import *
+
+from volcano.utils import *
+
+np.random.seed(42)
+starry.config.lazy = False
+numpyro.enable_x64()
+
+
+def fit_model(ydeg_inf, lc_in, lc_eg):
+    # Compute ephemeris
+    eph_list_io = []
+    eph_list_jup = []
+
+    for lc in (lc_in, lc_eg):
+        times = lc.time
+
+        eph_io = get_body_ephemeris(
+            times, body_id="501", step="1m", return_orientation=True
+        )
+        eph_jup = get_body_ephemeris(
+            times, body_id="599", step="1m", return_orientation=True
+        )
+
+        eph_list_io.append(eph_io)
+        eph_list_jup.append(eph_jup)
+
+    eph_io_in = eph_list_io[0]
+    eph_jup_in = eph_list_jup[0]
+    eph_io_eg = eph_list_io[1]
+    eph_jup_eg = eph_list_jup[1]
+
+    t_in = (lc_in.time.mjd - lc_in.time.mjd[0]) * 24 * 60
+    t_eg = (lc_eg.time.mjd - lc_eg.time.mjd[0]) * 24 * 60
+
+    f_obs_in = lc_in["flux"].value
+    f_err_in = lc_in["flux_err"].value
+    f_obs_eg = lc_eg["flux"].value
+    f_err_eg = lc_eg["flux_err"].value
+
+    f_obs = np.concatenate([f_obs_in, f_obs_eg])
+    f_err = np.concatenate([f_err_in, f_err_eg])
+
+    xo_in, yo_in, ro_in = get_occultor_position_and_radius(
+        eph_io_in, eph_jup_in, occultor_is_jupiter=True
+    )
+    xo_eg, yo_eg, ro_eg = get_occultor_position_and_radius(
+        eph_io_eg, eph_jup_eg, occultor_is_jupiter=True
+    )
+
+    # Phase
+    theta_in = eph_io_in["theta"].value
+    theta_eg = eph_io_eg["theta"].value
+
+    # Fit single map model with different map amplitudes for ingress and egress
+    map = starry.Map(ydeg_inf)
[…]

### 2021-02-08 paper/figures/simulated_ingress_egress.py

@@ -115,13 +115,11 @@ def model(f_obs_in, f_obs_eg, f_err_in, f_err_eg):
     beta_raw = numpyro.sample("beta_raw", dist.HalfNormal(1.0).expand([D]))
     lamda_raw = numpyro.sample("lamda_raw", dist.HalfCauchy(1.0).expand([D]))
     tau_raw = numpyro.sample("tau_raw", dist.HalfCauchy(1.0))
-    c2_raw = numpyro.sample(
-        "c2_raw", dist.InverseGamma(0.5 * slab_df, 1.)
-    )
+    c2_raw = numpyro.sample("c2_raw", dist.InverseGamma(0.5 * slab_df, 1.0))
 
     # Do the shifting/stretching
     tau = numpyro.deterministic("tau", tau_raw * tau0)
-    c2 = numpyro.deterministic("c2", 0.5 * slab_df*slab_scale ** 2 * c2_raw)
+    c2 = numpyro.deterministic("c2", 0.5 * slab_df * slab_scale ** 2 * c2_raw)
     lamda_tilde = numpyro.deterministic(
         "lamda_tilde",
         jnp.sqrt(c2) * lamda_raw / jnp.sqrt(c2 + tau ** 2 * lamda_raw ** 2),
@@ -260,7 +258,8 @@ def plot(
 
     # Set up the plot
     nim = 7
-    cmap_norm = colors.Normalize(vmin=-0.5, vmax=800)
+    cmap_norm = colors.Normalize(vmin=-0.5, vmax=300)
+    cmap = "Oranges"
     resol = 300
 
     # True and inferred maps
@@ -321,6 +320,7 @@ def plot(
         norm=cmap_norm,
         colorbar=True,
         res=resol,
+        cmap=cmap,
     )
     ax_true_map.set_title("True map")
 
@@ -331,6 +331,7 @@ def plot(
         projection="Mollweide",
         norm=cmap_norm,
         colorbar=True,
+        cmap=cmap,
     )
     ax_inf_map.set_title("Inferred map")
 
@@ -357,11 +358,19 @@ def plot(
             # Show the image
             if j == 0:
                 map.show(
-                    image=median_map_in, ax=a[n], grid=False, norm=cmap_norm
+                    image=median_map_in,
+                    ax=a[n],
+                    grid=False,
+                    norm=cmap_norm,
+                    cmap=cmap,
                 )
             else:
                 map.show(
[…]

### 2021-02-08 paper/figures/sphixels_to_pixels.py

@@ -110,6 +110,7 @@ fig.subplots_adjust(wspace=0.1, top=0.5)
 
 vmax = np.max(p_sample)
 order = np.argsort(p_sample)
+cmap = "plasma"
 im1 = ax[0, 0].scatter(
     x_mol[order],
     y_mol[order],
@@ -117,7 +118,7 @@ im1 = ax[0, 0].scatter(
     c=p_sample[order],
     alpha=0.7,
     ec="none",
-    cmap="plasma",
+    cmap=cmap,
     marker="o",
     norm=colors.Normalize(vmin=0, vmax=vmax),
 )
@@ -132,6 +133,7 @@ map.show(
     projection="molleweide",
     norm=colors.Normalize(vmin=0, vmax=vmax),
     res=resol,
+    cmap=cmap,
 )
 
 
@@ -143,7 +145,7 @@ im2 = ax[0, 2].scatter(
     c=p_back_sample[order],
     alpha=0.8,
     ec="none",
-    cmap="plasma",
+    cmap=cmap,
     marker="o",
     norm=colors.Normalize(vmin=0, vmax=10),
 )

### 2021-02-08 paper/paper.tex
more paragraphs

@@
 \bibliographystyle{aasjournal}
-
-% Begin!
-
+\setlength\LTcapwidth{\textwidth}
 \begin{document}
@@
 We built a generative model of Io's surface using the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic and differentiable computation of occultation light curves in emitted and reflected light.
-    Our (fully Bayesian) model is able to recover known bright features on the surface of Io with only two light curves and without any assumptions on where the features are located or how many there are.
-    This work is a first step towards constructing a model for time-variable surface features. 
-    Although we do not present new findings about Io in this work, the methods we have developed are directly applicable to the problem of mapping stars and exoplanets.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+    Our fully Bayesian model is able to recover known bright features on the surface of Io with only two light curves and without any assumptions on where the features are located or how many there are.
+    The methods we have developed are also directly applicable to the problem of mapping stars and exoplanets.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/irtf_max_flux.pdf}
+    \includegraphics[width=\linewidth]{figures/irtf_max_flux.pdf}
     \oscaption{irtf_dataset}{%
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/irtf_sample_lightcurves.pdf}
+        \includegraphics[width=0.7\linewidth]{figures/irtf_sample_lightcurves.pdf}
     \oscaption{irtf_dataset}{%
@@
     \mathbf{f}=\mathbf{A}\,\mathbf{y}
+    \quad,
     \label{eq:linear_model}
@@
 \mathbf{P}^\dagger=\left(\mathbf{P}^{\top} \mathbf{P}+\lambda \mathbf{I}\right)^{-1} \mathbf{P}^{\top}
+    \quad,
 \end{equation}
@@
     \boldsymbol{\Sigma}_l^{-1}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]
+    \quad,
     \label{eq:likelihood}
@@
     \mathbf{f}=\mathbf{A}'\,\mathbf{p}' +b\,\mathbf{1}_N
+    \quad,
     \label{eq:flux_model}
@@
 where we have added a fixed flux offset parameter for each light curve in order to account for stray flux which cannot be attributed to Io.
-This flux is mostly due to light emitted from Jupiter.
+This flux is mostly due to light emitted from Jupiter (TODO: is this right?).
 
@@
     k(\tau)=\sigma_\mathrm{GP}^{2}\left[(1+1 / \epsilon) e^{-(1-\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}(1-1 / \epsilon) e^{-(1+\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}\right]
+    \quad,
 \end{equation}
@@
 \begin{equation}
-    \boldsymbol{\Sigma}_{nm}=(K\sigma_n)^2\delta_{nm} + k(\tau\sigma_\mathrm{GP},\rho_\mathrm{GP})
+    \boldsymbol{\Sigma}_{nm}=\sigma_n^2\delta_{nm} + k(\tau\sigma_\mathrm{GP},\rho_\mathrm{GP})
+    \quad,
+    \label{eq:data_covariance_element}
 \end{equation}
-where $\sigma_n$ is the errorbar for the n-th data point and $K$ is a rescaling factor for the errorbar common to all data points in a single light curve.
+where $\sigma_n$ is the errorbar for the n-th data point.
 In cases where we fit multiple light curves assume independence and the total log likelihood is the product of individual likelihoods defined in Eq.~\ref{eq:likelihood}.
@@
 We can reformulate these statements more precisely by computing a measure of information content of the different kinds of observations.
-Given that our model is linear, assuming Gaussian priors on the spherical harmonic coefficients with covariance $\boldsymbol{\Lambda}$ and a Gaussian likelihood, the posterior can be computed analytically and its mean is given by
+Given that our model is linear, assuming Gaussian priors on the spherical harmonic coefficients with covariance $\boldsymbol{\Lambda}_\mathbf{y}$ and a Gaussian likelihood, the posterior can be computed analytically and its mean is given by
 \begin{equation}
     \widehat{\mathbf{y}}=\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}\left(\mathbf{A}^{\top} \boldsymbol{\Sigma}_{\mathbf{f}}^{-1} \mathbf{f}+\boldsymbol{\Lambda}_{\mathbf{y}}^{-1} \boldsymbol{\mu}_{\mathbf{y}}\right)
+    \quad,
 \end{equation}
@@
 \end{equation}
-The posterior covariance matrix depends on the design matrix $\mathbf{A}$, the prior covariance  $\boldsymbol{\Lambda}$ and the data covariance $\boldsymbol{\Sigma}_{\mathbf{f}}$.
 We define the information content as the variance reduction of the posterior relative to the prior which is called \emph{posterior shrinkage}.
-It is defined as
+The posterior shrinkage $S$ is defined as
 \begin{equation}
-    1-\frac{\sigma^2_\mathrm{post}}{\sigma^2_\mathrm{prior}}
+S \equiv 1-\lim _{\sigma_{0}^{2} \rightarrow \infty} \frac{\sigma^{2}}{\sigma_{0}^{2}}
+    \quad,
 \end{equation}
-where $\sigma^2_\mathrm{prior}$ is the prior and $\sigma^2_\mathrm{post}$ is the posterior variance for a given parameter.
-For each spherical harmonic coefficient in $\mathbf{y}$ the posterior shrinkage is then the ratio of the diagonal elements of matrices $\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}$ and $\boldsymbol{\Lambda}$.
+where $\sigma^2_0$ is the prior variance and $\sigma^2$ is the posterior variance for a given spherical harmonic coefficient.
+It tells us how well we can constrain a particular coefficient in the limit of infinite SNR observations, posterior shrinkage of 1 means that the data provides perfect information and a posterior shrinkage of 0 means that we didn't learn anything.
 In order to compute the posterior shrinkage we first compute the design matrices using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
 We take the ephemeris data from \textsf{JPL HORIZONS} and assume that it is known exactly and we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
-We need to assume some variance for the Gaussian prior on the $Y_{l,m}$ coefficients so we choose a broad prior $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$.
-Although the posterior shrinkage depends on this prior the main results do not change for a different choice of the prior.
 
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/information_content.pdf}
+    \includegraphics[width=\linewidth]{figures/information_content.pdf}
     \oscaption{InformationContent}{
-        The posterior shrinkage of different kinds of observations of Io as a function of spherical harmonic degree (angular scale), averaged across all $m$ modes.
+        The posterior shrinkage for different kinds of observations of Io as a function of spherical harmonic degree (angular scale), averaged across all $m$ modes.
     Posterior shrinkage of 1 represent maximum information gain in updating from the prior to the posterior while 0 represents no information gain. 
     The posterior variance has been computed for different kinds of simulated observations of Io over the course of a single year: phase curves (blue), occultations by Jupiter (orange), combined phase curves and occultations by Jupiter (green) and occulltations of Io by other Galilean moons (red lines).
-        Solid lines are for observations at SNR=100 and dashed are for observations at SNR=10.
         \label{fig:information_content}
@@
 Fig.~\ref{fig:information_content} shows the posterior shrinkage as a function of $l$ (averaged over all $m$ modes) for phase curve observations (blue lines), occultations by Jupiter (orange), the former two combined (green) and mutual occultations by other Galilean moons (red).
-Solid lines correspond to SNR=100 while dashed lines correspond to SNR=10 where the signal is defined as the min-max difference of the predicted flux.
-As expected, the mutual occultations of Io by other moons are by far the most informative with posterior shrinkage near unity at all angular scales up to $l=18$. 
+As expected, the mutual occultations of Io by other Galilean moons are by far the most informative with posterior shrinkage of unity at all angular scales. 
 Occultations by Jupiter are far less informative because we only see one side of Io during an occultation.
-This is also why there is a kink in the curve at $l=1$.
-We also see that the shrinkage is exactly zero for phase curves at all odd degrees above $l=2$ because phase curves for objects rotating about an axis perpendicular to the line of sight encode zero information on these coefficients because they are in the nullspace.
-Although observations of mutual occultations most easily break the degeneracies, they only occur every 6 years and more importantly they almost never occur while Io is in eclipse which means that only the brightest volcanoes will be visible above the reflected light background emission due to the Sun.
-Figure~\ref{fig:information_content} does not reflect this fact.
+Shrinkage for phase curve at odd degrees above $l=2$ is exactly zero because these coefficents are in the nullspace for objects rotating about an axis perpendicular to the line of sight these coefficients and therefore they cannot be constrained using only phase curves.
+Observations of mutual occultations most easily break the degeneracies but we have to keep in mind that they only happen every 6 years and they almost never happen while Io is in eclipse which means that only the brightest volcanoes are visible above the reflected light sunlight.
+This is not captured in \ref{fig:information_content}.
 
 Although Figure~\ref{fig:information_content} gives us some idea about which kinds of observations are most informative, it doesn't really tell us how well we can constrain very bright spot like features we expect to see on Io.
-To answer this question we have to simulate some data and the inference process.
+To answer this question we have to simulate data and the inference process.
 
@@
     B(\theta)=\frac{1}{\sqrt{2 \pi \sigma_s^{2}}}\exp \left(-\theta^{2} / 2 \sigma_s^{2}\right)
+    \quad,
 \end{equation}
@@
     B(\theta)=\sum_{l=0}^{\infty}\left(\frac{2 l+1}{4 \pi}\right) B_{l} \,\mathcal{P}_{l}(\cos \theta)
+    \quad,
 \end{equation}
@@
 \end{aligned}
+    \quad,
     \label{eq:horseshoe}
@@
     \tau_0=\frac{p_0}{D-p_0}\frac{\sigma}{\sqrt{n}}
+    \quad,
     \label{eq:horseshoe_tau0}
@@
 \subsection{1998 pair of occultations by Jupiter}
-Having demonstrated that our model works well on simulated data, int this section we use it to fit IRTF light curves of actual occultations of Io.
-Out of all the IRTF occultation light curves of Io by Jupiter, we choose two pairs of high quality ingress/egress light curves closely spaced in time so that that we can assume that the surface emission does not change substantially between the ingress and the egress occultation.
+Having demonstrated that our model works well on simulated data, we turn to fitting observations of actual occultation of Io observed with the IRTF telescope.
+We selected two pairs of high quality ingress/egress light curves closely spaced in time so that the assumption that the surface map is identical for both the ingress and the egress light curve is approximately correct; although we allow for a difference in the overall amplitude of the maps for the two occultations.
 We fit a pair of events from 1998, an ingress occultation observed on the 27th of August and an egress occultation observed on the 29th of November.
-For comparison, we also fit a pair of events from 2017, an ingress occultation observed on the 31st of March and an egress occultation observed on the 11th of May.
-
-We assume the same map for both the ingress and the egress light curve except for  a difference in the overall amplitude.
-The predicted fluxes are then:
+For comparison, we also fit a pair of events observed nearly two decades later in 2017.
+The predicted fluxes are given by 
 \begin{align}
@@
 \end{align}
-where $\mathbf{f}_I$ is the predicted flux for the ingress light curve and $\mathbf{f}_E$ is the predicted flux for the egress light curve.
+where $\mathbf{f}_I$ is the predicted flux for the ingress light curve with $N_I$ data points, $\mathbf{f}_E$ is the predicted flux for the egress light curve with $N_E$ data points, and $b_I$ and $b_E$ are constant flux offset parameters.
 Since we assume that the map is the same for both light curves up to an overall amplitude difference, we have
@@
     \mathbf{p}'_E=a\,\mathbf{p}'_I
+    \quad,
 \end{equation}
-where $a$ is the relative difference in amplitude.
-The log likelihood is the sum of the log likelihoods for individual light curves (Eq.~\ref{eq:likelihood}).
-We list all model parameters and their associated priors in Table~\ref{tab:priors}.
-\begin{table}
-\centering
-\begin{tabular}{l l l}
-    \hline
-Parameter & Description & Prior\\
- \hline
-    $\tau$ & Global sphixel scale &  \begin{minipage}{0.5\textwidth}  \shortstack[l]{$\mathrm{Half}-\mathcal{C}(0,\tau_0)$, $\tau_0$ defined by Eq.~\ref{eq:horseshoe_tau0} \\with $p_0=0.8D$}\end{minipage}\\
- $c^2$ & Slab scale squared & $\mathrm{Inv}-\mathcal{G}(2,2s^2)$, $s=10$\\
-    $\overline{\lambda}_m$  & Local sphixel scale & $\mathrm{Half}-\mathcal{C}(0,1)$\\
-    $p_m$ & Sphixels & $\mathcal{N}^+(0, \tau\lambda_m)$, $\lambda_{m} =c \overline{\lambda}_{m}/\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{m}^{2}}$\\
-    $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{Relative change in \\map amplitude}\end{minipage}& $\mathcal{N}(1, 0.1)$\\
-    $b_I$, $b_E$& Flux offset &$\mathcal{N}(0, 4)$\\
-    $K_I$, $K_E$& Errorbar rescaling factor&$\mathcal{N}(1,0.05)$\\
-    $\sigma_{\mathrm{GP},I}$, $\sigma_{\mathrm{GP},E}$ & GP standard deviation&$\mathcal{N}^+(0,0.1\sigma)$\\
-    $\rho_{\mathrm{GP},I}$, $\rho_{\mathrm{GP},E}$ & GP timescale  &  \begin{minipage}{0.5\textwidth}  \ \shortstack[l]{ \\$\mathrm{Inv}-\mathcal{G}(\alpha,\beta)$  with $\alpha$ and $\beta$ defined such that \\ $P(\rho_\mathrm{GP}<\Delta t_\mathrm{min})=P(\rho_\mathrm{GP}>(t_\mathrm{max}-t_\mathrm{min}))=0.01$}\end{minipage}
-\end{tabular}
-\caption{Parameters and priors for the final model. 
+where $a$ is a dimensionless parameter.
+
+The log likelihood is the sum of the log likelihoods for individual light curves (Eq.~\ref{eq:likelihood}), to compute it we also need to specify the data covariance matrix defined in Eq.~\ref{eq:data_covariance_element}.
+Each element of the covariance matrix consists of a white noise component (errobars) and a correlated noise component (Gaussian Process).
+Since the IRTF light curves are not provided with estimated errobars, we choose to fit for all errobars simultaneously using a hierarhical approach in which we assign a global scale $l$ for all errorbars in a given light curve and we draw each individual errobar from a Half Normal distribution with standard deviation equal to that scale.
+That is, we have 
+\begin{align}
+    \sigma_{i,I}&\sim \mathcal{N}^+(0, l_E),\quad i=1,\dots,N_I\\
+    \sigma_{i,E}&\sim \mathcal{N}^+(0,l_I),\quad i=1,\dots, N_E
+\end{align}
+where $\sigma_{i,I}$ are the errobars for the ingress light curve and $\sigma_{i,E}$ are the errobars for the egress light curve.
+Treating errobars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data.
+
+Our noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errobars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Matern 3/2 kernel.
+All model parameters and their associated priors are listed in Table~\ref{tab:priors}.
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{4cm} W{l}{4cm} W{l}{6cm}}
+            \label{tab:priors}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter(s)}}
+             &
+            \multicolumn{1}{c}{\textbf{Description}}
+             &
+            \multicolumn{1}{c}{\textbf{Prior}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            %
+            \caption{%
+Parameters and priors for the final model. 
             The subscript $I$ denotes parameters associated with the ingress light curve while the subscript $E$ denotes parameters associated with the egress light curve.
-    $\Delta t_\mathrm{min}$ is the minimum time between two consecutive data points in the ingress (egress) light curve and $(t_\mathrm{max}-t_\mathrm{min})$ is the duration of the ingress (egress) occultation.}
-    \label{tab:priors}
+$t_{\mathrm{max},I}$ and  $t_{\mathrm{max},E}$ are the durations of the ingress and egress occultations respectively.
+            }
+            \endfoot
+            %
+            %
+$\tau$ & global sphixel scale &  \begin{minipage}{0.5\textwidth}  \shortstack[l]{$\mathrm{Half}-\mathcal{C}(0,\tau_0)$, $\tau_0$ defined in Eq.~\ref{eq:horseshoe_tau0} \\with $p_0=0.8D$}\end{minipage}
+           %
+            \\
+            %
+            $c^2$ & slab scale squared & $\mathrm{Inv}-\mathcal{G}(\frac{\nu}{2},\frac{
+                nu}{2}s^2)$, $s=1000$ and $\nu=4$
+            %
+            \\
+            %
+    $\overline{\lambda}_m , \quad m=1,\dots,D$  & local sphixel scale & $\mathrm{Half}-\mathcal{C}(0,1)$
+            %
+            \\
+            $p_m, \quad m=1,\dots,D$& sphixels & $\mathcal{N}^+(0, \tau\lambda_m)$, $\lambda_{m} =c \overline{\lambda}_{m}/\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{m}^{2}}$
+            %
+            \\
+            %
+                $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage}& $\mathcal{N}(1, 0.1)$
+             %
+            \\
+            %
+    $b_I$, $b_E$& flux offset &$\mathcal{N}(0, 4)$
+            %
+            \\
+            %
+            $l_I$, $l_E$& errorbar global scale&$\mathcal{N}^+(0,0.1)$
+            %
+            \\
+            %
+            $\sigma_{i,I}$, $\sigma_{i,E},\quad i=1,\dots,N$& individual errobars&
+            $\mathcal{N}^+(0,l_I),\quad \mathcal{N}^+(0,l_E)$
+            %
+            \\
+            %
+            $\sigma_{\mathrm{GP}, I}$, $\sigma_{\mathrm{GP}, I}$ & GP standard deviation&$\mathcal{N}^+(0,0.1),\quad \mathcal{N}^+(0,0.1)$
+             %
+            \\
+            %
+            $\rho_{\mathrm{GP},I}$, $\rho_{\mathrm{GP},E}$ & GP timescale  & $\mathcal{N}^+(0, t_{max, I}),\quad  \mathcal{N}^+(0, t_{max, E})$
+        \\
+            %
+        \end{longtable}
+    \end{center}
 \end{table}
-One of the more important priors is the prior on the characteristic timescale of the Matern 3/2 kernel for the Gaussian Process. 
-We choose an Inverse Gamma prior for this parameter with the parameters $\alpha$ and $\beta$ chosen such that 1\% of the probability is assigned to timescales smaller than the median spacing between the data points in the light curve  on the left tail of the distribution and 1\% of probability on the right tail is assigned for timescales longer than the duration of the occultation.
-The purpose of this prior is to suppress the timescales for which the data provide much information\footnote{ \url{https://betanalpha.github.io/assets/case_studies/gaussian_processes.html}}.
 
-We run the MCMC for 500 warm-up steps and 2000 final steps, monitoring divergences and R-hat.
-The inferred map for the 1998 pair of events is shown in Figure~\ref{fig:irtf_ingress_egress_1998}.
-Selected inferred parameters parameters are shown in Table~\ref{tab:1998_parameters}. 
-The inferred map has two distinct hot spots, a bright hotspot and a faint hotspot.
-The orange lines in the second subplot from the bottom are posterior samples for the physical model in data space (not including the effects of the GP).
-The bottom panel shows the residuals with respect to the physical model and the posterior GP predictions.
-
-Most of the wiggles in the residuals are either due to surface emission features which were not accounted for by the model or due to atmospheric variability.
-The most notable feature in the residuals is visible at around 3.3 minutes in the ingress light curve and 3.6 minutes in the egress light curve when the bright spot comes in and out of view. 
-This feature is present because our model is limited in resolution so the inferred spot size is not small enough to explain the rapid change in flux seen in the data.
-The GP accounts for all three types of features - the model atmospheric variability, the emission due to surface features which are too faint to be well constrained by the physical model and the limitation of the physical model to capture the true size of the spot.
-Although the GP could easily account for the small dip in both light curves due to the faint hot spot, it does not too that because the physical model provides a better explanation for the data (TODO: formalize this argument).
-Thus there is a trade-off between the explanatory power of the noise model and the physical model.
-
-To obtain the inferred location of the hot spots we optimize for the location of maximum intensity in the spot for each posterior map. 
-The location of the bright hotspot is $16.295_{-0.009}^{0.009}$$^\circ$ N latitude and $53.098_{-0.004}^{0.006}$$^\circ$ E longitude which corresponds to the location of Loki Patera.
-Figure~\ref{fig:irtf_ingress_egress_loki} shows the hotspot overlaid on top overlaid on top of the U.S.
-Geological Survey's map of the surface of Io (CITE) which was constructed from Galileo observations.
-The faint hot spot is at $-11{-0.0}^{0.0}$$^\circ$ N latitude and $323_{-0.0}^{0.0}$$^\circ$ E longitude (TODO: input exact location) which is most likely Kanehekili (TODO: CITE, check if this is true).
+To fit the model we sample the posterior using the NUTS sampler for 500 warm-up steps and 3000 final steps.
+We monitor divergences and the R-hat statistic to ensure convergence.
+The inferred map for the 1998 pair of events is shown in Figure~\ref{fig:irtf_ingress_egress_1998} and the median, 16th and 84th percentile estimates from the samples are shown in Table~\ref{tab:irtf_1998}.
+The inferred map has two distinct hot spots, a bright hotspot in the Eastern hemisphere and a faint hotspot in the Western hemisphere.
+The orange lines in the second panels from the bottom are posterior samples for the physical (map) model in data space. 
+The bottom panel shows the residuals with respect to the (median) physical model prediction and the posterior predictions from the Gaussian Process (purple).
+We plot the model in this way so that we are able to distinguish between the features due to the physical model and those from the noise model.
+Each data point is shown with the median prediction of its errorbar.
 
@@
     Median estimates of two $l=20$ maps (top panel) inferred by fitting a pair of observations of occultations of Io by Jupiter from 1998.  
-        The map and light curve correspond to the ingress event and the ones on the right are the egress event. 
+        The map and light curve on the left correspond to the ingress event and the ones on the right are the egress event. 
         The two maps are (by construction) the same except for a difference in the overall amplitude. 
-        The observations were taken using the IRTF telescope in the NIR filter (TODO: which filter).
 The small circles beneath the inferred map show the progression of the occultation. 
-        Orange lines show posterior samples from the physical model (excluding the Gaussian Process).
-        The residuals (bottom) are computed with respect the median prediction from the physical model and the Gaussian Process predictions are shown on the same plot.
-The inferred map shows two hotspots, the bright hot spot is emission due to Loki and the faint hot spot is Kanehekili.
+        Orange lines show posterior samples from the physical model.
+        The residuals (bottom) are computed with respect the median prediction from the physical model and the Gaussian Process posterior predictions are shown on the same plot in purple.
+        The inferred map shows two hotspots, the bright hot spot is emission due to Loki and the faint hot spot is Kanehekili (TODO: check).
      \label{fig:irtf_ingress_egress_1998}
@@
 
-\begin{table}
-    \centering
-\begin{tabular}{l l l}
-    \hline
-    Parameter & Value & Unit\\
- \hline
- $\tau$ &  & \\
-    $c^2$ & &\\
-    $p_m$ & &\\
-    $a$ & &\\
-    $b_I$ & &\\
-    $b_E$ & &\\
-    $K_I$ & & \\
-    $K_E$ & &\\
-    $\sigma_{\mathrm{GP},I}$ && \\
-    $\sigma_{\mathrm{GP},E}$ & &\\
-    $\rho_{\mathrm{GP},I}$ & &\\
-    $\rho_{\mathrm{GP},E}$ &&  
-\end{tabular}
-    \caption{Inferred model parameters for the pair of occultations from 1998.}
-    \label{tab:1998_parameters}
+Despite the fact that our noise model is very flexible, it does not seem to overfit the data. 
+The physical model accounts for the prominent steps in the light curves while the noise model takes care  of the residual variability. 
+Most of the wiggles in the residuals are either due to surface emission features which were not accounted for by the model or due to atmospheric variability.
+The most notable feature in the residuals is visible at around 3.3 minutes in the ingress light curve and 3.6 minutes in the egress light curve when the bright hot spot comes in and out of view. 
+This feature is visible because our model is limited in resolution so the inferred spot size is not small enough to explain the rapid change in flux seen in the data.
+The Gaussian Process accounts for the  variation due to atmospheric variability, the emission due to surface features which are too faint to be well constrained by the physical model and the limitation of the physical model to capture the true size of the spot.
+
+There is a trade-off between the explanatory power of the noise model and the physical model. 
+In general, we expect that a given feature in the light curve will be accounted for by the physical model if the physical model provides a better explanation for the data relative to the noise model.
+This seems to be true for the most obvious features in Figure~\ref{fig:irtf_ingress_egress_1998} except (to an extent) for the first step in the ingress light curve at around 0.6 minutes which is only partially accounted for by the physical model because the model predictions are a bit too smooth compared to the data.
+Based on the ingress light curve alone, we would expect that the faint spot should be slightly brighter than the model predicted.
+Since the model had no trouble accounting for a similar a step for simulated data shown in Figure~\ref{fig:ingress_egress_sim_snr_50} the reason why it didn't do so in this case is probably because doing so would result in a poorer fit for the egress light curve.
+The two occultations were observed months apart so we expect our assumption that the map has not changed except for an overall amplitude to be wrong in detail.
+
+The posterior distribution for the errobars is shown in Figure~\ref{fig:irtf_ingress_egress_errorbars}.
+Both the global scale for the errobars and the individual errobars are well constrained by the data. 
+Looking at the plot one can see that outlier points are naturally accounted for in the model because those points end up having higher variance.
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/irtf_ingress_egress_1998_errobars.pdf}
+    \oscaption{irtf_ingress_egress_errobars}{%
+       \label{fig:irtf_ingress_egress_errorbars}
+    }
+    \end{centering}
+\end{figure}
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{2cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_1998}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Inferred parameters for the pair of occultations observed in 1998 using the IRTF telescope.
+                }
+            \endfoot
+            $\tau$ &   $0.870_{-0.221}^{+0.246}$ &  intensity
+            \\
+             $c$ & $4304.302_{-1162.250}^{+2123.962}$ & intensity 
+            \\
+                $a$ &  $1.154_{-0.013}^{+0.014}$ & dimensionless
+            \\
+            $b_I$ & $0.014_{-0.013}^{+0.077}$ & GW/um/sr
+            \\
+            $b_E$& $0.362_{-0.335}^{+0.438}$ & GW/um/sr
+            \\
+            $l_I$ & $0.253_{-0.030}^{+0.036}$ & GW/um/sr
+            \\
+            $l_E$& $0.461_{-0.042}^{+0.042}$ & GW/um/sr
+            \\
+            $\sigma_{\mathrm{GP}, I}$ & $0.633_{-0.042}^{+0.047}$ & GW/um/sr 
+            \\
+            $\sigma_{\mathrm{GP}, E}$ & $0.453_{-0.052}^{+0.054}$ & GW/um/sr
+            \\
+            $\rho_{\mathrm{GP},I}$ & $0.078_{-0.010}^{+0.011}$ & minutes
+            \\
+            $\rho_{\mathrm{GP},E}$ & $0.099_{-0.021}^{+0.027}$ & minutes
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
+
+To obtain the inferred location of both hot spots, we compute the centroid of pixels in the 90th percentile of intensity (meaning the brightest pixels) in a specific region (in latitude and longitude) around the hot spot.
+We repeat this for each posterior map to obtain uncertainty on the position. 
+In addition to the locations of the spots, we also compute the total power emitted within a 15 degree range in latitude and longitude around the (inferred) center of the spots.
+Both of these quantities are listed in Table~\ref{tab:irtf_1998_derived}. 
+The location of the bright hotspot is $16.414_{-0.011}^{+0.027}\quad^\circ$ N latitude and $53.107_{-0.033}^{+0.041}\quad^\circ$ E longitude which corresponds to the location of Loki Patera.
+The faint hot spot is at $-15.756_{-11.382}^{+3.812}\quad ^\circ$ N latitude and $321.568_{-4.208}^{2.803}\quad^\circ$ E longitude which is most likely Kanehekili (TODO: check if this is true).
+Figure~\ref{fig:irtf_ingress_egress_spots} shows  a contour map of both hot spots overlaid on top of the U.S.
+Geological Survey's map of the surface of Io \cite{williams2011} which was constructed from Galileo observations.
+Also shown is the inferred error in position (white lines).
+The error on the inferred position of Loki is only a fraction of a degree and thus much smaller than the minimum resolution of the map features which is set by the degree of the map.
+TODO: Mention the uncertainty due to Jupiter's radius.
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{4cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_1998_derived}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Derived parameters of the two hot spots visible in Figure~\ref{fig:irtf_ingress_egress_1998}.
+                The latitude and longitude of the spots are derived by computing the centroid of points around the spots which are in the 90th percentile of intensity.
+            The power is defined as the total emission from within a 15 degree circle around the (inferred) location of the spot.
+        }
+            \endfoot
+            Spot 1 latitude  & $16.414_{-0.011}^{+0.027}$& degrees 
+            \\
+             Spot 1 (East) longitude & $53.107_{-0.033}^{+0.041}$& degrees 
+            \\
+                Spot 1 power  ingress & $52.755_{-0.316}^{+1.090}$ & GW/um 
+            \\
+                Spot 1 power  egress & $61.055_{-1.000}^{+1.081}$ & GW/um 
+                \\
+            Spot 2 latitude  & $-15.756_{-11.382}^{+3.812}$& degrees 
+            \\
+             Spot 2 (East) longitude & $-38.432_{-4.208}^{+2.803}$ & degrees 
+            \\
+                Spot 2 power  ingress & $5.192_{-15.95}^{+0.484}$ & GW/um 
+                \\
+                Spot 2 power  egress & $6.026{-1.993}^{+0.534}$ & GW/um 
+            \\
+        \end{longtable}
+    \end{center}
 \end{table}
@@
     \begin{centering}
-    \includegraphics[width=.5\linewidth]{figures/irtf_spot_overlay_1998.pdf}
-    \oscaption{irtf_ingress_egress_loki}{%
-        Zoom in on the bright hot spot from Figure~\ref{fig:irtf_ingress_egress_1998} overlaid on top of the U.S.
-Geological Survey's map of the surface of Io (CITE) which was        constructed from Galileo observations.
-        The location of the hot spots matches the location of Loki Patera, the largest active volcano on the surface of Io. 
-        \label{fig:irtf_ingress_egress_loki}
+    \includegraphics[width=\linewidth]{figures/irtf_ingress_egress_1998_spots.pdf}
+    \oscaption{irtf_ingress_egress_1998_spots}{%
+        Contour plot of the hot spots shown in Figure~\ref{fig:irtf_ingress_egress_1998} overlaid on top of the U.S.
+Geological Survey's map of the surface of Io which has been constructed from observations by the Galileo spacecraft.
+        \label{fig:irtf_ingress_egress_spots}
+    }
+    \end{centering}
+\end{figure}
+
+To see how the results change if we don't include a Gaussian Process in the noise model we fit the same pair of occultations from 1998 using the same priors.
+The results are shown in Figure~\ref{fig:irtf_ingress_egress_1998_no_GP}.
+The model tries to account for the systematic variations in the data by inflating the individual errorbars.
+Compared to the map shown in Figure~\ref{fig:irtf_ingress_egress_1998} the map has two spurious extra spots. 
+We find that in general including a GP results in a simpler map with fewer features because the GP prevents the physical model from overfitting the data.
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress_1998_no_GP.pdf}
+    \oscaption{irtf_ingress_egress_1998_no_GP}{%
+        Same as Figure~\ref{fig:irtf_ingress_egress_1998} except this figure shows the output of a model which does not include a Gaussian Process to account for correlated structure in the data.
+    As a result, the model tries to account for the correlations by inflating individual errorbars. 
+    There are two additional hot spots which are almost certainly spurious.
+     \label{fig:irtf_ingress_egress_1998_no_GP}
     }
@@
 \subsection{2017 pair of occultations by Jupiter}
+To see what happens if we use the same model as the one used to generate the map shown in Figure~\ref{fig:irtf_ingress_egress_1998} to fit a pair of observations from 2017, an ingress occultation observed on the 31st of March and an egress occultation observed on the 11th of May.
+The results are shown in Figure~\ref{fig:irtf_ingress_egress_2017} and the inferred parameters are listed in Table~\ref{tab:irtf_2017}.
+The inferred map is very similar to the one shown in Figure~\ref{fig:irtf_ingress_egress_1998} because we again see two hot spots although the fainter one is located a higher latitude.
+A contour plots of the two spots overlaid on top of a surface map of Io from Galileo observations is shown in Figure~\ref{fig:irtf_ingress_egress_spots_2017} and the derived spot parameters are listed in Table~\ref{tab:irtf_2017_derived}.
 
@@
     \oscaption{irtf_ingress_egress_2017}{%
+    Median estimates of two $l=20$ maps (top panel) inferred by fitting a pair of observations of occultations of Io by Jupiter from 2017.  
+        The map and light curve on the left correspond to the ingress event and the ones on the right are the egress event. 
+        The two maps are (by construction) the same except for a difference in the overall amplitude. 
+The small circles beneath the inferred map show the progression of the occultation. 
+        Orange lines show posterior samples from the physical model.
+        The residuals (bottom) are computed with respect the median prediction from the physical model and the Gaussian Process posterior predictions are shown on the same plot in purple.
+        The inferred map shows two hotspots, the bright hot spot is emission due to Loki and the faint hot spot is Kanehekili (TODO: check).
                 \label{fig:irtf_ingress_egress_2017}
@@
 
-\subsection{What happens if we don't include the Gaussian Process?}
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{2cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_2017}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Inferred parameters for the pair of occultations observed in 1998 using the IRTF telescope.
+                }
+            \endfoot
+            $\tau$ &   $0.973_{-0.247}^{+0.255}$ &  intensity
+            \\
+             $c$ & $5866.860_{-1580.812}^{+2527.995}$ & intensity 
+            \\
+                $a$ &  $1.434_{-0.010}^{+0.011}$ & dimensionless
+            \\
+            $b_I$ & $0.025_{-0.024}^{+0.140}$ & GW/um/sr
+            \\
+            $b_E$& $1.026_{-0.263}^{+0.238}$ & GW/um/sr
+            \\
+            $l_I$ & $0.971_{-0.056}^{+0.056}$ & GW/um/sr
+            \\
+            $l_E$& $0.520_{-0.093}^{+0.079}$ & GW/um/sr
+            \\
+            $\sigma_{\mathrm{GP}, I}$ & $0.126_{-0.055}^{+0.129}$ & GW/um/sr 
+            \\
+            $\sigma_{\mathrm{GP}, E}$ & $0.601_{-0.093}^{+0.083}$ & GW/um/sr
+            \\
+            $\rho_{\mathrm{GP},I}$ & $2.160_{-2.030}^{+3.333}$ & minutes
+            \\
+            $\rho_{\mathrm{GP},E}$ & $0.020_{-0.013}^{+0.011}$ & minutes
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/irtf_ingress_egress_2017_spots.pdf}
+    \oscaption{irtf_ingress_egress_2017_spots}{%
+        Contour plot of the hot spots shown in Figure~\ref{fig:irtf_ingress_egress_2017} overlaid on top of the U.S.
+Geological Survey's map of the surface of Io which has been constructed from observations by the Galileo spacecraft.
+        \label{fig:irtf_ingress_egress_spots_2017}
+    }
+    \end{centering}
+\end{figure}
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{4cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_2017_derived}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Derived parameters of the two hot spots visible in Figure~\ref{fig:irtf_ingress_egress_2017}.
+                The latitude and longitude of the spots are derived by computing the centroid of points around the spots which are in the 90th percentile of intensity.
+            The power is defined as the total emission from within a 15 degree circle around the (inferred) location of the spot.
+        }
+            \endfoot
+            Spot 1 latitude  & $12.319_{-0.388}^{+0.391}$& degrees 
+            \\
+             Spot 1 (East) longitude & $52.743_{-0.095}^{+0.046}$& degrees 
+            \\
+                Spot 1 power  ingress & $70.719_{-0.275}^{+1.396}$ & GW/um 
+            \\
+                Spot 1 power  egress & $102.026_{-1.459}^{+1.737}$ & GW/um 
+                \\
+            Spot 2 latitude  & $-8.076_{-0.084}^{+0.715}$& degrees 
+            \\
+             Spot 2 (East) longitude & $-42.096_{-0.161}^{+0.417}$ & degrees 
+            \\
+                Spot 2 power  ingress & $4.513_{-0.742}^{+0.689}$ & GW/um 
+                \\
+                Spot 2 power  egress & $6.483{-1.059}^{+0.944}$ & GW/um 
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
 

### 2021-03-02 paper/paper.tex
Rodrigo's comments, a bunch of other changes

--- 2021-01-02 paper/paper.tex
@@
 \bibliographystyle{aasjournal}
-
-% Begin!
+\setlength\LTcapwidth{\textwidth}
 \begin{document}
@@
 % Title
-\title{Occultation mapping of Io's surface in the near-infrared I: Inferring static maps}
-
+\title{
+    \vspace{-3em}
+\textbf{    Occultation mapping of Io's surface in the near-infrared \\ I: Inferring static maps} 
+}
 % Author list
 \author{Fran Bartoli\'c}
-\email{fbartolic@flatironinstitute.org}
+\email{fb90@st-andrews.ac.uk}
+\affil{Centre for Exoplanet Science, SUPA, School of Physics and Astronomy, University of St. Andrews, St. Andrews, UK}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
-\affil{Centre for Exoplanet Science, SUPA, School of Physics and Astronomy, University of St. Andrews, St. Andrews, UK}
 \author{Rodrigo Luger}
@@
 We built a generative model of Io's surface using the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic and differentiable computation of occultation light curves in emitted and reflected light.
-    Our (fully Bayesian) model is able to recover known bright features on the surface of Io with only two light curves and without any assumptions on where the features are located or how many there are.
-    This work is a first step towards constructing a model for time-variable surface features. 
-    Although we do not present new findings about Io in this work, the methods we have developed are directly applicable to the problem of mapping stars and exoplanets.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+    Our fully Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of features.
+    The methods we have developed are also directly applicable to the problem of mapping stars and exoplanets.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 \section{Introduction}
-The surface of Jupiter's moon Io is littered with hundreds of volcanoes which appear as bright spots in the near infrared and in intensity on timescales ranging from days to decades.
-The volcanic activity is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
-Because of its extreme volcanic activity, Io is in many ways an analogue of a volcanically active exoplanet.
-Volcanic exoplanets, often dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019}.
-Studying extreme volcanism on both Io and exoplanets is scientifically valuable because it provides a window into the properties of the early Earth and it informs theories of planet formation.
+The surface of Jupiter's moon Io is covered with hundreds of volcanoes which appear as bright spots in the near infrared, their intensities vary on timescales ranging from days to decades.
+The global heat flow on its surface is about 40 times larger than Earth's \citep{breuer2007,davies2010}
+and about 50\% of the heat flow emanates from only 1.2\% of Io's surface \citep{veeder2012}.
+This intense volcanic activity cannot be explained by radioactive decay which is what drives Earth's volcanism, instead it is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
+Contrary to Earth, Io lacks plate tectonics.
+The heat transport mechanism which likely on Io is volcanism through the litosphere (the outermost shell of a terrestrial body), a process in which magma is transported to the surface by localised vents \cite{oreilly1981}.
+Heat-pipe volcanism might have occurred in the early history of terrestrial planets in the Solar System \cite{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
 
-Existing exoplanet detections with potential volcanism include CoRoT-7b \citep{barnes2010}, the first rock exoplanet to have been discovered and one which likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016a,hammond2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019} and many others.
-Not all exoplanets will have Io-like volcanism, some will have magma oceans due to their proximity to the star or volcanism caused by nuclear decay similar to early Earth volcanism.
+Besides providing a window into early volcanic activity in the Solar System, Io is also in many ways an analogue of a volcanically active exoplanet.
+Volcanic exoplanets, often dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
+Existing exoplanet detections with potential volcanism include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet to have been discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016a,hammond2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019} and many others.
+Not all such exoplanets will have Io-like volcanism; some may have magma oceans due to their proximity to the star or volcanism caused by nuclear decay, similar to volcanism on present day Earth.
 
@@
 Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter starting with \cite{spencer1990}.
-Occultations by Jupiter occur twice every orbit lasting ~1.7 days and mutual occultations with Europa, Ganymede or Callisto happen every ~6 years when Earth pasess through the orbital plane of Galilean satellites.
-The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow ("in eclipse") while mutual occultations are almost always observed in sunlight because mutual occultations while Io is in eclipse are extraordinarily rare.
-Only the brightest volcanoes are visible over the reflected light background when Io is illuminated by the Sun\citep{veeder1994,dekleer2016a}.
+Occultations by Jupiter occur twice every orbit of ~1.7 days.
+Mutual occultations with Europa, Ganymede or Callisto happen at different times over the course of a single year but this only happens every ~6 years or so when Earth passes through the orbital plane of the Galilean satellites.
+The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow (``in eclipse") while mutual occultations are almost always observed in sunlight.
+Only the brightest volcanoes are visible over the reflected light background when Io is illuminated by the Sun \citep{veeder1994,dekleer2016a}.
 
@@
 \cite{spencer1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
-\cite{rathbun2002, rathbun2006,rathbun2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots finding evidence of periodicity in Loki's eruptions and established the transient nature of the volcanoes (only Loki is persistently active).
-By studying an occultation of Io by Europa, \cite{dekleer2017} mapped the Loki region to a precision of about 2 kilometers.
-In addition to observations of occultations in near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot1974,saquet2018,morgado2016a} for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
+\cite{rathbun2002},\citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots, finding evidence of periodicity in Loki's eruptions and establishing the transient nature of the volcanoes (only Loki is persistently active).
+By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki region to a precision of about 2 kilometers.
+In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot1974,saquet2018,morgado2016a} for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
+Understanding the detailed albedo distribution is crucial to constraining the ephemeris to a very high precision.
 
 None of the studies of occultations in the infrared attempted to infer a two-dimensional map of Io's surface.
-The light curves are usually fit independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface.
-Strong priors on the locations of individual volcanoes are assumed based on maps from space mission observations.
-In this work, we build a fully probabilistic model in order to infer a two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infra red.
-We assume that the map generating a given set of light curves is static (up to an overall amplitude) so we are restricted to modeling the surface during a timespan when the surface emission hasn't changed drastically.
+The light curves are usually fit independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface, with
+strong priors on the locations of individual volcanoes based on maps from space mission observations.
+In this work, we build a fully probabilistic model in order to infer a two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infrared.
+We assume that the map corresponding to a given set of light curves is static (up to an overall amplitude) so we are restricted to modeling the surface during a timespan when the surface emission hasn't changed drastically.
 In a subsequent paper we build on the model we have developed here and generalize to a case where the surface is time-variable.
 
-The model is built on top of the recently developed code starry \citep[][Luger et al.
-2020 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
+The model is built on top of the recently developed code \textsf{starry}\citep[][Luger et al.
+2021 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
 Starry can compute phase curves and occultations in both emitted light (for modeling the isotropic thermal emission from Io's surface) and reflected light (for mapping albedo variations).
 It is many orders of magnitude faster and more accurate than pixel based codes and it computes exact gradients with respect to all parameters through automatic differentiation.
-Starry also comes with extensive tools for visualizing spherical harmonic maps and simulating data.
+\textsf{starry} also comes with extensive tools for visualizing spherical harmonic maps and simulating data.
 
-Our goal for this paper is to develop a general model for mapping surfaces of occulted bodies with sparse high contrast features and to test it on a real world dataset. 
-Because we have lots of prior information on what the surface of Io should look like, we can compare our inferences to known features on its surface and we can test the sensitivity of the inferred maps to different choices of priors and noise models.
+Our goal for this paper is to develop a general model for mapping surfaces of occulted bodies with sparse, high contrast features and to test it on a real world dataset. 
+Because we have lots of prior information on what the surface of Io should look like, we can compare our inferences to known features on its surface and test the sensitivity of the inferred maps to different choices of priors and noise models.
 The work should also be of interest to the Io research community as it presents a very different approach to modeling Io occultations without having to make strong assumptions on the locations of the hot spots.
@@
 The paper is organized as follows.
-In \S\ref{sec:data} we describe the IRTF light curves of occultations by Jupiter which we use to infer maps.
+In \S\ref{sec:data} we describe the IRTF light curves of occultations by Jupiter that we use to infer maps.
 In \S\ref{sec:model} we discuss the generative model for the data and we write down the relevant likelihood functions.
 In \S\ref{sec:inverse_problem} we focus on the question of how to do Bayesian inference given the forward model specifications defined in \S\ref{sec:model}.
-We discuss and test different priors on map features, the information content of light curves and fitting the modelsusing Hamiltonian Monte Carlo (HMC). 
-We show results on simulated data.
-\S\ref{sec:results} shows the results on real IRTF data for two pairs of light curves (closely spaced in time)
-In particular, the inferred dynamic map, the  different component maps and accompanying coefficients, the uncertainties of the maps, sensitivity to different choices of priors, comparison of inferred locations and intensities of spots to known values from the literature.
-Finally, in \S\ref{sec:exoplanets} we discuss applications of the model to future exoplanet obervations and test the model predictions on simulated JWST observations of a volcanic Super-Earth.
+We discuss and test different priors on map features, the information content of light curves and fitting the models using Hamiltonian Monte Carlo (HMC). 
+We then show results on simulated data.
+In \S\ref{sec:results} we show the results on real IRTF data for two pairs of light curves, one pair observed in 1998 and another in 2017.
+We show the inferred maps and the parameters quantifying the location and intensity of the hot spots, we discuss the sensitivity of the results to different choices of priors and compare the inferred values to previous results from the literature.
+Finally, in \S\ref{sec:discussion} we summarize the main results of the paper and discuss potential applications of our model to observations of volcanic exoplanets.
+
+TODO: say that this paper is first in series of awesome papers.
+
+\vspace{1em}
+
+All of the figures in this paper were auto-generated
+using the Azure Pipelines continuous integration (CI) service.
+Icons next to each of the figures \codeicon \,
+link to the exact script used to generate them to ensure the reproducibility
+of our results.
 
@@
 
-The dataset we use to infer maps of Io's surface consists of 112 observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994} (TODO: WHICH FILTERS), the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} (TODO: DETAILS) and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{johnrayner2016}.
+The dataset we use to infer maps of Io's surface consists of 112 sets of observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994} (TODO: WHICH FILTERS), the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} (TODO: DETAILS) and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{johnrayner2016} (TODO: fix citation).
 Although the observations span decades, the cadence is non-uniform, there are only a few observations taken between 2008 and 2016.
@@
 Observations of Io \emph{in sunlight} on the other hand probe both the thermal (volcanic) emission and the surface albedo variations in the near infrared.
-Figure~\ref{fig:irtf_max_flux} shows the maximum flux in units of $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ (TODO: UNDERSTAND THESE UNITS) for each light curve plotted as a function of time.
-This value is approximately equal to the total flux emitted from the Jupiter facing side of Io.
+Figure~\ref{fig:irtf_max_flux} shows the maximum flux for each occultation light curve in units of $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ as a function of time.
+This value is approximately equal to the total flux emitted from the Jupiter-facing side of Io.
 The baseline brightness is varying stochastically by a large amount and there are several notable events of intense volcanic activity.
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/irtf_sample_lightcurves.pdf}
+        \includegraphics[width=\linewidth]{figures/irtf_sample_lightcurves.pdf}
     \oscaption{irtf_dataset}{%
@@
 in the dataset. 
-All occultations last for $\sim4$ min.
-The exposure cadence for each light curve is around a second with some variation between light curves.
+Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress and ingress parts of the entire occultation.
+The exposure cadence for each light curve is about a second, with some variation between light curves.
 It follows that over the course of a single exposure Jupiter's limb passes over about 15km on Io's surface which provides a lower bound for the size of the features that we can reliably estimate.
@@
 The photometric quality of the light curves varies from year to year because multiple instruments were used over the years. 
-As with all ground based photometry, the observations are influenced by atmospheric variability which results in some correlated noise in the light curves and because of this the flux is not always monotonically increasing or decreasing as one would expect.
-The light curves lack errorbars. 
-To estimate the errorbars we do some basic pre-processing on the light curves. 
-We filter each light curve with the Savitzky-Golay filter as implemented in \textsf{SciPy} \citep{virtanen2020} with
-a third order polynomial and a window length equal to 5\% of the number of data points and rounded up to the nearest odd integer. 
-After filtering, we compute the residuals with respect to the filtered model and run iterative sigma-clipping, removing all data points 5 median absolute deviations (MAD) from the median value. 
-Finally, we estimate the errorbars by computing the standard deviation of the sigma clipped residuals.
-This estimate is far from perfect which is why we introducing a rescaling parameter when fitting the model.
+As with all ground-based photometry, the observations are influenced by atmospheric variability which results in some correlated noise in the light curves, because of this the flux is not always monotonically increasing or decreasing as one would expect.
+Complicating matters, the light curves lack errorbars. 
+We deal with this by treating all errobars as free parameters with a common characteristic scale in the final model.
 
@@
 To compute the geometry, we use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner2014} which is accurate to a few kilometers on Io's surface.
-For both Jupiter and Io we need the Right Ascension and Declination and the angular (equatorial) diameter (\textsf{Ang-diam}).
-In addition, we need to fix the orientation of Io we need the longitude and the latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}) and the counterclockwise angle between the Celestial North Pole unit vector projected onto the plane of the sky and the Io's north pole (\textsf{NP.ang}).
-All longitudes are positive  in the direction of West.
+For both Jupiter and Io we need the right ascension and declination and the angular (equatorial) diameter (\textsf{Ang-diam}).
+In addition, we need to fix the orientation of Io we need the longitude and the latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}) and the counterclockwise angle between the celestial north pole unit vector projected onto the plane of the sky and the Io's north pole (\textsf{NP.ang}).
+All longitudes are positive  in the direction of west.
 \textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 second so we interpolate all values so that we can evaluate them for arbitrary times.
@@
 The radius of the occulted sphere is fixed to 1 and the orientation is specified by three angles,
-the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the North Pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the North Pole is aligned with the $\hat{y}$ axis and the phase angle \textsf{theta} which rotates the sphere around the $\hat{y}$ axis in the eastward direction.
+the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the north pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the north pole is aligned with the $\hat{y}$ axis and the phase angle \textsf{theta} which rotates the sphere around the $\hat{y}$ axis in the eastward direction.
 We have $\mathrm{obl}=\textsf{NP.ang}$, $\mathrm{inc}=90^\circ-\textsf{Ob-lat}$ and
@@
 \end{align}
-where $\Delta\alpha$ and $\Delta\delta$ are differences in Right Ascension and Declination respectively relative to the occulted object and $\gamma$ is the angular radius of the occulted sphere.
+where $\Delta\alpha$ and $\Delta\delta$ are differences in right ascension and declination respectively relative to the occulted object and $\gamma$ is the angular radius of the occulted sphere.
 
 \subsection{Jupiter's effective radius}
+\label{ssec:effective_radius}
 Although the sky position of Jupiter relative to Io is known to a precision of a few kilometers, several complications arise when attempting to compute Jupiter's radius.
 First, Jupiter is not spherical and its equatorial radius is greater than the polar radius by thousands of kilometers. 
-Because \textsf{starry} does not support occultations by non-spherical occultors and because the effect is negligible at the resolution of our maps, we assume that Jupiter is locally spherical at the point of an occultation.
+Because \textsf{starry} does not (yet) support occultations by non-spherical occultors and because the effect is negligible at the resolution of our maps, we assume that Jupiter is locally spherical at the point of an occultation.
 We estimate an effective radius from the measurements of Jupiter's shape from Voyager radio occultation data \citep{lindal1981}.
@@
 Second, Jupiter is gaseous so it does not have a well defined boundary.
-In principle, we should compute an effective radius of Jupiter at different locations (pressure) in the atmosphere and model an occultation of Io by a fuzzy occultor.
-Although this is possible with Starry, it is unnecessary for our models because the characteristic scale height of Jupiter is around 27 km (CITE) which is below the uncertainty of our inferred maps.
+In principle, we should compute an effective radius of Jupiter at different altitudes (pressure) in the atmosphere and model an occultation of Io by a fuzzy occultor.
+Although this is possible with \textsf{starry}, it is unnecessary for our models because the characteristic scale height of Jupiter is around 27 km (CITE) which is below the uncertainty of our inferred maps.
 Instead, we follow the approach in \cite{spencer1990} and compute the effective radius of Jupiter at about 2.2 mbar, the pressure (and the associated effective radius) at which a  bright source on the surface of Io fades by 50\% due to differential refraction during the course of an occultation.
 
-Third, the information on the effective radius in \citep{lindal1981} is provided only at a fixed pressure of 100 mbar.
+Third, the information on the effective radius in \cite{lindal1981} is provided only at a fixed pressure of 100 mbar.
 To adjust the values for a lower pressure of 2.2 mbar we assume an exponential pressure profile $P=P_0\, e^{-\Delta r/H}$ where $H$ is the scale height and $\Delta r$ is the height difference between the two pressure levels.
@@
 
-Finally, we have to account for the fact that the light from Io is getting significantly bent at the point of half reflective intensity in Jupiter's atmosphere which results in a smaller shadow of Jupiter on the surface of Io then would be the case for a straight propagation.
+Finally, we have to account for the fact that the light from Io is getting significantly bent at the point of half reflective intensity in Jupiter's atmosphere which results in a smaller projected limb of Jupiter on the surface of Io then would be the case for straight propagation.
 It is zero at the beginning of the disappearance of a hot spot when there is no refraction, increasing to one scale height $H$ at the half intensity point and then increasing further to a large value when Io disappears behind Jupiter's limb.
@@
 There are substantial uncertainties in each of these steps.
-The data about on the shape profile are quite old and it is not known if the structure of Jupiter's atmosphere stayed the same since 1980s. 
+The data on the shape profile are quite old and it is not known if the structure of Jupiter's has remained constant since the 1980s. 
 The shape profile also depends on the wind velocity structure and temperature which we do not take into account.
 In addition to uncertainties about the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
-We digitized the figure by reading off the data points "by eye" and then interpolating them using cubic spline interpolation.
+We digitized the figure by reading off the data points ``by eye" and then interpolating them using cubic spline interpolation.
 
@@
 \textsf{starry} computes the integrated flux of an unocculted or an occulted sphere analytically assuming that the surface map can be expanded in terms of spherical harmonics $Y_{lm}(\theta,\phi)$ up to a certain \emph{degree} $l$.
-The map is thus defined by a vector of spherical harmonic coefficients $\mathbf{y}$ which multiplies the spherical harmonic basis $\tilde{\mathbf{y}}(x, y)=\left(Y_{0,0} Y_{1,-1} Y_{1,0} Y_{1,1} Y_{2,-2} Y_{2,-1} Y_{2,0} Y_{2,1} Y_{2,2} \cdots\right)^{\top}$ and the total number of coefficients is $(l+1)^2$.
+The map is thus defined by a vector of spherical harmonic coefficients $\mathbf{y}$ which multiplies the spherical harmonic basis $\left(Y_{0,0}\;Y_{1,-1}\;Y_{1,0}\;Y_{1,1}\;Y_{2,-2}\;Y_{2,-1}\;Y_{2,0}\;Y_{2,1}\;Y_{2,2}\; \cdots\right)^{\top}$ and the total number of coefficients is $(l+1)^2$.
 In addition to computing \emph{thermal} phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations when the sphere is illuminated by a distant light source \citep[Luger et al.
-2020 in prep][]{} which is complicated by the presence of the terminator line.
+2021 in prep][]{} which is complicated by the presence of the terminator line.
 In the case of a reflected light map, the coefficient vector $\mathbf{y}$ represents spherical albedo in a given wavelength range.
@@
 
-Importantly, conditional on the parameters specifying the geometry of the occultations being fixed, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
+Importantly, conditioned on the parameters specifying the geometry of the occultations being fixed, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
 \cite{luger2019} achieved this by representing all rotations, changes of basis transformations and integrals with complicated boundaries which are needed to compute the flux as linear transformations.
@@
     \mathbf{f}=\mathbf{A}\,\mathbf{y}
+    \quad,
     \label{eq:linear_model}
 \end{equation}
-where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and optionally the direction of the illumination source and $\mathbf{A}$ is the design
-matrix of shape $(T, N)$ (with $N=(l+1)^2$) which encodes information all operations needed to compute the integrated flux.
-If the geometry isn't known precisely then the matrix $\mathbf{A}$ is not fixed and the model is no longer linear.
+where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and optionally the direction of the illumination source and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
+in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes the operations needed to compute the integrated flux.
+If the geometry isn't known precisely the matrix $\mathbf{A}$ is not fixed and the model is in principle no longer linear although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
 
-The characteristic angular scale of features that can be represented with a given map is set by the degree of the map and it is approximately equal to $\frac{180^\circ}{l}$.
+The characteristic angular scale of features that can be represented with a given map is set by the degree of the map and it is approximately equal to $180^\circ/l$.
 For reference, state of the art inferences involving phase curves and secondary eclipses of exoplanets are able to constrain features of order $l=1$ (inferring a bright spot offset from the substellar point) but for Io we need to fit much higher order maps because the typical scale of volcanic spots is on the order of tens of kilometers (a few degrees).
-\textsf{starry} can handle maps up to $l\approx 20$ before numerical instabilities kick in (TODO: make this statement more precise).
+\textsf{starry} can handle occultations up to $l\approx 20$ before numerical instabilities kick in \citep{luger2019a}.
 
-Although \textsf{starry} is built around the idea of expanding surface features in a spherical harmonic basis, this is not the ideal basis for doing inference because it makes it difficult to ensure that the intensity is positive everywhere on the map.
-The positivity constraint is important not only because we want to avoid having unphysical regions on inferred maps but also because it imposes a strong constraint on the map which substantially reduces the complexity of the inference problem.
-Unfortunately, there is no analytic way to determine weather a given spherical harmonic map $\mathbf{y}$ is positive-valued everywhere on the sphere.
+Although \textsf{starry} was built around the idea of expanding surface features in a spherical harmonic basis in which we can compute all fluxes analytically, this basis is ideal basis for doing inference because it makes it difficult to encode assumptions (priors) on what we expect the map to look like.
+For example, the most important constraint on the map we would like to incorporate in the model is that the intensity of the map is positive at every location. 
+This constraint is important not only because we want to avoid having unphysical regions in inferred maps but also because it imposes a very strong prior on the map which substantially reduces the difficulty of inference when the data is not particularly informative.
+The are two ways of enforcing positivity that we are aware of, both of which involve evaluating the intensity on a fixed grid of \emph{pixels} and disallowing negative values of those pixels.
+The first is to fit for the spherical harmonic coefficients $\mathbf{y}$, evaluate the pixel grid at each MCMC step and reject all samples of the coefficient vector $\mathbf{y}$ which result in pixels with negative intensity.
+The issue with this procedure is that rejecting samples in this way implies a prior probability distribution on $\mathbf{y}$ which cannot be mapped to a parameter space with infinite support\footnote{For example, if we want to impose a positive prior on some parameter $x$, instead of sampling in $x$ using a prior with a hard boundary at zero, we can derive the equivalent prior for $\ln x$ and sample in the (unbounded) parameter $\ln x$.
+It is not clear how to use a similar trick to ensure that all pixels on a fixed grid generated from spherical harmonics are positive.} and Hamiltonian Monte Carlo does not work well with constrained parameter spaces.
+The second approach is to dispense with the spherical harmonics entirely and compute the full model using a high resolution grid of pixels.
+In practice this is very difficult to do because we would need a very high resolution grid to compute the light curves accurately with minimal discretization noise and the model.  
+\textsf{starry} uses spherical harmonics as a basis precisely to avoid this problem.
+\textbf{Instead, we opt for a hybrid approach in which we fit for pixels but at each MCMC step we convert the pixels to spherical harmonic coefficients to compute the light curve.}
 
-The are two ways of circumventing this problem that we are aware of.
-The first is to evaluate the intensity on a (sufficiently fine) discrete grid of \emph{pixels} $\mathbf{p}$ on the sphere and then either fit for $\mathbf{y}$ while rejecting steps when fitting the model for which any of the pixels $\mathbf{p}$ end up being negative.
-The second is to treat the pixels as model parameters but still compute the actual light curve model in the $Y_{lm}$ basis where everything is fast. 
-We opt for the latter approach because it is much easier to implement.
-The mapping from spherical harmonics $\mathbf{y}$ to pixels $\mathbf{p}$ can be expressed as a linear operator 
-$\mathbf{P}$:
+To implement the hybrid approach we need to be able to switch between spherical harmonics and pixels.
+Transforming spherical harmonics $\mathbf{y}$ to pixels $\mathbf{p}$ is straightforward because there exists a linear operator $\mathbf{P}$ which maps $\mathbf{y}$ to $\mathbf{p}$:
 \begin{equation}
     \mathbf{p}=\mathbf{P}\,\mathbf{y}
+    \label{eq:ylms_to_pixels}
 \end{equation}
 Each row of $\mathbf{P}$ contains values of each of spherical harmonic coefficients at a given point on the grid. 
-To construct the grid we use an equal area Molleweide projection so that we don't end up with more pixels in some areas of the sphere than others.
-The grid needs to be fine enough to ensure positivity over most of the sphere.
-We find that we need to have more pixels than spherical harmonics by a factor of at least 4.
-This increases the computational cost of the inference somewhat because the number of parameters we have to fit increases fourfold.
+To construct the grid we use an equal area Molleweide projection in order to have a uniform distribution of pixels across the sphere.
+The grid needs to be fine enough to ensure that intensity is positive over most of the sphere.
 
-Because $\mathbf{P}$ is not a square matrix, we cannot compute its inverse to obtain the inverse transform, however we can still compute the Moore-Penrose pseudoinverse $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$ where $\mathbf{I}$ is the identity matrix.
+Switching from pixels to spherical harmonics is somewhat more complicated because $\mathbf{P}$ is not a square matrix so we cannot compute its inverse to obtain the inverse transform.
+Instead, we can compute an approximate inverse (a pseudoinverse) $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$, where $\mathbf{I}$ is the identity matrix.
 The solution is given by
@@
 \mathbf{P}^\dagger=\left(\mathbf{P}^{\top} \mathbf{P}+\lambda \mathbf{I}\right)^{-1} \mathbf{P}^{\top}
+    \quad,
 \end{equation}
 where $\lambda$ is a small regularization parameter and $\mathbf{I}$ is the identity matrix.
-We then have 
+The mapping from pixels to spherical harmonics is then given by
 \begin{equation}
-    \mathbf{y}'=\mathbf{P}^\dagger\mathbf{p}'
+    \mathbf{y}\simeq\mathbf{P}^\dagger\mathbf{p}
+    \label{eq:pixels_to_ylms}
 \end{equation}
-Both matrices can easily be pre-computed with \textsf{starry} before doing inference.
-We use the symbol $\mathbf{p}'$ to denote pixels which are mapped to spherical harmonic coefficients using $\mathbf{P}^\dagger$ and $\mathbf{p}$ for those generated from $\mathbf{y}$ using $\mathbf{P}$.
-In the rest of the paper we call the former kind of pixels \emph{sphixels}.
-Setting $\mathbf{A}'\equiv \mathbf{A}\,\mathbf{P}^\dagger$, we see that the flux is also linear in the spixels:
-\begin{equation}
-    \mathbf{f}=\mathbf{A}'\,\mathbf{p}'
-    \label{eq:linear_model_pix}
-\end{equation}
+Both $\mathbf{P}$ and $\mathbf{P}^\dagger$ can be precomputed to speed up inference.
+When using pixels to impose a positivity constraint on the spherical harmonic map we need to make sure that number of pixels is greater than the number of spherical harmonic coefficients by a factor of a few to ensure positivity approximately everywhere on the sphere.
+In practice we find that we need to use at least 4 times as many pixels as spherical harmonics which means that the computational cost of this model is higher than if we just fit for spherical harmonics.
 
-\begin{figure}[h!]
+To summarize, in our hybrid model we first construct a fixed high resolution pixel grid in latitude and longitude, then use Equation~(\ref{eq:pixels_to_ylms}) to convert pixels to spherical harmonics and finally use Equation~(\ref{eq:linear_model}) to evaluate the model.
+Although we fit for the pixels $\mathbf{p}$ we store the spherical harmonic coefficient vectors $\mathbf{y}$ as the final product of the inference. 
+Figure~\ref{fig:pixels_to_harmonics} illustrates the transformation from the pixel basis to the spherical harmonic basis via $\mathbf{P}^\dagger$.
+On the left we show the pixel map where each pixel was independently drawn from an exponential prior. 
+On the right is the same pixel map transformed to a spherical harmonic basis via $\mathbf{P}^\dagger$. 
+The histograms underneath each map show the distribution of intensities.
+Since the pixel map is higher resolution than the spherical harmonic map it can only be approximately represented at a finite order of the spherical harmonic expansion so the map on the right appears to be smoother and the intensity distribution is more similar to a skewed Gaussian with a heavy right tail than an exponential distribution.
+Nevertheless, we find that setting priors on pixels is a far better solution than fitting the spherical harmonic coefficients directly and is worth the extra computational cost due the increased dimensionality of the parameter space (see Section~\ref{ssec:pixels_vs_harmonics} for a demonstration).
+
+\begin{figure}[t!]
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/sphixels_to_pixels.pdf}
-    \oscaption{sphixels_to_pixels}{%
-        Transformation of a pixelated map in which we set our priors (left) to the spherical harmonic basis which we use to compute the model (middle) and then again to pixels.
-        The mapping from spherical harmonics to pixels is exact but the reverse is not true so to differentiate between pixels mapped to spherical harmonics and pixels constructed from spherical harmonics we call the former "sphixels".
-        Since there are many more sphixels than there are spherical harmonics coefficients a sphixel map 
-       drawn from an Exponential prior on the left can only be approximately represented in the $Y_{lm}$ basis and the effective prior on pixels ends up looking more like a skewed Gaussian with a heavy right tail than an Exponential.
-  \label{fig:sphixels_to_pixels}
-    }
+    \includegraphics[width=1.\linewidth]{figures/pixels_to_spherical_harmonics.pdf}
+    \oscaption{pixels_to_harmonics}{%
+        Illustration of the transformation from a pixel map (left) defined on a fixed grid on the sphere into the spherical harmonic basis at $l=20$ (right) via a linear operator $\mathbf{P}^\dagger$.
+        The intensity of each pixel was drawn independently from an exponential prior.
+        The histograms below each of the maps show the distributions of intensities on the map. 
+        Since the pixel map is higher resolution than the spherical harmonic map at $l=20$, the         spherical harmonic map appears smoother and the intensity distribution is more similar to a skewed Gaussian rather than an exponential distribution.
+        Despite this fact we find that fitting for maps in the pixel basis and transforming them to spherical harmonics at each MCMC step in order to compute the light curve analytically with \textsf{starry} is superior to fitting for spherical harmonics because the pixel grid provides a strong constraint on the spherical harmonic map structure.
+  \label{fig:pixels_to_harmonics}}
     \end{centering}
@@
 
-To visualize the effect of the transformation from sphixels to spherical harmonics, in Figure~\ref{fig:sphixels_to_pixels} we plot a single draw of sphixels $\mathbf{p}'$ from an Exponential prior (left) in the Mollweide projection, map them to spherical harmonics (middle), and then generate another pixelated map from the spherical harmonics on a grid of the same size as the initial sphixel grid.
-The middle map is visibly smoother than the prior map and looking at the histograms (black) the effective prior looks more like a skewed Gaussian with a heavy right tail than an Exponential distribution.
-There is also minimal leakage into negative values of intensity.
-The reason for this is that the pixels $\mathbf{P}\,\mathbf{y}'$ generated from $\mathbf{P}^\dagger\mathbf{p}'$ do not completely respect the Exponential prior because some information is lost in going from sphixels to spherical harmonics.
-Nevertheless, in Section~\ref{ssec:sphixels_vs_harmonics} we find that setting priors on sphixels is a far better solution than using the spherical harmonic coefficients.
-
 \subsection{The likelihood}
 \label{ssec:likelihood}
-Given Eq.~\ref{eq:linear_model_pix} we can write down the likelihood for our data.
-We assume a Gaussian likelihood for the data with a dense covariance matrix generated with from a Gaussian Process.
-To compute the Gaussian process likelihood we use the fast Celerite method \citep{foreman-mackey2017} as implemented in the \textsf{celerite2} package (TODO: cite).
+Assuming we have a single light curve with $T$ data points and a map set by the pixels $\mathbf{p}$, the (Gaussian) log likelihood is given by
 \begin{equation}
-    \ln\mathcal{L}=-\frac{1}{2}\left[\mathbb{f}_\mathrm{obs}-(\mathbb{f} + \mathbb{b})\right]^{\top} \boldsymbol{\Sigma}^{-1}\left[\mathbb{f}_\mathrm{obs}-(\mathbb{f} + \mathbb{b})\right]
+    \ln\mathcal{L}=-\frac{1}{2}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]^{\top}
+    \boldsymbol{\Sigma}_l^{-1}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]
+    \quad,
+    \label{eq:likelihood}
 \end{equation}
-where $\mathbb{f}_\mathrm{obs}$ is the vector of stacked observed light curves, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbb{b}$ is a fixed flux offset per light curve accounting for stray flux not attributed to Io (mostly due to Jupiter).
-An important assumption here is that a single static map generates all of the light curves, an assumption which is violated if the surface emission changed substantially between observations. 
-For this reason we fit at most two light curves at a time relatively closely spaced in time.
+where $\mathbf{f}_\mathrm{obs}$ is the observed light curve, $\boldsymbol{\Sigma}$ is the data covariance matrix and $\mathbf{f}$ is predicted flux given by
+\begin{equation}
+    \mathbf{f}=\mathbf{A}'\,\mathbf{p} +b\,\mathbf{1}_T
+    \quad,
+    \label{eq:flux_model}
+\end{equation}
+where $\mathbf{A}'\equiv\mathbf{A}\mathbf{P}^\dagger$ and $b$ is a constant flux offset parameter which we have added to account for stray flux which cannot be attributed to Io (it is mostly due to emission from Jupiter).
+
+To model the data covariance $\boldsymbol{\Sigma}$ we use use a Gaussian Process and we compute the likelihood using the fast Celerite method \citep{foreman-mackey2017} as implemented in the \textsf{celerite2} package \citep{foreman-mackey2017a,foreman-mackey2018}.
+We use the simple (approximate) Matern 3/2 function which is parametrized by two values, a standard deviation parameter $\sigma_\mathrm{GP}$ and a characteristic timescale parameter $\rho_\mathrm{GP}$.
+The kernel is given by 
+\begin{equation}
+    k(\tau;\sigma_\mathrm{GP},
+    rho_\mathrm{GP})=\sigma_\mathrm{GP}^{2}\left[(1+1 / \epsilon) e^{-(1-\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}(1-1 / \epsilon) e^{-(1+\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}\right]
+    \quad,
+\end{equation}
+where $\tau=|t_n-t_m|$ and $\epsilon$ controls the quality of the approximation.
+A single element of the data covariance matrix $\boldsymbol{\Sigma}$ is then 
+\begin{equation}
+    \boldsymbol{\Sigma}_{nm}=\sigma_n^2\delta_{nm} + k(\tau;\sigma_\mathrm{GP},\rho_\mathrm{GP})
+    \quad,
+    \label{eq:data_covariance_element}
+\end{equation}
+where $\sigma_n$ is the errorbar for the n-th data point.
+In cases where we fit multiple independent light curves the total log likelihood is the sum of individual likelihoods defined in Equation~(\ref{eq:likelihood}).
 
@@
 \label{ssec:information_content}
-The mapping problem is famously ill posed meaning that specific linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Eq.~\ref{eq:linear_model}.
+The mapping problem is famously ill posed meaning that specific linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Equation~(\ref{eq:linear_model}) \citep{luger2021}.
 This means that even if we had noiseless observations it would still be impossible to recover certain features.
 To recover the greatest information about the surface we need to have some mechanism which breaks the various degeneracies.
-With phase curves only we can recover longitudinal variations in emission.
-Occultations are a lot better because the limb of the occultor sweeps across the surface of the occulted sphere, thereby exposing or blocking light from different points on the surface.
-Best case scenario is having phase curve observations plus a series of occultations by a small occultor at different latitudes and different phases.
-Observing phase curves and occultations in reflected light improves the model even more because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
-2020 in prep]{luger2019a}.
-In some cases for reflected light observations (phase curves of an inclined planet for example) there is no nullspace at all at low degrees of the map.
+With phase curves only we can recover primarily longitudinal variations in emission.
+Occultations are substantially better because the limb of the occultor sweeps across the surface of the occulted sphere, thereby exposing or blocking light from different points on the surface.
+An ideal set of observations would consist of phase curves together with observations of multiple occultations by a small occultor at different latitudes and different phases.
+Observing phase curves and occultations in reflected light improves the model further because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
+2021 in prep]{luger2019a}.
+In some cases for reflected light observations (phase curves of an inclined planet for example) there can even be no nullspace \emph{at all} low spherical harmonic degrees.
 
 We can reformulate these statements more precisely by computing a measure of information content of the different kinds of observations.
-Given that our model is linear, assuming Gaussian priors on the spherical harmonic coefficients with covariance $\boldsymbol{\Lambda}$ and a Gaussian likelihood, the posterior can be computed analytically and its mean is given by
+Given that our model is linear, assuming Gaussian priors on the spherical harmonic coefficients with covariance $\boldsymbol{\Lambda}_\mathbf{y}$ and a Gaussian likelihood, the posterior can be computed analytically and its mean is given by
 \begin{equation}
     \widehat{\mathbf{y}}=\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}\left(\mathbf{A}^{\top} \boldsymbol{\Sigma}_{\mathbf{f}}^{-1} \mathbf{f}+\boldsymbol{\Lambda}_{\mathbf{y}}^{-1} \boldsymbol{\mu}_{\mathbf{y}}\right)
+    \quad,
 \end{equation}
@@
 \end{equation}
-The posterior covariance matrix depends on the design matrix $\mathbf{A}$, the prior covariance  $\boldsymbol{\Lambda}$ and the data covariance $\boldsymbol{\Sigma}_{\mathbf{f}}$.
 We define the information content as the variance reduction of the posterior relative to the prior which is called \emph{posterior shrinkage}.
-It is defined as
+The posterior shrinkage $S$ is defined as \citep{luger2021a,betancourt2018}:
 \begin{equation}
-    1-\frac{\sigma^2_\mathrm{post}}{\sigma^2_\mathrm{prior}}
+S \equiv 1-\lim _{\sigma_{0}^{2} \rightarrow \infty} \frac{\sigma^{2}}{\sigma_{0}^{2}}
+    \quad,
 \end{equation}
-where $\sigma^2_\mathrm{prior}$ is the prior and $\sigma^2_\mathrm{post}$ is the posterior variance for a given parameter.
-For each spherical harmonic coefficient in $\mathbf{y}$ the posterior shrinkage is then the ratio of the diagonal elements of matrices $\boldsymbol{\Sigma}_{\hat{\mathbf{y}}}$ and $\boldsymbol{\Lambda}$.
-In order to compute the posterior shrinkage we first compute the design matrices using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
+where $\sigma^2_0$ is the prior variance and $\sigma^2$ is the posterior variance for a given spherical harmonic coefficient.
+It tells us how well we can constrain a particular coefficient in the limit of infinite SNR observations.
+Posterior shrinkage of 1 indicates that the data provides perfect information on the parameters while 0 indicates no gain in information relative to the prior.
+
+In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
 We take the ephemeris data from \textsf{JPL HORIZONS} and assume that it is known exactly and we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
-We need to assume some variance for the Gaussian prior on the $Y_{l,m}$ coefficients so we choose a broad prior $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$.
-Although the posterior shrinkage depends on this prior the main results do not change for a different choice of the prior.
 
-\begin{figure}[h!]
+\begin{figure}[t!]
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/information_content.pdf}
+    \includegraphics[width=\linewidth]{figures/information_content.pdf}
     \oscaption{InformationContent}{
-        The posterior shrinkage of different kinds of observations of Io as a function of spherical harmonic degree (angular scale), averaged across all $m$ modes.
+        The posterior shrinkage for different kinds of observations of Io as a function of spherical harmonic degree (angular scale), averaged across all $m$ modes.
     Posterior shrinkage of 1 represent maximum information gain in updating from the prior to the posterior while 0 represents no information gain. 
     The posterior variance has been computed for different kinds of simulated observations of Io over the course of a single year: phase curves (blue), occultations by Jupiter (orange), combined phase curves and occultations by Jupiter (green) and occulltations of Io by other Galilean moons (red lines).
-        Solid lines are for observations at SNR=100 and dashed are for observations at SNR=10.
         \label{fig:information_content}
@@
 Fig.~\ref{fig:information_content} shows the posterior shrinkage as a function of $l$ (averaged over all $m$ modes) for phase curve observations (blue lines), occultations by Jupiter (orange), the former two combined (green) and mutual occultations by other Galilean moons (red).
-Solid lines correspond to SNR=100 while dashed lines correspond to SNR=10 where the signal is defined as the min-max difference of the predicted flux.
-As expected, the mutual occultations of Io by other moons are by far the most informative with posterior shrinkage near unity at all angular scales up to $l=18$. 
+As expected, the mutual occultations of Io by other Galilean moons are by far the most informative with posterior shrinkage of unity at all angular scales considered. 
 Occultations by Jupiter are far less informative because we only see one side of Io during an occultation.
-This is also why there is a kink in the curve at $l=1$.
-We also see that the shrinkage is exactly zero for phase curves at all odd degrees above $l=2$ because phase curves for objects rotating about an axis perpendicular to the line of sight encode zero information on these coefficients because they are in the nullspace.
-Although observations of mutual occultations most easily break the degeneracies, they only occur every 6 years and more importantly they almost never occur while Io is in eclipse which means that only the brightest volcanoes will be visible above the reflected light background emission due to the Sun.
-Figure~\ref{fig:information_content} does not reflect this fact.
+Shrinkage for phase curve at odd degrees above $l=2$ is exactly zero because these coefficents are in the nullspace for objects rotating about an axis perpendicular to the line of sight these coefficients and therefore they cannot be constrained using only phase curves \citep{luger2021}.
+Observations of mutual occultations most easily break the degeneracies but they only happen every 6 years and they almost never happen while Io is in eclipse, which means that only the brightest volcanoes are visible above the reflected sunlight.
+This is not captured in Figure~\ref{fig:information_content}.
 
-Although Figure~\ref{fig:information_content} gives us some idea about which kinds of observations are most informative, it doesn't really tell us how well we can constrain very bright spot like features we expect to see on Io.
-To answer this question we have to simulate some data and the inference process.
+Although Figure~\ref{fig:information_content} gives us some idea about which kinds of observations are most informative, it doesn't really tell us how well we can constrain very bright spot-like features we expect to see on Io.
+To answer this question we have to simulate data and conduct the inference process.
 
-\subsection{Sphixels vs. spherical harmonics}
-\label{ssec:sphixels_vs_harmonics}
+\subsection{Pixels vs. spherical harmonics}
+\label{ssec:pixels_vs_harmonics}
 We use \textsf{starry} to generate a single simulated light curve of an occultation of Io by Jupiter from an $l=30$ map with known coefficients.
-The simulated map consists of a spherical harmonic expansion of a bright spot with a Gaussian profile which we add to a featureless map using the built in \textsf{add\_spot} function in \textsf{starry}.
+The simulated map consists of a spherical harmonic expansion of a bright spot with a Gaussian profile which we add to a uniform brightness map using the built in \textsf{add\_spot} function in \textsf{starry}.
 The expansion is in the quantity $\cos(\Delta\theta)$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere. 
-We place the spot at $13^\circ$ N latitude and $51^\circ$ E longitude, we set the diameter of the spot (given by  $2\Delta\theta$) to $5^\circ$ and the amplitude of the spot such that the total \emph{luminosity} (by default equal to 4 in \textsf{starry}) of the map increases by 50\% with the addition of the spot.
-We take ephemeris parameters (assumed to be fixed) from a real occultation of Io and assume an observational cadence of 1s and SNR=50.
-We use this dataset to test the difference between fitting setting a prior in the spherical harmonic basis (Eq.~\ref{eq:linear_model}) and in the sphixel basis (Eq.~\ref{eq:linear_model_pix}) by fitting an $l=20$ map to the dataset.
-Since we are only fitting a single light curve the inferred maps will be strongly prior dominated.
+We place the spot at $13^\circ$ N latitude and $51^\circ$ E longitude, we set the diameter of the spot ($2\Delta\theta$) to $5^\circ$ and the amplitude of the spot such that the total \emph{luminosity} of the map increases by 50\% with the addition of the spot.
+We generate two light curves with 150 data points, one for the duration of the ingress of the full occultation and the other for the egress.
+Because the limb of the occultor sweeps over the disc of Io at different angles during ingress and ingress, this makes it possible break most degeneracies in the map and recover the location of the true spot.
+We set the phase of the simulated map to $10^\circ$ W at the beginning of ingress and a phase of $10^\circ$ E at the end of egress.
+We assume that the geometry of the occultation is known exactly and set the errorbars such that SNR=50 where SNR is the signal is defined as the maximum flux of light curve.
+    We use this dataset to test the difference between setting a prior in the spherical harmonic basis $\mathbf{y}$ and in the pixel basis $\mathbf{p}$ by fitting an $l=20$ map to the dataset.
 
-In the first case we place a Gaussian prior on $Y_{lm}$ coefficients with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.1^2,\dots,0.1^2)$ and optimize for the values of the coefficients.
-In the second case we fit for sphixels $\mathbf{p}'$ evaluated on a fixed (latitude, longitude) grid with two sets of positive priors, a Half Gaussian prior with zero mean and an Exponential prior.
-We use four times as many sphixels as spherical harmonics.
-To evaluate the flux (Eq.~\ref{eq:linear_model_pix}) we map the sphixels to a spherical harmonic coefficient vector $\mathbf{y}$ using the matrix $\mathbf{P}^\dagger$ at each evaluation of the posterior.
-As the end product of the inference we do not use the sphixels $\mathbf{p}'$ but rather the spherical harmonic coefficients $\mathbf{y}'=\mathbf{P}^\dagger\mathbf{p}'$ generated from the sphixels.
-The coefficents $\mathbf{y}'$ can then be used to evaluate the map on a pixelated grid of arbitrary resolution via the matrix $\mathbf{P}$.
+In the spherical harmonic model we place a Gaussian prior on the $\mathbf{y}$ with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.5^2,\dots,0.5^2)$.
+Since the model is linear and the prior is Gaussian, the posterior probability distribution is also Gaussian and we can solve for the posterior mean and covariance matrix analytically \citep{luger2019a}.
+In the hybrid pixel model we place a positive exponential prior on the pixels evaluated on a Mollweide grid. 
+The purpose of the exponential prior is to favor sparser solutions for map because the exponential distribution pushes most pixels towards zero intensity.
+We use four times as many pixels as spherical harmonics.
+Although the model is also linear in this case, the posterior distribution for the pixels is not analytic because of the non-Gaussian prior so we sample the posterior distribution using MCMC instead.
+As the end product of inference we save the spherical harmonic coefficients $\mathbf{y}=\mathbf{P}^\dagger\mathbf{p}$ rather than the pixels themselves.
+The coefficients $\mathbf{y}$ can then be used to evaluate the map on a pixelated grid of arbitrary resolution via the matrix $\mathbf{P}$.
 
-\begin{figure}[h!]
+To ensure that the difference in the inferred maps is not in part due to a difference in the scale of the priors, we take 5000 samples from the prior on $y$ and evaluate $\mathbf{P}\mathbf{y}$ for each; we then compute the standard deviation of these pixels use that as the scale parameter in the exponential prior.
+We implement the pixel model in the probabilistic programming language \textsf{numpyro} \citep{phan2019a} which is built on top of the \textsf{JAX} \citep{jax2018github} library, and we fit it using Hamiltonian Monte Carlo with the No-U-Turn-Sampler (NUTS) \citep{hoffman2014}.
+\textsf{JAX} is a \textsf{numpy} like library which supports automatic differentiation, parallelization and GPUs.
+We run the chains until for 1000 tuning steps and 2000 final steps, monitoring divergences \citep{betancourt2013} and the R-hat  diagnostic  \citep{gelman1992a} to check for convergence.
+Since all models in this paper have hundreds if not thousands of parameters, it would not be possible to sample the posterior  without the use of automatic differentiation and Hamiltonian Monte Carlo (at least for non-Gaussian priors).
+
+\begin{figure}[t!]
     \begin{centering}
     \includegraphics[width=1.\linewidth]{figures/pixels_vs_harmonics.pdf}
-    \oscaption{sphixels_vs_harmonics}{%
-        Median estimates of $l=20$ maps (second panel from the top) produced by fitting a simulated light curve (bottom) which had been generated from an $l=30$ map consisting of a single bright spot (top).
-        The small circles beneath each inferred map show the progression of the occultation.
-        The map on the left corresponds to a model in which we directly fit for spherical harmonic coefficients $\mathbf{y}$ with a Gaussian prior.
-        The map in the middle corresponds to a model in which we instead fit for sphixels $\mathbf{p}'$ with a Half Gaussian prior but still use $\mathbf{y}$ to compute the flux.
-        The map on the right is the same as the middle one except we use an Exponential prior.
-        The scale parameter of the Half Gaussian and the Exponential prior is set to a value which approximates the scale of Gaussian prior on $\mathbf{y}$ to ensure fair comparison between the solutions.
-        The location of the true spot is not recovered correctly because a single light curve does not contain enough information to break the degeneracy in position along the limb of the occultor.
-        \label{fig:sphixels_vs_harmonics}
+    \oscaption{pixels_vs_harmonics}{%
+        Comparison between two models fitted to a simulated light curve of an occultation by Jupiter which was generated from a map consisting of a single bright spot (top map).  
+       Each of the columns beneath the true map shows the (median) posterior estimate of the map (top), the data and the posterior flux samples (middle row) and the residuals (bottom row).
+        The left column corresponds to a model in which we place a Gaussian prior on spherical harmonic coefficients $\mathbf{y}$ and fit for $\mathbf{y}$ while the right column correspond to a hybrid model in which we fit for pixels $\mathbf{p}$ (with an exponential prior on pixel intensity) but we use $\mathbf{y}$ to compute the flux analytically with \textsf{starry}.
+        The benefit of using pixels is that it is much easier to encode assumptions on what the map should look like in pixel space rather than spherical harmonic space.
+        With the pixel model we are able to recover the true map precisely while the spherical harmonic model fails to do that. 
+               \label{fig:pixels_vs_harmonics}
     }
@@
 
-To ensure that the difference in the inferred maps is not in part due to a difference in the scale of the priors, we take 10000 prior samples of the $y$ in the spherical harmonic model, compute the standard deviation and use that as the scale parameter of the Half Gaussian and the Exponential prior.
-We implement the model in the probabilistic programming language \textsf{numpyro} (CITE) which is built on top of the \textsf{JAX} library and fit it with Hamiltonian Monte Carlo using the No-U-Turn-Sampler (NUTS) (CITE).
-\textsf{JAX} is a \textsf{numpy} like library which supports automatic differentiation, parallelization and GPUs.
-We run the chains until for X tuning steps and Y final steps (TODO: HOW MANY?), monitoring divergences and the R-hat  diagnostic to check for convergence.
-Because these models have many hundreds if not thousands of parameters, it wouldn't be possible to fit them (at least for nontrivial priors) without automatic differentiation.
+To visualize the inferred maps we plot the heatmap of the median intensity at each point on the map computed from posterior samples.
+Results are shown in Figure~\ref{fig:pixels_vs_harmonics}.
+The top row shows the true map, beneath it we show the inferred maps in Mollweide projection for the two models (second row), the data and posterior flux samples (orange lines) and the residuals with respect to the median flux (bottom row).
+The difference between the two models is striking, the left map has an elongated feature which does not resemble the spot in the true map while the map on the right is nearly identical to the true map.
+We should emphasize here that the fact that the pixel model results in a spot-like map is mostly a consequence of the exponential prior which favors sparse solutions in pixel space.
+When we compared the spherical harmonic model to the pixel model using a prior with a lighter tail such as a Half Gaussian (Gaussian truncated at zero), we obtained a more elongated feature similar to shown on the left map in Figure~\ref{fig:pixels_vs_harmonics} but the map was still noticeably less complex because the positivity constraint substantially reduces the space of maps which fit the data well.
+Thus, the benefit of using the pixel model is that it easy to impose the positivity constraint on the map but also other constraints such as sparsity.
 
-The results are shown in Figure~\ref{fig:sphixels_vs_harmonics}.
-The top subplot shows the true map with a localized bright spot and the 
-inferred maps are shown in the second row from the top together with the progression of the occultation (miniature maps). 
-Bottom subplots show the simulated light curves, the predicted flux from the model and the normalized residuals.
-The difference between the inferred maps is substantial despite the fact that the predicted flux is similar in all three cases.
-The inferred map from the spherical harmonic model (left) has near zero intensity on the observer facing side of Io except for a bright arc tracing the projected limb of Jupiter at the location of the true spot.
-The flux on the unobserved side of Io is nearly uniform and significantly higher than the flux on the observer facing side which results in an unrealistic transition between the bright and the dark region at $\pm 90^\circ$ longitude.
-A very clear "ringing" pattern is visible in the with high intensity peaks and low (in some regions negative) intensity troughs.
-These features are a consequence of the finite order spherical harmonic expansion of the map and we could in principle get rid of them by fitting a much higher order map but at $l=20$ we are already pushing the limits of what \textsf{starry} can handle.
-Besides avoiding unphysical negative intensities, ringing is undesirable because we want to avoid situations in which the model uses the rings to explain the data instead of just placing a spot directly.
-For example, we find that for some fits at low $l$, the model would place a bright spot on the unobserved side of Io in order to produce a ringing artefact on the observed side to explain an increase or decrease in brightness in the light curve.
-This is happening to a lesser extent in the shown map where a small spot is visible at the right edge of the observed hemisphere in order to amplify the visible bright arc through ringing.
-
-The sphixel model with Half Gaussian priors produces a simpler map in which the unobserved hemisphere has much lower intensity but the arc is less sharply defined and more extended and as a result the predicted flux does not rise steeply enough compared to the light curve.
-Finally, the Exponential prior on sphixels results in a map with the most spot like feature 
-which is somewhat surprising because based on Figure~\ref{fig:sphixels_to_pixels}, we wouldn't expect much difference between the Half Gaussian and the Exponential priors.
-It seems that the heavier tail of the Exponential is nevertheless able to induce a sparser solution.
-The rightmost map also has the most visible ringing artefacts, an issue which we discuss in the following section.
+One issue with the map on the right is that there is a series of concentric rings around the spot which result in a wave-like pattern in the predicted flux and the residuals.
+This ringing pattern arises because representing spot-like features requires constructive interference between different spherical harmonic modes inside the spot and destructive interference elsewhere.
+The pattern is more pronounced when we fit a low resolution map (approximately $180/20=9^\circ$ in this case) and the model tries to represent a feature below the resolution of the map.
+Ringing is undesirable because we want to avoid situations in which the model uses the rings to explain the data instead of just placing a spot directly. 
+For example, we find that in some cases when we fit low degree maps, the model would place a bright spot on the unobserved side of Io in order to produce a ringing artefact on the observed side to explain an increase or decrease in brightness in the light curve.
+Fortunately, convolving the map with a spatial smoothing filter prior to evaluating the flux fixes this issue. 
+We describe how to apply the smoothing filter in the following section.
 
@@
 \label{ssec:spurious_features}
-To suppress ringing which results in regions of negative intensity surrounding a spot like feature as in Figure~\ref{fig:sphixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonics.
+To suppress ringing, which results in regions of negative intensity surrounding a spot-like feature as in Figure~\ref{fig:pixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonic coefficients.
 Mathematically, the filtering operation is a convolution between the map and some kernel function $B(\theta,\phi)$.
 Assuming both the map and the kernel function are expanded in terms of spherical harmonics, the convolution operation is simply a multiplication between the two sets of spherical harmonic coefficients.
-We choose a simple azimuthally symmetric Gaussian kernel function given by
+We use a Gaussian-like kernel function given by
 \begin{equation}
-    B(\theta)=\frac{1}{\sqrt{2 \pi \sigma_s^{2}}}\exp \left(-\theta^{2} / 2 \sigma_s^{2}\right)
+    B(\theta)=\frac{\exp \left(-\theta^{2} / 2 \sigma_s^{2}\right)}{2 \pi \sigma_s^{2}}
+    \quad,
 \end{equation}
-where $\sigma_s$ sets the characteristic scale of the smoothing.
+where $\sigma_s$ is a parameter which sets the characteristic scale of the smoothing.
 This function can be expanded in terms of spherical harmonics as
@@
 
-Figure~\ref{fig:smoothing_kernel} shows the effect of (Gaussian) smoothing on a spherical harmonic expansion of a spot with a Gaussian intensity profile.
-We place the spot at $0^\circ$ latitude and longitude and set the size of the spot $\Delta\theta$ to $5^\circ$.
-All three subplots show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
-The subplot on the left shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
-The middle subplot shows an intermediate level of smoothing where $\sigma_s=0.1$, meaning that all features on scales above $l\approx 10$ are exponentially suppressed.
-The negative ringing is a lot less visible albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
-For $\sigma_s=0.2$ (right) there is practically no ringing, but the expansions at $l=10$, $l=15$ and $l=20$ result in the spot of the same size because all coefficients above $l=5$ are significantly suppressed.
-
-\begin{figure}[h!]
+\begin{figure}[t!]
     \begin{centering}
@@
 
+Figure~\ref{fig:smoothing_kernel} shows the effect of (Gaussian) smoothing on a spherical harmonic expansion of a spot with a Gaussian intensity profile.
+We place the spot at $0^\circ$ latitude and longitude and set the size of the spot $\Delta\theta$ to $5^\circ$.
+All three subplots show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
+The subplot on the left shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
+The middle subplot shows an intermediate level of smoothing where $\sigma_s=0.1$, meaning that all features on scales above $l\approx 10$ are exponentially suppressed.
+The negative ringing is a lot less visible albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
+For $\sigma_s=0.2$ (right) there is practically no ringing, but the expansions at $l=10$, $l=15$ and $l=20$ result in the spot of the same size because all coefficients above $l=5$ are significantly suppressed.
+
 Thus, there is a trade-off between smoothing and the ability to resolve smaller scale features
@@
 In principle we can always get rid of ringing by fitting sufficiently high order maps.
-In practice, computing the analytic integrals computed by \textsf{starry} becomes computationally unstable above $l\approx 25$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
+In practice, computing the analytic integrals computed in \textsf{starry} becomes computationally unstable above $l\approx 20$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
 We find that setting $\sigma_s=2/l$ where $l$ is the order of expansion of the map  is a good default setting for $\sigma_s$.
 
-\section{Results with simulated data}
+\section{Results for simulated data}
 \label{sec:results_sim}
 \subsection{Fitting simulated ingress/egress light curves}
-In this section we use the same map to generate the data as in Figure~\ref{fig:sphixels_vs_harmonics} except now we simulate two light curves in order to break the degeneracy in the location of the spot, an ingress light curve generated from real ephemeris of Io disappearing behind the limb of Jupiter and egress light curve generated when Io reappears.
-We generate the light curves from an $l=25$ map and fit a map of the same order. 
-We apply a Gaussian smoothing filter to both the simulated map and the map we fit to the data and set the smoothing parameter to $\sigma_s=2/l=2/25$.
+\label{ssec:fitting_sim_ingress_egress}
+In this section we generalize the example from Section~\ref{ssec:pixels_vs_harmonics} such that the simulated map includes an additional faint hot spot located at $-15^\circ$ N latitude and $-40^\circ$ E longitude with a diameter of $5^\circ$.
+We set the amplitude of the ``faint" spot to 20\% of the luminosity of the featureless map.
+As before we assume that we know the ephemeris exactly.
+We generate the light curves from an $l=20$ map and fit a map of the same order and we apply a Gaussian smoothing filter to both the simulated map and the inferred map with the smoothing parameter set to $\sigma_s=2/l=0.1$.
+We fit the model with NUTS with 1000 warm-up steps and 2000 final steps.
 
-The prior we place on the sphixels is a sparse prior called the Regularized Horseshoe Prior (also known as the "Finnish Horseshoe") (CITE). 
-It is an improvement on the Horseshoe Prior (CITE).
-The horseshoe prior is a prior designed for use in sparse linear regression which is exactly what we are doing.
-The horseshoe prior sets a scale for each of the regression coefficients (sphixels) which is a product of a global scale $\tau$ and a local scale $\lambda_m$.
-It is defined hierarchically as 
-\begin{equation}
-\mathcal{Half}-\mathcal{C} 
-\end{equation}
-\begin{equation}
-\begin{aligned}
-\beta_{m} & \sim \mathcal{N}\left(0, \tau \cdot \lambda_{m}\right) \\
-    \lambda_{m} & \sim \mathcal{Half}-\mathcal{C} (0,1) \\
-    \tau & \sim \mathcal{Half-C} \left(0, \tau_{0}\right)
-\end{aligned}
-\end{equation}
-where $\tau_0$ is a characteristic global scale.
+We found that in cases where the simulated map consists of a bright and a faint spot the pixel model with an exponential prior such as the one we used in Section~\ref{ssec:pixels_vs_harmonics} does not recover the faint spot.
+Instead, we use a different heavy tailed prior called the Regularized Horseshoe prior\footnote{To be precise, we use the truncated version of the Regularized Horseshoe prior where the coefficients are required to be positive.} (also known as the ``Finnish Horseshoe") \citep{piironen2017}.
+This prior is specifically designed for use in Bayesian sparse linear regression. 
+It is an improvement on the Horseshoe prior introduced in \cite{carvalho2010a}.
+The key idea behind both kinds of Horseshoe priors is to set the scale for each regression coefficient (pixel) to a product of a global scale $\tau$ and a local scale $\lambda_i$ (where $i$ indexes all the pixels) and marginalize over these scales by setting a prior for each.
+For clarity, we discuss the Horseshoe priors in Appendix~\ref{app:horseshoe}.
 
-The regularized horseshoe prior is 
-\begin{equation}
-\begin{aligned}
-\beta_{m} & \sim \mathcal{N}\left(0, \tau \cdot \lambda_{m}\right) \\
-\tilde{\lambda}_{m} &=\frac{c \lambda_{m}}{\sqrt{c^{2}+\tau^{2} \lambda_{m}^{2}}} \\
-\lambda_{m} & \sim \mathcal{Half-C}(0,1) \\
-c^{2} & \sim \mathcal{Inv-G}\left(\frac{\nu}{2}, \frac{\nu}{2} s^{2}\right) \\
-\tau & \sim \mathcal{Half-C}\left(0, \tau_{0}\right)
-\end{aligned}
-\end{equation}
-
-The results are shown in Figure~\ref{fig:ingress_egress_simulated}.
-\begin{figure}[h!]
+\begin{figure}[t!]
     \begin{centering}
@@
     \oscaption{ingress_egress_sim_snr_50}{%
-Maximum A Posteriori (MAP) estimate of an $l=25$ map (right) produced by fitting a pair of simulated ingress and egress occultation light curves (bottom) which were generated from a $l=25$ map consisting of a single bright spot (left).
-       A Gaussian smoothing filter is applied to reduce the ringing artefacts.
-       Small circles beneath each inferred map show the progression of the occultation.
-        The model is able to recover the position of the true spot (marked with a grey cross) and there is noticeably less ringing than in Figure~\ref{fig:sphixels_vs_harmonics}.
+        Inferred $l=20$ map obtained by fitting a pair of simulated ingress/egress occultation light curves of Io using a hybrid pixel model with a Regularized Horseshoe prior on the pixels.
+With this prior, the model is able to accurately recover the true map.
+        The plot shows the true $l=20$ map (top), the posterior (median) estimate of the inferred map (second row), the inferred map as seen by the observer during the occultation (small circles), the data and posterior samples of the flux (orange lines), and the normalized residuals (bottom).
+        The location of the true spots on the inferred map is marker with a grey cross (X).
        \label{fig:ingress_egress_sim_snr_50}
@@
 
-\begin{figure}[h!]
+The results for a high signal-to-noise light curve (SNR=50) are shown in Fig.~\ref{fig:ingress_egress_sim_snr_50}, the model recovers both spots.
+The plot shows the true map (top row), the median posterior estimate of the inferred map (second row), the inferred map as seen by the observer during the occultation (small circles), the data and posterior samples of flux (orange lines) and the residuals with respect to a median estimate of the flux (bottom).
+The location of the true spots on the inferred map is marker with a grey cross (X).
+The bright spot is nearly indistinguishable from the true spot; the fainter spot is somewhat less well constrained but the error in position for both is at most a few degrees.
+Ringing artifacts are minimal because of the smoothing filter and there are no discernible patterns in the residuals.
+We found that without the Horseshoe priors the model was not able to capture the first step in the light curve which is due to the fainter spot coming in our out of view; it would only recover the brighter spot.
+In Fig.~\ref{fig:ingress_egress_sim_snr_10} we show the output of the same model assuming we have data of worse quality (SNR=10). 
+In this case the model still recovers both spots but the error in position of the spots is greater.
+
+\begin{figure}[t!]
     \begin{centering}
@@
 
-The inferred map looks significantly better than the one in Figure~\ref{fig:sphixels_vs_harmonics}. 
-With two occultation light curves the model is able to break the degeneracy in the location of the spot and thanks to the smoothing filter there is almost no visible ringing around the spot in the inferred map.
-Some residuals in the data are still present (WHY).
+\subsection{Comparison to a parametric model}
+It is instructive to compare the model developed in the previous section to a parametric model in which we assume that the map contains some fixed number of spot and we fit for the positions, amplitudes and the sizes of the spots.
+A parametric spot model might be useful if we want to fit for a small number of spots and we know what the map should look like.
+To test how the parametrized spot model compares to the model defined in Section~\ref{ssec:fitting_sim_ingress_egress} we fit it to the light curves shown in Figure~\ref{fig:ingress_egress_sim_snr_50}.
+The model consists of 4 parameters: the latitude, longitude, amplitude and size of the spot.
+We place uniform priors on the angles and positive Gaussian priors on other parameters. 
+We find that if the number of modeled spots matches the number of true spots the model easily converges to the true solution. 
+If the number of modeled spots is larger or smaller than the true number the model does not converge due to pathologies in the posterior distribution.
 
-\subsection{Comparison to a parametric model}
+Although a parametric approach would likely have been sufficient for modeling the light curves shown in this work, it does not work well when the number of spots is unknown or if the features aren't spots.
+There is no need to restrict ourselves to a parametric model because the pixel model gives the same results with only weak assumptions about the global structure of the map. 
+The computational advantages of the parametric spot model relative to the pixel model are minimal. 
+Even though the spot model has only 5 parameters per spot and the pixel model has thousands of parameters, the runtime for the pixel model is longer only by a factor of a few.
 
-\section{Results with IRTF data}
+\section{Results for IRTF data}
 \label{sec:results}
+\subsection{1998 pair of occultations by Jupiter}
+Having demonstrated that our model works well on simulated data, we turn to fitting observations of actual occultation of Io observed with the IRTF telescope.
+We selected two pairs of high quality ingress/egress light curves relatively closely spaced in time so that the assumption that the surface map is identical for both the ingress and the egress light curve is at least approximately correct; although we allow for a difference in the overall amplitude of the maps between the two occultations.
+We fit a pair of events from 1998, an ingress occultation observed on the 27th of August and an egress occultation observed on the 29th of November.
+For comparison, we also fit a pair of events observed nearly two decades later in 2017.
+The predicted fluxes are given by 
+\begin{align}
+    \mathbf{f}_I&=\mathbf{A}_I'\,\mathbf{p}_I +b_I\,\mathbf{1}_{N_I}\\
+    \mathbf{f}_E&=\mathbf{A}_E'\,\mathbf{p}_E +b_E\,\mathbf{1}_{N_E}
+\end{align}
+where $\mathbf{f}_I$ is the predicted flux for the ingress light curve with $N_I$ data points, $\mathbf{f}_E$ is the predicted flux for the egress light curve with $N_E$ data points, and $b_I$ and $b_E$ are constant flux offset parameters.
+Since we assume that the map is the same for both light curves up to an overall amplitude difference, we have
+\begin{equation}
+    \mathbf{p}_E=a\,\mathbf{p}_I
+    \quad,
+\end{equation}
+where $a$ is a dimensionless parameter.
+
+The total log likelihood is the sum of the log likelihoods for individual light curves (Equation~(\ref{eq:likelihood})). 
+To compute it we also need to specify the data covariance matrix defined in Equation~(\ref{eq:data_covariance_element}).
+Each element of the covariance matrix consists of a white noise component (errobars) and a correlated noise component (Gaussian Process).
+Since the IRTF light curves are not provided with estimated errobars, we choose to fit for all errobars simultaneously using a hierarchical approach in which we assign a global scale $l$ for all errorbars in a given light curve and we draw each individual errobar from a Half Normal distribution with standard deviation equal to that scale.
+That is, we have 
+\begin{align}
+    \sigma_{i,I}&\sim \mathcal{N}^+(0, l_E),\quad i=1,\dots,N_I\\
+    \sigma_{i,E}&\sim \mathcal{N}^+(0,l_I),\quad i=1,\dots, N_E
+\end{align}
+where $\sigma_{i,I}$ are the errobars for the ingress light curve and $\sigma_{i,E}$ are the errobars for the egress light curve.
+Treating errobars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data (and our model is regularized).
+The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errobars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Matern 3/2 kernel.
+All model parameters and their associated priors are listed in Table~\ref{tab:priors}.
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{4cm} W{l}{4cm} W{l}{6cm}}
+            \label{tab:priors}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter(s)}}
+             &
+            \multicolumn{1}{c}{\textbf{Description}}
+             &
+            \multicolumn{1}{c}{\textbf{Prior}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            %
+            \caption{%
+Parameters and priors for the final model. 
+            The subscript $I$ denotes parameters associated with the ingress light curve while the subscript $E$ denotes parameters associated with the egress light curve.
+$t_{\mathrm{max},I}$ and  $t_{\mathrm{max},E}$ are the durations of the ingress and egress occultations respectively.
+            The symbol $\mathcal{N}^+$ refers the normal distribution truncated at zero so that it only has support for positive values.
+            }
+            \endfoot
+            %
+            %
+            $\tau$ & global pixel scale &  \begin{minipage}{0.5\textwidth}  \shortstack[l]{$\mathrm{Half}-\mathcal{C}(0,\tau_0)$, $\tau_0$ defined in Equation~(\ref{eq:horseshoe_tau0}) \\with $p_0=0.8D$}\end{minipage}
+           %
+            \\
+            %
+            $c^2$ & slab scale squared & $\mathrm{Inv}-\mathcal{G}(\frac{\nu}{2},\frac{
+                \nu}{2}s^2)$, $s=1000$ and $\nu=4$
+            %
+            \\
+            %
+    $\overline{\lambda}_i , \quad m=1,\dots,D$  & local pixel scale & $\mathrm{Half}-\mathcal{C}(0,1)$
+            %
+            \\
+            $p_i, \quad i=1,\dots,D$& pixels & $\mathcal{N}^+(0, \tau\lambda_i)$, $\lambda_{i} =c \overline{\lambda}_{i}/\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{i}^{2}}$
+            %
+            \\
+            %
+                $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage}& $\mathcal{N}(1, 0.1)$
+             %
+            \\
+            %
+    $b_I$, $b_E$& flux offset &$\mathcal{N}(0, 4)$
+            %
+            \\
+            %
+            $l_I$, $l_E$& errorbar global scale&$\mathcal{N}^+(0,0.1)$
+            %
+            \\
+            %
+            $\sigma_{i,I}$, $\sigma_{i,E},\quad i=1,\dots,N$& individual errobars&
+            $\mathcal{N}^+(0,l_I),\quad \mathcal{N}^+(0,l_E)$
+            %
+            \\
+            %
+            $\sigma_{\mathrm{GP}, I}$, $\sigma_{\mathrm{GP}, I}$ & GP standard deviation&$\mathcal{N}^+(0,0.1),\quad \mathcal{N}^+(0,0.1)$
+             %
+            \\
+            %
+            $\rho_{\mathrm{GP},I}$, $\rho_{\mathrm{GP},E}$ & GP timescale  & $\mathcal{N}^+(0, t_{max, I}),\quad  \mathcal{N}^+(0, t_{max, E})$
+        \\
+            %
+        \end{longtable}
+    \end{center}
+\end{table}
+
+To fit the model we sample the posterior using the NUTS sampler for 1000 warm-up steps and 3000 final steps and as before, we monitor divergences and the R-hat statistic to ensure convergence.
+The inferred map for the 1998 pair of events is shown in Figure~\ref{fig:irtf_1998} and the median, 16th and 84th percentile estimates of model parameters from posterior samples are shown in Table~\ref{tab:irtf_1998}.
+The inferred map has two distinct hot spots, a bright hotspot in the Eastern hemisphere and a faint hotspot in the western hemisphere.
+The orange lines in the second panels from the bottom are posterior samples of flux from the full model which includes the map model and the Gaussian Process.
+The bottom panel shows the residuals with respect to the median flux.
+Each data point is shown with the median prediction of its errorbar.
+The posterior distribution for the errobars is shown in Figure~\ref{fig:irtf_1998_errorbars}.
+Both the global scale for the errobars and the individual errobars are well constrained by the data. 
+The outlier points are naturally accounted for in our model because those points end up having higher variance.
 
@@
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress_1998.pdf}
-    \oscaption{irtf_ingress_egress_1998}{%
-        Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
-       The small circles beneath each inferred map show the progression of the occultation.
-        Both light curves are assumed to be generated from the same map except for a difference in the overall amplitude.
-        We allow for multiplicative rescaling of the error bars and an additive flux offset for each light curve.
-        The model places a single bright spot to explain most of the variance in the data.
-        The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
-        \label{fig:irtf_ingress_egress_1998}
+    \includegraphics[width=1.\linewidth]{figures/irtf_1998.pdf}
+    \oscaption{irtf_main_plots}{%
+Inferred $l=20$ maps obtained by fitting a pair of observations of occultations of Io by Jupiter in 1998.
+        The observations were made several months apart with the NASA Infrared Telescope Facility (IRTF).
+We fit a single map to both observations simultaneously although we allow for a difference in the overall amplitude of the map between ingress and egress.
+Our model includes a Gaussian Process which accounts for both the correlated noise due to seeing in the data, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
+We also fit for all errobars simultaneously using a hierarchical model and we plot the median estimates of those errobars.
+        The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
+        The maps show two hotspots, the bright one is emission from Loki and the faint one is most likely emission from Kanehekili.
+        A detailed view of the two hot spots is shown in Figure~\ref{fig:irtf_1998_spots}.
+     \label{fig:irtf_1998}
     }
@@
 
-\begin{figure}[ht!]
+Despite the fact that our noise model is extremely flexible, it does not seem to overfit the data because the two major steps in the light curves correspond to spots on the map.
+The Gaussian Process accounts for the  variation in the data due to atmospheric variability, the emission due to surface features which are too faint to be well constrained by the physical model and the limitation of the physical model to capture the true size of the spot.
+There is a trade-off between the explanatory power of the noise model and the physical model. 
+In general, we expect that a given feature in the light curve will be accounted for by the physical model if the physical model provides a better explanation for the data than the noise model.
+We will return to this point later.
+
+\begin{figure}[t!]
     \begin{centering}
-    \includegraphics[width=1.\linewidth]{figures/irtf_ingress_egress_2017.pdf}
-    \oscaption{irtf_ingress_egress_2017}{%
-        Maximum A Posteriori (MAP) estimate of $l=25$ maps (top) produced by fitting a pair of IRTF ingress (left) and egress (right) occultation light curves of Io by Jupiter from 1998.
-       The small circles beneath each inferred map show the progression of the occultation.
-        Both light curves are assumed to be generated from the same map except for a difference in the overall amplitude.
-        We allow for multiplicative rescaling of the error bars and an additive flux offset for each light curve.
-        The model places a single bright spot to explain most of the variance in the data.
-        The visible patterns in the residuals are likely due to additional hot spots and the limited resolution of our maps.
-        \label{fig:irtf_ingress_egress_2017}
+    \includegraphics[width=\linewidth]{figures/irtf_1998_errobars.pdf}
+    \oscaption{irtf_main_plots}{%
+        Posterior distribution for the errobars of the 1998 pair of light curves shown in Figure~\ref{fig:irtf_1998}. 
+        Each color corresponds to a single data point in the light curve.
+        The errobars are estimated using a hierarchical model in which we assume  that each errobar is drawn from a Half Gaussian distribution with a global scale parameter common to all errobars in a single light curve.
+       \label{fig:irtf_1998_errorbarss}
     }
@@
 
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{2cm} W{l}{5cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_1998}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Description}}
+            &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Inferred parameters for the pair of occultations observed in 1998 using the IRTF telescope.
+                }
+            \endfoot
+            $\tau$ & global pixel scale &   $0.870_{-0.221}^{+0.246}$ &  intensity
+            \\
+             $c$ & slab scale & $4304.302_{-1162.250}^{+2123.962}$ & intensity 
+            \\
+                $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage} &  $1.154_{-0.013}^{+0.014}$ & dimensionless
+            \\
+            $b_I$ & flux offset ingress & $0.014_{-0.013}^{+0.077}$ & GW/um/sr
+            \\
+            $b_E$&flux offset egress & $0.362_{-0.335}^{+0.438}$ & GW/um/sr
+            \\
+            $l_I$& errorbar scale ingress & $0.253_{-0.030}^{+0.036}$ & GW/um/sr
+            \\
+            $l_E$& errorbar scale egress &$0.461_{-0.042}^{+0.042}$ & GW/um/sr
+            \\
+            $\sigma_{\mathrm{GP}, I}$ & GP standard deviation ingress & $0.633_{-0.042}^{+0.047}$ & GW/um/sr 
+            \\
+            $\sigma_{\mathrm{GP}, E}$ & GP standard deviation egress &$0.453_{-0.052}^{+0.054}$ & GW/um/sr
+            \\
+            $\rho_{\mathrm{GP},I}$ & GP timescale ingress & $0.078_{-0.010}^{+0.011}$ & minutes
+            \\
+            $\rho_{\mathrm{GP},E}$ & GP timescale egress & $0.099_{-0.021}^{+0.027}$ & minutes
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
+
+To obtain some measure of the location of the inferred spots and its uncertainty, for each posterior sample of the spherical harmonic coefficients $\mathbf{y}$ we find the local maximum of intensity in a region around each of the spots, we then compute percentile estimates of spot latitude and longitude.
+In addition to the locations of the spots, we also compute the total power emitted within a 15 degree range in latitude and longitude around the (inferred) center of the spots.
+Both of these quantities are listed in Table~\ref{tab:irtf_1998_derived}.
+
+Figure~\ref{fig:irtf_1998_spots} shows  a contour map of both hot spots overlaid on top of the U.S.
+Geological Survey's map of the surface of Io \cite{williams2011} which was constructed from Galileo observations.
+The plot shows the error in the inferred latitude and longitude for each spot (white lines) and a contour map computed from the median posterior estimate of the map.
+The contour lines correspond to the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background" region around the spot.
+
+The location of the bright hotspot is $16.414_{-0.011}^{+0.027}\quad^\circ$ N latitude and $53.107_{-0.033}^{+0.041}\quad^\circ$ E longitude which corresponds to the location of Loki Patera.
+The faint hot spot is at $-15.756_{-11.382}^{+3.812}\quad ^\circ$ N latitude and $321.568_{-4.208}^{2.803}\quad^\circ$ E longitude which is the Kanehekili Fluctus lava flow.
+The error on the inferred position of peak intensity of the Loki hotspot is only a fraction of a degree which is much smaller than the minimum resolution of the map features set by the degree of the map; this corresponds to an uncertainty of less than a kilometer on the surface of Io.
+Thus, \textbf{despite the fact that at $l=20$ the resolution of maps is limited to about $9^\circ$, we can constrain the centroid of the spots much more precisely}.
+We should note however that this errorbar does not include a possible systematic shift in position due to a wrong estimate of Jupiter's effective radius (see Section~\ref{ssec:effective_radius}).
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{4cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_1998_derived}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Derived parameters of the two hot spots visible in Figure~\ref{fig:irtf_1998}.
+                The latitude and longitude of the spots are estimated by finding the peak intensity of each spot for each posterior sample.
+            The power of the spot is defined as the total emission from within a 15 degree circle around the (inferred) location of the spot.
+        }
+            \endfoot
+            Spot 1 latitude  & $16.295^{+0.009}_{-0.010}$& degrees 
+            \\
+             Spot 1 (East) longitude & $53.105^{+0.011}_{-0.011}$& degrees 
+            \\
+                Spot 1 power  ingress & $52.394^{+0.898}_{-0.773}$ & GW/um 
+            \\
+                Spot 1 power  egress & $60.422_{-1.151}^{+1.194}$ & GW/um 
+                \\
+            Spot 2 latitude  & $-16.129_{-7.929}^{+4.268}$& degrees 
+            \\
+             Spot 2 (East) longitude & $-37.422_{-0.264}^{+0.778}$ & degrees 
+            \\
+                Spot 2 power  ingress & $5.156_{-0.634}^{+0.818}$ & GW/um 
+                \\
+                Spot 2 power  egress & $5.949_{-0.721}^{+0.957}$ & GW/um 
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
+
 \begin{figure}[ht!]
     \begin{centering}
-    \includegraphics[width=.5\linewidth]{figures/irtf_spot_overlay_1998.pdf}
-    \oscaption{irtf_ingress_egress_loki}{%
-        Hot spot from the inferred maps shown in Figure~\ref{fig:irtf_ingress_egress} overlaid on top of the U.S. Geological Survey's map of the surface of Io (CITE) which was
-        constructed from Galileo observations.
-        The location of the hot spots matches the location of Loki Patera, the largest active volcano on the surface of Io. 
-        \label{fig:irtf_ingress_egress_loki}
+    \includegraphics[width=\linewidth]{figures/irtf_1998_spots.pdf}
+    \oscaption{irtf_spots_plot}{%
+        Contour plot of the hot spots shown in Figure~\ref{fig:irtf_1998} overlaid on top of the U.S.
+Geological Survey's map of the surface of Io which has been constructed from observations by the Galileo spacecraft.
+        The left hotspot is centered around Loki Patera, the right hotspot is centered at the Kanehekili Fluctus lava flow.
+The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background" region around the spot.
+        \label{fig:irtf_1998_spots}
     }
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
+To see how the above results change if we don't include a Gaussian Process in the noise model we fit the same pair of occultations from 1998 using the same priors, the results are shown in Figure~\ref{fig:irtf_1998_no_GP}.
+The main difference in the inferred map compared to Figure~\ref{fig:irtf_1998} is that there are two extra spots visible in the map.
+The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve which is Loki coming out and into view during the occultation.
+The model inflates the errobars around those times because it unable to make the spot small enough.
+This results in the single hot spot at the location of Loki shown in Figure~\ref{fig:irtf_1998} morphing into two spots.
+While this feature is almost certainly spurious, the other spot in the northwestern hemisphere appears more likely to be real.
+Looking at the miniature maps in Figure~\ref{fig:irtf_1998_no_GP}, this spot is in view only at egress and it corresponds to a small step in the light curve starting at 0.9 minutes.
+The estimated location of this spot is $20.449_{-0.066}^{+1.253}\quad^\circ$ N latitude and $53.107_{-0.115}^{+0.296}\quad^\circ$ W longitude.
+This location is to the mountain Mongibello Mons but it does not correspond to a well known hotspot.
+Overall, we conclude that that including the Gaussian Process prevents the physical model from overfitting the data although it might occasionally pick up a feature in thedat which is due to a faint real hot spot.
+With a particular scientific goal in mind, it is straightforward to experiment with different noise models to test how the properties of any given spot change.
+
+One other notable feature in Figure~\ref{fig:irtf_1998_no_GP} is that the first step in the ingress light curve at around 0.6 minutes isn't fully accounted for by the model.
+Since the model had no trouble accounting for a similar a step for simulated data shown in Figure~\ref{fig:ingress_egress_sim_snr_50} the reason why it didn't do so in this case is likely because doing so would result in a poorer fit for the egress light curve.
+The two occultations were observed months apart so we expect that our assumption that the map has not changed except for an overall amplitude is wrong in detail.
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/irtf_1998_no_GP.pdf}
+    \oscaption{irtf_main_plots}{%
+        Same as Figure~\ref{fig:irtf_1998} except this figure shows the output of a model which does not include a Gaussian Process to account for correlated structure in the data.
+        As a result, the model tries to account for correlations in the data by placing two extra spots on the map and inflating errorbars.
+        At least one of the two extra spots is artificial. 
+     \label{fig:irtf_1998_no_GP}
+    }
+    \end{centering}
+\end{figure}
+
+\subsection{2017 pair of occultations by Jupiter}
+To test how our model generalizes to a different dataset we fit a pair of observations from 2017, an ingress occultation observed on the 31st of March and an egress occultation observed on the 11th of May.
+We use the exact same model as the one we used to produce Figure~\ref{fig:irtf_1998}.
+The results are shown in Figure~\ref{fig:irtf_2017} and the inferred parameters are listed in Table~\ref{tab:irtf_2017}.
+A contour plots of the two spots overlaid on top of a surface map of Io from Galileo observations is shown in Figure~\ref{fig:irtf_2017_spots} and the derived spot parameters are listed in Table~\ref{tab:irtf_2017_derived}.
+The inferred map shows two spots, one of which is Loki. 
+Figure~\ref{fig:irtf_2017_spots} shows that the peak emission from Loki is again constrained very precisely but the location of the peak appears to have shifted southward since 1998.
+The location of the other hotspot corresponds to Janus Patera.
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=1.\linewidth]{figures/irtf_2017.pdf}
+    \oscaption{irtf_2017}{%
+Inferred $l=20$ maps obtained by fitting a pair of observations of occultations of Io by Jupiter in 2017.
+        The observations were made several months apart with the NASA Infrared Telescope Facility (IRTF).
+We fit a single map to both observations simultaneously although we allow for a difference in the overall amplitude of the map between ingress and egress.
+Our model includes a Gaussian Process which accounts for both the correlated noise due to seeing in the data, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
+We also fit for all errobars simultaneously using a hierarchical model and we plot the median estimates of those errobars.
+        The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
+        The maps show two hotspots, the bright one is emission from Loki and the faint one is emission from Janus.
+        A detailed view of the two hot spots is shown in Figure~\ref{fig:irtf_2017_spots}.
+                \label{fig:irtf_2017}
+    }
+    \end{centering}
+\end{figure}
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{2cm} W{l}{5cm} W{l}{3cm}  W{l}{3cm}}
+            \label{tab:irtf_2017}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Description}}
+            &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Inferred parameters for the pair of occultations observed in 2017 using the IRTF telescope.
+                }
+            \endfoot
+            $\tau$ & global pixel scale &   $0.973_{-0.247}^{+0.255}$ &  intensity
+            \\
+             $c$ & slab scale & $5866.860_{-1580.812}^{+2527.995}$ & intensity 
+            \\
+                $a$ &   \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage}  & $1.434_{-0.010}^{+0.011}$ & dimensionless
+            \\
+            $b_I$ & flux offset ingress & $0.025_{-0.024}^{+0.140}$ & GW/um/sr
+            \\
+            $b_E$& flux offset egress & $1.026_{-0.263}^{+0.238}$ & GW/um/sr
+            \\
+            $l_I$ & errobar scale ingress &$0.971_{-0.056}^{+0.056}$ & GW/um/sr
+            \\
+            $l_E$& errorbar scale egress & $0.520_{-0.093}^{+0.079}$ & GW/um/sr
+            \\
+            $\sigma_{\mathrm{GP}, I}$ & GP standard deviation ingress  & $0.126_{-0.055}^{+0.129}$ & GW/um/sr 
+            \\
+            $\sigma_{\mathrm{GP}, E}$ & GP standard deviation egress & $0.601_{-0.093}^{+0.083}$ & GW/um/sr
+            \\
+            $\rho_{\mathrm{GP},I}$ &  GP timescale ingress & $2.160_{-2.030}^{+3.333}$ & minutes
+            \\
+            $\rho_{\mathrm{GP},E}$ & GP timescale egress & $0.020_{-0.013}^{+0.011}$ & minutes
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/irtf_2017_spots.pdf}
+    \oscaption{irtf_spots_plot}{%
+        Contour plot of the hot spots shown in Figure~\ref{fig:irtf_2017} overlaid on top of the U.S.
+Geological Survey's map of the surface of Io which has been constructed from observations by the Galileo spacecraft.
+        The left hotspot is centered around Loki Patera, the right hotspot is centered at Janus Patera.
+The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background" region around the spot.
+        \label{fig:irtf_2017_spots}
+    }
+    \end{centering}
+\end{figure}
+
+\renewcommand*{\arraystretch}{1.4}
+\begin{table}[t!]
+    \begin{center}
+        \begin{longtable}{W{l}{4cm} W{l}{3cm} W{l}{3cm}}
+            \label{tab:irtf_2017_derived}
+            \\
+            %
+            \toprule
+            \multicolumn{1}{c}{\textbf{Parameter}}
+             &
+            \multicolumn{1}{c}{\textbf{Value}}
+             &
+            \multicolumn{1}{c}{\textbf{Unit}}
+            \\
+            \midrule
+            \endhead
+            \bottomrule                                 
+            \\
+            \caption{%
+                Derived parameters of the two hot spots visible in Figure~\ref{fig:irtf_2017}.
+                The latitude and longitude of the spots are derived by computing the centroid of points around the spots which are in the 90th percentile of intensity.
+            The power is defined as the total emission from within a 15 degree circle around the (inferred) location of the spot.
+        }
+            \endfoot
+                            Spot 1 latitude  & $12.193^{+0.011}_{-0.008}$ & degrees 
+            \\
+             Spot 1 (East) longitude & $52.515_{-0.009}^{+0.008}$ & degrees 
+            \\
+                Spot 1 power  ingress & $74.059_{-0.689}^{+0.911}$ & GW/um 
+            \\
+                Spot 1 power  egress & $106.158_{-1.412}^{+1.440}$ & GW/um 
+                \\
+            Spot 2 latitude  & $-4.114_{-8.327}^{+4.029}$ & degrees 
+            \\
+             Spot 2 (East) longitude & $-41.055_{-8.588}^{+0.433}$ & degrees 
+            \\
+                Spot 2 power  ingress & $5.171_{-1.007}^{+1.543}$ & GW/um 
+                \\
+                Spot 2 power  egress & $7.431_{-1.403}^{+2.227}$ & GW/um 
+            \\
+        \end{longtable}
+    \end{center}
+\end{table}
+
+\section{Discussion}
+\label{sec:discussion}
+\subsection{Occultation mapping of Io}
+We have presented a novel model for reconstructing volcanic emission features on Io from occultation light curves.
+It is built on top of the \textsf{starry} algorithm which enables fast analytic computation of occultation light curves using spherical harmonics.
+This approach is substantially different from past work because we do not assume where the volcanic features are located on the surface of Io, how many there are or what they look like.
+Instead, we place weaker assumptions on the global structure of the map by requiring that the inferred map has positive intensity everywhere and more importantly that it is \emph{sparse}.
+Besides the map model, our method also incorporates a sophisticated noise model which includes a Gaussian Process and a hierarchical model for the errorbars which are unknown.
+As a result of the sparsity and positivity constraints and the flexible noise model,
+our model is parsimonious, it places features on the map only if the data provides strong evidence for existence of those features.
+This property is not always desirable but it works very well for Io, whose surface is covered with small bright volcanic hotspots.
+Our model is superior to parametric methods in which we assume some fixed number of spots on the surface of Io and fit for the locations of those spots because we do not need to make such strong assumptions on the surface and the computational cost of the parametric models is comparable to our approach.
+
+We test the model first on simulated data and then on observations of actual occultations of Io by Jupiter taken using NASA's Infrared Telescope Facility.
+We choose two pairs of light curves to demonstrate that the model gives useful results.
+Each pair consists of an ingress observation and an egress observation of an occultation. 
+The two observations are sufficient to break the degeneracy in the position of the spots because Jupiter's limb sweeps across the projected disc of Io at different angles at ingress and egress.
+Using a pair of observations from 1998 we infer a map consisting of two hot spots.
+Locations of both hotspots correspond to well known features on the surface of Io, the major volcano Loki and the lava flow Kanehekili.
+We also find circumstantial evidence for a third hot spot.
+Because our model is fully probabilistic, we can derive uncertainties on location of the inferred hot spots and the total power emitted from the hot spot.
+In addition to the pair of observations from 1998, we test the model on another pair of observations from 2017.
+We again find two hotspots, one of which is Loki (although the peak of the intensity shifted relative to the 1998 map) and the other is Janus Patera.
+
+This paper is merely a first step in a series of papers dedicated to probabilistic modeling of Io's surface and also extending the models to exoplanet surfaces. 
+The major issue with the model presented in this work is that we can only fit a static map to some number of light curves.
+We are unable to model time variable features and quantify that variability.
+In Paper II we aim to develop a generalized model with which we will be able to fit all IRTF light curves simultaneously and infer a time-dependent map.
+
+The main limitation of our model besides the fact that we cannot account for time-dependent maps is the limited resolution of the spherical harmonic maps for which \textsf{starry} can compute occultation light curves.
+Although we can still constrain the peak intensity of spots (or some other measure of the center of emission) with much higher precision, we do lose the ability to resolve two spots close to each other and the ability to constrain the actual size of the spots.
+It is quite possible that we can get around this problem by computing the various integrals in starry numerically using high precision arithmetic.
+Since all these operations are contained in the design matrix $\mathbf{A}$ (assuming that the ephemeris is fixed) we would only need to compute the expensive numerical integrals once for each occultation.
+To be able to constrain the size of the Loki hotspot for example, we would need to fit maps on the order of $l\approx 50$.
+
+\subsection{Relevance to mapping of exoplanets} 
+Exoplanets with likely extreme volcanism are prime targets for future secondary eclipse observations by the James Webb Space Telescope. 
+The formalism presented in this paper easily generalizes to exoplanets. 
+Nearly every aspect of the model we have discussed applies to exoplanets as well.
+In fact, modeling secondary eclipses exoplanets is simpler in a way because with exoplanets we can only hope to constrain lower resolution features on the map.
+
+\subsection{Future work}
+
+\appendix
+\section{Horseshoe priors}
+\label{app:horseshoe}
+The Regularized Horseshoe prior \citep{piironen2017} is specifically designed for use in Bayesian sparse linear regression. 
+It is a generalization of the Horseshoe prior introduced in \cite{carvalho2010a}.
+The idea behind the Horseshoe prior is to set the scale for each regression coefficient (pixel) to a product of a global scale $\tau$ and a local scale $\lambda_i$ where $i$ indexes all the pixels.
+The Horseshoe prior is defined hierarchically as 
+\begin{equation}
+\begin{aligned}
+    &\tau  \sim \mathrm{Half}-\mathcal{C} \left(0, \tau_{0}\right)\\
+    &\lambda_{i}  \sim \mathrm{Half}-\mathcal{C} (0,1) \\
+    &p_{i}  \sim \mathcal{N}\left(0, \tau \lambda_{i}\right) 
+\end{aligned}
+    \quad,
+    \label{eq:horseshoe}
+\end{equation}
+where $p_i$ are the pixels.
+Each local scale parameter is drawn from a unit scale heavy tailed Half Cauchy distribution which allows for very large values of the pixels.
+The global scale parameter is also a free parameter, drawn from a Half Cauchy distribution with the scale equal to $\tau_0$.
+The Horseshoe prior is closely related to the spike-and-slab prior which is a mixture between a delta function prior at zero (\emph{spike}) and some other prior elsewhere (\emph{slab}).
+
+The Regularized Horseshoe prior adds another level to Equation~(\ref{eq:horseshoe}) in order to allow fine tuned control of sparsity and to regularize very large values of coefficients in cases where the data is only weakly constraining.
+\cite{piironen2017} show that the Regularized Horseshoe prior can be considered as a continuous counterpart of the spike-and-slab prior with a finite slab width $c$ whereas the Horseshoe prior resembles a spike-and-slab prior with a slab of infinite width.
+The prior is defined by
+\begin{equation}
+\begin{aligned}
+    &\tau  \sim \mathrm{Half}-\mathcal{C}\left(0, \tau_{0}\right)\\
+    &c^{2}  \sim \mathrm{Inv}-\mathcal{G}\left(\frac{\nu}{2}, \frac{\nu}{2} s^{2}\right) \\
+    &\overline{\lambda}_{i}  \sim \mathrm{Half}-\mathcal{C}(0,1)\\
+    &\lambda_{i} =\frac{c \overline{\lambda}_{i}}{\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{i}^{2}}} \\
+    &p_{i}  \sim \mathcal{N}^+\left(0, \tau \lambda_{i}\right) 
+\end{aligned}
+    \label{eq:reg_horseshoe}
+\end{equation}
+Integrating out the slab scale $c$ implies a marginal $\mathrm{Student}-\mathit{t}\,(\nu,0,s)$ prior for pixels far from zero.
+When pixels $p_i$ are close to zero ($\tau^2\overline{\lambda}_i^2\ll c^2$) we have $\lambda_i^2\rightarrow\overline{\lambda}_i^2$ and the prior approaches the original Horseshoe.
+When pixels are far from zero ($\tau^2\overline{\lambda}_i^2\gg c^2$) then $\lambda_i^2\rightarrow c^2/\tau^2$ and the prior approaches $\mathcal{N}(0, c)$.
+
+\cite{piironen2017} suggest the following expression to set the scale parameter $\tau_0$ which is an estimate of the global scale of the pixels 
+\begin{equation}
+    \tau_0=\frac{p_0}{D-p_0}\frac{\sigma}{\sqrt{n}}
+    \quad,
+    \label{eq:horseshoe_tau0}
+\end{equation}
+where $p_0$ is our prior guess for the number of significant pixels that are sufficiently far above zero, $D$ is the total number of pixels, $n$ is the number of data points and $\sigma$ is the standard deviation of the data points (the errobars).
+Thus, we only need to specify $p_0$, the degree of freedom parameter $\nu$ and the slab width $c$.
+
+When using the Regularized Horseshoe prior in a small data regime it is often necessary to use the non-centered parametrization to avoid funnels in the posterior which are often present in hierarchical models\footnote{\url{https://mc-stan.org/docs/2_26/stan-users-guide/reparameterization-section.html}}.
+The purpose of this reparametrization is to reduce the dependence between the hyperparameters in the posterior.
+To implement the non-centered parametrization we replace priors in Equation~\ref{eq:reg_horseshoe} with zero mean and unit variance priors and rescale them with deterministic transforms as follows
+\begin{equation}
+\begin{aligned}
+    &\overline{\tau} \sim \mathrm{Half}-\mathcal{C}\left(0, 1\right)\\
+    &\overline{c^{2}}  \sim \mathrm{Inv}-\mathcal{G}\left(\frac{\nu}{2}, 1\right) \\
+    &\overline{\lambda}_{i}  \sim \mathrm{Half}-\mathcal{C}(0,1) \\
+    &\overline{p}_{i}  \sim \mathcal{N}^+\left(0, 1\right)\\
+    &\tau=\tau_0\overline{\tau}\\
+    &c^2=\frac{\nu}{2}s^2\,\overline{c^2}\\
+    &\lambda_{i} =\frac{c \overline{\lambda}_{i}}{\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{i}^{2}}} \\
+    &p_i = \tau\lambda_i\,\overline{p}_i
+\end{aligned}
+    \label{eq:reg_horseshoe_noncentered}
+\end{equation}
+We find that without using the non-centered parametrization the sampling is problematic and there are lots of divergences in the gradients of the parameters; with the non-centered parametrization there are no problems with sampling.
+
 \clearpage

### 2021-03-02 paper/figures/pixels_vs_harmonics.py
Changed the figure again.

@@ -6,6 +6,8 @@ from matplotlib import pyplot as plt
 from matplotlib import colors
 import matplotlib.gridspec as gridspec
 from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+import matplotlib.cm as cm
+
 
 import starry
 import jax.numpy as jnp
@@ -16,10 +18,13 @@ from numpyro.infer import *
 
 from volcano.utils import get_smoothing_filter
 
+from scipy import optimize
+
 numpyro.enable_x64()
+numpyro.set_host_device_count(4)
 
 np.random.seed(42)
-starry.config.lazy = True
+starry.config.lazy = False
 
 
 def get_median_map(
@@ -28,7 +33,7 @@ def get_median_map(
     projection="Mollweide",
     inc=90,
     theta=0.0,
-    nsamples=20,
+    nsamples=100,
     resol=300,
 ):
     imgs = []
@@ -41,17 +46,26 @@ def get_median_map(
         map[1:, :] = x[1:] / map.amp
 
         if projection == "Mollweide":
-            im = map.render(projection="Mollweide", res=resol).eval()
+            im = map.render(projection="Mollweide", res=resol)
         else:
-            im = map.render(theta=theta, res=resol).eval()
+            im = map.render(theta=theta, res=resol)
         imgs.append(im)
 
     return np.median(imgs, axis=0)
 
 
-# Set up mock map
-xo_sim = np.linspace(37.15, 39.43, 120)
-yo_sim = np.linspace(-8.284, -8.27, 120)
+npts = 150
+xo_eg = np.linspace(37.15, 39.43, npts)
+yo_eg = np.linspace(-8.284, -8.27, npts)
+
+xo_in = np.linspace(-39.5, -37.3, npts)
+yo_in = np.linspace(-7.714, -7.726, npts)
+
+xo_com = np.concatenate([xo_in, xo_eg])
+yo_com = np.concatenate([yo_in, yo_eg])
+
+theta_in = 350.0
+theta_eg = 10.0
 ro = 39.1
 
 ydeg_true = 30
@@ -59,22 +73,29 @@ map_true = starry.Map(ydeg_true)
 spot_ang_dim = 5 * np.pi / 180
[…]

### 2021-03-02 paper/figures/simulated_ingress_egress.py
Some minor changes

@@ -19,6 +19,7 @@ from volcano.utils import *
 np.random.seed(42)
 starry.config.lazy = False
 numpyro.enable_x64()
+numpyro.set_host_device_count(4)
 
 xo_eg = np.linspace(37.15, 39.43, 150)
 yo_eg = np.linspace(-8.284, -8.27, 150)
@@ -41,7 +42,7 @@ map_true.add_spot(
     amp=1.0, sigma=spot_sigma, lat=13.0, lon=51.0, relative=False
 )
 map_true.add_spot(
-    amp=0.2, sigma=spot_sigma, lat=-15.0, lon=-40.0, relative=False
+    amp=0.25, sigma=spot_sigma, lat=-15.0, lon=-40.0, relative=False
 )
 map_true.amp = 20
 
@@ -153,13 +154,19 @@ def model(f_obs_in, f_obs_eg, f_err_in, f_err_eg):
 
     numpyro.sample(
         "obs_in",
-        dist.Normal(flux_in, f_err_in * np.ones_like(f_obs_in),),
+        dist.Normal(
+            flux_in,
+            f_err_in * np.ones_like(f_obs_in),
+        ),
         obs=f_obs_in,
     )
 
     numpyro.sample(
         "obs_eg",
-        dist.Normal(flux_eg, f_err_eg * np.ones_like(f_obs_eg),),
+        dist.Normal(
+            flux_eg,
+            f_err_eg * np.ones_like(f_obs_eg),
+        ),
         obs=f_obs_eg,
     )
 
@@ -179,12 +186,12 @@ nuts_kernel = NUTS(
 )
 
 # Run MCMC
-mcmc = MCMC(nuts_kernel, num_warmup=500, num_samples=1500)
+mcmc = MCMC(nuts_kernel, num_warmup=1000, num_samples=2000, num_chains=2)
 rng_key = random.PRNGKey(0)
 mcmc.run(rng_key, f_obs_in_50, f_obs_eg_50, f_err_in_50, f_err_eg_50)
 samples_50 = mcmc.get_samples()
 
-mcmc = MCMC(nuts_kernel, num_warmup=500, num_samples=1500)
+mcmc = MCMC(nuts_kernel, num_warmup=1000, num_samples=2000, num_chains=2)
 rng_key = random.PRNGKey(1)
 mcmc.run(rng_key, f_obs_in_10, f_obs_eg_10, f_err_in_10, f_err_eg_10)
[…]

### 2021-03-02 paper/figures/irtf_spots_plots.py
Switiching to color version of the galileo map. Added scale ruler, other minor changes

@@ -8,7 +8,9 @@ import starry
 from matplotlib import colors
 import matplotlib.gridspec as gridspec
 from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
-from matplotlib.lines import Line2D
+from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
+import matplotlib.font_manager as fm
+
 
 from scipy.integrate import dblquad
 
@@ -57,7 +59,21 @@ def find_centroid(lats, lons, img, bounds):
     return np.mean(lon_grid[mask]), np.mean(lat_grid[mask])
 
 
-def get_spot_position_and_power(samples, bounds=None, nsamples=100):
+def get_contour_levels(lats, lons, img, bounds, percentiles):
+    mask_lat = np.logical_and(lats > bounds[0][0], lats < bounds[0][1])
+    mask_lon = np.logical_and(lons > bounds[1][0], lons < bounds[1][1])
+
+    img_bounded = img[mask_lat][:, mask_lon]
+
+    # Define background as all pix < 0.5 * max intensity
+    I_min = 0.5 * np.nanmax(img_bounded)
+    mask = img_bounded > I_min
+
+    lon_grid, lat_grid = np.meshgrid(lons[mask_lon], lats[mask_lat])
+    return np.nanpercentile(img_bounded[mask].reshape(-1), percentiles)
+
+
+def get_spot_position_and_power(samples, bounds=None, nsamples=300):
     """
     For each sample find local maximum to get spot position,
     then compute emitted power from the spot.
@@ -69,18 +85,18 @@ def get_spot_position_and_power(samples, bounds=None, nsamples=100):
 
     map = starry.Map(20)
 
-    for n in np.random.randint(len(samples), size=nsamples):
+    for n in np.random.randint(len(samples["x_in"]), size=nsamples):
         x = samples["x_in"][n]
         map[1:, :] = x[1:] / x[0]
         map.amp = x[0]
 
         # Find maximum
-        #        map[1:, :] = -map[1:, :]
-        #        lat, lon, _ = map.minimize(oversample=2, ntries=2, bounds=bounds)
-        #        map[1:, :] = -map[1:, :]
-        img = map.render(res=400, projection="rect")
[…]

### 2021-03-02 paper/figures/irtf_main_plots.py
Minor improvements to figure

@@ -110,6 +110,11 @@ def make_plots(
         nsamples=50,
     )
 
+    median_map_moll_in = np.clip(median_map_moll_in, 0.1, 1e5)
+    median_map_moll_eg = np.clip(median_map_moll_eg, 0.1, 1e5)
+    median_map_in = np.clip(median_map_in, 0.1, 1e5)
+    median_map_eg = np.clip(median_map_eg, 0.1, 1e5)
+
     # Make plot
     if gp:
         gp_pred_in = []
@@ -128,8 +133,13 @@ def make_plots(
                 kernel_in, t=t_in, mean=np.array(samples["flux_in"])[i]
             )
             gp.compute(t_in, yerr=(samples["f_err_in_mod"][i]))
+            gp_pred_in.append(
+                gp.predict(f_obs_in, t=t_in, include_mean=False)
+                + samples["flux_in"][i]
+            )
             gp_pred_in_dense.append(
                 gp.predict(f_obs_in, t=t_in_dense, include_mean=False)
+                + samples["flux_in_dense"][i]
             )
             # Egress
             kernel_eg = terms.Matern32Term(
@@ -140,22 +150,34 @@ def make_plots(
                 kernel_eg, t=t_eg, mean=np.array(samples["flux_eg"])[i]
             )
             gp.compute(t_eg, yerr=(samples["f_err_eg_mod"][i]))
+            gp_pred_eg.append(
+                gp.predict(f_obs_eg, t=t_eg, include_mean=False)
+                + samples["flux_eg"][i]
+            )
             gp_pred_eg_dense.append(
                 gp.predict(f_obs_eg, t=t_eg_dense, include_mean=False)
+                + samples["flux_eg_dense"][i]
             )
 
     # Compute residuals
     f_in_median = np.median(samples["flux_in"], axis=0)
     f_eg_median = np.median(samples["flux_eg"], axis=0)
 
-    res_in = f_obs_in - f_in_median
-    res_eg = f_obs_eg - f_eg_median
+    if gp:
+        f_in_median_gp = np.median(gp_pred_in, axis=0)
+        f_eg_median_gp = np.median(gp_pred_eg, axis=0)
+
+        res_in = f_obs_in - f_in_median_gp
+        res_eg = f_obs_eg - f_eg_median_gp
+    else:
+        res_in = f_obs_in - f_in_median
[…]

### 2021-03-02 paper/figures/irtf_spots_plots.py
Switch to png format for the image of Galileo map

@@ -129,7 +129,7 @@ def get_errobar(samples):
 
 
 # Load Galileo map
-combined_mosaic = Image.open("Io_color_merged_clon180.tif")
+combined_mosaic = Image.open("Io_color_merged_clon180.png")
 # Longitude is defined on [0,360] while Starry expects [-180, 180]
 shifted_map = np.roll(combined_mosaic, int(11445 / 2), axis=1)
 

### 2021-03-02 paper/paper.tex
Robert's comments, adding Robert to the paper

@@
 \email{fb90@st-andrews.ac.uk}
-\affil{Centre for Exoplanet Science, SUPA, School of Physics and Astronomy, University of St. Andrews, St. Andrews, UK}
+\affil{Centre~for~Exoplanet~Science, SUPA, School~of~Physics~and~Astronomy, University~of~St.~Andrews, St.~Andrews, UK}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
@@
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+\author{Robert R. Howell}
+\affil{Department~of~Geology~\&~Geophysics, University~of~Wyoming, Laramie, WY}
 %
@@
 \cite{spencer1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
-\cite{rathbun2002},\citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots, finding evidence of periodicity in Loki's eruptions and establishing the transient nature of the volcanoes (only Loki is persistently active).
+\cite{rathbun2002},\citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots, finding evidence of periodicity in Loki's eruptions and establishing the transient nature of observed emission from most volcanoes.
 By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki region to a precision of about 2 kilometers.
@@
 
-None of the studies of occultations in the infrared attempted to infer a two-dimensional map of Io's surface.
-The light curves are usually fit independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface, with
-strong priors on the locations of individual volcanoes based on maps from space mission observations.
+Most studies of occultations of Io fit multiple light curves independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface (notable exceptions are \cite{spencer1994} and \cite{dekleer2017}), assuming strong priors on the locations of individual volcanoes based on maps from space mission observations.
 In this work, we build a fully probabilistic model in order to infer a two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infrared.
@@
 This value is approximately equal to the total flux emitted from the Jupiter-facing side of Io.
-The baseline brightness is varying stochastically by a large amount and there are several notable events of intense volcanic activity.
+The major variation in the baseline brightness is driven by Loki.
+Most hotspots can be divided into those who are persistently active for a year or longer at moderate intensity, and those which have bursts of activity and reach very high intensities for short periods of time \cite{dekleer2016}.
 
@@
 To model the occultations we need to know the projected relative position of Jupiter with respect to Io and the orientation of Io at any given time.
-To compute the geometry, we use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} and the latest planetary ephemeris DE430 \citep{folkner2014} which is accurate to a few kilometers on Io's surface.
+To compute the geometry, we use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} which uses the latest JUPxxx satellite ephemeris \citep{jacobson2015}.
+The JUPxxx ephemeris is usually accurate to a few kilometers on Io's surface.
 For both Jupiter and Io we need the right ascension and declination and the angular (equatorial) diameter (\textsf{Ang-diam}).
@@
 All longitudes are positive  in the direction of west.
-\textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 second so we interpolate all values so that we can evaluate them for arbitrary times.
+\textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 minute, we interpolate these values so that we can evaluate them for arbitrary times.
 
@@
 \end{equation}
-where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and optionally the direction of the illumination source and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
-in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes the operations needed to compute the integrated flux.
+where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
+in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes the operations needed to compute the integrated flux at different viewing angles of the occulted sphere.
 If the geometry isn't known precisely the matrix $\mathbf{A}$ is not fixed and the model is in principle no longer linear although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
@@
 \end{equation}
-where $\mathbf{A}'\equiv\mathbf{A}\mathbf{P}^\dagger$ and $b$ is a constant flux offset parameter which we have added to account for stray flux which cannot be attributed to Io (it is mostly due to emission from Jupiter).
+where $\mathbf{A}'\equiv\mathbf{A}\mathbf{P}^\dagger$ and $b$ is a constant flux offset parameter which we have added to account for stray flux which cannot be attributed to Io and is likely due to residual light from Jupiter.
 
@@
 
-In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ using \textsf{starry} for different kinds of events a over the course of a single year: occultations by Jupiter, occultations by Europa, Ganymede and Callisto and phase curves.
-We take the ephemeris data from \textsf{JPL HORIZONS} and assume that it is known exactly and we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
+In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ using \textsf{starry} for different kinds of observations of Io in the period starting on the 1st of January 2009 and ending on the 1st of May 2010.
+We chose this period because it covers the full season of mutual occultations which occur every 6 years.
+We compute $\mathbf{A}$ for all observable Io by Galilean moons during that period, for occultations of Io by Jupiter and phase curves.
+We make sure that the number of observations and the cadence for each observation covers all possible geometries because the purpose of this exercise is do determine the upper bound on what we can learn about the surface.
+We take the ephemeris from \textsf{JPL HORIZONS} and assume that it is known exactly; we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
 
@@
 Shrinkage for phase curve at odd degrees above $l=2$ is exactly zero because these coefficents are in the nullspace for objects rotating about an axis perpendicular to the line of sight these coefficients and therefore they cannot be constrained using only phase curves \citep{luger2021}.
-Observations of mutual occultations most easily break the degeneracies but they only happen every 6 years and they almost never happen while Io is in eclipse, which means that only the brightest volcanoes are visible above the reflected sunlight.
-This is not captured in Figure~\ref{fig:information_content}.
+Observations of mutual occultations most easily break the degeneracies but the drawback of these types of observations is that they only happen every 6 years and they almost never happen while Io is in eclipse, meaning that only the brightest volcanoes are visible above the reflected sunlight.
+This fact is not captured in Figure~\ref{fig:information_content}.
 
@@
 Because the limb of the occultor sweeps over the disc of Io at different angles during ingress and ingress, this makes it possible break most degeneracies in the map and recover the location of the true spot.
-We set the phase of the simulated map to $10^\circ$ W at the beginning of ingress and a phase of $10^\circ$ E at the end of egress.
+We set the phase of the simulated map to be $10^\circ$ E at the beginning of ingress and $10^\circ$ W at the end of egress.
 We assume that the geometry of the occultation is known exactly and set the errorbars such that SNR=50 where SNR is the signal is defined as the maximum flux of light curve.
@@
 \textsf{JAX} is a \textsf{numpy} like library which supports automatic differentiation, parallelization and GPUs.
-We run the chains until for 1000 tuning steps and 2000 final steps, monitoring divergences \citep{betancourt2013} and the R-hat  diagnostic  \citep{gelman1992a} to check for convergence.
+We run the chains for 1000 tuning steps and 2000 final steps, monitoring divergences \citep{betancourt2013} and the R-hat  diagnostic  \citep{gelman1992a} to check for convergence.
 Since all models in this paper have hundreds if not thousands of parameters, it would not be possible to sample the posterior  without the use of automatic differentiation and Hamiltonian Monte Carlo (at least for non-Gaussian priors).
@@
 \subsection{Comparison to a parametric model}
-It is instructive to compare the model developed in the previous section to a parametric model in which we assume that the map contains some fixed number of spot and we fit for the positions, amplitudes and the sizes of the spots.
+It is instructive to compare the model developed in the previous section to a parametric model in which we assume that the map contains some fixed number of spots and we fit for the positions, amplitudes and the sizes of the spots.
 A parametric spot model might be useful if we want to fit for a small number of spots and we know what the map should look like.

### 2021-03-04 paper/paper.tex
Rodrigo's comments round 2

@@
     \vspace{-3em}
-\textbf{    Occultation mapping of Io's surface in the near-infrared \\ I: Inferring static maps} 
+\textbf{Occultation mapping of Io's surface in the near-infrared \\ I: Inferring static maps} 
 }
@@
 \affil{Centre~for~Exoplanet~Science, SUPA, School~of~Physics~and~Astronomy, University~of~St.~Andrews, St.~Andrews, UK}
-\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY, USA}
 \author{Rodrigo Luger}
 \author{Daniel Foreman-Mackey}
-\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY, USA}
 \author{Robert R. Howell}
-\affil{Department~of~Geology~\&~Geophysics, University~of~Wyoming, Laramie, WY}
+\affil{Department~of~Geology~\&~Geophysics, University~of~Wyoming, Laramie, WY, USA}
+\author{Julie A. Rathbun}
+\affil{Planetary~Science~Institute, Tuscon, AZ, USA}
 %
@@
     Our fully Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of features.
-    The methods we have developed are also directly applicable to the problem of mapping stars and exoplanets.\href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+    The methods we have developed are also directly applicable to the problem of mapping stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 \section{Introduction}
-The surface of Jupiter's moon Io is covered with hundreds of volcanoes which appear as bright spots in the near infrared, their intensities vary on timescales ranging from days to decades.
-The global heat flow on its surface is about 40 times larger than Earth's \citep{breuer2007,davies2010}
-and about 50\% of the heat flow emanates from only 1.2\% of Io's surface \citep{veeder2012}.
-This intense volcanic activity cannot be explained by radioactive decay which is what drives Earth's volcanism, instead it is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
+The surface of Io is covered with hundreds of volcanoes which appear as bright spots in the near infrared, their intensities varying on timescales ranging from days to decades.
+The global heat flow on its surface is about 40 times larger than Earth's \citep{breuer2007,davies2010} and about 50\% of the heat flow emanates from only 1.2\% of Io's surface \citep{veeder2012}.
+This intense volcanic activity cannot be explained by radioactive decay, the mechanism which drives Earth's volcanism; instead, the volcanism on Io is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
 Contrary to Earth, Io lacks plate tectonics.
-The heat transport mechanism which likely on Io is volcanism through the litosphere (the outermost shell of a terrestrial body), a process in which magma is transported to the surface by localised vents \cite{oreilly1981}.
-Heat-pipe volcanism might have occurred in the early history of terrestrial planets in the Solar System \cite{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
+The heat transport mechanism likely operating on Io is volcanism through the lithosphere (the outermost shell of a terrestrial body), also known as \emph{Heat-pipe volcanism}, a process in which magma is transported to the surface through localised vents \citep{oreilly1981}.
+Heat-pipe volcanism might have occurred in the early history of terrestrial planets in the Solar System \citep{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
 
 Besides providing a window into early volcanic activity in the Solar System, Io is also in many ways an analogue of a volcanically active exoplanet.
-Volcanic exoplanets, often dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
-Existing exoplanet detections with potential volcanism include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet to have been discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016a,hammond2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019} and many others.
+Volcanic exoplanets, sometimes dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
+Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016d,hammond2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019}, and many others.
 Not all such exoplanets will have Io-like volcanism; some may have magma oceans due to their proximity to the star or volcanism caused by nuclear decay, similar to volcanism on present day Earth.
@@
 High resolution images of Io's surface were taken by space missions such as Voyager \citep{smith1979}, Galileo \citep{belton1996} and Juno \citep{mura2020}.
-It has also been resolved from the ground in the near infrared using disk resolved imaging
-\citep{howell1985,simonelli1986,spencer1990} and adaptive optics observations \citep{marchis2000,marchis2005,dekleer2016}.
-Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter starting with \cite{spencer1990}.
-Occultations by Jupiter occur twice every orbit of ~1.7 days.
-Mutual occultations with Europa, Ganymede or Callisto happen at different times over the course of a single year but this only happens every ~6 years or so when Earth passes through the orbital plane of the Galilean satellites.
+The surface has also been resolved from ground based observations in the near infrared using disk resolved imaging \citep{howell1985,simonelli1986,spencer1990} and adaptive optics observations \citep{marchis2000,marchis2005,dekleer2016}.
+Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter, starting with \cite{spencer1990}.
+Occultations by Jupiter occur twice every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called \emph{mutual occultations}) happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites, multiple occultations are then observable over a course of approximately one year.
 The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow (``in eclipse") while mutual occultations are almost always observed in sunlight.
@@
 \cite{spencer1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
-\cite{rathbun2002},\citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's IRTF telescope to study the long term variability of different volcanic spots, finding evidence of periodicity in Loki's eruptions and establishing the transient nature of observed emission from most volcanoes.
-By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki region to a precision of about 2 kilometers.
+\cite{rathbun2002},\citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's 
+Infrared Telescope Facility (IRTF) telescope to study the long term variability of different volcanic spots, finding evidence of periodicity in Loki's eruptions and establishing the transient nature of observed emission from most volcanoes.
+By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki Patera (\emph{Patera} is a type of an irregular crater) region to a precision of about 2 kilometers.
 In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot1974,saquet2018,morgado2016a} for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
-Understanding the detailed albedo distribution is crucial to constraining the ephemeris to a very high precision.
+Understanding the detailed albedo distribution is crucial to constraining the ephemeris of Io to a very high precision.
 
 Most studies of occultations of Io fit multiple light curves independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface (notable exceptions are \cite{spencer1994} and \cite{dekleer2017}), assuming strong priors on the locations of individual volcanoes based on maps from space mission observations.
-In this work, we build a fully probabilistic model in order to infer a two-dimensional \emph{map} of Io's volcanic surface from archival IRTF observations in the near infrared.
-We assume that the map corresponding to a given set of light curves is static (up to an overall amplitude) so we are restricted to modeling the surface during a timespan when the surface emission hasn't changed drastically.
-In a subsequent paper we build on the model we have developed here and generalize to a case where the surface is time-variable.
-
-The model is built on top of the recently developed code \textsf{starry}\citep[][Luger et al.
-2021 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface features are represented in terms of spherical harmonics.
-Starry can compute phase curves and occultations in both emitted light (for modeling the isotropic thermal emission from Io's surface) and reflected light (for mapping albedo variations).
-It is many orders of magnitude faster and more accurate than pixel based codes and it computes exact gradients with respect to all parameters through automatic differentiation.
+In this work, we build a fully probabilistic model in order to infer a \emph{two-dimensional map} of Io's volcanic surface from archival IRTF observations of Io in the near infrared.
+We assume that the map corresponding to a given set of light curves is static (up to an overall amplitude), that is, that it didn't change substantially between the times of observations.
+In Paper II in this series we will relax this assumption by constructing a model which can be used to infer a time-variable map of Io from an any number of light curves observed at arbitrary times.
+
+The model relies on the recently developed code \textsf{starry} \citep[][Luger et al.
+2021 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface can represented in terms of spherical harmonics.
+\textsf{starry} can compute phase curves and occultations in both emitted light (for modeling the isotropic thermal emission from Io's surface) and reflected light (for mapping albedo variations).
+It is many orders of magnitude faster and more accurate than pixel based algorithms and it computes exact gradients of the flux with respect to all parameters through automatic differentiation.
 \textsf{starry} also comes with extensive tools for visualizing spherical harmonic maps and simulating data.
 
-Our goal for this paper is to develop a general model for mapping surfaces of occulted bodies with sparse, high contrast features and to test it on a real world dataset. 
-Because we have lots of prior information on what the surface of Io should look like, we can compare our inferences to known features on its surface and test the sensitivity of the inferred maps to different choices of priors and noise models.
-The work should also be of interest to the Io research community as it presents a very different approach to modeling Io occultations without having to make strong assumptions on the locations of the hot spots.
-
+Our main goal in this paper is to develop a general model for mapping surfaces of occulted bodies with sparse, high contrast features and apply it to observations of Io.
+Because we have lots of prior information on what the surface of Io should look like, we can compare features in our inferred maps to known volcanic hotspots and test the sensitivity of the inferred maps to different choices of priors and noise models.
 The paper is organized as follows.
-In \S\ref{sec:data} we describe the IRTF light curves of occultations by Jupiter that we use to infer maps.
-In \S\ref{sec:model} we discuss the generative model for the data and we write down the relevant likelihood functions.
+In \S\ref{sec:data} we describe the IRTF light curves of occultations by Jupiter which we use to infer maps.
+In \S\ref{sec:model} we discuss the generative model for the data and we write down the likelihood function.
 In \S\ref{sec:inverse_problem} we focus on the question of how to do Bayesian inference given the forward model specifications defined in \S\ref{sec:model}.
-We discuss and test different priors on map features, the information content of light curves and fitting the models using Hamiltonian Monte Carlo (HMC). 
-We then show results on simulated data.
+We discuss and test different priors on map features, we quantify the information content of light curves and fit the models using Hamiltonian Monte Carlo (HMC). 
+We then test the model on realistic simulated data.
 In \S\ref{sec:results} we show the results on real IRTF data for two pairs of light curves, one pair observed in 1998 and another in 2017.
-We show the inferred maps and the parameters quantifying the location and intensity of the hot spots, we discuss the sensitivity of the results to different choices of priors and compare the inferred values to previous results from the literature.
+We show the inferred maps and the parameters quantifying the location and intensity of the hot spots, we discuss the sensitivity of the results to different choices of priors and plot the inferred hotspots on an optical map of Io constructed from Galieleo observations.
 Finally, in \S\ref{sec:discussion} we summarize the main results of the paper and discuss potential applications of our model to observations of volcanic exoplanets.
-
-TODO: say that this paper is first in series of awesome papers.
 
@@
 
-The dataset we use to infer maps of Io's surface consists of 112 sets of observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994} (TODO: WHICH FILTERS), the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} (TODO: DETAILS) and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{johnrayner2016} (TODO: fix citation).
-Although the observations span decades, the cadence is non-uniform, there are only a few observations taken between 2008 and 2016.
-All of the observations were taken while Io was \emph{in eclipse}, meaning that it was in Jupiter's shadow and all of the observed emission from the surface is due to thermal radiation.
-Observations of Io \emph{in sunlight} on the other hand probe both the thermal (volcanic) emission and the surface albedo variations in the near infrared.
-Figure~\ref{fig:irtf_max_flux} shows the maximum flux for each occultation light curve in units of $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ as a function of time.
+The complete dataset consists of 112 sets of observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994}, the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{johnrayner2016}.
+%(TODO: fix citation).
+Although the observations span decades, the timespan between observations varies and there were very few observations taken between 2008 and 2016.
+All of the observations were taken while Io was \emph{in eclipse}, meaning that it was in Jupiter's shadow so the source of observed emission from the surface is thermal radiation.
+On the other hand, for observations of Io \emph{in sunlight} the observed flux is a sum of thermal (volcanic) emission and reflected sunlight which depends on the albedo map in the near infrared.
+In figure~\ref{fig:irtf_max_flux} we plot the maximum flux for each occultation light curve in units of $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ as a function of time.
 This value is approximately equal to the total flux emitted from the Jupiter-facing side of Io.
 The major variation in the baseline brightness is driven by Loki.
-Most hotspots can be divided into those who are persistently active for a year or longer at moderate intensity, and those which have bursts of activity and reach very high intensities for short periods of time \cite{dekleer2016}.
+Most hotspots on Io can be divided into those who are persistently active for a year or longer at moderate intensity, and those which have bursts of activity and reach very high intensities for short periods of time \citep{dekleer2016}.
 
@@
     \oscaption{irtf_dataset}{%
-        A selection of sample light curves taken during occultations of Io by Jupiter in our dataset.
-        The step-like morphology of the light curves is due to bright volcanoes on Io's surface coming in or out of view during an occultation.
-        These light curves thus visibly encode information about the features on the surface.
+        A selection of sample light curves observed using NASA's IRTF telescope during occultations of Io by Jupiter in our dataset.
+        The step-like morphology of the light curves is due to bright volcanoes on Io's surface coming in or out of view during the course of an occultation.
+        These light curves visibly encode information about the features on the surface.
         \label{fig:irtf_sample_lightcurves}
@@
 in the dataset. 
-Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress and ingress parts of the entire occultation.
+Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress (or egress) part of the entire occultation.
 The exposure cadence for each light curve is about a second, with some variation between light curves.
 It follows that over the course of a single exposure Jupiter's limb passes over about 15km on Io's surface which provides a lower bound for the size of the features that we can reliably estimate.
-The shapes of light curves strongly deviate from the smooth variability one would expect assuming uniform thermal surface emission.
-Especially prominent are light curves with clear step-like features which are present when bright localized spots come in or out of view during the course of an occultation.
-The fact that these features are so clearly visible means that even individual light curves encode precise information on the longitudinal position of the spots.
+The shapes of light curves strongly deviate from a smooth variation that one would expect to see if the surface thermal emission was uniformly distributed.
+Especially prominent are light curves with clear step-like features which are due to bright localized spots coming in and out of view during the course of an occultation.
+The fact that these features are so clearly visible means that even individual light curves encode a wealth of information about the spots.
 
@@
 \label{sec:model}
+In this section we describe the generative model for the occultation light curves of Io.
+To simulate the observed light curves, we first need to specify the geometry of each occultation event (Section~\ref{ssec:orbital_parameters}), we then need to specify what the surface of Io looks like in a spherical harmonic basis and compute the theoretical flux at the times of observations using \textsf{starry} (Section~\ref{ssec:model_spec}), finally, we need to specify a noise model for the observed data (Section~\ref{ssec:likelihood}).
+
 \subsection{Orbital parameters}
 \label{ssec:orbital_parameters}
-To model the occultations we need to know the projected relative position of Jupiter with respect to Io and the orientation of Io at any given time.
-To compute the geometry, we use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} which uses the latest JUPxxx satellite ephemeris \citep{jacobson2015}.
-The JUPxxx ephemeris is usually accurate to a few kilometers on Io's surface.
-For both Jupiter and Io we need the right ascension and declination and the angular (equatorial) diameter (\textsf{Ang-diam}).
-In addition, we need to fix the orientation of Io we need the longitude and the latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon}, \textsf{Ob-lat}) and the counterclockwise angle between the celestial north pole unit vector projected onto the plane of the sky and the Io's north pole (\textsf{NP.ang}).
-All longitudes are positive  in the direction of west.
-\textsf{HORIZONS} provides all ephemeris with a minimum cadence of 1 minute, we interpolate these values so that we can evaluate them for arbitrary times.
+To compute the geometry of every occultation, we use the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database} which uses the latest ephemeris for the position of Jupiter \citep{folkner2014}, and its satellites \citep{jacobson2015}.
+The ephemeris is usually accurate to a few kilometers on Io's surface.
+We access JPL Horizons through the Python package \textsf{astroquery} \citep{ginsburg2019}.
+To compute the relative position of Jupiter and Io we need the right ascension and declination and to to fix the orientation of Io we need the longitude and the latitude at the center of Io's disc as seen from Earth (\textsf{Ob-lon} and \textsf{Ob-lat} in \textsf{astroquery}) and the counterclockwise angle between the celestial north pole unit vector projected onto the plane of the sky and Io's north pole (\textsf{NP.ang}).
+All longitudes provided by Horizons are positive  in the direction of west.
+Horizons provides all ephemeris with a minimum cadence of 1 minute, we interpolate these values so that we can evaluate them for arbitrary times.
 
@@
 The radius of the occulted sphere is fixed to 1 and the orientation is specified by three angles,
-the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the north pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the north pole is aligned with the $\hat{y}$ axis and the phase angle \textsf{theta} which rotates the sphere around the $\hat{y}$ axis in the eastward direction.
-We have $\mathrm{obl}=\textsf{NP.ang}$, $\mathrm{inc}=90^\circ-\textsf{Ob-lat}$ and
-$\mathrm{theta}=\textsf{Ob-lon}$.
+the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the north pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the north pole is aligned with the $\hat{y}$ axis, and the phase angle \textsf{theta} which rotates the sphere around the $\hat{y}$ axis in the eastward direction.
+Expressed in terms of Horizons variables, these angles are given by $\mathrm{obl}=\textsf{NP.ang}$, $\mathrm{inc}=90^\circ-\textsf{Ob-lat}$ and $\mathrm{theta}=\textsf{Ob-lon}$.
 The occultor position relative to the occulted object is given by
@@
 First, Jupiter is not spherical and its equatorial radius is greater than the polar radius by thousands of kilometers. 
-Because \textsf{starry} does not (yet) support occultations by non-spherical occultors and because the effect is negligible at the resolution of our maps, we assume that Jupiter is locally spherical at the point of an occultation.
-We estimate an effective radius from the measurements of Jupiter's shape from Voyager radio occultation data \citep{lindal1981}.
-These data come in the form of a plot of effective radius  as a function of Jupiter's planetocentric latitude at a fixed pressure of 100 mbar \citep[Fig.~7 in ][]{lindal1981}.
+Because \textsf{starry} does not (yet) support occultations for non-spherical objects and because the effect is negligible at the resolution of our maps, we assume that Jupiter is locally spherical at the point of an occultation.
+We estimate an effective radius from the measurements of Jupiter's shape from Voyager radio occultation data \citep[Fig.~7]{lindal1981}.
 When computing the occultation latitude we fix Jupiter's latitude to the value at the center of Io's disc because 
@@
 In principle, we should compute an effective radius of Jupiter at different altitudes (pressure) in the atmosphere and model an occultation of Io by a fuzzy occultor.
-Although this is possible with \textsf{starry}, it is unnecessary for our models because the characteristic scale height of Jupiter is around 27 km (CITE) which is below the uncertainty of our inferred maps.
-Instead, we follow the approach in \cite{spencer1990} and compute the effective radius of Jupiter at about 2.2 mbar, the pressure (and the associated effective radius) at which a  bright source on the surface of Io fades by 50\% due to differential refraction during the course of an occultation.
+Although this is possible with \textsf{starry}, it is unnecessary for our models because the characteristic scale height of Jupiter is around 27 km  which is below the uncertainty of our inferred maps.
+We instead follow the approach in \cite{spencer1990} and compute the effective radius of Jupiter at about 2.2 mbar, the pressure (and the associated effective radius) at which a  bright source on the surface of Io fades by 50\% due to differential refraction during the course of an occultation.
+
+%These data come in the form of a plot of effective radius  as a function of Jupiter's planetocentric latitude at a fixed pressure of 100 mbar \citep[Fig.~7 in ][]{lindal1981}.
+%
 
@@
 There are substantial uncertainties in each of these steps.
-The data on the shape profile are quite old and it is not known if the structure of Jupiter's has remained constant since the 1980s. 
+The shape profile data are quite old and it is not known if the structure of Jupiter's has remained constant since the 1980s. 
 The shape profile also depends on the wind velocity structure and temperature which we do not take into account.
 In addition to uncertainties about the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
-We digitized the figure by reading off the data points ``by eye" and then interpolating them using cubic spline interpolation.
-
-Throughout this paper the highest resolution maps we fit to the data are of order $l=25$ which corresponds to a characteristic length scale of around 230 km on the surface of Io.
-This is about an order of magnitude larger than the errors introduced in the effective radius estimate above so we are not concerned with substantial errors in our radius estimate.
-
-\subsection{Model specification}
+Since our main focus in this work is the map model, we leave a detailed investigation into the various sources of error that go into the radius estimate for future work.
+
+\subsection{Linear model for the flux}
 \label{ssec:model_spec}
-Given the geometry of on occultation event at an arbitrary time, computing the predicted flux with \textsf{starry} is straightforward.
-\textsf{starry} computes the integrated flux of an unocculted or an occulted sphere analytically assuming that the surface map can be expanded in terms of spherical harmonics $Y_{lm}(\theta,\phi)$ up to a certain \emph{degree} $l$.
-The map is thus defined by a vector of spherical harmonic coefficients $\mathbf{y}$ which multiplies the spherical harmonic basis $\left(Y_{0,0}\;Y_{1,-1}\;Y_{1,0}\;Y_{1,1}\;Y_{2,-2}\;Y_{2,-1}\;Y_{2,0}\;Y_{2,1}\;Y_{2,2}\; \cdots\right)^{\top}$ and the total number of coefficients is $(l+1)^2$.
-In addition to computing \emph{thermal} phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations when the sphere is illuminated by a distant light source \citep[Luger et al.
-2021 in prep][]{} which is complicated by the presence of the terminator line.
-In the case of a reflected light map, the coefficient vector $\mathbf{y}$ represents spherical albedo in a given wavelength range.
-We only use data taken while Io was in eclipse shadowed by Jupiter so we do not need to model the reflected light component. 
-If instead we had occultation data or phase curves taken while Io is illuminated by the Sun and if both the thermal component and the reflected sunlight component of observed flux were comparable, it would be necessary to simultaneously fit for two vectors of spherical harmonic coefficients,
-one for the albedo distribution and the other for thermal emission.
-
-Importantly, conditioned on the parameters specifying the geometry of the occultations being fixed, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
+Given the geometry of on occultation event at the times of observations, computing the predicted flux with \textsf{starry} is straightforward.
+\textsf{starry} computes the integrated flux of an unocculted or occulted sphere analytically given an expansion of the surface map in spherical harmonics $Y_{lm}(\theta,\phi)$ up to a certain \emph{degree} $l$.
+The map is defined by a vector of spherical harmonic coefficients $\mathbf{y}$ which is dotted into the spherical harmonic basis vector $\left(Y_{0,0}\;Y_{1,-1}\;Y_{1,0}\;Y_{1,1}\;Y_{2,-2}\;Y_{2,-1}\;Y_{2,0}\;Y_{2,1}\;Y_{2,2}\; \cdots\right)^{\top}$.
+The total number of spherical harmonic coefficients is $(l+1)^2$.
+In addition to computing thermal phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations in which the occulted object is illuminated by a distant light source \citep[Luger et al.
+2021 in prep][]{}.
+In that case the coefficient vector $\mathbf{y}$ represents spherical albedo.
+For observations of Io in sunlight in a wavelength range where where both the thermal component and the reflected sunlight component of observed flux are comparable, it would be necessary to simultaneously fit for two vectors of spherical harmonic coefficients, one for the albedo distribution and the other for thermal emission.
+In this paper we only use observations of Io in eclipse so we do not need to model the reflected light component.
+
+Conditioned on fixed parameters specifying the geometry of the occultations, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
 \cite{luger2019} achieved this by representing all rotations, changes of basis transformations and integrals with complicated boundaries which are needed to compute the flux as linear transformations.
@@
 where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
-in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes the operations needed to compute the integrated flux at different viewing angles of the occulted sphere.
+in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed to compute the integrated flux at different viewing angles of the occulted sphere.
 If the geometry isn't known precisely the matrix $\mathbf{A}$ is not fixed and the model is in principle no longer linear although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
 
-The characteristic angular scale of features that can be represented with a given map is set by the degree of the map and it is approximately equal to $180^\circ/l$.
+The characteristic angular size of features that can be represented with a given map is set by the degree of the map and it is approximately equal to $180^\circ/l$.
 For reference, state of the art inferences involving phase curves and secondary eclipses of exoplanets are able to constrain features of order $l=1$ (inferring a bright spot offset from the substellar point) but for Io we need to fit much higher order maps because the typical scale of volcanic spots is on the order of tens of kilometers (a few degrees).
-\textsf{starry} can handle occultations up to $l\approx 20$ before numerical instabilities kick in \citep{luger2019a}.
-
-Although \textsf{starry} was built around the idea of expanding surface features in a spherical harmonic basis in which we can compute all fluxes analytically, this basis is ideal basis for doing inference because it makes it difficult to encode assumptions (priors) on what we expect the map to look like.
+\textsf{starry} can handle occultations up to $l\approx 20$ before numerical instabilities kick in \citep{luger2019a} which corresponds to a minimum resolution of $9^\circ$ which means that we are not able to constrain the physical size of the spot.
+We discuss the implication of this resolution limit in Section~\ref{sec:results} and Section~\ref{sec:discussion}.
+
+Although \textsf{starry} was built around the idea of expanding surface features in a spherical harmonic basis in which we can compute all fluxes analytically, this basis may not be ideal for doing inference because it can be difficult to encode assumptions (priors) on what we expect the map to look like.
 For example, the most important constraint on the map we would like to incorporate in the model is that the intensity of the map is positive at every location. 
 This constraint is important not only because we want to avoid having unphysical regions in inferred maps but also because it imposes a very strong prior on the map which substantially reduces the difficulty of inference when the data is not particularly informative.
-The are two ways of enforcing positivity that we are aware of, both of which involve evaluating the intensity on a fixed grid of \emph{pixels} and disallowing negative values of those pixels.
+
+There are two ways of enforcing positivity that we are aware of, both of which involve evaluating the intensity on a fixed grid of \emph{pixels} and disallowing negative values of those pixels.
 The first is to fit for the spherical harmonic coefficients $\mathbf{y}$, evaluate the pixel grid at each MCMC step and reject all samples of the coefficient vector $\mathbf{y}$ which result in pixels with negative intensity.
-The issue with this procedure is that rejecting samples in this way implies a prior probability distribution on $\mathbf{y}$ which cannot be mapped to a parameter space with infinite support\footnote{For example, if we want to impose a positive prior on some parameter $x$, instead of sampling in $x$ using a prior with a hard boundary at zero, we can derive the equivalent prior for $\ln x$ and sample in the (unbounded) parameter $\ln x$.
-It is not clear how to use a similar trick to ensure that all pixels on a fixed grid generated from spherical harmonics are positive.} and Hamiltonian Monte Carlo does not work well with constrained parameter spaces.
+The issue with this procedure is that rejecting samples in this way implies a prior probability distribution on $\mathbf{y}$ which cannot be mapped to a parameter space with infinite support and Hamiltonian Monte Carlo does not work well with constrained parameter spaces.
 The second approach is to dispense with the spherical harmonics entirely and compute the full model using a high resolution grid of pixels.
-In practice this is very difficult to do because we would need a very high resolution grid to compute the light curves accurately with minimal discretization noise and the model.  
+In practice this is very difficult to do because we would need a very high resolution grid to compute the light curves accurately with minimal discretization noise.  
 \textsf{starry} uses spherical harmonics as a basis precisely to avoid this problem.
@@
 \end{equation}
-Each row of $\mathbf{P}$ contains values of each of spherical harmonic coefficients at a given point on the grid. 
+Each row of $\mathbf{P}$ contains values of each of the spherical harmonic coefficients at a given point on the grid. 
 To construct the grid we use an equal area Molleweide projection in order to have a uniform distribution of pixels across the sphere.
-The grid needs to be fine enough to ensure that intensity is positive over most of the sphere.
-
-Switching from pixels to spherical harmonics is somewhat more complicated because $\mathbf{P}$ is not a square matrix so we cannot compute its inverse to obtain the inverse transform.
+The grid needs to be fine enough to ensure that the intensity is positive over most of the sphere.
+
+Switching from pixels to spherical harmonics is somewhat more complicated because $\mathbf{P}$ is in general not a square matrix so we cannot compute its inverse to obtain the inverse transform.
 Instead, we can compute an approximate inverse (a pseudoinverse) $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$, where $\mathbf{I}$ is the identity matrix.
@@
 Both $\mathbf{P}$ and $\mathbf{P}^\dagger$ can be precomputed to speed up inference.
-When using pixels to impose a positivity constraint on the spherical harmonic map we need to make sure that number of pixels is greater than the number of spherical harmonic coefficients by a factor of a few to ensure positivity approximately everywhere on the sphere.
+When using pixels to impose a positivity constraint on the spherical harmonic map we need to make sure that the number of pixels is greater than the number of spherical harmonic coefficients by a factor of a few to ensure positivity approximately everywhere on the sphere.
 In practice we find that we need to use at least 4 times as many pixels as spherical harmonics which means that the computational cost of this model is higher than if we just fit for spherical harmonics.
@@
 Since the pixel map is higher resolution than the spherical harmonic map it can only be approximately represented at a finite order of the spherical harmonic expansion so the map on the right appears to be smoother and the intensity distribution is more similar to a skewed Gaussian with a heavy right tail than an exponential distribution.
-Nevertheless, we find that setting priors on pixels is a far better solution than fitting the spherical harmonic coefficients directly and is worth the extra computational cost due the increased dimensionality of the parameter space (see Section~\ref{ssec:pixels_vs_harmonics} for a demonstration).
+Nevertheless, we find that setting priors on pixels is a far better solution than fitting the spherical harmonic coefficients directly and is worth the extra computational cost which comes with the increased dimensionality of the parameter space (see Section~\ref{ssec:pixels_vs_harmonics} for a demonstration).
 
@@
 \label{ssec:likelihood}
-Assuming we have a single light curve with $T$ data points and a map set by the pixels $\mathbf{p}$, the (Gaussian) log likelihood is given by
+Finally, we have to specify the noise model which means we have to define a likelihood function.
+Assuming we have a single light curve with $T$ data points and a map defined by the pixels $\mathbf{p}$, the (Gaussian) log likelihood is given by
 \begin{equation}
     \ln\mathcal{L}=-\frac{1}{2}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]^{\top}
-    \boldsymbol{\Sigma}_l^{-1}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]
+    \boldsymbol{\Sigma}^{-1}\left[\mathbf{f}_\mathrm{obs}-\mathbf{f} \right]
     \quad,
@@
 \end{equation}
-where $\mathbf{A}'\equiv\mathbf{A}\mathbf{P}^\dagger$ and $b$ is a constant flux offset parameter which we have added to account for stray flux which cannot be attributed to Io and is likely due to residual light from Jupiter.
+where $\mathbf{A}'\equiv\mathbf{A}\mathbf{P}^\dagger$ and $b$ is a constant flux offset parameter which we have added to account for stray flux which cannot be attributed to Io.
+Depending on the observation, this flux is most often residual light from Jupiter.
 
 To model the data covariance $\boldsymbol{\Sigma}$ we use use a Gaussian Process and we compute the likelihood using the fast Celerite method \citep{foreman-mackey2017} as implemented in the \textsf{celerite2} package \citep{foreman-mackey2017a,foreman-mackey2018}.
-We use the simple (approximate) Matern 3/2 function which is parametrized by two values, a standard deviation parameter $\sigma_\mathrm{GP}$ and a characteristic timescale parameter $\rho_\mathrm{GP}$.
-The kernel is given by 
+We use the simple (approximate) Mat\'ern 3/2 kernel function which is parametrized by two values, a standard deviation parameter $\sigma_\mathrm{GP}$ and a characteristic timescale parameter $\rho_\mathrm{GP}$.
+It is given by 
 \begin{equation}
@@
 where $\sigma_n$ is the errorbar for the n-th data point.
-In cases where we fit multiple independent light curves the total log likelihood is the sum of individual likelihoods defined in Equation~(\ref{eq:likelihood}).
+Since we fit multiple independent light curves the total log likelihood is the sum of individual likelihoods defined in Equation~(\ref{eq:likelihood}).
 
@@
 \label{sec:inverse_problem}
-Having defined the forward model in the previous section, in this section we describe how to solve the inverse problem in a Bayesian setting.
+Having defined a probabilistic model which describes how to compute a realistic light curve for an occultation of Io in the previous section, in this section we discuss the inverse problem of inferring a surface map by fitting a set of occultation light curves in a Bayesian framework.
 
@@
 \label{ssec:information_content}
-The mapping problem is famously ill posed meaning that specific linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Equation~(\ref{eq:linear_model}) \citep{luger2021}.
-This means that even if we had noiseless observations it would still be impossible to recover certain features.
-To recover the greatest information about the surface we need to have some mechanism which breaks the various degeneracies.
-With phase curves only we can recover primarily longitudinal variations in emission.
+The mapping problem is famously ill posed, meaning that specific linear combinations of spherical harmonic coefficients will be in the nullspace of the linear mapping  $\mathbf{A}$ in Equation~(\ref{eq:linear_model}) \citep{luger2021}.
+This means that in general, even if we had noiseless observations, it would still be impossible to recover certain features on the surface.
+To recover the greatest information about the surface we need to have a mechanism which breaks the various degeneracies.
+For example, with phase curves we can recover primarily longitudinal variations in emission.
 Occultations are substantially better because the limb of the occultor sweeps across the surface of the occulted sphere, thereby exposing or blocking light from different points on the surface.
 An ideal set of observations would consist of phase curves together with observations of multiple occultations by a small occultor at different latitudes and different phases.
-Observing phase curves and occultations in reflected light improves the model further because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
+Phase curves and occultations in reflected light are even more informative because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
 2021 in prep]{luger2019a}.
@@
 
-We can reformulate these statements more precisely by computing a measure of information content of the different kinds of observations.
+We can reformulate these statements on how useful given observations are more precisely by computing a measure of their information content.
 Given that our model is linear, assuming Gaussian priors on the spherical harmonic coefficients with covariance $\boldsymbol{\Lambda}_\mathbf{y}$ and a Gaussian likelihood, the posterior can be computed analytically and its mean is given by
@@
     \quad,
+    \label{eq:linear_solve_mean}
 \end{equation}
@@
 \boldsymbol{\Sigma}_{\hat{\mathbf{y}}}=\left( \mathbf{A}^{\top} \boldsymbol{\Sigma}_{\mathbf{f}}^{-1} \mathbf{A} +\boldsymbol{\Lambda}_{\mathbf{y}}^{-1}\right)^{-1}
+    \label{eq:linear_solve_cov}
 \end{equation}
@@
 
-In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ using \textsf{starry} for different kinds of observations of Io in the period starting on the 1st of January 2009 and ending on the 1st of May 2010.
+In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ with \textsf{starry} for different kinds of observations of Io in the period starting on the 1st of January 2009 and ending on the 1st of May 2010.
 We chose this period because it covers the full season of mutual occultations which occur every 6 years.
-We compute $\mathbf{A}$ for all observable Io by Galilean moons during that period, for occultations of Io by Jupiter and phase curves.
-We make sure that the number of observations and the cadence for each observation covers all possible geometries because the purpose of this exercise is do determine the upper bound on what we can learn about the surface.
-We take the ephemeris from \textsf{JPL HORIZONS} and assume that it is known exactly; we also assume all observations are of the emitted light component independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
+We compute $\mathbf{A}$ for all observable occultations of Io by Galilean moons during that period, for occultations of Io by Jupiter and for phase curve observations.
+The purpose of this is to determine the upper bound on what we can learn about the surface. 
+We take the ephemeris from \textsf{JPL Horizons} and assume that it is known exactly; we also assume all observations are observations of thermal emission independent of whether Io is in sunlight or in eclipse because we are interested in constraining the volcanic emission rather than the albedo.
 
@@
 
-Fig.~\ref{fig:information_content} shows the posterior shrinkage as a function of $l$ (averaged over all $m$ modes) for phase curve observations (blue lines), occultations by Jupiter (orange), the former two combined (green) and mutual occultations by other Galilean moons (red).
+Fig.~\ref{fig:information_content} shows the posterior shrinkage as a function of $l$ (averaged over all $m$ modes) for phase curve observations (blue lines), occultations by Jupiter (orange), the former two combined (green), and mutual occultations by other Galilean moons (red).
 As expected, the mutual occultations of Io by other Galilean moons are by far the most informative with posterior shrinkage of unity at all angular scales considered. 
-Occultations by Jupiter are far less informative because we only see one side of Io during an occultation.
-Shrinkage for phase curve at odd degrees above $l=2$ is exactly zero because these coefficents are in the nullspace for objects rotating about an axis perpendicular to the line of sight these coefficients and therefore they cannot be constrained using only phase curves \citep{luger2021}.
-Observations of mutual occultations most easily break the degeneracies but the drawback of these types of observations is that they only happen every 6 years and they almost never happen while Io is in eclipse, meaning that only the brightest volcanoes are visible above the reflected sunlight.
+Occultations by Jupiter are less informative because we only see one side of Io during an occultation.
+Shrinkage for phase curves at odd degrees above $l=2$ is exactly zero because these coefficents are in the nullspace for objects rotating about an axis perpendicular to the line of sight and therefore cannot be constrained using only phase curves \citep{luger2021}.
+Although observations of mutual occultations most easily break the degeneracies, the drawback of these types of observations is that they only happen every 6 years and they almost never happen while Io is in eclipse, meaning that only the brightest volcanoes are visible above the reflected sunlight.
 This fact is not captured in Figure~\ref{fig:information_content}.
 
-Although Figure~\ref{fig:information_content} gives us some idea about which kinds of observations are most informative, it doesn't really tell us how well we can constrain very bright spot-like features we expect to see on Io.
-To answer this question we have to simulate data and conduct the inference process.
+Figure~\ref{fig:information_content} gives us some idea about which kinds of observations are most informative but it doesn't really tell us how well we can constrain bright spot-like features we expect to see on Io.
+To answer this question we have to create a simulated dataset and conduct the whole inference process.
 
@@
 The expansion is in the quantity $\cos(\Delta\theta)$ where $\Delta\theta$ is the angular separation between the center of the spot and another point on the surface of the sphere. 
-We place the spot at $13^\circ$ N latitude and $51^\circ$ E longitude, we set the diameter of the spot ($2\Delta\theta$) to $5^\circ$ and the amplitude of the spot such that the total \emph{luminosity} of the map increases by 50\% with the addition of the spot.
-We generate two light curves with 150 data points, one for the duration of the ingress of the full occultation and the other for the egress.
-Because the limb of the occultor sweeps over the disc of Io at different angles during ingress and ingress, this makes it possible break most degeneracies in the map and recover the location of the true spot.
+We place the spot at $13^\circ$ N latitude and $51^\circ$ E longitude, we set the diameter of the spot ($2\Delta\theta$) to $5^\circ$ and we set the amplitude of the spot such that the total \emph{luminosity} of the map increases by 50\% with the addition of the spot.
+We generate two light curves with 150 data points each, one for the duration of the ingress of the full occultation and the other for the egress.
+Because the limb of the occultor sweeps over the disc of Io at different angles during ingress and ingress, this makes it possible break most degeneracies in the map and recover the location of the simulated spot.
 We set the phase of the simulated map to be $10^\circ$ E at the beginning of ingress and $10^\circ$ W at the end of egress.
-We assume that the geometry of the occultation is known exactly and set the errorbars such that SNR=50 where SNR is the signal is defined as the maximum flux of light curve.
+We assume that the geometry of the occultation is known exactly and we set the errorbars such that SNR=50 where the signal is defined to be the maximum value of the computed flux.
     We use this dataset to test the difference between setting a prior in the spherical harmonic basis $\mathbf{y}$ and in the pixel basis $\mathbf{p}$ by fitting an $l=20$ map to the dataset.
 
-In the spherical harmonic model we place a Gaussian prior on the $\mathbf{y}$ with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.5^2,\dots,0.5^2)$.
-Since the model is linear and the prior is Gaussian, the posterior probability distribution is also Gaussian and we can solve for the posterior mean and covariance matrix analytically \citep{luger2019a}.
-In the hybrid pixel model we place a positive exponential prior on the pixels evaluated on a Mollweide grid. 
-The purpose of the exponential prior is to favor sparser solutions for map because the exponential distribution pushes most pixels towards zero intensity.
+In the spherical harmonic model we place a Gaussian prior on $\mathbf{y}$ with covariance $\boldsymbol{\Lambda}=\mathrm{diag}(1^2,0.5^2,\dots,0.5^2)$.
+Since the model is linear and the prior is Gaussian, the posterior probability distribution is also Gaussian and we can solve for the posterior mean (Equation~(\ref{eq:linear_solve_mean})) and covariance (Equation~(\ref{eq:linear_solve_cov})) analytically.
+In the hybrid pixel model we place a positive exponential prior on the pixels which are defined on a Mollweide grid. 
+The purpose of the exponential prior is to favor sparser solutions for the map because the exponential distribution pushes most pixels towards zero intensity.
 We use four times as many pixels as spherical harmonics.
-Although the model is also linear in this case, the posterior distribution for the pixels is not analytic because of the non-Gaussian prior so we sample the posterior distribution using MCMC instead.
+Although the model is also linear in this case, the posterior distribution for the pixels is not analytic because of the non-Gaussian prior so we sample the posterior using MCMC instead.
 As the end product of inference we save the spherical harmonic coefficients $\mathbf{y}=\mathbf{P}^\dagger\mathbf{p}$ rather than the pixels themselves.
@@
 
-To ensure that the difference in the inferred maps is not in part due to a difference in the scale of the priors, we take 5000 samples from the prior on $y$ and evaluate $\mathbf{P}\mathbf{y}$ for each; we then compute the standard deviation of these pixels use that as the scale parameter in the exponential prior.
+To ensure that the difference in the inferred maps is not in part due to a difference in the scale of the priors, we take 5000 samples from the prior on $y$ and evaluate $\mathbf{P}\,\mathbf{y}$ for each; we then compute the standard deviation of these pixels and use that as the scale parameter in the exponential prior.
 We implement the pixel model in the probabilistic programming language \textsf{numpyro} \citep{phan2019a} which is built on top of the \textsf{JAX} \citep{jax2018github} library, and we fit it using Hamiltonian Monte Carlo with the No-U-Turn-Sampler (NUTS) \citep{hoffman2014}.
@@
 We run the chains for 1000 tuning steps and 2000 final steps, monitoring divergences \citep{betancourt2013} and the R-hat  diagnostic  \citep{gelman1992a} to check for convergence.
-Since all models in this paper have hundreds if not thousands of parameters, it would not be possible to sample the posterior  without the use of automatic differentiation and Hamiltonian Monte Carlo (at least for non-Gaussian priors).
+Since all models we fit in this paper have hundreds if not thousands of parameters, it would be extremely challenging to sample the posterior  without the use of automatic differentiation and Hamiltonian Monte Carlo (at least for non-Gaussian priors).
 
@@
         Comparison between two models fitted to a simulated light curve of an occultation by Jupiter which was generated from a map consisting of a single bright spot (top map).  
-       Each of the columns beneath the true map shows the (median) posterior estimate of the map (top), the data and the posterior flux samples (middle row) and the residuals (bottom row).
+       Each of the columns beneath the simulated map shows the (median) posterior estimate of the map (top), the data and the posterior flux samples (middle row) and the residuals (bottom row).
         The left column corresponds to a model in which we place a Gaussian prior on spherical harmonic coefficients $\mathbf{y}$ and fit for $\mathbf{y}$ while the right column correspond to a hybrid model in which we fit for pixels $\mathbf{p}$ (with an exponential prior on pixel intensity) but we use $\mathbf{y}$ to compute the flux analytically with \textsf{starry}.
         The benefit of using pixels is that it is much easier to encode assumptions on what the map should look like in pixel space rather than spherical harmonic space.
-        With the pixel model we are able to recover the true map precisely while the spherical harmonic model fails to do that. 
+        With the pixel model we are able to recover the simulated map precisely while the spherical harmonic model fails to do that. 
                \label{fig:pixels_vs_harmonics}
@@
 Results are shown in Figure~\ref{fig:pixels_vs_harmonics}.
-The top row shows the true map, beneath it we show the inferred maps in Mollweide projection for the two models (second row), the data and posterior flux samples (orange lines) and the residuals with respect to the median flux (bottom row).
-The difference between the two models is striking, the left map has an elongated feature which does not resemble the spot in the true map while the map on the right is nearly identical to the true map.
+The top row shows the simulated map, beneath it we show the inferred maps in Mollweide projection for the two models (second row), the data and posterior flux samples (orange lines) and the residuals with respect to the median flux (bottom row).
+The difference between the two models is striking. 
+The left map has an elongated feature which does not resemble the spot in the simulated map while the map on the right is nearly identical (except for a difference in intensity) to the simulated map. 
 We should emphasize here that the fact that the pixel model results in a spot-like map is mostly a consequence of the exponential prior which favors sparse solutions in pixel space.
 When we compared the spherical harmonic model to the pixel model using a prior with a lighter tail such as a Half Gaussian (Gaussian truncated at zero), we obtained a more elongated feature similar to shown on the left map in Figure~\ref{fig:pixels_vs_harmonics} but the map was still noticeably less complex because the positivity constraint substantially reduces the space of maps which fit the data well.
-Thus, the benefit of using the pixel model is that it easy to impose the positivity constraint on the map but also other constraints such as sparsity.
-
-One issue with the map on the right is that there is a series of concentric rings around the spot which result in a wave-like pattern in the predicted flux and the residuals.
+Thus, the benefit of using the pixel model makes it easy to impose the positivity constraint on the map but also other constraints such as sparsity.
+
+An important issue with the map on the right is that there is a series of concentric rings around the spot which result in a wave-like pattern in the predicted flux and the residuals.
 This ringing pattern arises because representing spot-like features requires constructive interference between different spherical harmonic modes inside the spot and destructive interference elsewhere.
 The pattern is more pronounced when we fit a low resolution map (approximately $180/20=9^\circ$ in this case) and the model tries to represent a feature below the resolution of the map.
-Ringing is undesirable because we want to avoid situations in which the model uses the rings to explain the data instead of just placing a spot directly. 
+
+Ringing is also the reason why the inferred spot for the pixel model appears to be noticeably dimmer than the simulated spot.
+There is non-negligible leakage of total flux from the spot into the rings surrounding it, meaning that if we were to integrate the map intensity over a region encompassing the brightest part of the inferred spot, it would be an underestimate of the total emitted flux from the true spot within the same area.
+Ringing is also undesirable because we want to avoid situations in which the model uses the rings to explain the data instead of just placing a spot directly. 
 For example, we find that in some cases when we fit low degree maps, the model would place a bright spot on the unobserved side of Io in order to produce a ringing artefact on the observed side to explain an increase or decrease in brightness in the light curve.
@@
 \label{ssec:spurious_features}
-To suppress ringing, which results in regions of negative intensity surrounding a spot-like feature as in Figure~\ref{fig:pixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonic coefficients.
+To suppress ringing artefacts which appear around inferred spots such as the one shown in Figure~\ref{fig:pixels_vs_harmonics}, we apply a spatial smoothing filter to the spherical harmonic coefficients.
 Mathematically, the filtering operation is a convolution between the map and some kernel function $B(\theta,\phi)$.
@@
 They depend only on $l$ because all nonzero $m$ modes vanish due to azimuthal symmetry.
-For $\sigma_s\ll 1$ $B_l$ can be approximated as \citep{seon2007,white1995}
+For $\sigma_s\ll 1$, $B_l$can be approximated as \citep{seon2007,white1995}
 \begin{equation}
@@
 We place the spot at $0^\circ$ latitude and longitude and set the size of the spot $\Delta\theta$ to $5^\circ$.
-All three subplots show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
-The subplot on the left shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
-The middle subplot shows an intermediate level of smoothing where $\sigma_s=0.1$, meaning that all features on scales above $l\approx 10$ are exponentially suppressed.
-The negative ringing is a lot less visible albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
+All three panels show the exact profile of the spot (black line) and expansions up to three different orders $l$ (colored lines).
+The panel on the left shows the expansion with no smoothing ($\sigma_s=0$) in which case the symmetric ringing around the center of the spot is clearly visible even at relatively high order ($l=20$).
+The middle panel shows an intermediate level of smoothing with $\sigma_s=0.1$, meaning that all features on scales above $l\approx 10$ are exponentially suppressed.
+The negative ringing is a lot less visible, albeit at the cost of having a slightly larger spot because suppressing higher order harmonics necessarily means that we lose some ability to represent smaller scale features.
 For $\sigma_s=0.2$ (right) there is practically no ringing, but the expansions at $l=10$, $l=15$ and $l=20$ result in the spot of the same size because all coefficients above $l=5$ are significantly suppressed.
@@
 In principle we can always get rid of ringing by fitting sufficiently high order maps.
-In practice, computing the analytic integrals computed in \textsf{starry} becomes computationally unstable above $l\approx 20$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
+In practice, the analytic integrals computed in \textsf{starry} become computationally unstable above $l\approx 20$ so instead of going to very high order we apply some smoothing to mitigate the ringing.
 We find that setting $\sigma_s=2/l$ where $l$ is the order of expansion of the map  is a good default setting for $\sigma_s$.
 
-\section{Results for simulated data}
+\section{Results -- simulated data}
 \label{sec:results_sim}
@@
 In this section we generalize the example from Section~\ref{ssec:pixels_vs_harmonics} such that the simulated map includes an additional faint hot spot located at $-15^\circ$ N latitude and $-40^\circ$ E longitude with a diameter of $5^\circ$.
-We set the amplitude of the ``faint" spot to 20\% of the luminosity of the featureless map.
-As before we assume that we know the ephemeris exactly.
-We generate the light curves from an $l=20$ map and fit a map of the same order and we apply a Gaussian smoothing filter to both the simulated map and the inferred map with the smoothing parameter set to $\sigma_s=2/l=0.1$.
-We fit the model with NUTS with 1000 warm-up steps and 2000 final steps.
+We set the amplitude of the ``faint" spot to 30\% of the luminosity of the featureless map.
+As before we assume that we know the geometry of the occultation exactly.
+We generate the light curves from an $l=30$ map and fit an $l=20$ map and we apply a Gaussian smoothing filter to both the simulated map and the inferred map with the smoothing parameter set to $\sigma_s=2/l=0.1$.
+We fit the model using NUTS with 1000 warm-up steps and 2000 final steps.
 
@@
 It is an improvement on the Horseshoe prior introduced in \cite{carvalho2010a}.
-The key idea behind both kinds of Horseshoe priors is to set the scale for each regression coefficient (pixel) to a product of a global scale $\tau$ and a local scale $\lambda_i$ (where $i$ indexes all the pixels) and marginalize over these scales by setting a prior for each.
-For clarity, we discuss the Horseshoe priors in Appendix~\ref{app:horseshoe}.
+The key idea behind both kinds of Horseshoe priors is to set the scale for each regression coefficient (pixel) to a product of a global scale $\tau$ and a local scale $\lambda_i$ (where $i$ indexes all the pixels) and we marginalize over these scales by setting a prior for each.
+For clarity, we omit the discussion of  the Horseshoe priors here and refer the reader to Appendix~\ref{app:horseshoe}.
 
@@
         Inferred $l=20$ map obtained by fitting a pair of simulated ingress/egress occultation light curves of Io using a hybrid pixel model with a Regularized Horseshoe prior on the pixels.
-With this prior, the model is able to accurately recover the true map.
-        The plot shows the true $l=20$ map (top), the posterior (median) estimate of the inferred map (second row), the inferred map as seen by the observer during the occultation (small circles), the data and posterior samples of the flux (orange lines), and the normalized residuals (bottom).
-        The location of the true spots on the inferred map is marker with a grey cross (X).
+With this prior, the model is able to accurately recover the simulated map.
+        The plot shows the simulated $l=20$ map (top), the posterior (median) estimate of the inferred map (second row), the inferred map as seen by the observer during the occultation (small circles), the data and posterior samples of the flux (orange lines), and the normalized residuals (bottom).
+        The location of the simulated spots on the inferred map is marker with a grey cross (X).
        \label{fig:ingress_egress_sim_snr_50}
@@
 
-The results for a high signal-to-noise light curve (SNR=50) are shown in Fig.~\ref{fig:ingress_egress_sim_snr_50}, the model recovers both spots.
-The plot shows the true map (top row), the median posterior estimate of the inferred map (second row), the inferred map as seen by the observer during the occultation (small circles), the data and posterior samples of flux (orange lines) and the residuals with respect to a median estimate of the flux (bottom).
-The location of the true spots on the inferred map is marker with a grey cross (X).
-The bright spot is nearly indistinguishable from the true spot; the fainter spot is somewhat less well constrained but the error in position for both is at most a few degrees.
+The results for a high signal-to-noise light curve (SNR=50) are shown in Fig.~\ref{fig:ingress_egress_sim_snr_50}: the model recovers both spots.
+The plot shows the simulated map (top row), the median posterior estimate of the inferred map (second row), the inferred map as seen by the observer during the occultation (small circles), the data and posterior samples of flux (orange lines) and the residuals with respect to a median estimate of the flux (bottom).
+The location of the simulated spots on the inferred map is marker with a grey cross (X).
+The bright spot is nearly indistinguishable from the simulated spot; the fainter spot is somewhat less well constrained but the error in position for both is at most a few degrees.
 Ringing artifacts are minimal because of the smoothing filter and there are no discernible patterns in the residuals.
@@
 We place uniform priors on the angles and positive Gaussian priors on other parameters. 
-We find that if the number of modeled spots matches the number of true spots the model easily converges to the true solution. 
-If the number of modeled spots is larger or smaller than the true number the model does not converge due to pathologies in the posterior distribution.
+We find that if the number of modeled spots matches the number of simulated spots the model easily converges to the true solution. 
+If the number of modeled spots is larger or smaller than the true number of spots the model does not converge to the true solution due to pathologies in the posterior distribution.
 
@@
 
-\section{Results for IRTF data}
+\section{Results -- IRTF light curves}
 \label{sec:results}
 \subsection{1998 pair of occultations by Jupiter}
-Having demonstrated that our model works well on simulated data, we turn to fitting observations of actual occultation of Io observed with the IRTF telescope.
-We selected two pairs of high quality ingress/egress light curves relatively closely spaced in time so that the assumption that the surface map is identical for both the ingress and the egress light curve is at least approximately correct; although we allow for a difference in the overall amplitude of the maps between the two occultations.
+Having demonstrated that our model works well on simulated data, we turn to fitting observations of actual occultations of Io observed with the IRTF telescope.
+We selected two pairs of high quality ingress/egress light curves relatively closely spaced in time so that the assumption that the surface map is identical for both the ingress and the egress light curve is at least approximately correct, although we allow for a difference in the overall amplitude of the maps between the two occultations.
 We fit a pair of events from 1998, an ingress occultation observed on the 27th of August and an egress occultation observed on the 29th of November.
@@
 where $\sigma_{i,I}$ are the errobars for the ingress light curve and $\sigma_{i,E}$ are the errobars for the egress light curve.
-Treating errobars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data (and our model is regularized).
+The symbol $\mathcal{N}^+$ denotes a truncated Gaussian distribution restricted to positive values.
+Treating errobars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data and our model is regularized.
 The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errobars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Matern 3/2 kernel.
@@
             %
-            $\tau$ & global pixel scale &  \begin{minipage}{0.5\textwidth}  \shortstack[l]{$\mathrm{Half}-\mathcal{C}(0,\tau_0)$, $\tau_0$ defined in Equation~(\ref{eq:horseshoe_tau0}) \\with $p_0=0.8D$}\end{minipage}
+            $\tau$ & global pixel scale &  \begin{minipage}{0.5\textwidth}  \shortstack[l]{$\mathrm{Half}-\mathcal{C}(0,\tau_0)$, $\tau_0$ defined by\\Equation~(\ref{eq:horseshoe_tau0}) with $p_0=0.8D$}\end{minipage}
            %
@@
 The posterior distribution for the errobars is shown in Figure~\ref{fig:irtf_1998_errorbars}.
-Both the global scale for the errobars and the individual errobars are well constrained by the data. 
+Both the global scale for of the errobars and the individual errobars are well constrained by the data. 
 The outlier points are naturally accounted for in our model because those points end up having higher variance.
@@
 In general, we expect that a given feature in the light curve will be accounted for by the physical model if the physical model provides a better explanation for the data than the noise model.
-We will return to this point later.
+We will return to this point shortly.
 
@@
         The errobars are estimated using a hierarchical model in which we assume  that each errobar is drawn from a Half Gaussian distribution with a global scale parameter common to all errobars in a single light curve.
-       \label{fig:irtf_1998_errorbarss}
+       \label{fig:irtf_1998_errorbars}
     }
@@
 Figure~\ref{fig:irtf_1998_spots} shows  a contour map of both hot spots overlaid on top of the U.S.
-Geological Survey's map of the surface of Io \cite{williams2011} which was constructed from Galileo observations.
+Geological Survey's map of the surface of Io \citep{williams2011} which was constructed from observations by the Galileo satellite.
 The plot shows the error in the inferred latitude and longitude for each spot (white lines) and a contour map computed from the median posterior estimate of the map.
@@
 Thus, \textbf{despite the fact that at $l=20$ the resolution of maps is limited to about $9^\circ$, we can constrain the centroid of the spots much more precisely}.
-We should note however that this errorbar does not include a possible systematic shift in position due to a wrong estimate of Jupiter's effective radius (see Section~\ref{ssec:effective_radius}).
+We should note however that this errorbar does not include a possible systematic shift in position due to a wrong estimate of Jupiter's effective radius (see Section~\ref{ssec:effective_radius}) or an error in the ephemeris data.
 
@@
 The main difference in the inferred map compared to Figure~\ref{fig:irtf_1998} is that there are two extra spots visible in the map.
-The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve which is Loki coming out and into view during the occultation.
+The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve, which is due to  Loki coming out and into view during the occultation.
 The model inflates the errobars around those times because it unable to make the spot small enough.
@@
 The estimated location of this spot is $20.449_{-0.066}^{+1.253}\quad^\circ$ N latitude and $53.107_{-0.115}^{+0.296}\quad^\circ$ W longitude.
-This location is to the mountain Mongibello Mons but it does not correspond to a well known hotspot.
-Overall, we conclude that that including the Gaussian Process prevents the physical model from overfitting the data although it might occasionally pick up a feature in thedat which is due to a faint real hot spot.
-With a particular scientific goal in mind, it is straightforward to experiment with different noise models to test how the properties of any given spot change.
+This location corresponds to the mountain Mongibello Mons but it does not correspond to a well known hotspot.
+Overall, we conclude that including the Gaussian Process prevents the physical model from overfitting the data although it might occasionally pick up a feature which is due to a faint real hot spot.
+With a particular scientific goal in mind, it is straightforward to experiment with different noise models to test how the properties of any given spot change with different assumptions.
 
@@
 \subsection{Occultation mapping of Io}
-We have presented a novel model for reconstructing volcanic emission features on Io from occultation light curves.
-It is built on top of the \textsf{starry} algorithm which enables fast analytic computation of occultation light curves using spherical harmonics.
-This approach is substantially different from past work because we do not assume where the volcanic features are located on the surface of Io, how many there are or what they look like.
-Instead, we place weaker assumptions on the global structure of the map by requiring that the inferred map has positive intensity everywhere and more importantly that it is \emph{sparse}.
-Besides the map model, our method also incorporates a sophisticated noise model which includes a Gaussian Process and a hierarchical model for the errorbars which are unknown.
-As a result of the sparsity and positivity constraints and the flexible noise model,
-our model is parsimonious, it places features on the map only if the data provides strong evidence for existence of those features.
-This property is not always desirable but it works very well for Io, whose surface is covered with small bright volcanic hotspots.
-Our model is superior to parametric methods in which we assume some fixed number of spots on the surface of Io and fit for the locations of those spots because we do not need to make such strong assumptions on the surface and the computational cost of the parametric models is comparable to our approach.
-
-We test the model first on simulated data and then on observations of actual occultations of Io by Jupiter taken using NASA's Infrared Telescope Facility.
-We choose two pairs of light curves to demonstrate that the model gives useful results.
+We have presented a novel method for mapping the volcanic emission on Io from occultation light curves.
+The method relies on the \textsf{starry} algorithm which enables fast analytic computation of occultation light curves by expanding the surface emission map in spherical harmonics.
+Our method is substantially different from past work because we do not assume where the volcanic features are located on the surface of Io, how many there are or what they look like.
+Instead, we place weaker assumptions on the global structure of the map by requiring that the inferred map has positive intensity everywhere and most importantly, that it is \emph{sparse}.
+\cite{aizawa2020} also find the sparsity assumption useful in the context of exoplanet mapping.
+Besides the model for the surface map, our method also incorporates a sophisticated noise model which includes a Gaussian Process and a hierarchical model for the (unknown) errorbars.
+As a result of the sparsity and positivity constraints and the flexibility of the noise model,
+our model is parsimonious: it places features on the map only if the data provides strong evidence for the existence of those features.
+This property is not always desirable but it works very well for Io, whose surface is covered with small highly localized and bright volcanic hotspots.
+Our model is superior to parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface and the computational cost of the parametric models is comparable to our approach.
+
+We test the model first on simulated data and then on observations of real occultations of Io by Jupiter observed using NASA's Infrared Telescope Facility.
+We choose two pairs of light curves to demonstrate that the model can recover known hotspots.
 Each pair consists of an ingress observation and an egress observation of an occultation. 
 The two observations are sufficient to break the degeneracy in the position of the spots because Jupiter's limb sweeps across the projected disc of Io at different angles at ingress and egress.
-Using a pair of observations from 1998 we infer a map consisting of two hot spots.
-Locations of both hotspots correspond to well known features on the surface of Io, the major volcano Loki and the lava flow Kanehekili.
+By fitting a pair of observations from 1998 we infer a map consisting of two spots whose locations correspond to well known hotspots on the surface of Io, the major volcano Loki and the lava flow Kanehekili.
 We also find circumstantial evidence for a third hot spot.
-Because our model is fully probabilistic, we can derive uncertainties on location of the inferred hot spots and the total power emitted from the hot spot.
+Because our model is fully probabilistic, we can derive uncertainties on location of the inferred hot spots and the total power emitted from each spot.
 In addition to the pair of observations from 1998, we test the model on another pair of observations from 2017.
@@
 
-This paper is merely a first step in a series of papers dedicated to probabilistic modeling of Io's surface and also extending the models to exoplanet surfaces. 
-The major issue with the model presented in this work is that we can only fit a static map to some number of light curves.
-We are unable to model time variable features and quantify that variability.
-In Paper II we aim to develop a generalized model with which we will be able to fit all IRTF light curves simultaneously and infer a time-dependent map.
-
 The main limitation of our model besides the fact that we cannot account for time-dependent maps is the limited resolution of the spherical harmonic maps for which \textsf{starry} can compute occultation light curves.
-Although we can still constrain the peak intensity of spots (or some other measure of the center of emission) with much higher precision, we do lose the ability to resolve two spots close to each other and the ability to constrain the actual size of the spots.
-It is quite possible that we can get around this problem by computing the various integrals in starry numerically using high precision arithmetic.
-Since all these operations are contained in the design matrix $\mathbf{A}$ (assuming that the ephemeris is fixed) we would only need to compute the expensive numerical integrals once for each occultation.
+Although we can still constrain the peak intensity of hotspots (or some other measure of the center of emission) with much higher precision, we lose the ability to resolve two spots close to each other and the ability to constrain the actual size of the spots.
+It is quite possible that there is a way around this problem if we compute the various integrals in \textsf{starry} numerically using high precision arithmetic.
+Since all these operations are contained in the design matrix $\mathbf{A}$ (assuming that the ephemeris is fixed) we would only need to do the expensive computation once for each occultation.
 To be able to constrain the size of the Loki hotspot for example, we would need to fit maps on the order of $l\approx 50$.
+However, the kind of detailed mapping of Loki's magma lake with a precision of a few km done by \cite{dekleer2017} will not be possible with a spherical harmonic model because it would require maps of extremely large degrees ($l\gtrapprox 700$).
 
 \subsection{Relevance to mapping of exoplanets} 
-Exoplanets with likely extreme volcanism are prime targets for future secondary eclipse observations by the James Webb Space Telescope. 
-The formalism presented in this paper easily generalizes to exoplanets. 
-Nearly every aspect of the model we have discussed applies to exoplanets as well.
-In fact, modeling secondary eclipses exoplanets is simpler in a way because with exoplanets we can only hope to constrain lower resolution features on the map.
+\label{ssec:discussion_exoplanets}
+Hot Super Earths with likely molten surfaces such as 55 Cancri e are prime targets for future observations with the James Webb Space Telescope (JWST) \citep{samuel2014,henning2018}.
+The model we have presented in this paper can easily be applied to observations of exoplanets.
+All one has to do is compute the design matrix $\mathbf{A}$ given a specification of the planet's orbit.
+This is very straightforward in \textsf{starry} because the code was designed primarily for modeling occultations of exoplanets.
+Given that the observations of the secondary eclipses (occultations) of exoplanets will never be as high quality as observations of Io, the limited resolution spherical harmonic maps are more than sufficient for modeling exoplanet observations.
+The question of what kind of features on the surfaces of volcanic exoplanets it will be possible to constrain with secondary eclipse observations using JWST and with what precision is one we aim to address in future work.
+
+Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model is also likely to useful for modeling features on gaseous exoplanets with sparse surface features.
+These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
+Even if the sparsity assumption is not valid for these types of planets the hybrid pixel/spherical harmonic model can be easily be used with a different set of priors more appropriate for observations.
+For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry.
 
 \subsection{Future work}
+This paper is a first step in a series of papers dedicated to probabilistic modeling of Io's surface. 
+A major issue with the model presented in this work is that we cannot naturally account for the time variability of surface emission.
+In Paper II in this series, we aim to fit an ensemble of light curves (occultations by Jupiter, mutual occultations and phase curves) with a generalized model which will enable us to infer a time-dependent map of the entire surface and quantify the time variability over time scales of decades.
+A spatio-temporal map of volcanic emission spanning such a long timescale will help us better understand global evolution of volcanism on Io.
+
+Besides extending the model to time-dependent maps, it should be straightforward to extend it for use in fitting \emph{resolved} observations of Io (either occulted or not) such as the adaptive optics observations done by \cite{dekleer2016a} and \cite{dekleer2016}.
+Since we would not need to compute integrated flux over complicated boundaries in that case, we could fit maps of much higher order.
+
+% Bibliography
+\bibliography{bib}
 
@@
 
-% Bibliography
-\bibliography{bib}
-
 \end{document}

### 2021-03-04 paper/paper.tex
Dan's comments

@@
 % Author list
-\author{Fran Bartoli\'c}
+\author[0000-0001-8630-9794]{Fran Bartoli\'c}
 \email{fb90@st-andrews.ac.uk}
@@
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY, USA}
-\author{Rodrigo Luger}
-\author{Daniel Foreman-Mackey}
+\author[0000-0002-0296-3826]{Rodrigo Luger}
+\author[0000-0002-9328-5652]{Daniel Foreman-Mackey}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY, USA}
-\author{Robert R. Howell}
+\author[0000-0003-4859-2060]{Robert R. Howell}
 \affil{Department~of~Geology~\&~Geophysics, University~of~Wyoming, Laramie, WY, USA}
-\author{Julie A. Rathbun}
+\author[0000-0001-7619-652X]{Julie A. Rathbun}
 \affil{Planetary~Science~Institute, Tuscon, AZ, USA}
@@
 We built a generative model of Io's surface using the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic and differentiable computation of occultation light curves in emitted and reflected light.
-    Our fully Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of features.
+    Our probabilistic Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of features.
     The methods we have developed are also directly applicable to the problem of mapping stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
@@
 Contrary to Earth, Io lacks plate tectonics.
-The heat transport mechanism likely operating on Io is volcanism through the lithosphere (the outermost shell of a terrestrial body), also known as \emph{Heat-pipe volcanism}, a process in which magma is transported to the surface through localised vents \citep{oreilly1981}.
+The heat transport mechanism likely operating on Io is volcanism through the lithosphere (the outermost shell of a terrestrial body), also known as \emph{heat-pipe volcanism}, a process in which magma is transported to the surface through localised vents \citep{oreilly1981}.
 Heat-pipe volcanism might have occurred in the early history of terrestrial planets in the Solar System \citep{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
@@
 Volcanic exoplanets, sometimes dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
-Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016d,hammond2017}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019}, and many others.
+Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016d,hammond2017a}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019}, and many others.
 Not all such exoplanets will have Io-like volcanism; some may have magma oceans due to their proximity to the star or volcanism caused by nuclear decay, similar to volcanism on present day Earth.
@@
 
-Most studies of occultations of Io fit multiple light curves independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface (notable exceptions are \cite{spencer1994} and \cite{dekleer2017}), assuming strong priors on the locations of individual volcanoes based on maps from space mission observations.
+Most studies of (unresolved) occultations of Io fit multiple light curves independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface (notable exceptions are \cite{spencer1994} and \cite{dekleer2017}), assuming relatively strong priors on the locations of individual volcanoes.
 In this work, we build a fully probabilistic model in order to infer a \emph{two-dimensional map} of Io's volcanic surface from archival IRTF observations of Io in the near infrared.
@@
 Our main goal in this paper is to develop a general model for mapping surfaces of occulted bodies with sparse, high contrast features and apply it to observations of Io.
-Because we have lots of prior information on what the surface of Io should look like, we can compare features in our inferred maps to known volcanic hotspots and test the sensitivity of the inferred maps to different choices of priors and noise models.
+Because of high resolution resolved imaging of Io, we can compare features in our inferred maps to known volcanic hotspots and test the sensitivity of the inferred maps to different choices of priors and noise models.
 The paper is organized as follows.
@@
 
+The code associated with this paper is publicly hosted in a GitHub repository\footnote{\url{https://github.com/fbartolic/volcano}}. 
 All of the figures in this paper were auto-generated
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
     \begin{centering}
@@
 
-The complete dataset consists of 112 sets of observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994}, the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{johnrayner2016}.
-%(TODO: fix citation).
+The complete dataset consists of 112 sets of observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994}, the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{rayner2016}.
 Although the observations span decades, the timespan between observations varies and there were very few observations taken between 2008 and 2016.
@@
         Since the pixel map is higher resolution than the spherical harmonic map at $l=20$, the         spherical harmonic map appears smoother and the intensity distribution is more similar to a skewed Gaussian rather than an exponential distribution.
-        Despite this fact we find that fitting for maps in the pixel basis and transforming them to spherical harmonics at each MCMC step in order to compute the light curve analytically with \textsf{starry} is superior to fitting for spherical harmonics because the pixel grid provides a strong constraint on the spherical harmonic map structure.
+        Despite this fact, we find that fitting for maps in the pixel basis and transforming them to spherical harmonics at each MCMC step in order to compute the light curve analytically with \textsf{starry} is better than fitting for spherical harmonics because the pixel grid provides a strong constraint on the spherical harmonic map structure.
   \label{fig:pixels_to_harmonics}}
@@
 We use the simple (approximate) Mat\'ern 3/2 kernel function which is parametrized by two values, a standard deviation parameter $\sigma_\mathrm{GP}$ and a characteristic timescale parameter $\rho_\mathrm{GP}$.
-It is given by 
+The Mat\'ern 3/2 kernel is defined by
 \begin{equation}
     k(\tau;\sigma_\mathrm{GP},
-    rho_\mathrm{GP})=\sigma_\mathrm{GP}^{2}\left[(1+1 / \epsilon) e^{-(1-\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}(1-1 / \epsilon) e^{-(1+\epsilon) \sqrt{3} \tau / \rho_\mathrm{GP}}\right]
+    \rho_\mathrm{GP})=\
+    \sigma_\mathrm{GP}^{2}\left(1+\frac{\sqrt{3} \tau}{\rho_\mathrm{GP}}\right) \exp \left(-\frac{\sqrt{3} \tau}{\rho_\mathrm{GP}}\right)
     \quad,
@@
 Treating errobars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data and our model is regularized.
-The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errobars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Matern 3/2 kernel.
+The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errobars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Mat\'ern 3/2 kernel.
 All model parameters and their associated priors are listed in Table~\ref{tab:priors}.
@@
 Looking at the miniature maps in Figure~\ref{fig:irtf_1998_no_GP}, this spot is in view only at egress and it corresponds to a small step in the light curve starting at 0.9 minutes.
-The estimated location of this spot is $20.449_{-0.066}^{+1.253}\quad^\circ$ N latitude and $53.107_{-0.115}^{+0.296}\quad^\circ$ W longitude.
-This location corresponds to the mountain Mongibello Mons but it does not correspond to a well known hotspot.
+The estimated location of this spot is approximatel $\sim 20\quad^\circ$ N latitude and $\sim 69\quad^\circ$ W longitude.
+This location corresponds to southern end of the mountain Mongibello Mons but there are no known persistent hotspots at that location so we cannot say if the hotspots is real or not without independently detecting it in other light curves.
 Overall, we conclude that including the Gaussian Process prevents the physical model from overfitting the data although it might occasionally pick up a feature which is due to a faint real hot spot.
@@
 This property is not always desirable but it works very well for Io, whose surface is covered with small highly localized and bright volcanic hotspots.
-Our model is superior to parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface and the computational cost of the parametric models is comparable to our approach.
+Our model is better than parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface and the computational cost of the parametric models is comparable to our approach.
 
@@
 
-The main limitation of our model besides the fact that we cannot account for time-dependent maps is the limited resolution of the spherical harmonic maps for which \textsf{starry} can compute occultation light curves.
+The main limitation of our model besides the fact that we do not yet account for time-dependent maps is the limited resolution of the spherical harmonic maps for which \textsf{starry} can compute occultation light curves.
 Although we can still constrain the peak intensity of hotspots (or some other measure of the center of emission) with much higher precision, we lose the ability to resolve two spots close to each other and the ability to constrain the actual size of the spots.
@@
 
-Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model is also likely to useful for modeling features on gaseous exoplanets with sparse surface features.
+Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model is also likely to be useful for modeling features on gaseous exoplanets with sparse surface features.
 These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
@@
 \end{equation}
-We find that without using the non-centered parametrization the sampling is problematic and there are lots of divergences in the gradients of the parameters; with the non-centered parametrization there are no problems with sampling.
+We find that without using the non-centered parametrization the sampling is problematic and there are many divergences in the gradients of the parameters; with the non-centered parametrization there are no problems with sampling.
 

### 2021-03-04 paper/paper.tex
minor changes to abstract and introduction.

@@
 Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
-Existing photometric observations in the near infrared taken during occultations by Jupiter and other Galilean moons encode a wealth of information about its surface.
-These data are ideal for testing methods for inferring surface features of occulted bodies from time series observations.
-We built a generative model of Io's surface using the code starry \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast analytic and differentiable computation of occultation light curves in emitted and reflected light.
-    Our probabilistic Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of features.
-    The methods we have developed are also directly applicable to the problem of mapping stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+Io has been observed during occultations by Jupiter and other Galilean moons using high-cadence near infrared photometry since the 1980s. 
+These observations encode a wealth of information about its surface.
+They are ideal for testing methods for inferring surface maps of occulted bodies from time series observations.
+    We built a generative model of Io's surface using the code \textsf{starry} \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
+    Our probabilistic Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of these features.
+    The methods we have developed are also easily applicable to the problem of mapping stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 The global heat flow on its surface is about 40 times larger than Earth's \citep{breuer2007,davies2010} and about 50\% of the heat flow emanates from only 1.2\% of Io's surface \citep{veeder2012}.
-This intense volcanic activity cannot be explained by radioactive decay, the mechanism which drives Earth's volcanism; instead, the volcanism on Io is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
+This intense volcanic activity cannot be explained by radioactive decay, the mechanism which drives Earth's volcanism.
+Instead, the volcanism on Io is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
 Contrary to Earth, Io lacks plate tectonics.
-The heat transport mechanism likely operating on Io is volcanism through the lithosphere (the outermost shell of a terrestrial body), also known as \emph{heat-pipe volcanism}, a process in which magma is transported to the surface through localised vents \citep{oreilly1981}.
-Heat-pipe volcanism might have occurred in the early history of terrestrial planets in the Solar System \citep{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
+The heat transport mechanism most likely operating on Io is volcanism generated in the lithosphere (the outermost shell of a terrestrial body).
+This process is also known as \emph{heat-pipe volcanism}, whereby magma is transported to the surface through localised vents \citep{oreilly1981}.
+Heat-pipe volcanism likely occurred in the early history of terrestrial planets in the Solar System \citep{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
 
 Besides providing a window into early volcanic activity in the Solar System, Io is also in many ways an analogue of a volcanically active exoplanet.
-Volcanic exoplanets, sometimes dubbed \emph{super-Ios} or \emph{lava worlds}, have gathered a lot of interest in recent years because both photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
-Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to, among other things, lava flows on the surface \citep{demory2016,demory2016d,hammond2017a}; several planets in the TRAPPIST-1 system in a Laplace-like resonance with likely volcanic activity \citep{kislyakova2017,dobos2019}, and many others.
-Not all such exoplanets will have Io-like volcanism; some may have magma oceans due to their proximity to the star or volcanism caused by nuclear decay, similar to volcanism on present day Earth.
+Volcanic exoplanets, sometimes dubbed ``super-Ios" or ``lava worlds", have gathered a lot of interest in recent years.
+Photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
+Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to (among other things) lava flows on the surface \citep{demory2016,demory2016d,hammond2017a}; several planets in the TRAPPIST-1 system in a Laplace-like resonance likely exhibiting volcanic activity \citep{kislyakova2017,dobos2019}, and many others.
+Not all such exoplanets are expected to have Io-like volcanism.
+Some will have magma oceans because of their proximity to the star and others will have volcanism powered by nuclear decay, similar to volcanism on present day Earth.
 
@@
 The surface has also been resolved from ground based observations in the near infrared using disk resolved imaging \citep{howell1985,simonelli1986,spencer1990} and adaptive optics observations \citep{marchis2000,marchis2005,dekleer2016}.
-Most importantly for this work, Io has been sporadically observed for decades using high cadence near infrared photometry taken during occultations by Jupiter, starting with \cite{spencer1990}.
-Occultations by Jupiter occur twice every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called \emph{mutual occultations}) happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites, multiple occultations are then observable over a course of approximately one year.
+Most importantly for this work,  starting with \cite{spencer1990} Io has been sporadically observed over a timespan of decades using high cadence near infrared photometry taken during occultations by Jupiter.
+Occultations by Jupiter occur twice every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called \emph{mutual occultations}) happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites.
+Multiple occultations are then observable over a course of approximately one year.
 The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow (``in eclipse") while mutual occultations are almost always observed in sunlight.
@@
 By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki Patera (\emph{Patera} is a type of an irregular crater) region to a precision of about 2 kilometers.
-In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical \citep[][and references therein]{arlot1974,saquet2018,morgado2016a} for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites.
+In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites \citep[][and references therein]{arlot1974,saquet2018,morgado2016a}.
 Understanding the detailed albedo distribution is crucial to constraining the ephemeris of Io to a very high precision.
@@
 We selected two pairs of high quality ingress/egress light curves relatively closely spaced in time so that the assumption that the surface map is identical for both the ingress and the egress light curve is at least approximately correct, although we allow for a difference in the overall amplitude of the maps between the two occultations.
-We fit a pair of events from 1998, an ingress occultation observed on the 27th of August and an egress occultation observed on the 29th of November.
+We fit a pair of events from 1998, an ingress occultation observed on the 27th of August and an egress occultation observed  94 days later on the 29th of November.
+As a reminder, the period of Loki's variability is around 540 days \citep{rathbun2002}.
 For comparison, we also fit a pair of events observed nearly two decades later in 2017.
+
 The predicted fluxes are given by 
@@
 \subsection{2017 pair of occultations by Jupiter}
-To test how our model generalizes to a different dataset we fit a pair of observations from 2017, an ingress occultation observed on the 31st of March and an egress occultation observed on the 11th of May.
+To test how our model generalizes to a different dataset we fit a pair of observations from 2017, an ingress occultation observed on the 31st of March and an egress occultation observed 41 days later on the 11th of May.
 We use the exact same model as the one we used to produce Figure~\ref{fig:irtf_1998}.
@@
 The method relies on the \textsf{starry} algorithm which enables fast analytic computation of occultation light curves by expanding the surface emission map in spherical harmonics.
-Our method is substantially different from past work because we do not assume where the volcanic features are located on the surface of Io, how many there are or what they look like.
-Instead, we place weaker assumptions on the global structure of the map by requiring that the inferred map has positive intensity everywhere and most importantly, that it is \emph{sparse}.
-\cite{aizawa2020} also find the sparsity assumption useful in the context of exoplanet mapping.
+Our method is different from past work because we do not assume we know where the volcanic features are located on the surface of Io, how many there are or what they look like.
+Instead, we place weaker assumptions on the global structure of the map by requiring that the inferred map has positive intensity everywhere and most importantly, that it is \emph{sparse} \footnote{\cite{aizawa2020} also find the sparsity assumption useful in the context of exoplanet mapping.}.
 Besides the model for the surface map, our method also incorporates a sophisticated noise model which includes a Gaussian Process and a hierarchical model for the (unknown) errorbars.
@@
 our model is parsimonious: it places features on the map only if the data provides strong evidence for the existence of those features.
-This property is not always desirable but it works very well for Io, whose surface is covered with small highly localized and bright volcanic hotspots.
-Our model is better than parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface and the computational cost of the parametric models is comparable to our approach.
-
-We test the model first on simulated data and then on observations of real occultations of Io by Jupiter observed using NASA's Infrared Telescope Facility.
+This property is not always desirable but it works very well for Io, a moon whose surface is covered with small, highly localized, and bright volcanic hotspots.
+Our model is substantially more flexible than parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface.
+The computational cost of the parametric models is comparable to our approach.
+
+To test our method we first fit a simulated dataset and then observations of real occultations of Io by Jupiter, observed using NASA's Infrared Telescope Facility.
 We choose two pairs of light curves to demonstrate that the model can recover known hotspots.
@@
 The two observations are sufficient to break the degeneracy in the position of the spots because Jupiter's limb sweeps across the projected disc of Io at different angles at ingress and egress.
-By fitting a pair of observations from 1998 we infer a map consisting of two spots whose locations correspond to well known hotspots on the surface of Io, the major volcano Loki and the lava flow Kanehekili.
+From the 1998 observations we infer a map consisting of two spots whose locations correspond to well known hotspots on the surface of Io, the major volcano Loki and the lava flow Kanehekili.
 We also find circumstantial evidence for a third hot spot.
-Because our model is fully probabilistic, we can derive uncertainties on location of the inferred hot spots and the total power emitted from each spot.
+Because our model is fully probabilistic, we can derive uncertainties on the location of the inferred hot spots and the total flux emitted from each spot.
 In addition to the pair of observations from 1998, we test the model on another pair of observations from 2017.
@@
 To be able to constrain the size of the Loki hotspot for example, we would need to fit maps on the order of $l\approx 50$.
-However, the kind of detailed mapping of Loki's magma lake with a precision of a few km done by \cite{dekleer2017} will not be possible with a spherical harmonic model because it would require maps of extremely large degrees ($l\gtrapprox 700$).
+However, the kind of detailed mapping of Loki's magma lake with a precision of a few kilometers done by \cite{dekleer2017} will not be possible with a spherical harmonic model because it would require maps of extremely large degrees ($l\gtrapprox 700$).
 
@@
 \label{ssec:discussion_exoplanets}
-Hot Super Earths with likely molten surfaces such as 55 Cancri e are prime targets for future observations with the James Webb Space Telescope (JWST) \citep{samuel2014,henning2018}.
+Hot Super Earths with (probably) molten surfaces such as 55 Cancri e are prime targets for future observations with the James Webb Space Telescope (JWST) \citep{samuel2014,henning2018}.
 The model we have presented in this paper can easily be applied to observations of exoplanets. 
-All one has to do is compute the design matrix $\mathbf{A}$ given a specification of the planet's orbit.
-This is very straightforward in \textsf{starry} because the code was designed primarily for modeling occultations of exoplanets.
-Given that the observations of the secondary eclipses (occultations) of exoplanets will never be as high quality as observations of Io, the limited resolution spherical harmonic maps are more than sufficient for modeling exoplanet observations.
+In fact, one of the motivations for this work was to test methods developed largely for the purpose of mapping exoplanets in a context where the ground truth is more easily accessible because Io is in the Solar System.
+To apply our model to exoplanet observations we just need to compute the design matrix $\mathbf{A}$ given a specification of the planet's orbit which is very straightforward in \textsf{starry}
+and since the observations of the secondary eclipses (occultations) of exoplanets will never be as high quality as observations of Io, the limited resolution of spherical harmonic maps is more than sufficient for modeling exoplanet observations.
 The question of what kind of features on the surfaces of volcanic exoplanets it will be possible to constrain with secondary eclipse observations using JWST and with what precision is one we aim to address in future work.
@@
 These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
-Even if the sparsity assumption is not valid for these types of planets the hybrid pixel/spherical harmonic model can be easily be used with a different set of priors more appropriate for observations.
-For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry.
+Even if the sparsity assumption is not valid for these types of planets the hybrid pixel/spherical harmonic model can be easily be used with a different set of priors more appropriate for these observations.
+For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry for the inferred map.
 
@@
 In Paper II in this series, we aim to fit an ensemble of light curves (occultations by Jupiter, mutual occultations and phase curves) with a generalized model which will enable us to infer a time-dependent map of the entire surface and quantify the time variability over time scales of decades.
-A spatio-temporal map of volcanic emission spanning such a long timescale will help us better understand global evolution of volcanism on Io.
-
-Besides extending the model to time-dependent maps, it should be straightforward to extend it for use in fitting \emph{resolved} observations of Io (either occulted or not) such as the adaptive optics observations done by \cite{dekleer2016a} and \cite{dekleer2016}.
+A spatio-temporal map of volcanic emission spanning such a long timescale will help us better understand the global evolution of volcanism on Io. 
+In addition to modeling global properties of volcanism of Io, it would also be interesting to constrain the time evolution of peak emission in Loki Patera with high accuracy in order to better understand the resurfacing process.
+
+Finally, it should be straightforward to extend our model for use in fitting \emph{resolved} observations of Io (either occulted or not) such as the adaptive optics observations done by \cite{dekleer2016a} and \cite{dekleer2016}.
 Since we would not need to compute integrated flux over complicated boundaries in that case, we could fit maps of much higher order.
+
+\vspace{+3em}
+
+We would like to thank Will Farr, Katherine de Kleer, David W.
+Hogg, and the Astronomical Data Group at the Center for Computational Astrophysics for their help and thought-provoking discussions.
+Fran Bartoli\'c acknowledges the support and funding from the 2020 Flatiron Institute Center for Computational Astrophysics Pre-Doctoral program which made this paper possible.
 

### 2021-03-04 paper/paper.tex
minor

@@
 
-Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model is also likely to be useful for modeling features on gaseous exoplanets with sparse surface features.
+Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model can be used for modeling surfaces of gaseous exoplanets with sparse features.
 These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
@@
 For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry for the inferred map.
-
+\newline
 \subsection{Future work}

### 2021-03-04 paper/figures/irtf_dataset.py
add dates

@@ -40,8 +40,8 @@ ax.grid()
 plt.savefig("irtf_max_flux.pdf", bbox_inches="tight", dpi=500)
 
 # Plot a few example light curves
-fig, ax = plt.subplots(4, 3, figsize=(10, 6), sharex=True)
-fig.subplots_adjust(wspace=0.2)
+fig, ax = plt.subplots(4, 3, figsize=(10, 8), sharex=True)
+fig.subplots_adjust(wspace=0.2, hspace=0.3)
 
 idcs = np.random.randint(0, len(lcs) - 1, size=3 * 4)
 
@@ -55,7 +55,8 @@ for a, idx in zip(ax.flatten(), idcs):
     a.locator_params(nbins=8, axis="x")
     a.yaxis.set_major_locator(MaxNLocator(integer=True, nbins=5))
     a.set_ylim(bottom=-1)
+    a.set_title(f"{lcs[idx].time[0].isot[:19]}", fontdict={"fontsize": 12})
 
-fig.text(0.5, 0.01, "Duration [minutes]", ha="center")
+fig.text(0.5, 0.02, "Duration [minutes]", ha="center")
 fig.text(0.035, 0.5, "Flux [GW/um/sr]", va="center", rotation="vertical")
 plt.savefig("irtf_sample_lightcurves.pdf", bbox_inches="tight", dpi=500)

### 2021-03-04 paper/figures/irtf_spots_plots.py
minor changes

@@ -11,7 +11,6 @@ from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
 from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
 import matplotlib.font_manager as fm
 
-
 from scipy.integrate import dblquad
 
 from volcano.utils import get_median_map
@@ -27,11 +26,15 @@ def integrand(theta, phi, map):
     return map.intensity(lat=lat, lon=lon) * np.sin(theta)
 
 
-def get_power_emitted(map, lat_range, lon_range):
-    phi_min = lon_range[0] * np.pi / 180
-    phi_max = lon_range[1] * np.pi / 180
-    theta_min = lat_range[0] * np.pi / 180 + np.pi / 2
-    theta_max = lat_range[1] * np.pi / 180 + np.pi / 2
+def get_emitted_power(map, lat_center, lon_center, delta):
+    # Rotate so the spot is at the North pole
+    map.rotate([0, 1, 0], -lon_center)
+    map.rotate([1, 0, 0], -(90 - lat_center))
+
+    phi_min = -180 * np.pi / 180
+    phi_max = 180 * np.pi / 180
+    theta_min = (90 - delta) * np.pi / 180 + np.pi / 2
+    theta_max = 90 * np.pi / 180 + np.pi / 2
 
     res, _ = dblquad(
         integrand,
@@ -43,6 +46,11 @@ def get_power_emitted(map, lat_range, lon_range):
         epsrel=1e-4,
         args=(map,),
     )
+
+    # Rotate back
+    map.rotate([1, 0, 0], (90 - lat_center))
+    map.rotate([0, 1, 0], lon_center)
+
     return res
 
 
@@ -102,9 +110,7 @@ def get_spot_position_and_power(samples, bounds=None, nsamples=300):
         lon_list.append(lon)
 
         # Get total emitted power in circle around inferred spot center
-        power = get_power_emitted(
-            map, (lat - 15, lat + 15), (lon - 15, lon + 15)
-        )
+        power = get_emitted_power(map, lat, lon, 20)
         power_list_in.append(power)
         power_list_eg.append(samples["amp_eg"] * power)
 

### 2021-03-04 paper/figures/simulated_ingress_egress.py
fix typo, tweak model

@@ -34,7 +34,7 @@ theta_in = 350.0
 theta_eg = 10.0
 ro = 39.1
 
-ydeg_true = 20
+ydeg_true = 30
 map_true = starry.Map(ydeg_true)
 spot_ang_dim = 10 * np.pi / 180
 spot_sigma = 1 - np.cos(spot_ang_dim / 2)
@@ -42,7 +42,7 @@ map_true.add_spot(
     amp=1.0, sigma=spot_sigma, lat=13.0, lon=51.0, relative=False
 )
 map_true.add_spot(
-    amp=0.25, sigma=spot_sigma, lat=-15.0, lon=-40.0, relative=False
+    amp=0.3, sigma=spot_sigma, lat=-15.0, lon=-40.0, relative=False
 )
 map_true.amp = 20
 
@@ -265,7 +265,7 @@ def plot(
 
     # Set up the plot
     nim = 7
-    cmap_norm = colors.Normalize(vmin=0.0, vmax=250)
+    cmap_norm = colors.Normalize(vmin=0.0, vmax=300)
     cmap = "Oranges"
     resol = 300
 
@@ -329,7 +329,7 @@ def plot(
         res=resol,
         cmap=cmap,
     )
-    ax_true_map.set_title("True map")
+    ax_true_map.set_title("Simulated map")
 
     # Inferred mean map
     im = map.show(

### 2021-03-04 paper/figures/pixels_vs_harmonics.py
minor tweaks

@@ -40,7 +40,7 @@ def get_median_map(
     map = starry.Map(ydeg=ydeg_inf)
     map.inc = inc
 
-    for n in np.random.randint(0, len(samples), 10):
+    for n in np.random.randint(0, len(samples), nsamples):
         x = samples[n]
         map.amp = x[0]
         map[1:, :] = x[1:] / map.amp
@@ -218,7 +218,7 @@ resol = 300
 
 median_map_moll_ylm = get_median_map(ydeg_inf, samples_ylm["x"], resol=resol)
 median_map_moll_pix = get_median_map(ydeg_inf, samples_pix["x"], resol=resol)
-true_map_image = map_true.render(res=300, projection="Mollweide")
+true_map_image = map_true.render(res=resol, projection="Mollweide")
 
 fig = plt.figure(figsize=(14, 16))
 
@@ -279,7 +279,7 @@ map.show(
     colorbar=False,
     cmap=cmap,
 )
-ax_true_map.set_title("True map\n")
+ax_true_map.set_title("Simulated map\n")
 
 ax_inf_map[0].set_title("Spherical harmonic model\n(Gaussian prior)")
 map.show(

### 2021-03-04 paper/figures/scripts/irtf_fit.py
Minor tweaks to model

@@ -60,6 +60,7 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
         occultor_is_jupiter=True,
         rotate=True,
         return_occ_lat=True,
+        method="",
     )
     (xo_eg, yo_eg, ro_eg, occ_lat_eg,) = get_occultor_position_and_radius(
         eph_io_eg,
@@ -67,6 +68,7 @@ def fit_model(ydeg_inf, lc_in, lc_eg):
         occultor_is_jupiter=True,
         rotate=True,
         return_occ_lat=True,
+        method="",
     )
 
     print("Ingress occultation latitude: ", occ_lat_in)
@@ -296,7 +298,7 @@ with open("../../../data/irtf_processed/lc_1998-11-29.pkl", "rb") as handle:
 
 samples = fit_model(20, lc_in, lc_eg)
 
-with open("irtf_1998_samples.pkl", "wb") as handle:
+with open("irtf_1998_samples_cubic.pkl", "wb") as handle:
     pkl.dump(samples, handle)
 
 # Fit the 2017 pair of light curves
@@ -308,5 +310,5 @@ with open("../../../data/irtf_processed/lc_2017-05-11.pkl", "rb") as handle:
 
 samples2 = fit_model(20, lc_in, lc_eg)
 
-with open("irtf_2017_samples.pkl", "wb") as handle:
+with open("irtf_2017_samples_cubic.pkl", "wb") as handle:
     pkl.dump(samples2, handle)

### 2021-03-05 paper/paper.tex
streamlined the abstract

@@
 Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
-Io has been observed during occultations by Jupiter and other Galilean moons using high-cadence near infrared photometry since the 1980s. 
-These observations encode a wealth of information about its surface.
-They are ideal for testing methods for inferring surface maps of occulted bodies from time series observations.
-    We built a generative model of Io's surface using the code \textsf{starry} \href{https://rodluger.github.io/starry/}{\color{linkcolor}\faGithub} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
-    Our probabilistic Bayesian model is able to recover known bright features on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of these features.
-    The methods we have developed are also easily applicable to the problem of mapping stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+Io has been observed during occultations of its surface by other Galilean moons and Jupiter since the 1980s, using high-cadence near infrared photometry. 
+These observations encode a wealth of information about the volcanic features on its surface.
+    We built a generative model of Io's surface emission using the code \textsf{starry} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
+    Our probabilistic Bayesian model is able to recover known hotspots on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of spots.
+    The methods we have developed are also directly applicable to the problem of mapping surfaces of stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
     \includegraphics[width=1.\linewidth]{figures/pixels_to_spherical_harmonics.pdf}
-    \oscaption{pixels_to_harmonics}{%
+    \oscaption{pixels_to_spherical_harmonics}{%
         Illustration of the transformation from a pixel map (left) defined on a fixed grid on the sphere into the spherical harmonic basis at $l=20$ (right) via a linear operator $\mathbf{P}^\dagger$.
@@
     \includegraphics[width=\linewidth]{figures/information_content.pdf}
-    \oscaption{InformationContent}{
+    \oscaption{information_content}{
         The posterior shrinkage for different kinds of observations of Io as a function of spherical harmonic degree (angular scale), averaged across all $m$ modes.
@@
     \includegraphics[width=1.\linewidth]{figures/ingress_egress_sim_snr_50.pdf}
-    \oscaption{ingress_egress_sim_snr_50}{%
+    \oscaption{simulated_ingress_egress}{%
         Inferred $l=20$ map obtained by fitting a pair of simulated ingress/egress occultation light curves of Io using a hybrid pixel model with a Regularized Horseshoe prior on the pixels.
@@
         \includegraphics[width=1.\linewidth]{figures/ingress_egress_sim_snr_10.pdf}
-    \oscaption{ingress_egress_sim_snr_10}{%
+    \oscaption{simulated_ingress_egress}{%
         Same as Fig.~\ref{fig:ingress_egress_sim_snr_50} except for light curves with SNR=10.
@@
     \includegraphics[width=\linewidth]{figures/irtf_1998_spots.pdf}
-    \oscaption{irtf_spots_plot}{%
+    \oscaption{irtf_spots_plots}{%
         Contour plot of the hot spots shown in Figure~\ref{fig:irtf_1998} overlaid on top of the U.S.
@@
     \includegraphics[width=1.\linewidth]{figures/irtf_2017.pdf}
-    \oscaption{irtf_2017}{%
+    \oscaption{irtf_main_plots}{%
 Inferred $l=20$ maps obtained by fitting a pair of observations of occultations of Io by Jupiter in 2017.
@@
     \includegraphics[width=\linewidth]{figures/irtf_2017_spots.pdf}
-    \oscaption{irtf_spots_plot}{%
+    \oscaption{irtf_spots_plots}{%
         Contour plot of the hot spots shown in Figure~\ref{fig:irtf_2017} overlaid on top of the U.S.
@@
 For example, a sensible prior for the surface of a fast rotating gaseous exoplanet might be requiring some degree of azimuthal symmetry for the inferred map.
-\newline
+
 \subsection{Future work}

### 2021-03-05 paper/paper.tex
quoteation marks

@@
     Our probabilistic Bayesian model is able to recover known hotspots on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of spots.
-    The methods we have developed are also directly applicable to the problem of mapping surfaces of stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+    The methods we have developed are also directly applicable to the problem of mapping the surfaces of stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 Besides providing a window into early volcanic activity in the Solar System, Io is also in many ways an analogue of a volcanically active exoplanet.
-Volcanic exoplanets, sometimes dubbed ``super-Ios" or ``lava worlds", have gathered a lot of interest in recent years.
+Volcanic exoplanets, sometimes dubbed ``super-Ios'' or ``lava worlds'', have gathered a lot of interest in recent years.
 Photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
@@
 Multiple occultations are then observable over a course of approximately one year.
-The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow (``in eclipse") while mutual occultations are almost always observed in sunlight.
+The majority of occultations by Jupiter are observed when Io is in Jupiter's shadow (``in eclipse'') while mutual occultations are almost always observed in sunlight.
 Only the brightest volcanoes are visible over the reflected light background when Io is illuminated by the Sun \citep{veeder1994,dekleer2016a}.
@@
 
-The model relies on the recently developed code \textsf{starry} \citep[][Luger et al.
+The model relies on the recently developed code \textsf{starry} \footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep[][Luger et al.
 2021 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface can represented in terms of spherical harmonics.
@@
 In this section we generalize the example from Section~\ref{ssec:pixels_vs_harmonics} such that the simulated map includes an additional faint hot spot located at $-15^\circ$ N latitude and $-40^\circ$ E longitude with a diameter of $5^\circ$.
-We set the amplitude of the ``faint" spot to 30\% of the luminosity of the featureless map.
+We set the amplitude of the ``faint'' spot to 30\% of the luminosity of the featureless map.
 As before we assume that we know the geometry of the occultation exactly.
@@
 We found that in cases where the simulated map consists of a bright and a faint spot the pixel model with an exponential prior such as the one we used in Section~\ref{ssec:pixels_vs_harmonics} does not recover the faint spot.
-Instead, we use a different heavy tailed prior called the Regularized Horseshoe prior\footnote{To be precise, we use the truncated version of the Regularized Horseshoe prior where the coefficients are required to be positive.} (also known as the ``Finnish Horseshoe") \citep{piironen2017}.
+Instead, we use a different heavy tailed prior called the Regularized Horseshoe prior\footnote{To be precise, we use the truncated version of the Regularized Horseshoe prior where the coefficients are required to be positive.} (also known as the ``Finnish Horseshoe'') \citep{piironen2017}.
 This prior is specifically designed for use in Bayesian sparse linear regression. 
@@
 The plot shows the error in the inferred latitude and longitude for each spot (white lines) and a contour map computed from the median posterior estimate of the map.
-The contour lines correspond to the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background" region around the spot.
+The contour lines correspond to the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
 
@@
         The left hotspot is centered around Loki Patera, the right hotspot is centered at the Kanehekili Fluctus lava flow.
-The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background" region around the spot.
+The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
         \label{fig:irtf_1998_spots}
@@
         The left hotspot is centered around Loki Patera, the right hotspot is centered at Janus Patera.
-The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background" region around the spot.
+The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
         \label{fig:irtf_2017_spots}

### 2021-03-05 paper/figures/smoothing_kernel.py
minor

@@ -76,7 +76,7 @@ for a in ax.flatten():
     a.yaxis.set_minor_locator(AutoMinorLocator())
 #     a.grid()
 
-ax[-1].legend(loc=1, prop={"size": 12})
+ax[-1].legend(loc=1, prop={"size": 11.2})
 fig.text(0.5, -0.08, "Longitude [deg]", ha="center")
 fig.text(0.04, 0.5, "Normalized intensity", va="center", rotation="vertical")
 

### 2021-03-05 paper/paper.tex
fixing issue with astropy units

@@
 Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
-Io has been observed during occultations of its surface by other Galilean moons and Jupiter since the 1980s, using high-cadence near infrared photometry. 
+Io has been observed during occultations by other Galilean moons and Jupiter since the 1980s, using high-cadence near infrared photometry. 
 These observations encode a wealth of information about the volcanic features on its surface.
-    We built a generative model of Io's surface emission using the code \textsf{starry} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
+    We built a generative model for the observed occultations using the code \textsf{starry} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
     Our probabilistic Bayesian model is able to recover known hotspots on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of spots.
@@
 Most importantly for this work,  starting with \cite{spencer1990} Io has been sporadically observed over a timespan of decades using high cadence near infrared photometry taken during occultations by Jupiter.
-Occultations by Jupiter occur twice every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called \emph{mutual occultations}) happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites.
+Occultations by Jupiter occur twice every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called ``mutual occultations'') happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites.
 Multiple occultations are then observable over a course of approximately one year.
@@
 
-The model relies on the recently developed code \textsf{starry} \footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep[][Luger et al.
+The model relies on the recently developed code \textsf{starry}\footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep[][Luger et al.
 2021 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface can represented in terms of spherical harmonics.

### 2021-03-05 volcano/utils.py

@@ -498,8 +498,10 @@ def get_occultor_position_and_radius(
         yo_unrot = yo.value
 
         # Rotate to coordinate system where the obliquity of Io is 0
-        theta_rot = -obl.to(u.rad)
-        xo_rot, yo_rot = rotate_vectors(xo_unrot, yo_unrot, theta_rot)
+        theta_rot = -obl.to(u.rad).value
+        xo_rot, yo_rot = rotate_vectors(
+            np.array(xo_unrot), np.array(yo_unrot), np.array(theta_rot)
+        )
 
         # Choose point inside Jupiter
         idx = np.argmin(np.abs(xo_rot))
@@ -514,8 +516,10 @@ def get_occultor_position_and_radius(
 
     # Rotate position vefctors such that obliquity of the occultor is 0
     if rotate:
-        theta_rot = -eph_occulted["obl"].to(u.rad)
-        xo, yo = rotate_vectors(xo.value, yo.value, theta_rot)
+        theta_rot = -eph_occulted["obl"].to(u.rad).value
+        xo, yo = rotate_vectors(
+            np.array(xo), np.array(yo), np.array(theta_rot)
+        )
     else:
         xo = xo
         yo = yo

### 2021-03-05 paper/gen_links.py
figure links

@@ -3,7 +3,11 @@ import subprocess
 import os
 
 # Generate the github links
-hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1]
+if os.getenv("CI", False):
+    hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1]
+else:
+    hash = "0a3c2c1146e90206a77908016b9c3c26b60eba64"
+
 slug = os.getenv("TRAVIS_REPO_SLUG", "fbartolic/volcano")
 with open("gitlinks.tex", "w") as f:
     print(

### 2021-06-03 paper/figures/irtf_dataset.py
Change data plot so that only the light curves used for inference are shown.

@@ -1,62 +1,56 @@
-import os
-import pickle as pkl
-
 import numpy as np
-from astropy.table import vstack
-from matplotlib import pyplot as plt
-from matplotlib.ticker import MaxNLocator
+import matplotlib.pyplot as plt
+from matplotlib.ticker import FormatStrFormatter, AutoMinorLocator
+import pickle as pkl
+import astropy.units as u
 
 np.random.seed(42)
 
-# Load all light curves
-directory = "../../data/irtf_processed/"
-lcs = []
-for file in os.listdir(directory):
-    with open(os.path.join(directory, file), "rb") as handle:
-        lcs.append(pkl.load(handle))
-lcs_stacked = vstack(lcs, metadata_conflicts="silent")
-lcs_stacked.sort()
+# The 1998 pair of light curves
+with open("../../data/irtf_processed/lc_1998-08-27.pkl", "rb") as handle:
+    lc1_in = pkl.load(handle)
 
-## Plot stacked light curves
-# fig, ax = plt.subplots(figsize=(6, 2))
-# ax.plot(lcs_stacked.time.decimalyear, lcs_stacked["flux"], "k.", alpha=0.1)
-# ax.set_ylabel("Flux [GW/um/sr]")
-# ax.set_xlabel("time [years]")
-# ax.set_xticks(np.arange(1996, 2024, 4))
-# ax.set_yticks(np.arange(0, 250, 50))
+with open("../../data/irtf_processed/lc_1998-11-29.pkl", "rb") as handle:
+    lc1_eg = pkl.load(handle)
 
-# Plot maximum flux for each light curve
-max_f = np.array([np.sort(lcs[i]["flux"].value)[-2] for i in range(len(lcs))])
-yr = np.array([lc.time.decimalyear[0] for lc in lcs])
-idx_sorted = np.argsort(yr)
 
-fig, ax = plt.subplots(figsize=(8, 4))
-ax.plot(yr[idx_sorted], max_f[idx_sorted], "ko", alpha=0.6)
-ax.set_ylabel("Peak flux [GW/um/sr]")
-ax.set_xlabel("Time [years]")
-ax.set_xticks(np.arange(1996, 2024, 4))
-ax.set_yticks(np.arange(0, 250, 50))
-ax.grid()
[…]

### 2021-06-03 paper/paper.tex
Rewrote data section so it fits in better with the rest of the paper

@@
 % !TeX root = ./paper.tex
-\documentclass[modern]{aastex62}
+\documentclass[linenumbers,modern]{aastex62}
 
@@
 In this work, we build a fully probabilistic model in order to infer a \emph{two-dimensional map} of Io's volcanic surface from archival IRTF observations of Io in the near infrared.
-We assume that the map corresponding to a given set of light curves is static (up to an overall amplitude), that is, that it didn't change substantially between the times of observations.
+We assume that the map corresponding to a given set of light curves is static (up to an overall amplitude), that is, we assume that it didn't change substantially between the times of observations.
 In Paper II in this series we will relax this assumption by constructing a model which can be used to infer a time-variable map of Io from an any number of light curves observed at arbitrary times.
@@
 \label{sec:data}
+The observations of Io we use in this work were first described in \cite{spencer1994} who began the observing campaign and were joined by others to collect the data we use here \citep{stansberry1997,rathbun2002,rathbun2006,rathbun2010,tate2020}.
+These data are currently being organized to be posted on the Planetary Data System (PDS) (Julie Rathbun, personal communication).  
+We used an early version of this data archive.
+The archive contains on the order of ~100 separate light curves of occultations of Io by Jupiter, observed at times when Io was in Jupiter's shadow (``in eclipse") so that the source of the observed flux is thermal emission.
+The geometry of the occultations is such that depending on the time of the year, Io is in eclipse during either the ingress or the egress of the occultation.
+This means that in any given year, the observations consist of only ingress (egress) observations during one fraction of the year and egress (ingress) observations during the other fraction. 
+In Paper II we plan to simultaneously fit a large fraction of the light curves in the complete archive with a generalized version of the model presented in this paper.
+
+Since we have restricted the scope of this work to fitting static maps of Io's thermal emission, we need light curves which are closely spaced in time so that Io's the surface emission doesn't drastically change between the observations.
+In addition, we need observations of both the ingress and the egress of an occultation  because Jupiter's limb sweeps across Io's projected disc at different angles at ingress and egress and this breaks the degeneracy in the position of a hotspot on the surface.
+Given these requirements, we chose a single pair of ingress/egress observations from 1998 observed 94 days apart and another pair of ingress/egress observations from 2017 observed 54 days apart.
+We fit one map for each of the two pairs of light curves.
+
+The 1998 occultations (Figure \ref{fig:irtf_1998_data}) have been observed with the NSFCam 1-5 $\mu m$ camera \citep{shure1994} while the 2017 occultations were observed with the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003}.
+Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress (egress) part of the entire occultation.
+The observing cadence for each light curve is about a second which sets a lower limit for the size of the inferred spatial features (~15km).
+The selected light curves have high signal to noise ratio and they encode information about the surface emission.
+One can clearly see step-like features which correspond to a volcanic hotspot coming in or out of view during the course of the occultation.
+As with all ground-based photometry, the observations are influenced by atmospheric variability which results in some correlated noise in the light curves which needs to be accounted for in the model.
 
@@
     \begin{centering}
-    \includegraphics[width=\linewidth]{figures/irtf_max_flux.pdf}
+    \includegraphics[width=\linewidth]{figures/irtf_1998_occultations.pdf}
     \oscaption{irtf_dataset}{%
-        Maximum flux for each IRTF light curve of Io observed during an occultation of Io by Jupiter.
-       \label{fig:irtf_max_flux}
-    }
-    \end{centering}
-\end{figure}
-
-The complete dataset consists of 112 sets of observations of Io in the near infrared taken from 1996 until 2018 using different instruments at NASA's IRTF observatory, the NSFCam  1-5 $\mu m$ camera \citep{shure1994}, the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003} and the iShell 1.1-5.3 $\mu m$  spectrographer/imager \citep{rayner2016}.
-Although the observations span decades, the timespan between observations varies and there were very few observations taken between 2008 and 2016.
-All of the observations were taken while Io was \emph{in eclipse}, meaning that it was in Jupiter's shadow so the source of observed emission from the surface is thermal radiation.
-On the other hand, for observations of Io \emph{in sunlight} the observed flux is a sum of thermal (volcanic) emission and reflected sunlight which depends on the albedo map in the near infrared.
-In figure~\ref{fig:irtf_max_flux} we plot the maximum flux for each occultation light curve in units of $\mathrm{GW}/\mu \mathrm{m}/\mathrm{sr}$ as a function of time.
-This value is approximately equal to the total flux emitted from the Jupiter-facing side of Io.
-The major variation in the baseline brightness is driven by Loki.
-Most hotspots on Io can be divided into those who are persistently active for a year or longer at moderate intensity, and those which have bursts of activity and reach very high intensities for short periods of time \citep{dekleer2016}.
-
-\begin{figure}[h!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/irtf_sample_lightcurves.pdf}
-    \oscaption{irtf_dataset}{%
-        A selection of sample light curves observed using NASA's IRTF telescope during occultations of Io by Jupiter in our dataset.
-        The step-like morphology of the light curves is due to bright volcanoes on Io's surface coming in or out of view during the course of an occultation.
-        These light curves visibly encode information about the features on the surface.
-        \label{fig:irtf_sample_lightcurves}
-    }
-    \end{centering}
-\end{figure}
-
-In Figure~\ref{fig:irtf_sample_lightcurves} we display a random subset of all the light curves
-in the dataset. 
-Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress (or egress) part of the entire occultation.
-The exposure cadence for each light curve is about a second, with some variation between light curves.
-It follows that over the course of a single exposure Jupiter's limb passes over about 15km on Io's surface which provides a lower bound for the size of the features that we can reliably estimate.
-The shapes of light curves strongly deviate from a smooth variation that one would expect to see if the surface thermal emission was uniformly distributed.
-Especially prominent are light curves with clear step-like features which are due to bright localized spots coming in and out of view during the course of an occultation.
-The fact that these features are so clearly visible means that even individual light curves encode a wealth of information about the spots.
-
-The photometric quality of the light curves varies from year to year because multiple instruments were used over the years. 
-As with all ground-based photometry, the observations are influenced by atmospheric variability which results in some correlated noise in the light curves, because of this the flux is not always monotonically increasing or decreasing as one would expect.
-Complicating matters, the light curves lack errorbars. 
-We deal with this by treating all errobars as free parameters with a common characteristic scale in the final model.
+       Occultations of Io by Jupiter observed 3 months apart in 1998 using NASA's IRTF telescope.
+        The light curve on the left is the ingress of the occultation (Io disappearing behind the limb of Jupiter) and the one on the right is the egress (Io appearing behind Jupiter).
+       Each visible step-like feature in the light curve (a rapid increase/decrease in total flux at particular times) is a  consequence of a volcanic hotspot coming in or out of view during the course of the occultation.
+        The two light curves contain a wealth of information about thermal emission from Io's surface. 
+       \label{fig:irtf_1998_data}
+    }
+    \end{centering}
+\end{figure}
 

### 2021-06-03 paper/figures/irtf_dataset.py
Flux -> intensity

@@ -42,7 +42,7 @@ ax[1].set(xticks=np.arange(0, 6, 1))
 ax[0].set_title(lc1_in.time.datetime[0].strftime("%Y-%m-%d %H:%M"))
 ax[1].set_title(lc1_eg.time.datetime[0].strftime("%Y-%m-%d %H:%M"))
 
-ax[0].set(ylabel="Flux [ GW/um/sr]")
+ax[0].set(ylabel="Spectral intensity [ GW/um/sr]")
 
 
 for a in ax:

### 2021-06-03 paper/figures/irtf_main_plots.py

@@ -411,7 +411,7 @@ def make_plots(
 
     # Set common labels
     fig.text(0.5, 0.04, "Duration [minutes]", ha="center", va="center")
-    ax_lc[0].set_ylabel("Flux [GW/sr/um]")
+    ax_lc[0].set_ylabel("Intensity [GW/sr/um]")
     ax_res[0].set_ylabel("Residuals")
 
     year = lc_in.time[0].isot[:4]

### 2021-06-03 paper/figures/pixels_vs_harmonics.py

@@ -441,7 +441,7 @@ for ax in (ax_lc[:2], ax_res[:2], ax_lc[2:], ax_res[2:]):
     ax[1].plot((-d, +d), (1 - d, 1 + d), **kwargs)
     ax[1].plot((-d, +d), (-d, +d), **kwargs)
 
-ax_lc[0].set_ylabel("Flux")
+ax_lc[0].set_ylabel("Intensity")
 
 fig.text(
     0.27, 0.07, "Occultor x position [Io radii]", ha="center", va="center"

### 2021-06-03 paper/figures/simulated_ingress_egress.py

@@ -514,7 +514,7 @@ def plot(
     fig.text(
         0.5, 0.06, "Occultor x position [Io radii]", ha="center", va="center"
     )
-    ax_lc[0].set_ylabel("Flux")
+    ax_lc[0].set_ylabel("Intensity")
     ax_res[0].set_ylabel("Residuals\n (norm.)")
 
     fig.savefig(fname, bbox_inches="tight", dpi=500)

### 2021-06-03 volcano/utils.py
Fixing insignificant mistake in the definition

@@ -160,7 +160,7 @@ def get_body_ephemeris(
     epochs = {"start": start, "stop": end, "step": step}
     obj = Horizons(id=body_id, epochs=epochs, id_type="id")
 
-    eph = obj.ephemerides(quantities="1,13,20", extra_precision=True)
+    eph = obj.ephemerides(extra_precision=True)
     times_jpl = Time(eph["datetime_jd"], format="jd")
 
     # Store all data in a TimeSeries object
@@ -466,7 +466,7 @@ def get_occultor_position_and_radius(
 
     xo = (
         -delta_ra
-        * np.cos(eph_occultor["DEC"].to(u.rad))
+        * np.cos(eph_occulted["DEC"].to(u.rad))
         / (0.5 * eph_occulted["ang_width"].to(u.arcsec))
     ).value
     yo = delta_dec / (0.5 * eph_occulted["ang_width"].to(u.arcsec)).value

### 2021-06-07 paper/paper.tex
A few more minor changes requested by the reviewer

@@
 The global heat flow on its surface is about 40 times larger than Earth's \citep{breuer2007,davies2010} and about 50\% of the heat flow emanates from only 1.2\% of Io's surface \citep{veeder2012}.
-This intense volcanic activity cannot be explained by radioactive decay, the mechanism which drives Earth's volcanism.
+This intense volcanic activity cannot be explained by radioactive decay, the mechanism which (in addition to residual heat from formation) drives Earth's volcanism.
 Instead, the volcanism on Io is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
 Contrary to Earth, Io lacks plate tectonics.
-The heat transport mechanism most likely operating on Io is volcanism generated in the lithosphere (the outermost shell of a terrestrial body).
-This process is also known as \emph{heat-pipe volcanism}, whereby magma is transported to the surface through localised vents \citep{oreilly1981}.
+The heat transport mechanism most likely operating on Io is \emph{heat-pipe volcanism}, a process in which magma is transported to the surface through localised vents from the litosphere  (the outermost shell of a terrestrial body) \citep{oreilly1981}.
 Heat-pipe volcanism likely occurred in the early history of terrestrial planets in the Solar System \citep{moore2013,moore2017}, most notably on early Earth prior to the onset of plate tectonics.
@@
 Most importantly for this work,  starting with \cite{spencer1990} Io has been sporadically observed over a timespan of decades using high cadence near infrared photometry taken during occultations by Jupiter.
-Occultations by Jupiter occur twice every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called ``mutual occultations'') happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites.
+Occultations by Jupiter occur once every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called ``mutual occultations'') happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites.
 Multiple occultations are then observable over a course of approximately one year.
@@
 By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki Patera (\emph{Patera} is a type of an irregular crater) region to a precision of about 2 kilometers.
-In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites \citep[][and references therein]{arlot1974,saquet2018,morgado2016a}.
+In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites \citep[][and references therein]{arlot1974,lainey2009,saquet2018,morgado2016a}.
 Understanding the detailed albedo distribution is crucial to constraining the ephemeris of Io to a very high precision.
@@
 
-The model relies on the recently developed code \textsf{starry}\footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep[][Luger et al.
-2021 in prep]{luger2019a} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface can represented in terms of spherical harmonics.
+The model relies on the recently developed code \textsf{starry}\footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep{luger2019a,luger2021b} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface can represented in terms of spherical harmonics.
 \textsf{starry} can compute phase curves and occultations in both emitted light (for modeling the isotropic thermal emission from Io's surface) and reflected light (for mapping albedo variations).
@@
 Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress (egress) part of the entire occultation.
-The observing cadence for each light curve is about a second which sets a lower limit for the size of the inferred spatial features (~15km).
+The observing cadence for each light curve is about a second which sets a lower limit for the size of the inferred spatial features ($\sim 15$km).
 The selected light curves have high signal to noise ratio and they encode information about the surface emission.
@@
 Because \textsf{starry} does not (yet) support occultations for non-spherical objects and because the effect is negligible at the resolution of our maps, we assume that Jupiter is locally spherical at the point of an occultation.
-We estimate an effective radius from the measurements of Jupiter's shape from Voyager radio occultation data \citep[Fig.~7]{lindal1981}.
+We estimate an effective radius from the measurements of Jupiter's shape from Pioneer and Voyager radio occultation data \citep[Fig.~7 of][]{lindal1981}.
 When computing the occultation latitude we fix Jupiter's latitude to the value at the center of Io's disc because 
@@
 In addition to uncertainties about the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
+The problems with Galileo's high gain antenna prevented it from obtaining more recent radio occultations of the neutral atmosphere and Juno's orbit has thus far avoided such occultations.  
+However, over the 2023-2025 period an extended Juno mission may be able to obtain radio occultations which will refine our understanding of Jupiter's size and shape \citep{hodges2020}.
+
 Since our main focus in this work is the map model, we leave a detailed investigation into the various sources of error that go into the radius estimate for future work.
@@
 The total number of spherical harmonic coefficients is $(l+1)^2$.
-In addition to computing thermal phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations in which the occulted object is illuminated by a distant light source \citep[Luger et al.
-2021 in prep][]{}.
+In addition to computing thermal phase curves and occultation light curves, \textsf{starry} also solves the considerably more complex problem of computing reflected light phase curves and occultations in which the occulted object is illuminated by a distant light source \citep{luger2021b}.
 In that case the coefficient vector $\mathbf{y}$ represents spherical albedo.
@@
 Conditioned on fixed parameters specifying the geometry of the occultations, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
-\cite{luger2019} achieved this by representing all rotations, changes of basis transformations and integrals with complicated boundaries which are needed to compute the flux as linear transformations.
+\cite{luger2019a} achieved this by representing all rotations, changes of basis transformations and integrals with complicated boundaries which are needed to compute the flux as linear transformations.
 Since a sequence of linear mappings is also linear, the predicted flux can be written as
@@
 where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
-in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed to compute the integrated flux at different viewing angles of the occulted sphere.
-If the geometry isn't known precisely the matrix $\mathbf{A}$ is not fixed and the model is in principle no longer linear although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
+in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed for computing the integrated flux at different viewing angles of the occulted sphere (including the cosine emission law).
+If the geometry isn't known precisely $\mathbf{A}$ is not fixed and the model is in principle no longer linear, although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
 
@@
 
-There are two ways of enforcing positivity that we are aware of, both of which involve evaluating the intensity on a fixed grid of \emph{pixels} and disallowing negative values of those pixels.
+There are two ways of enforcing positivity that we are aware of, both of which involve evaluating the map intensity on a fixed grid of \emph{pixels} (intensity evaluated at fixed set of points on the sphere) and disallowing negative values of those pixels because they are unphysical.
 The first is to fit for the spherical harmonic coefficients $\mathbf{y}$, evaluate the pixel grid at each MCMC step and reject all samples of the coefficient vector $\mathbf{y}$ which result in pixels with negative intensity.
 The issue with this procedure is that rejecting samples in this way implies a prior probability distribution on $\mathbf{y}$ which cannot be mapped to a parameter space with infinite support and Hamiltonian Monte Carlo does not work well with constrained parameter spaces.
-The second approach is to dispense with the spherical harmonics entirely and compute the full model using a high resolution grid of pixels.
-In practice this is very difficult to do because we would need a very high resolution grid to compute the light curves accurately with minimal discretization noise.  
+The second approach is to dispense with the spherical harmonics entirely and compute the full model using a pixelated intensity map.
+This is very difficult to do in practice because we would need a very high resolution grid to compute the light curves accurately with minimal discretization noise.  
 \textsf{starry} uses spherical harmonics as a basis precisely to avoid this problem.
-\textbf{Instead, we opt for a hybrid approach in which we fit for pixels but at each MCMC step we convert the pixels to spherical harmonic coefficients to compute the light curve.}
-
-To implement the hybrid approach we need to be able to switch between spherical harmonics and pixels.
-Transforming spherical harmonics $\mathbf{y}$ to pixels $\mathbf{p}$ is straightforward because there exists a linear operator $\mathbf{P}$ which maps $\mathbf{y}$ to $\mathbf{p}$:
+\textbf{Instead, we opt for a hybrid approach in which we fit for a vector of pixel intensities but at each MCMC step we convert the pixels to spherical harmonic coefficients to compute the light curve.}
+
+To implement the hybrid approach we need to be able to switch back and forth between spherical harmonics and pixels.
+Given pixels $\mathbf{p}$ evaluated on an equal are Mollweide grid, the transformation from spherical harmonics $\mathbf{y}$ to $\mathbf{p}$ is given by a linear operator $\mathbf{P}$:
 \begin{equation}
@@
 Each row of $\mathbf{P}$ contains values of each of the spherical harmonic coefficients at a given point on the grid. 
-To construct the grid we use an equal area Molleweide projection in order to have a uniform distribution of pixels across the sphere.
 The grid needs to be fine enough to ensure that the intensity is positive over most of the sphere.
@@
 When using pixels to impose a positivity constraint on the spherical harmonic map we need to make sure that the number of pixels is greater than the number of spherical harmonic coefficients by a factor of a few to ensure positivity approximately everywhere on the sphere.
-In practice we find that we need to use at least 4 times as many pixels as spherical harmonics which means that the computational cost of this model is higher than if we just fit for spherical harmonics.
-
-To summarize, in our hybrid model we first construct a fixed high resolution pixel grid in latitude and longitude, then use Equation~(\ref{eq:pixels_to_ylms}) to convert pixels to spherical harmonics and finally use Equation~(\ref{eq:linear_model}) to evaluate the model.
+In practice we find that we need to use at least 4 times as many pixels as spherical harmonics which means that the computational cost of this model is higher than if we just fit for spherical harmonic coefficients.
+
+To summarize, in our hybrid model we first construct a fixed high resolution pixel grid in latitude and longitude, then use Equation~(\ref{eq:pixels_to_ylms}) to convert a vector of pixel intensities to spherical harmonic coefficients and finally use Equation~(\ref{eq:linear_model}) to evaluate the model.
 Although we fit for the pixels $\mathbf{p}$ we store the spherical harmonic coefficient vectors $\mathbf{y}$ as the final product of the inference. 
@@
 An ideal set of observations would consist of phase curves together with observations of multiple occultations by a small occultor at different latitudes and different phases.
-Phase curves and occultations in reflected light are even more informative because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep[][Luger et al.
-2021 in prep]{luger2019a}.
+Phase curves and occultations in reflected light are even more informative because of the nonuniform illumination profile of the incident radiation and the presence of a day/night terminator line \citep{luger2021b}.
 In some cases for reflected light observations (phase curves of an inclined planet for example) there can even be no nullspace \emph{at all} low spherical harmonic degrees.
@@
         The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
-        The maps show two hotspots, the bright one is emission from Loki and the faint one is most likely emission from Kanehekili.
+        The maps show two hotspots, the bright one is emission from Loki Patera and the faint one is most likely emission from Kanehekili.
         A detailed view of the two hot spots is shown in Figure~\ref{fig:irtf_1998_spots}.
@@
 The faint hot spot is at $-15.756_{-11.382}^{+3.812}\quad ^\circ$ N latitude and $321.568_{-4.208}^{2.803}\quad^\circ$ E longitude which is the Kanehekili Fluctus lava flow.
-The error on the inferred position of peak intensity of the Loki hotspot is only a fraction of a degree which is much smaller than the minimum resolution of the map features set by the degree of the map; this corresponds to an uncertainty of less than a kilometer on the surface of Io.
+The error on the inferred position of peak intensity of the Loki Patera hotspot is only a fraction of a degree which is much smaller than the minimum resolution of the map features set by the degree of the map; this corresponds to an uncertainty of less than a kilometer on the surface of Io.
 Thus, \textbf{despite the fact that at $l=20$ the resolution of maps is limited to about $9^\circ$, we can constrain the centroid of the spots much more precisely}.
@@
 The main difference in the inferred map compared to Figure~\ref{fig:irtf_1998} is that there are two extra spots visible in the map.
-The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve, which is due to  Loki coming out and into view during the occultation.
+The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve, which is due to  Loki Patera coming out and into view during the occultation.
 The model inflates the errobars around those times because it unable to make the spot small enough.
-This results in the single hot spot at the location of Loki shown in Figure~\ref{fig:irtf_1998} morphing into two spots.
+This results in the single hot spot at the location of Loki Patera shown in Figure~\ref{fig:irtf_1998} morphing into two spots.
 While this feature is almost certainly spurious, the other spot in the northwestern hemisphere appears more likely to be real.
@@
 A contour plots of the two spots overlaid on top of a surface map of Io from Galileo observations is shown in Figure~\ref{fig:irtf_2017_spots} and the derived spot parameters are listed in Table~\ref{tab:irtf_2017_derived}.
-The inferred map shows two spots, one of which is Loki. 
-Figure~\ref{fig:irtf_2017_spots} shows that the peak emission from Loki is again constrained very precisely but the location of the peak appears to have shifted southward since 1998.
+The inferred map shows two spots, one of which is Loki Patera. 
+Figure~\ref{fig:irtf_2017_spots} shows that the peak emission from Loki Patera is again constrained very precisely but the location of the peak appears to have shifted southward since 1998.
 The location of the other hotspot corresponds to Janus Patera.
@@
         The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
-        The maps show two hotspots, the bright one is emission from Loki and the faint one is emission from Janus.
+        The maps show two hotspots, the bright one is emission from Loki Patera and the faint one is emission from Janus.
         A detailed view of the two hot spots is shown in Figure~\ref{fig:irtf_2017_spots}.
@@
 In addition to the pair of observations from 1998, we test the model on another pair of observations from 2017.
-We again find two hotspots, one of which is Loki (although the peak of the intensity shifted relative to the 1998 map) and the other is Janus Patera.
+We again find two hotspots, one of which is Loki Patera (although the peak of the intensity shifted relative to the 1998 map) and the other is Janus Patera.
 
@@
 Since all these operations are contained in the design matrix $\mathbf{A}$ (assuming that the ephemeris is fixed) we would only need to do the expensive computation once for each occultation.
-To be able to constrain the size of the Loki hotspot for example, we would need to fit maps on the order of $l\approx 50$.
-However, the kind of detailed mapping of Loki's magma lake with a precision of a few kilometers done by \cite{dekleer2017} will not be possible with a spherical harmonic model because it would require maps of extremely large degrees ($l\gtrapprox 700$).
+To be able to constrain the size of the Loki Patera hotspot for example, we would need to fit maps on the order of $l\approx 50$.
+However, the kind of detailed mapping of Loki Patera magma lake with a precision of a few kilometers done by \cite{dekleer2017} will not be possible with a spherical harmonic model because it would require maps of extremely large degrees ($l\gtrapprox 700$).
 

### 2021-06-12 paper/paper.tex
Some changes to figure captions. Round up mcmc estimates of spot positions.

@@
 The shape profile also depends on the wind velocity structure and temperature which we do not take into account.
-In addition to uncertainties about the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
+In addition to uncertainties on the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
 The problems with Galileo's high gain antenna prevented it from obtaining more recent radio occultations of the neutral atmosphere and Juno's orbit has thus far avoided such occultations.  
@@
 where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
-in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed for computing the integrated flux at different viewing angles of the occulted sphere (including the cosine emission law).
+in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed for computing the integrated flux at different viewing angles of the occulted sphere (relative positions and radii of the occultor and the occulted object, rotations, basis transformations, integrals over the visible disc of the occulted object and the cosine emission law).
 If the geometry isn't known precisely $\mathbf{A}$ is not fixed and the model is in principle no longer linear, although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
@@
 
-In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ with \textsf{starry} for different kinds of observations of Io in the period starting on the 1st of January 2009 and ending on the 1st of May 2010.
+In order to compute the posterior shrinkage we first compute the design matrices $\mathbf{A}$ using \textsf{starry} for different kinds of observations of Io for the period starting on the 1st of January 2009 and ending on the 1st of May 2010.
 We chose this period because it covers the full season of mutual occultations which occur every 6 years.
@@
 Shrinkage for phase curves at odd degrees above $l=2$ is exactly zero because these coefficents are in the nullspace for objects rotating about an axis perpendicular to the line of sight and therefore cannot be constrained using only phase curves \citep{luger2021}.
-Although observations of mutual occultations most easily break the degeneracies, the drawback of these types of observations is that they only happen every 6 years and they almost never happen while Io is in eclipse, meaning that only the brightest volcanoes are visible above the reflected sunlight.
+Although observations of mutual occultations most easily break the degeneracies because of the varying impact parameters and differents sizes of occultors, the drawback of these types of observations is that they only happen every 6 years and they almost never happen while Io is in eclipse which means that only the brightest volcanoes are visible above the reflected sunlight.
 This fact is not captured in Figure~\ref{fig:information_content}.
@@
 We set the phase of the simulated map to be $10^\circ$ E at the beginning of ingress and $10^\circ$ W at the end of egress.
-We assume that the geometry of the occultation is known exactly and we set the errorbars such that SNR=50 where the signal is defined to be the maximum value of the computed flux.
+We assume that the geometry of the occultation is known exactly and we set the errorbars such that SNR = 50 where the signal is defined to be the maximum value of the computed flux.
     We use this dataset to test the difference between setting a prior in the spherical harmonic basis $\mathbf{y}$ and in the pixel basis $\mathbf{p}$ by fitting an $l=20$ map to the dataset.
@@
         The left column corresponds to a model in which we place a Gaussian prior on spherical harmonic coefficients $\mathbf{y}$ and fit for $\mathbf{y}$ while the right column correspond to a hybrid model in which we fit for pixels $\mathbf{p}$ (with an exponential prior on pixel intensity) but we use $\mathbf{y}$ to compute the flux analytically with \textsf{starry}.
-        The benefit of using pixels is that it is much easier to encode assumptions on what the map should look like in pixel space rather than spherical harmonic space.
-        With the pixel model we are able to recover the simulated map precisely while the spherical harmonic model fails to do that. 
+        The benefit of using pixels is that it is much easier to encode assumptions on what the map should look like in pixel space rather than spherical harmonic space, this results in a visibly more accurate inferred map.
+        The residuals for the pixel model show undesirable patterns due to ringing artefacts which are a consequence of the Exponential prior favoring more localized features, we discuss how to alleviate this issue in the text.
                \label{fig:pixels_vs_harmonics}
@@
 To compute it we also need to specify the data covariance matrix defined in Equation~(\ref{eq:data_covariance_element}).
-Each element of the covariance matrix consists of a white noise component (errobars) and a correlated noise component (Gaussian Process).
-Since the IRTF light curves are not provided with estimated errobars, we choose to fit for all errobars simultaneously using a hierarchical approach in which we assign a global scale $l$ for all errorbars in a given light curve and we draw each individual errobar from a Half Normal distribution with standard deviation equal to that scale.
+Each element of the covariance matrix consists of a white noise component (errorbars) and a correlated noise component (Gaussian Process).
+Since the IRTF light curves are not provided with estimated errorbars, we choose to fit for all errorbars simultaneously using a hierarchical approach in which we assign a global scale $l$ for all errorbars in a given light curve and we draw each individual errobar from a Half Normal distribution with standard deviation equal to that scale.
 That is, we have 
@@
 \end{align}
-where $\sigma_{i,I}$ are the errobars for the ingress light curve and $\sigma_{i,E}$ are the errobars for the egress light curve.
+where $\sigma_{i,I}$ are the errorbars for the ingress light curve and $\sigma_{i,E}$ are the errorbars for the egress light curve.
 The symbol $\mathcal{N}^+$ denotes a truncated Gaussian distribution restricted to positive values.
-Treating errobars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data and our model is regularized.
-The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errobars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Mat\'ern 3/2 kernel.
+Treating errorbars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data and our model is regularized.
+The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errorbars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Mat\'ern 3/2 kernel.
 All model parameters and their associated priors are listed in Table~\ref{tab:priors}.
@@
             %
-            $\sigma_{i,I}$, $\sigma_{i,E},\quad i=1,\dots,N$& individual errobars&
+            $\sigma_{i,I}$, $\sigma_{i,E},\quad i=1,\dots,N$& individual errorbars&
             $\mathcal{N}^+(0,l_I),\quad \mathcal{N}^+(0,l_E)$
@@
 Each data point is shown with the median prediction of its errorbar.
-The posterior distribution for the errobars is shown in Figure~\ref{fig:irtf_1998_errorbars}.
-Both the global scale for of the errobars and the individual errobars are well constrained by the data. 
+The posterior distribution for the errorbars is shown in Figure~\ref{fig:irtf_1998_errorbars}.
+Both the global scale for of the errorbars and the individual errorbars are well constrained by the data. 
 The outlier points are naturally accounted for in our model because those points end up having higher variance.
@@
 Our model includes a Gaussian Process which accounts for both the correlated noise due to seeing in the data, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
-We also fit for all errobars simultaneously using a hierarchical model and we plot the median estimates of those errobars.
+We also fit for all errorbars simultaneously using a hierarchical model and we plot the median estimates of those errorbars.
         The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
@@
 
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/irtf_1998_errobars.pdf}
-    \oscaption{irtf_main_plots}{%
-        Posterior distribution for the errobars of the 1998 pair of light curves shown in Figure~\ref{fig:irtf_1998}. 
-        Each color corresponds to a single data point in the light curve.
-        The errobars are estimated using a hierarchical model in which we assume  that each errobar is drawn from a Half Gaussian distribution with a global scale parameter common to all errobars in a single light curve.
-       \label{fig:irtf_1998_errorbars}
-    }
-    \end{centering}
-\end{figure}
-
+%\begin{figure}[t!]
+%    \begin{centering}
+%    \includegraphics[width=\linewidth]{figures/irtf_1998_errorbars.pdf}
+%    \oscaption{irtf_main_plots}{%
+%        Posterior distribution for the errorbars of the 1998 pair of light curves shown in Figure~\ref{fig:irtf_1998}. 
+%        Each color corresponds to a single data point in the light curve.
+%        The errorbars are estimated using a hierarchical model in which we assume  that each errobar is drawn from a Half Gaussian distribution with a global scale parameter common to all errorbars in a single light curve.
+%       \label{fig:irtf_1998_errorbars}
+%    }
+%    \end{centering}
+%\end{figure}
+%
 \renewcommand*{\arraystretch}{1.4}
@@
             \endfoot
-            Spot 1 latitude  & $16.295^{+0.009}_{-0.010}$& degrees 
-            \\
-             Spot 1 (East) longitude & $53.105^{+0.011}_{-0.011}$& degrees 
-            \\
-                Spot 1 power  ingress & $52.394^{+0.898}_{-0.773}$ & GW/um 
-            \\
-                Spot 1 power  egress & $60.422_{-1.151}^{+1.194}$ & GW/um 
-                \\
-            Spot 2 latitude  & $-16.129_{-7.929}^{+4.268}$& degrees 
-            \\
-             Spot 2 (East) longitude & $-37.422_{-0.264}^{+0.778}$ & degrees 
-            \\
-                Spot 2 power  ingress & $5.156_{-0.634}^{+0.818}$ & GW/um 
-                \\
-                Spot 2 power  egress & $5.949_{-0.721}^{+0.957}$ & GW/um 
+            Spot 1 latitude  & $16.30^{+0.01}_{-0.01}$& degrees 
+            \\
+             Spot 1 (West) longitude & $306.90^{+0.01}_{-0.01}$& degrees 
+            \\
+                Spot 1 power  ingress & $52^{+1}_{-1}$ & GW/um 
+            \\
+                Spot 1 power  egress & $60_{-1}^{+1}$ & GW/um 
+                \\
+            Spot 2 latitude  & $-16_{-4}^{+8}$& degrees 
+            \\
+             Spot 2 (West) longitude & $37.4_{-0.2}^{+0.8}$ & degrees 
+            \\
+                Spot 2 power  ingress & $5.4_{-0.7}^{+0.6}$ & GW/um 
+                \\
+                Spot 2 power  egress & $6.2_{-0.8}^{+0.7}$ & GW/um 
             \\
@@
 The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
+        The asymmetric white cross in the center of the contours in each panel shows the uncertainty in the inferred position of the peak intensity of the hotspot.
+        This uncertainty is so small for the spot on the left that the cross is barely visible.
+        It is much larger for the spot on the right where the uncertainty in longitude is $\sim 2$ degrees and the uncertainty in the latitude of the spot is $\sim 15$ degrees.
         \label{fig:irtf_1998_spots}
@@
 The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve, which is due to  Loki Patera coming out and into view during the occultation.
-The model inflates the errobars around those times because it unable to make the spot small enough.
+The model inflates the errorbars around those times because it unable to make the spot small enough.
 This results in the single hot spot at the location of Loki Patera shown in Figure~\ref{fig:irtf_1998} morphing into two spots.
@@
 The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
+        The asymmetric white cross in the center of the contours in each panel shows the uncertainty in the inferred position of the peak intensity of the hotspot (barely visible in the left panel).
         \label{fig:irtf_2017_spots}
@@
             \endfoot
-                            Spot 1 latitude  & $12.193^{+0.011}_{-0.008}$ & degrees 
-            \\
-             Spot 1 (East) longitude & $52.515_{-0.009}^{+0.008}$ & degrees 
-            \\
-                Spot 1 power  ingress & $74.059_{-0.689}^{+0.911}$ & GW/um 
-            \\
-                Spot 1 power  egress & $106.158_{-1.412}^{+1.440}$ & GW/um 
-                \\
-            Spot 2 latitude  & $-4.114_{-8.327}^{+4.029}$ & degrees 
-            \\
-             Spot 2 (East) longitude & $-41.055_{-8.588}^{+0.433}$ & degrees 
-            \\
-                Spot 2 power  ingress & $5.171_{-1.007}^{+1.543}$ & GW/um 
-                \\
-                Spot 2 power  egress & $7.431_{-1.403}^{+2.227}$ & GW/um 
+                            Spot 1 latitude  & $12.19^{+0.01}_{-0.01}$ & degrees 
+            \\
+             Spot 1 (West) longitude & $307.49_{-0.01}^{+0.01}$ & degrees 
+            \\
+                Spot 1 power  ingress & $73.4_{-0.8}^{+0.8}$ & GW/um 
+            \\
+                Spot 1 power  egress & $105_{-1}^{+1}$ & GW/um 
+                \\
+            Spot 2 latitude  & $-4_{-4}^{+5}$ & degrees 
+            \\
+             Spot 2 (West) longitude & $41_{-4}^{+1}$ & degrees 
+            \\
+                Spot 2 power  ingress & $6_{-2}^{+1}$ & GW/um 
+                \\
+                Spot 2 power  egress & $8_{-2}^{+1}$ & GW/um 
             \\
@@
 \end{equation}
-where $p_0$ is our prior guess for the number of significant pixels that are sufficiently far above zero, $D$ is the total number of pixels, $n$ is the number of data points and $\sigma$ is the standard deviation of the data points (the errobars).
+where $p_0$ is our prior guess for the number of significant pixels that are sufficiently far above zero, $D$ is the total number of pixels, $n$ is the number of data points and $\sigma$ is the standard deviation of the data points (the errorbars).
 Thus, we only need to specify $p_0$, the degree of freedom parameter $\nu$ and the slab width $c$.

### 2021-06-13 paper/paper.tex
Improved sentence structure in the abstract

@@
 \begin{abstract}
-Jupiter's moon Io is the most volcanically active body in the Solar System with hundreds of active volcanoes varying in intensity on different timescales.
-Io has been observed during occultations by other Galilean moons and Jupiter since the 1980s, using high-cadence near infrared photometry. 
+With hundreds of active volcanoes varying in intensity on different timescales, Jupiter's moon Io is the most volcanically active body in the Solar System.
+Io has been observed from Earth using high-cadence near infrared photometry during occultations by Jupiter  and other Galilean moons since the 1980s.
 These observations encode a wealth of information about the volcanic features on its surface.
-    We built a generative model for the observed occultations using the code \textsf{starry} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
-    Our probabilistic Bayesian model is able to recover known hotspots on the surface of Io using only two light curves and without any assumptions on the locations, shapes or the number of spots.
-    The methods we have developed are also directly applicable to the problem of mapping the surfaces of stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
+    We built a generative model for the observed occultation light curves using the code \textsf{starry} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
+    Using this model we are able to recover surface emission maps of Io containing known volcanic hotspots, without having to make assumptions about the locations, shapes or the number of these hotspots.
+    Our model is also directly applicable to the problem of mapping the surfaces of stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 \end{equation}
-where $\tau=|t_n-t_m|$ and $\epsilon$ controls the quality of the approximation.
+where $\tau=|t_n-t_m|$.
 A single element of the data covariance matrix $\boldsymbol{\Sigma}$ is then 
@@
 \end{equation}
-where $p_i$ are the pixels.
+where $p_i$ are the pixels and $\mathrm{Half}-\mathcal{C}$ is the Half Cauchy distribution.
 Each local scale parameter is drawn from a unit scale heavy tailed Half Cauchy distribution which allows for very large values of the pixels.
@@
     &\lambda_{i} =\frac{c \overline{\lambda}_{i}}{\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{i}^{2}}} \\
-    &p_{i}  \sim \mathcal{N}^+\left(0, \tau \lambda_{i}\right) 
+    &p_{i}  \sim \mathrm{Half}-\mathcal{N}\left(\tau \lambda_{i}\right) 
 \end{aligned}
+\quad,
     \label{eq:reg_horseshoe}
 \end{equation}
+where $\mathrm{Inv}-\mathcal{G}$ is the Inverse Gamma distribution and  $\mathrm{Half}-\mathcal{N}$ is the Half Normal distribution.
 Integrating out the slab scale $c$ implies a marginal $\mathrm{Student}-\mathit{t}\,(\nu,0,s)$ prior for pixels far from zero.
@@
     &\overline{\lambda}_{i}  \sim \mathrm{Half}-\mathcal{C}(0,1) \\
-    &\overline{p}_{i}  \sim \mathcal{N}^+\left(0, 1\right)\\
+    &\overline{p}_{i}  \sim \mathrm{Half}-\mathcal{N}\left(1\right)\\
     &\tau=\tau_0\overline{\tau}\\

### 2021-06-13 paper/figures/irtf_main_plots.py
Add missing ticks

@@ -237,8 +237,9 @@ def make_plots(
         colorbar=True,
         cmap=cmap,
     )
-    ax_map_in.set_title(f"Ingress map\n {lc_in.time[0].isot[:19]}")
-    ax_map_eg.set_title(f"Egress map\n {lc_eg.time[0].isot[:19]}")
+    
+    ax_map_in.set_title("Ingress map\n", {lc_in.time[0].datetime.strftime("%Y-%m-%d %H:%M")})
+    ax_map_eg.set_title("Egress map\n", {lc_eg.time[0].datetime.strftime("%Y-%m-%d %H:%M")})
 
     # Plot minimaps
     xo_im_in = np.linspace(xo_in[0], xo_in[-1], nim)
@@ -525,7 +526,7 @@ yticks = np.arange(0, 100, 20)
 ylim = (-2, 82)
 xticks_in = np.arange(0, 5, 1)
 xticks_eg = np.arange(0, 6, 1)
-res_yticks = np.arange(-5, 5, 2.5)
+res_yticks = np.arange(-5, 7.5, 2.5)
 res_ylim = (-5.5, 5.5)
 
 # Model including a GP

### 2021-06-18 paper/paper.tex
Additional small additions/changes in response to reviewer comments.

@@
 \section{Introduction}
-The surface of Io is covered with hundreds of volcanoes which appear as bright spots in the near infrared, their intensities varying on timescales ranging from days to decades.
+The surface of Io is covered with hundreds of volcanoes which appear as bright spots in the near infrared, their intensities vary on timescales ranging from days to decades.
 The global heat flow on its surface is about 40 times larger than Earth's \citep{breuer2007,davies2010} and about 50\% of the heat flow emanates from only 1.2\% of Io's surface \citep{veeder2012}.
-This intense volcanic activity cannot be explained by radioactive decay, the mechanism which (in addition to residual heat from formation) drives Earth's volcanism.
+This intense volcanic activity cannot be explained by radioactive decay and residual heat from formation, the mechanisms which  drive volcanism on Earth.
 Instead, the volcanism on Io is driven by tidal interactions with Jupiter and sustained by the Laplace resonance with Europa and Ganymede \citep{peale1979}.
@@
 Photometric and spectral signatures of volcanic activity on such worlds will likely be detectable in the near future with telescopes such as JWST and LUVOIR \citep{kaltenegger2010,henning2018,oza2019,chao2020}.
-Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to (among other things) lava flows on the surface \citep{demory2016,demory2016d,hammond2017a}; several planets in the TRAPPIST-1 system in a Laplace-like resonance likely exhibiting volcanic activity \citep{kislyakova2017,dobos2019}, and many others.
+Existing exoplanet detections of planets with potential volcanic activity include CoRoT-7b \citep{barnes2010}, the first rocky exoplanet discovered and one which is likely heated by strong tidal forces; 55 Cancri e, whose inferred longitudinal offset in peak surface emission has been attributed to (among other things) lava flows on the surface \citep{demory2016,demory2016d,hammond2017a}; several planets in the TRAPPIST-1 system which are in a Laplace-like resonance and are likely exhibiting volcanic activity \citep{kislyakova2017,dobos2019}, and there are many others.
 Not all such exoplanets are expected to have Io-like volcanism.
-Some will have magma oceans because of their proximity to the star and others will have volcanism powered by nuclear decay, similar to volcanism on present day Earth.
-
-Io has been observed extensively using both space and ground observatories.
+Some will have magma oceans because of their proximity to the star and others will have volcanism powered by nuclear decay and residual heat, similar to volcanism on present day Earth.
+
+Io has been extensively observed using both space and ground observatories.
 High resolution images of Io's surface were taken by space missions such as Voyager \citep{smith1979}, Galileo \citep{belton1996} and Juno \citep{mura2020}.
@@
 Most importantly for this work,  starting with \cite{spencer1990} Io has been sporadically observed over a timespan of decades using high cadence near infrared photometry taken during occultations by Jupiter.
-Occultations by Jupiter occur once every orbit of ~1.7 days whereas occultations by Europa, Ganymede or Callisto (so-called ``mutual occultations'') happen every ~6 years when Earth passes through the orbital plane of the Galilean satellites.
+Occultations by Jupiter occur once every orbit of $\sim 1.7$ days whereas occultations by Europa, Ganymede or Callisto (so-called ``mutual occultations'') happen every $\sim 6$ years when Earth passes through the orbital plane of the Galilean satellites.
 Multiple occultations are then observable over a course of approximately one year.
@@
 \cite{spencer1994} observed several occultations of Io by Europa and detected a major brightening of the most powerful of Io's volcanoes, Loki, relative to previous Voyager observations.
-\cite{rathbun2002},\citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's 
+\cite{rathbun2002}, \citet{rathbun2006} and \citet{rathbun2010} used observations from NASA's 
 Infrared Telescope Facility (IRTF) telescope to study the long term variability of different volcanic spots, finding evidence of periodicity in Loki's eruptions and establishing the transient nature of observed emission from most volcanoes.
 By studying a (spatially resolved) occultation of Io by Europa, \cite{dekleer2017} mapped the Loki Patera (\emph{Patera} is a type of an irregular crater) region to a precision of about 2 kilometers.
-In addition to observations of occultations in the near infrared, several groups have been observing mutual occultations in the optical for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites \citep[][and references therein]{arlot1974,lainey2009,saquet2018,morgado2016a}.
-Understanding the detailed albedo distribution is crucial to constraining the ephemeris of Io to a very high precision.
+In addition to observing occultations in the near infrared, several groups have been observing mutual occultations in the optical for decades with the purpose of inferring the optical albedo of Io and improving ephemeris precision for Galilean satellites \citep[][and references therein]{arlot1974,lainey2009,saquet2018,morgado2016a}.
+Understanding the detailed albedo distribution on Io's surface is crucial to constraining the ephemeris of Io to a very high precision.
 
 Most studies of (unresolved) occultations of Io fit multiple light curves independently with the goal of inferring one-dimensional longitudinal variations in brightness on its surface (notable exceptions are \cite{spencer1994} and \cite{dekleer2017}), assuming relatively strong priors on the locations of individual volcanoes.
-In this work, we build a fully probabilistic model in order to infer a \emph{two-dimensional map} of Io's volcanic surface from archival IRTF observations of Io in the near infrared.
-We assume that the map corresponding to a given set of light curves is static (up to an overall amplitude), that is, we assume that it didn't change substantially between the times of observations.
+In this work, we build a fully probabilistic model in order to infer a \emph{two-dimensional map} of Io's surface thermal emission using archival IRTF observations of Io in the near infrared.
+We assume that the map we fit to a given set of light curves is static (up to an overall amplitude), an assumption which is justified if the spatial structure and intensity of hotspots doesn't change substantially  between the times of observations.
 In Paper II in this series we will relax this assumption by constructing a model which can be used to infer a time-variable map of Io from an any number of light curves observed at arbitrary times.
 
-The model relies on the recently developed code \textsf{starry}\footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep{luger2019a,luger2021b} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface can represented in terms of spherical harmonics.
+The model relies on the recently developed code \textsf{starry}\footnote{\url{https://starry.readthedocs.io/en/latest/}} \citep{luger2019a,luger2021b} which enables fast analytic computation of occultation light curves and phase curves for objects whose surface features can represented in terms of spherical harmonics.
 \textsf{starry} can compute phase curves and occultations in both emitted light (for modeling the isotropic thermal emission from Io's surface) and reflected light (for mapping albedo variations).
@@
 Our main goal in this paper is to develop a general model for mapping surfaces of occulted bodies with sparse, high contrast features and apply it to observations of Io.
-Because of high resolution resolved imaging of Io, we can compare features in our inferred maps to known volcanic hotspots and test the sensitivity of the inferred maps to different choices of priors and noise models.
+Because of existing high resolution resolved imaging data of Io, we have some knowledge of the ground truth so we are able to validate our model.
 The paper is organized as follows.
@@
 In \S\ref{sec:inverse_problem} we focus on the question of how to do Bayesian inference given the forward model specifications defined in \S\ref{sec:model}.
-We discuss and test different priors on map features, we quantify the information content of light curves and fit the models using Hamiltonian Monte Carlo (HMC). 
-We then test the model on realistic simulated data.
-In \S\ref{sec:results} we show the results on real IRTF data for two pairs of light curves, one pair observed in 1998 and another in 2017.
-We show the inferred maps and the parameters quantifying the location and intensity of the hot spots, we discuss the sensitivity of the results to different choices of priors and plot the inferred hotspots on an optical map of Io constructed from Galieleo observations.
+We discuss and test the use of different priors on map features and quantify the information content of light curves. 
+We then fit the model with realistic simulated data using Hamiltonian Monte Carlo (HMC).
+In \S\ref{sec:results} we show the results for IRTF data for two separate pairs of light curves, one pair observed in 1998 and another in 2017.
+We show the inferred maps and the parameters quantifying the location and intensity of the hot spots, we discuss the sensitivity of the results to different choices of priors and plot the inferred hotspots overlaid on a high resolution optical map of Io constructed from Galieleo observations.
 Finally, in \S\ref{sec:discussion} we summarize the main results of the paper and discuss potential applications of our model to observations of volcanic exoplanets.
@@
 \label{sec:data}
-The observations of Io we use in this work were first described in \cite{spencer1994} who began the observing campaign and were joined by others to collect the data we use here \citep{stansberry1997,rathbun2002,rathbun2006,rathbun2010,tate2020}.
+The observations of Io we use in this work were first described in \cite{spencer1994} who began the observing campaign and were joined by others to collect the data we use \citep{stansberry1997,rathbun2002,rathbun2006,rathbun2010,tate2020}.
 These data are currently being organized to be posted on the Planetary Data System (PDS) (Julie Rathbun, personal communication).  
 We used an early version of this data archive.
-The archive contains on the order of ~100 separate light curves of occultations of Io by Jupiter, observed at times when Io was in Jupiter's shadow (``in eclipse") so that the source of the observed flux is thermal emission.
-The geometry of the occultations is such that depending on the time of the year, Io is in eclipse during either the ingress or the egress of the occultation.
-This means that in any given year, the observations consist of only ingress (egress) observations during one fraction of the year and egress (ingress) observations during the other fraction. 
-In Paper II we plan to simultaneously fit a large fraction of the light curves in the complete archive with a generalized version of the model presented in this paper.
-
-Since we have restricted the scope of this work to fitting static maps of Io's thermal emission, we need light curves which are closely spaced in time so that Io's the surface emission doesn't drastically change between the observations.
-In addition, we need observations of both the ingress and the egress of an occultation  because Jupiter's limb sweeps across Io's projected disc at different angles at ingress and egress and this breaks the degeneracy in the position of a hotspot on the surface.
-Given these requirements, we chose a single pair of ingress/egress observations from 1998 observed 94 days apart and another pair of ingress/egress observations from 2017 observed 54 days apart.
+The final version of the archive will contain on the order of 100 separate light curves of occultations of Io by Jupiter, observed at times when Io was in Jupiter's shadow (``in eclipse"). 
+The observations for each year consist of a sequence of only ingress (egress) light curves followed by only egress (ingress) light curves. 
+This is because the geometry of the occultations of Io by Jupiter is such that depending on the time of the year, Io is in eclipse during either the ingress or the egress of the occultation.
+
+Since we have restricted the scope of this work to fitting static maps of Io's thermal emission, we selected light curves which are closely spaced in time so that Io's the surface emission doesn't drastically change between the observations.
+In addition, we selected observations of both the ingress and the egress of an occultation because Jupiter's limb sweeps across Io's projected disc at different angles at ingress and egress and this means with both kinds of light curves we can break the degeneracy in the position of the hotspots.
+The final set of light curves consists of a single pair of ingress/egress observations from 1998 observed 94 days apart and another pair of ingress/egress observations from 2017 observed 54 days apart.
 We fit one map for each of the two pairs of light curves.
-
-The 1998 occultations (Figure \ref{fig:irtf_1998_data}) have been observed with the NSFCam 1-5 $\mu m$ camera \citep{shure1994} while the 2017 occultations were observed with the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003}.
-Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress (egress) part of the entire occultation.
+In Paper II we plan to simultaneously fit nearly all light curves in the archive simultaneously.
+
+The 1998 occultations have been observed with the NSFCam 1-5 $\mu m$ camera \citep{shure1994} while the 2017 occultations were observed with the SpeX 0.8-5.5 $\mu m$ spectrographer/imager \citep{rayner2003}.
+The pair of observations from 1998 is shown in Figure \ref{fig:irtf_1998_data}, the observations from 2017 are qualitatively similar.
+Each light curve covers a timespan of $\sim 4$ minutes which is the duration of the ingress (egress) part of the complete occultation.
 The observing cadence for each light curve is about a second which sets a lower limit for the size of the inferred spatial features ($\sim 15$km).
-The selected light curves have high signal to noise ratio and they encode information about the surface emission.
-One can clearly see step-like features which correspond to a volcanic hotspot coming in or out of view during the course of the occultation.
-As with all ground-based photometry, the observations are influenced by atmospheric variability which results in some correlated noise in the light curves which needs to be accounted for in the model.
+Step-like features visible in Figure \ref{fig:irtf_1998_data} correspond to  volcanic hotspots coming in or out of view during the course of the occultation so the light curves clearly encode information about emission features on the surface of Io.
+
+Because the early version of the data archive which is going to be uploaded on the PDS does not contain estimates of errorbars for the light curves, we work around this limitation by estimating the errorbars from the data (see \S\ref{ssec:irtf_1998} for more details).
+As with all ground-based photometry, the observations are influenced by atmospheric variability which results in the presence of some correlated noise which needs to be accounted for in the model.
 
@@
 \end{figure}
-
+\vspace{2em}
 \section{Model}
 \label{sec:model}
-In this section we describe the generative model for the occultation light curves of Io.
-To simulate the observed light curves, we first need to specify the geometry of each occultation event (Section~\ref{ssec:orbital_parameters}), we then need to specify what the surface of Io looks like in a spherical harmonic basis and compute the theoretical flux at the times of observations using \textsf{starry} (Section~\ref{ssec:model_spec}), finally, we need to specify a noise model for the observed data (Section~\ref{ssec:likelihood}).
+In this section we describe the generative model for the data presented in \S\ref{sec:data}.
+To simulate the observed light curves, we first need to specify the geometry of each occultation event (Section~\ref{ssec:orbital_parameters}). 
+We then need to specify what the surface emission of Io looks like in a spherical harmonic basis and compute the theoretical flux at the times of observations using \textsf{starry} (Section~\ref{ssec:model_spec}).
+Finally, we need to specify a noise model for the observed data (Section~\ref{ssec:likelihood}).
 
@@
 All longitudes provided by Horizons are positive  in the direction of west.
-Horizons provides all ephemeris with a minimum cadence of 1 minute, we interpolate these values so that we can evaluate them for arbitrary times.
+Horizons provides all ephemeris with a minimum cadence of 1 minute, we interpolate these values so that we can evaluate them at arbitrary times.
 
@@
 axis points towards the observer and the $\hat{x}$ axis points to the right on the plane of the sky.
-The radius of the occulted sphere is fixed to 1 and the orientation is specified by three angles,
-the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the north pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the north pole is aligned with the $\hat{y}$ axis, and the phase angle \textsf{theta} which rotates the sphere around the $\hat{y}$ axis in the eastward direction.
+The radius of the occulted sphere is fixed to 1 and the orientation is specified by three angles:  the counterclockwise obliquity angle \textsf{obl} between the $\hat{y}$ axis and the north pole of the sphere, the inclination angle \textsf{inc} which is set to $90^\circ$ if the north pole is aligned with the $\hat{y}$ axis, and the phase angle \textsf{theta} which determines the rotation of the sphere around the $\hat{y}$ axis in the eastward direction.
 Expressed in terms of Horizons variables, these angles are given by $\mathrm{obl}=\textsf{NP.ang}$, $\mathrm{inc}=90^\circ-\textsf{Ob-lat}$ and $\mathrm{theta}=\textsf{Ob-lon}$.
@@
 In addition to uncertainties on the atmospheric structure, there are uncertainties associated with digitizing the data shown in Fig.~7 in \cite{lindal1981} because it is not available in table form.
-The problems with Galileo's high gain antenna prevented it from obtaining more recent radio occultations of the neutral atmosphere and Juno's orbit has thus far avoided such occultations.  
-However, over the 2023-2025 period an extended Juno mission may be able to obtain radio occultations which will refine our understanding of Jupiter's size and shape \citep{hodges2020}.
-
-Since our main focus in this work is the map model, we leave a detailed investigation into the various sources of error that go into the radius estimate for future work.
+
+Problems with Galileo's high gain antenna prevented it from obtaining more recent radio occultations of the neutral atmosphere which could be used to improve the shape measurements and Juno's orbit has thus far avoided such occultations.
+However, over the 2023-2025 period an extended Juno mission may be able to obtain radio occultations which would refine our understanding of Jupiter's size and shape \citep{hodges2020}.
+Since our main focus in this work is the map model, we leave a detailed investigation of the various sources of error that go into the radius estimate for future work.
 
@@
 
-Conditioned on fixed parameters specifying the geometry of the occultations, the \textsf{starry} model is \emph{linear} for both emitted and reflected light maps.
-\cite{luger2019a} achieved this by representing all rotations, changes of basis transformations and integrals with complicated boundaries which are needed to compute the flux as linear transformations.
+Conditioned on fixed parameters specifying the geometry of the occultations, the \textsf{starry} model is \emph{linear} in the spherical harmonic coefficients.
+\cite{luger2019a} achieved this by representing all operations needed to compute the flux as linear transformations.
 Since a sequence of linear mappings is also linear, the predicted flux can be written as
@@
 where the column vector $\mathbf{f}$ of shape $(T, 1)$ is the predicted flux for different values of the occultor position and $\mathbf{A}$ is the design matrix \citep[see appendix B.1.
-in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed for computing the integrated flux at different viewing angles of the occulted sphere (relative positions and radii of the occultor and the occulted object, rotations, basis transformations, integrals over the visible disc of the occulted object and the cosine emission law).
+in ][]{luger2021a} of shape $(T, N)$ (with $N=(l+1)^2$) which encodes all operations needed for computing the integrated flux at different viewing angles of the occulted sphere: relative positions and radii of the occultor and the occulted object, rotations, basis transformations, integrals over the visible disc of the occulted object, and the cosine emission law.
 If the geometry isn't known precisely $\mathbf{A}$ is not fixed and the model is in principle no longer linear, although one can still use the fact that it is linear when conditioned on a particular values of the nonlinear parameters to speed up inference.
@@
 Although \textsf{starry} was built around the idea of expanding surface features in a spherical harmonic basis in which we can compute all fluxes analytically, this basis may not be ideal for doing inference because it can be difficult to encode assumptions (priors) on what we expect the map to look like.
-For example, the most important constraint on the map we would like to incorporate in the model is that the intensity of the map is positive at every location. 
+For example, the most important constraint on the map we would like to incorporate in the model is that the intensity (power per unit area) of the map at any given point is positive. 
 This constraint is important not only because we want to avoid having unphysical regions in inferred maps but also because it imposes a very strong prior on the map which substantially reduces the difficulty of inference when the data is not particularly informative.
 
-There are two ways of enforcing positivity that we are aware of, both of which involve evaluating the map intensity on a fixed grid of \emph{pixels} (intensity evaluated at fixed set of points on the sphere) and disallowing negative values of those pixels because they are unphysical.
+There are two ways of enforcing positivity that we are aware of, both of which involve evaluating the map intensity on a fixed grid of \emph{pixels} (intensity evaluated at fixed set of points on the sphere) and not allowing negative values of those pixels because they are unphysical.
 The first is to fit for the spherical harmonic coefficients $\mathbf{y}$, evaluate the pixel grid at each MCMC step and reject all samples of the coefficient vector $\mathbf{y}$ which result in pixels with negative intensity.
@@
 To implement the hybrid approach we need to be able to switch back and forth between spherical harmonics and pixels.
-Given pixels $\mathbf{p}$ evaluated on an equal are Mollweide grid, the transformation from spherical harmonics $\mathbf{y}$ to $\mathbf{p}$ is given by a linear operator $\mathbf{P}$:
+Given a vector of pixel intensities $\mathbf{p}$ evaluated on an equal area Mollweide grid, the transformation from spherical harmonics $\mathbf{y}$ to $\mathbf{p}$ is given by a linear operator $\mathbf{P}$:
 \begin{equation}
@@
 Each row of $\mathbf{P}$ contains values of each of the spherical harmonic coefficients at a given point on the grid. 
+We choose to use the Mollweide grid so that each area element on the sphere has approximately the same number of pixels.
 The grid needs to be fine enough to ensure that the intensity is positive over most of the sphere.
@@
 \subsection{1998 pair of occultations by Jupiter}
+\label{ssec:irtf_1998}
 Having demonstrated that our model works well on simulated data, we turn to fitting observations of actual occultations of Io observed with the IRTF telescope.
@@
     \mathbf{f}_E&=\mathbf{A}_E'\,\mathbf{p}_E +b_E\,\mathbf{1}_{N_E}
+    \quad,
 \end{align}
@@
             \endfoot
-            $\tau$ & global pixel scale &   $0.870_{-0.221}^{+0.246}$ &  intensity
-            \\
-             $c$ & slab scale & $4304.302_{-1162.250}^{+2123.962}$ & intensity 
-            \\
-                $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage} &  $1.154_{-0.013}^{+0.014}$ & dimensionless
-            \\
-            $b_I$ & flux offset ingress & $0.014_{-0.013}^{+0.077}$ & GW/um/sr
-            \\
-            $b_E$&flux offset egress & $0.362_{-0.335}^{+0.438}$ & GW/um/sr
-            \\
-            $l_I$& errorbar scale ingress & $0.253_{-0.030}^{+0.036}$ & GW/um/sr
-            \\
-            $l_E$& errorbar scale egress &$0.461_{-0.042}^{+0.042}$ & GW/um/sr
-            \\
-            $\sigma_{\mathrm{GP}, I}$ & GP standard deviation ingress & $0.633_{-0.042}^{+0.047}$ & GW/um/sr 
-            \\
-            $\sigma_{\mathrm{GP}, E}$ & GP standard deviation egress &$0.453_{-0.052}^{+0.054}$ & GW/um/sr
-            \\
-            $\rho_{\mathrm{GP},I}$ & GP timescale ingress & $0.078_{-0.010}^{+0.011}$ & minutes
-            \\
-            $\rho_{\mathrm{GP},E}$ & GP timescale egress & $0.099_{-0.021}^{+0.027}$ & minutes
+            $\tau$ & global pixel scale &   $0.9_{-0.2}^{+0.2}$ &  intensity
+            \\
+             $c$ & slab scale & $4000_{-1000}^{+2000}$ & intensity 
+            \\
+                $a$ & \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage} &  $1.15_{-0.01}^{+0.01}$ & dimensionless
+            \\
+            $b_I$ & flux offset ingress & $0.01_{-0.01}^{+0.01}$ & GW/um/sr
+            \\
+            $b_E$&flux offset egress & $0.3_{-0.3}^{+0.4}$ & GW/um/sr
+            \\
+            $l_I$& errorbar scale ingress & $0.25_{-0.03}^{+0.04}$ & GW/um/sr
+            \\
+            $l_E$& errorbar scale egress &$0.46_{-0.04}^{+0.04}$ & GW/um/sr
+            \\
+            $\sigma_{\mathrm{GP}, I}$ & GP standard deviation ingress & $0.63_{-0.04}^{+0.05}$ & GW/um/sr 
+            \\
+            $\sigma_{\mathrm{GP}, E}$ & GP standard deviation egress &$0.45_{-0.05}^{+0.05}$ & GW/um/sr
+            \\
+            $\rho_{\mathrm{GP},I}$ & GP timescale ingress & $0.08_{-0.01}^{+0.01}$ & minutes
+            \\
+            $\rho_{\mathrm{GP},E}$ & GP timescale egress & $0.01_{-0.02}^{+0.03}$ & minutes
             \\
@@
             \endfoot
-            $\tau$ & global pixel scale &   $0.973_{-0.247}^{+0.255}$ &  intensity
-            \\
-             $c$ & slab scale & $5866.860_{-1580.812}^{+2527.995}$ & intensity 
-            \\
-                $a$ &   \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage}  & $1.434_{-0.010}^{+0.011}$ & dimensionless
-            \\
-            $b_I$ & flux offset ingress & $0.025_{-0.024}^{+0.140}$ & GW/um/sr
-            \\
-            $b_E$& flux offset egress & $1.026_{-0.263}^{+0.238}$ & GW/um/sr
-            \\
-            $l_I$ & errobar scale ingress &$0.971_{-0.056}^{+0.056}$ & GW/um/sr
-            \\
-            $l_E$& errorbar scale egress & $0.520_{-0.093}^{+0.079}$ & GW/um/sr
-            \\
-            $\sigma_{\mathrm{GP}, I}$ & GP standard deviation ingress  & $0.126_{-0.055}^{+0.129}$ & GW/um/sr 
-            \\
-            $\sigma_{\mathrm{GP}, E}$ & GP standard deviation egress & $0.601_{-0.093}^{+0.083}$ & GW/um/sr
-            \\
-            $\rho_{\mathrm{GP},I}$ &  GP timescale ingress & $2.160_{-2.030}^{+3.333}$ & minutes
-            \\
-            $\rho_{\mathrm{GP},E}$ & GP timescale egress & $0.020_{-0.013}^{+0.011}$ & minutes
+            $\tau$ & global pixel scale &   $1.0_{-0.2}^{+0.3}$ &  intensity
+            \\
+             $c$ & slab scale & $6000_{-2000}^{+3000}$ & intensity 
+            \\
+                $a$ &   \begin{minipage}{0.2\textwidth}\shortstack[l]{relative change in \\map amplitude}\end{minipage}  & $1.43_{-0.01}^{+0.01}$ & dimensionless
+            \\
+            $b_I$ & flux offset ingress & $0.03_{-0.02}^{+0.14}$ & GW/um/sr
+            \\
+            $b_E$& flux offset egress & $1.0_{-0.3}^{+0.2}$ & GW/um/sr
+            \\
+            $l_I$ & errobar scale ingress &$0.97_{-0.06}^{+0.06}$ & GW/um/sr
+            \\
+            $l_E$& errorbar scale egress & $0.52_{-0.09}^{+0.08}$ & GW/um/sr
+            \\
+            $\sigma_{\mathrm{GP}, I}$ & GP standard deviation ingress  & $0.13_{-0.06}^{+0.13}$ & GW/um/sr 
+            \\
+            $\sigma_{\mathrm{GP}, E}$ & GP standard deviation egress & $0.60_{-0.09}^{+0.08}$ & GW/um/sr
+            \\
+            $\rho_{\mathrm{GP},I}$ &  GP timescale ingress & $2.0_{-2}^{+3}$ & minutes
+            \\
+            $\rho_{\mathrm{GP},E}$ & GP timescale egress & $0.02_{-0.01}^{+0.01}$ & minutes
             \\

### 2021-06-24 paper/paper.tex
Hopefully final changes

@@
     We built a generative model for the observed occultation light curves using the code \textsf{starry} which enables fast, analytic, and differentiable computation of occultation light curves in emitted and reflected light.
-    Using this model we are able to recover surface emission maps of Io containing known volcanic hotspots, without having to make assumptions about the locations, shapes or the number of these hotspots.
+    Using this model we are able to recover surface thermal emission maps of Io containing known volcanic hotspots, without having to make assumptions about the locations, shapes or the number of the hotspots.
     Our model is also directly applicable to the problem of mapping the surfaces of stars and exoplanets. \href{https://github.com/fbartolic/volcano}{\color{linkcolor}\faGithub}
@@
 
-Switching from pixels to spherical harmonics is somewhat more complicated because $\mathbf{P}$ is in general not a square matrix so we cannot compute its inverse to obtain the inverse transform.
+Switching from pixels to spherical harmonics is somewhat more complicated because $\mathbf{P}$ is not in general a square matrix so we cannot compute its inverse to obtain the inverse transform.
 Instead, we can compute an approximate inverse (a pseudoinverse) $\mathbf{P}^\dagger$ by solving the linear system $\mathbf{P}\,\mathbf{P}^\dagger=\mathbf{I}$, where $\mathbf{I}$ is the identity matrix.
@@
 When using pixels to impose a positivity constraint on the spherical harmonic map we need to make sure that the number of pixels is greater than the number of spherical harmonic coefficients by a factor of a few to ensure positivity approximately everywhere on the sphere.
-In practice we find that we need to use at least 4 times as many pixels as spherical harmonics which means that the computational cost of this model is higher than if we just fit for spherical harmonic coefficients.
+In practice we find that we need to use at least 4 times as many pixels as spherical harmonics which means that the computational cost of this model is larger than for a pure spherical harmonic model.
 
@@
 \end{equation}
-where $\sigma_n$ is the errorbar for the n-th data point.
+where $\sigma_n$ is the errorbar for the n-th data point (a free parameter).
 Since we fit multiple independent light curves the total log likelihood is the sum of individual likelihoods defined in Equation~(\ref{eq:likelihood}).
@@
 
-The predicted fluxes are given by 
+The predicted fluxes for the ingress and egress of the occultation are given by 
 \begin{align}
@@
 The total log likelihood is the sum of the log likelihoods for individual light curves (Equation~(\ref{eq:likelihood})). 
-To compute it we also need to specify the data covariance matrix defined in Equation~(\ref{eq:data_covariance_element}).
+To compute it we need to specify the data covariance matrix defined in Equation~(\ref{eq:data_covariance_element}).
 Each element of the covariance matrix consists of a white noise component (errorbars) and a correlated noise component (Gaussian Process).
-Since the IRTF light curves are not provided with estimated errorbars, we choose to fit for all errorbars simultaneously using a hierarchical approach in which we assign a global scale $l$ for all errorbars in a given light curve and we draw each individual errobar from a Half Normal distribution with standard deviation equal to that scale.
-That is, we have 
+Because the IRTF light curves from the preliminary archive of occulation light curves do not contain robust estimates of the errorbars and the number of data points per light curve is quite small, we choose to treat each errorbar as a free parameter and fit for all errorbars using a hierarchical model.
+We assume that there is a common global scale $l$ for all data point in a given light curve and that the errorbar for each data point is drawn from a Half Normal distribution with a scale parameter equal to $l$.
+In other words, we have 
 \begin{align}
-    \sigma_{i,I}&\sim \mathcal{N}^+(0, l_E),\quad i=1,\dots,N_I\\
-    \sigma_{i,E}&\sim \mathcal{N}^+(0,l_I),\quad i=1,\dots, N_E
+    \sigma_{i,I}&\sim \mathrm{Half}-\mathcal{N}(l_I),\quad i=1,\dots,N_I\\
+    \sigma_{i,E}&\sim \mathrm{Half}-\mathcal{N}(l_E),\quad i=1,\dots, N_E
 \end{align}
-where $\sigma_{i,I}$ are the errorbars for the ingress light curve and $\sigma_{i,E}$ are the errorbars for the egress light curve.
-The symbol $\mathcal{N}^+$ denotes a truncated Gaussian distribution restricted to positive values.
-Treating errorbars as free parameters means that we are introducing hundreds of more parameters (as many as there are data points) which is not an issue as long as these parameters are constrained by the data and our model is regularized.
-The noise model as defined above is extremely flexible, it can account for a given feature in the light curve by inflating individual errorbars (white noise) or by varying the characteristic timescale $\rho_\mathrm{GP}$ in the Mat\'ern 3/2 kernel.
-All model parameters and their associated priors are listed in Table~\ref{tab:priors}.
+where $\sigma_{i,I}$ are the errorbars for the ingress light curve, $\sigma_{i,E}$ are the errorbars for the egress light curve, $l_I$ is the common scale for the ingress light curve errorbars and $l_E$ is the scale for the egress light curve errorbars.
+
+By fitting for errorbars in this way we do not have to make any parametric assumptions about the dependence of the variance of the data on the measured flux and we are able to account for outliers and heteroscedasticity in the data.
+Although this means that we are introducing hundreds of additional parameters in the model, this is not a problem for the Hamiltonian Monte Carlo sampler when the parameters are well constrained by the data and the model is regularized.
+The noise model as defined above is extremely flexible -- a given feature in the light curve can be accounted for by inflating the errorbars or varying the timescale or the variance of the Gaussian Process with the Mat\'ern 3/2 kernel.
 
@@
             The subscript $I$ denotes parameters associated with the ingress light curve while the subscript $E$ denotes parameters associated with the egress light curve.
-$t_{\mathrm{max},I}$ and  $t_{\mathrm{max},E}$ are the durations of the ingress and egress occultations respectively.
-            The symbol $\mathcal{N}^+$ refers the normal distribution truncated at zero so that it only has support for positive values.
+$t_{\mathrm{max},I}$ and  $t_{\mathrm{max},E}$ are the durations of the ingress and egress occultation light curves respectively.
             }
@@
             \\
-            $p_i, \quad i=1,\dots,D$& pixels & $\mathcal{N}^+(0, \tau\lambda_i)$, $\lambda_{i} =c \overline{\lambda}_{i}/\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{i}^{2}}$
+            $p_i, \quad i=1,\dots,D$& pixel intensities& $\mathrm{Half}-\mathcal{N}(\tau\lambda_i)$, $\lambda_{i} =c \overline{\lambda}_{i}/\sqrt{c^{2}+\tau^{2} \overline{\lambda}_{i}^{2}}$
             %
@@
             %
-            $l_I$, $l_E$& errorbar global scale&$\mathcal{N}^+(0,0.1)$
+            $l_I$, $l_E$& errorbar global scale&$\mathrm{Half}-\mathcal{N}(0.1)$
             %
@@
             $\sigma_{i,I}$, $\sigma_{i,E},\quad i=1,\dots,N$& individual errorbars&
-            $\mathcal{N}^+(0,l_I),\quad \mathcal{N}^+(0,l_E)$
-            %
-            \\
-            %
-            $\sigma_{\mathrm{GP}, I}$, $\sigma_{\mathrm{GP}, I}$ & GP standard deviation&$\mathcal{N}^+(0,0.1),\quad \mathcal{N}^+(0,0.1)$
-             %
-            \\
-            %
-            $\rho_{\mathrm{GP},I}$, $\rho_{\mathrm{GP},E}$ & GP timescale  & $\mathcal{N}^+(0, t_{max, I}),\quad  \mathcal{N}^+(0, t_{max, E})$
+            $\mathrm{Half}-\mathcal{N}(l_I),\quad \mathrm{Half}- \mathcal{N}(l_E)$
+            %
+            \\
+            %
+            $\sigma_{\mathrm{GP}, I}$, $\sigma_{\mathrm{GP}, I}$ & GP standard deviation&$ \mathrm{Half}-\mathcal{N}(0.1),\quad \mathrm{Half}-\mathcal{N}(0.1)$
+             %
+            \\
+            %
+            $\rho_{\mathrm{GP},I}$, $\rho_{\mathrm{GP},E}$ & GP timescale  & $ \mathrm{Half}-\mathcal{N}( t_{max, I}),\quad  \mathrm{Half}-\mathcal{N}(t_{max, E})$
         \\
@@
 
-To fit the model we sample the posterior using the NUTS sampler for 1000 warm-up steps and 3000 final steps and as before, we monitor divergences and the R-hat statistic to ensure convergence.
-The inferred map for the 1998 pair of events is shown in Figure~\ref{fig:irtf_1998} and the median, 16th and 84th percentile estimates of model parameters from posterior samples are shown in Table~\ref{tab:irtf_1998}.
+All model parameters and their associated priors are listed in Table~\ref{tab:priors}. 
+To fit the model we sample the posterior using the NUTS sampler for 1000 warm-up steps and 3000 final steps, monitoring divergences and the R-hat statistic to ensure convergence.
+The inferred map for the 1998 pair of events is shown in Figure~\ref{fig:irtf_1998} and the median, 16th and 84th percentile estimates of model parameters from the posterior samples are shown in Table~\ref{tab:irtf_1998}.
 The inferred map has two distinct hot spots, a bright hotspot in the Eastern hemisphere and a faint hotspot in the western hemisphere.
-The orange lines in the second panels from the bottom are posterior samples of flux from the full model which includes the map model and the Gaussian Process.
+The orange lines visible in the second pair of panels from the bottom are posterior samples for flux from the complete model (map model plus the gaussian process noise model).
+
 The bottom panel shows the residuals with respect to the median flux.
-Each data point is shown with the median prediction of its errorbar.
-The posterior distribution for the errorbars is shown in Figure~\ref{fig:irtf_1998_errorbars}.
-Both the global scale for of the errorbars and the individual errorbars are well constrained by the data. 
+Each data point is shown with the median estimate of its errorbar while the full posterior for all erorrbars is shown in Figure~\ref{fig:irtf_1998_errorbars}.
+Both the global scale for the errorbars and the individual errorbars are well constrained by the data. 
 The outlier points are naturally accounted for in our model because those points end up having higher variance.
+Despite the fact that our noise model is very flexible, it does not seem to overfit the data because the two major steps in the light curves don't end up being absorbed by the noise model.
+The Gaussian Process captures the  variation in the data which is due to atmospheric variability, the emission due to surface features which are too faint to be well constrained by the physical model and also the limitation of the physical model to capture the true size of the spot.
+There is a trade-off between the explanatory power of the noise model and the physical model. 
+In general, we expect that a given feature in the light curve will be accounted for by the physical model if the physical model provides a better explanation for the data than the noise model.
+We will return to this point shortly.
 
@@
 We fit a single map to both observations simultaneously although we allow for a difference in the overall amplitude of the map between ingress and egress.
-Our model includes a Gaussian Process which accounts for both the correlated noise due to seeing in the data, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
-We also fit for all errorbars simultaneously using a hierarchical model and we plot the median estimates of those errorbars.
+The model includes a Gaussian Process to account for correlated noise caused by atmospheric variability, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
+We treat all errorbars as random variables and plot the median posterior estimates of those errobars. 
         The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
@@
 
-Despite the fact that our noise model is extremely flexible, it does not seem to overfit the data because the two major steps in the light curves correspond to spots on the map.
-The Gaussian Process accounts for the  variation in the data due to atmospheric variability, the emission due to surface features which are too faint to be well constrained by the physical model and the limitation of the physical model to capture the true size of the spot.
-There is a trade-off between the explanatory power of the noise model and the physical model. 
-In general, we expect that a given feature in the light curve will be accounted for by the physical model if the physical model provides a better explanation for the data than the noise model.
-We will return to this point shortly.
-
-%\begin{figure}[t!]
-%    \begin{centering}
-%    \includegraphics[width=\linewidth]{figures/irtf_1998_errorbars.pdf}
-%    \oscaption{irtf_main_plots}{%
-%        Posterior distribution for the errorbars of the 1998 pair of light curves shown in Figure~\ref{fig:irtf_1998}. 
-%        Each color corresponds to a single data point in the light curve.
-%        The errorbars are estimated using a hierarchical model in which we assume  that each errobar is drawn from a Half Gaussian distribution with a global scale parameter common to all errorbars in a single light curve.
-%       \label{fig:irtf_1998_errorbars}
-%    }
-%    \end{centering}
-%\end{figure}
-%
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/irtf_1998_errorbars.pdf}
+    \oscaption{irtf_errorbar_posteriors}{%
+        Posterior distribution for the errorbars of the 1998 pair of light curves shown in Figure~\ref{fig:irtf_1998}. 
+        Each color corresponds to a single data point in the light curve.
+        The errorbars are estimated using a hierarchical model in which we assume  that each errorbar is drawn from a Half Gaussian distribution with a scale parameter common to all errorbars in a single light curve.
+       \label{fig:irtf_1998_errorbars}
+    }
+    \end{centering}
+\end{figure}
+
 \renewcommand*{\arraystretch}{1.4}
@@
             \caption{%
-                Inferred parameters for the pair of occultations observed in 1998 using the IRTF telescope.
+                Inferred parameters for the 1998 pair of occultations observed using the IRTF telescope.
                 }
@@
 
-To obtain some measure of the location of the inferred spots and its uncertainty, for each posterior sample of the spherical harmonic coefficients $\mathbf{y}$ we find the local maximum of intensity in a region around each of the spots, we then compute percentile estimates of spot latitude and longitude.
+To obtain some measure of the location of the inferred spots and its uncertainty, for each posterior sample of the spherical harmonic coefficients $\mathbf{y}$ we find the local maximum of intensity in a region around each of the spots and then compute percentile estimates of the spot latitude and longitude.
 In addition to the locations of the spots, we also compute the total power emitted within a 15 degree range in latitude and longitude around the (inferred) center of the spots.
 Both of these quantities are listed in Table~\ref{tab:irtf_1998_derived}. 
-
 Figure~\ref{fig:irtf_1998_spots} shows  a contour map of both hot spots overlaid on top of the U.S.
 Geological Survey's map of the surface of Io \citep{williams2011} which was constructed from observations by the Galileo satellite.
-The plot shows the error in the inferred latitude and longitude for each spot (white lines) and a contour map computed from the median posterior estimate of the map.
+The plot shows the error for the inferred latitude and longitude for each spot (white lines) and a contour map computed from the median posterior estimate of the map.
 The contour lines correspond to the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
 
-The location of the bright hotspot is $16.414_{-0.011}^{+0.027}\quad^\circ$ N latitude and $53.107_{-0.033}^{+0.041}\quad^\circ$ E longitude which corresponds to the location of Loki Patera.
-The faint hot spot is at $-15.756_{-11.382}^{+3.812}\quad ^\circ$ N latitude and $321.568_{-4.208}^{2.803}\quad^\circ$ E longitude which is the Kanehekili Fluctus lava flow.
-The error on the inferred position of peak intensity of the Loki Patera hotspot is only a fraction of a degree which is much smaller than the minimum resolution of the map features set by the degree of the map; this corresponds to an uncertainty of less than a kilometer on the surface of Io.
+The location of the bright hotspot is $16.30_{-0.01}^{+0.03}\quad^\circ$ N latitude and $306.90_{-0.01}^{+0.01}\quad^\circ$ W longitude which corresponds to the location of Loki Patera.
+The faint hot spot is at $-16_{-4}^{+8}\quad ^\circ$ N latitude and $37.4_{-0.2}^{+0.8}\quad^\circ$ W longitude which is the Kanehekili Fluctus lava flow.
+The error for the inferred position of peak intensity of the Loki Patera hotspot is only a fraction of a degree which is much smaller than the minimum resolution of the map features set by the degree of the map.
+This corresponds to an uncertainty of less than a kilometer on the surface of Io.
 Thus, \textbf{despite the fact that at $l=20$ the resolution of maps is limited to about $9^\circ$, we can constrain the centroid of the spots much more precisely}.
-We should note however that this errorbar does not include a possible systematic shift in position due to a wrong estimate of Jupiter's effective radius (see Section~\ref{ssec:effective_radius}) or an error in the ephemeris data.
+We should note however that this uncertainty does not include a possible systematic shift in position due to a wrong estimate of Jupiter's effective radius (see Section~\ref{ssec:effective_radius}) or an error in the ephemeris data.
 
@@
             \caption{%
-                Derived parameters of the two hot spots visible in Figure~\ref{fig:irtf_1998}.
+                Derived properties of the two hot spots visible in Figure~\ref{fig:irtf_1998}.
                 The latitude and longitude of the spots are estimated by finding the peak intensity of each spot for each posterior sample.
-            The power of the spot is defined as the total emission from within a 15 degree circle around the (inferred) location of the spot.
+            The power of the spot is defined as the total emission from within a 15 degree circle centered at the inferred location of the spot.
         }
@@
         The left hotspot is centered around Loki Patera, the right hotspot is centered at the Kanehekili Fluctus lava flow.
-The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of ``background'' region around the spot.
+The contour lines show the 5th, 50th, and 95th percentiles of intensity above an arbitrarily defined intensity of the ``background'' region around the spot.
         The asymmetric white cross in the center of the contours in each panel shows the uncertainty in the inferred position of the peak intensity of the hotspot.
@@
 The main difference in the inferred map compared to Figure~\ref{fig:irtf_1998} is that there are two extra spots visible in the map.
-The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in ingress light curve and 3.8 minutes in the egress light curve, which is due to  Loki Patera coming out and into view during the occultation.
-The model inflates the errorbars around those times because it unable to make the spot small enough.
-This results in the single hot spot at the location of Loki Patera shown in Figure~\ref{fig:irtf_1998} morphing into two spots.
-While this feature is almost certainly spurious, the other spot in the northwestern hemisphere appears more likely to be real.
+The two spots in the eastern hemisphere are the result of the model struggling to explain the main feature in the light curve at around 3.2 minutes in the ingress light curve and 3.8 minutes in the egress light curve which is due to  Loki Patera coming out and into view during the occultation.
+The model inflates the errorbars around those times because it unable to make the spot small enough, this results in the single hot spot at the location of Loki Patera shown in Figure~\ref{fig:irtf_1998} morphing into two spots.
+While this feature is almost certainly spurious, the other spot in the northwestern hemisphere is more likely to be real.
 Looking at the miniature maps in Figure~\ref{fig:irtf_1998_no_GP}, this spot is in view only at egress and it corresponds to a small step in the light curve starting at 0.9 minutes.
-The estimated location of this spot is approximatel $\sim 20\quad^\circ$ N latitude and $\sim 69\quad^\circ$ W longitude.
+The estimated location of this spot is approximately $\sim 20\quad^\circ$ N latitude and $\sim 69\quad^\circ$ W longitude.
 This location corresponds to southern end of the mountain Mongibello Mons but there are no known persistent hotspots at that location so we cannot say if the hotspots is real or not without independently detecting it in other light curves.
@@
 
-One other notable feature in Figure~\ref{fig:irtf_1998_no_GP} is that the first step in the ingress light curve at around 0.6 minutes isn't fully accounted for by the model.
+One other notable feature in Figure~\ref{fig:irtf_1998_no_GP} is that the first step in the ingress light curve at around 0.6 minutes is not fully accounted for by the model.
 Since the model had no trouble accounting for a similar a step for simulated data shown in Figure~\ref{fig:ingress_egress_sim_snr_50} the reason why it didn't do so in this case is likely because doing so would result in a poorer fit for the egress light curve.
@@
         Same as Figure~\ref{fig:irtf_1998} except this figure shows the output of a model which does not include a Gaussian Process to account for correlated structure in the data.
-        As a result, the model tries to account for correlations in the data by placing two extra spots on the map and inflating errorbars.
+        As a result, the model tries to capture the correlations in the data by placing two extra spots on the map and inflating the errorbars.
         At least one of the two extra spots is artificial. 
@@
 We fit a single map to both observations simultaneously although we allow for a difference in the overall amplitude of the map between ingress and egress.
-Our model includes a Gaussian Process which accounts for both the correlated noise due to seeing in the data, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
-We also fit for all errorbars simultaneously using a hierarchical model and we plot the median estimates of those errorbars.
+The model includes a Gaussian Process to account for correlated noise caused by atmospheric variability, and the fact that our limited resolution map cannot fully capture the sharp steps in data.
+We treat all errorbars as random variables and plot the median posterior estimates of those errobars. 
          The plot shows  the inferred maps (top row), the same maps from the perspective of the observer during the occultation (small circles), the light curves and posterior samples of the flux including the Gaussian Process (orange lines), and the residuals with respect to a median flux estimate.
@@
             \\
-            $l_I$ & errobar scale ingress &$0.97_{-0.06}^{+0.06}$ & GW/um/sr
+            $l_I$ & errorbar scale ingress &$0.97_{-0.06}^{+0.06}$ & GW/um/sr
             \\
@@
             \caption{%
-                Derived parameters of the two hot spots visible in Figure~\ref{fig:irtf_2017}.
+                Derived properties of the two hot spots visible in Figure~\ref{fig:irtf_2017}.
                 The latitude and longitude of the spots are derived by computing the centroid of points around the spots which are in the 90th percentile of intensity.
-            The power is defined as the total emission from within a 15 degree circle around the (inferred) location of the spot.
+            The power is defined as the total emission from within a 15 degree circle centered at the inferred location of the spot.
         }
@@
 \subsection{Occultation mapping of Io}
-We have presented a novel method for mapping the volcanic emission on Io from occultation light curves.
+We have presented a novel method for mapping the volcanic emission on Io using occultation light curves.
 The method relies on the \textsf{starry} algorithm which enables fast analytic computation of occultation light curves by expanding the surface emission map in spherical harmonics.
-Our method is different from past work because we do not assume we know where the volcanic features are located on the surface of Io, how many there are or what they look like.
+Our method is different from past work because we do not assume that we know where the volcanic features are located on the surface of Io, how many there are or what they look like.
 Instead, we place weaker assumptions on the global structure of the map by requiring that the inferred map has positive intensity everywhere and most importantly, that it is \emph{sparse} \footnote{\cite{aizawa2020} also find the sparsity assumption useful in the context of exoplanet mapping.}.
-Besides the model for the surface map, our method also incorporates a sophisticated noise model which includes a Gaussian Process and a hierarchical model for the (unknown) errorbars.
+Besides the model for the surface map, our method also incorporates a sophisticated noise model which includes a Gaussian Process and a hierarchical model for the errorbars.
 As a result of the sparsity and positivity constraints and the flexibility of the noise model,
-our model is parsimonious: it places features on the map only if the data provides strong evidence for the existence of those features.
+our model is parsimonious -- it places features on the map only if the data provides strong evidence for the existence of those features.
 This property is not always desirable but it works very well for Io, a moon whose surface is covered with small, highly localized, and bright volcanic hotspots.
-Our model is substantially more flexible than parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface.
-The computational cost of the parametric models is comparable to our approach.
+Our model is substantially more flexible than parametric methods which assume some fixed number of spots on the surface of Io and parametrize the spot properties because we do not need to make such strong assumptions about the surface features.
+The computational cost is small and it is comparable to parametric models.
 
 To test our method we first fit a simulated dataset and then observations of real occultations of Io by Jupiter, observed using NASA's Infrared Telescope Facility.
-We choose two pairs of light curves to demonstrate that the model can recover known hotspots.
+We chose two pairs of light curves to demonstrate that the model can recover known hotspots.
 Each pair consists of an ingress observation and an egress observation of an occultation. 
@@
 Although we can still constrain the peak intensity of hotspots (or some other measure of the center of emission) with much higher precision, we lose the ability to resolve two spots close to each other and the ability to constrain the actual size of the spots.
-It is quite possible that there is a way around this problem if we compute the various integrals in \textsf{starry} numerically using high precision arithmetic.
+It is possible that there is a way around this problem if we compute the various integrals in \textsf{starry} numerically using high precision arithmetic.
 Since all these operations are contained in the design matrix $\mathbf{A}$ (assuming that the ephemeris is fixed) we would only need to do the expensive computation once for each occultation.
@@
 \label{ssec:discussion_exoplanets}
-Hot Super Earths with (probably) molten surfaces such as 55 Cancri e are prime targets for future observations with the James Webb Space Telescope (JWST) \citep{samuel2014,henning2018}.
+Hot Super Earths with (likely) molten surfaces such as 55 Cancri e are prime targets for future observations with the James Webb Space Telescope (JWST) \citep{samuel2014,henning2018}.
 The model we have presented in this paper can easily be applied to observations of exoplanets. 
 In fact, one of the motivations for this work was to test methods developed largely for the purpose of mapping exoplanets in a context where the ground truth is more easily accessible because Io is in the Solar System.
-To apply our model to exoplanet observations we just need to compute the design matrix $\mathbf{A}$ given a specification of the planet's orbit which is very straightforward in \textsf{starry}
-and since the observations of the secondary eclipses (occultations) of exoplanets will never be as high quality as observations of Io, the limited resolution of spherical harmonic maps is more than sufficient for modeling exoplanet observations.
-The question of what kind of features on the surfaces of volcanic exoplanets it will be possible to constrain with secondary eclipse observations using JWST and with what precision is one we aim to address in future work.
+To apply our model to exoplanet observations we simply need to compute the design matrix $\mathbf{A}$ given a specification of the planet's orbit which is very straightforward in \textsf{starry}.
+Since the observations of the secondary eclipses (occultations) of exoplanets will never be as high quality as observations of Io, the limited resolution of spherical harmonic maps is more than sufficient for modeling exoplanet observations.
+The question of what kind of features on the surfaces of volcanic exoplanets it will be possible to constrain with secondary eclipse observations using JWST is one that can be answered using the framework presented in this paper.
 
 Besides being useful for modeling secondary eclipses of volcanic Super-Earths, our model can be used for modeling surfaces of gaseous exoplanets with sparse features.
-These will be much easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
+These will be easier to observe with JWST  than Super-Earths because of their larger size and higher surface temperatures.
 Even if the sparsity assumption is not valid for these types of planets the hybrid pixel/spherical harmonic model can be easily be used with a different set of priors more appropriate for these observations.

### 2021-06-24 paper/figures/irtf_errorbar_posteriors.py
forgot to include this script in the repo

@@ -1,0 +1,39 @@
+import numpy as np
+from matplotlib import pyplot as plt
+import pickle as pkl
+
+import seaborn as sns
+
+with open("scripts/irtf_1998_samples.pkl", "rb") as handle:
+    samples = pkl.load(handle)
+
+fig, ax = plt.subplots(1, 2, figsize=(12, 4), sharex=True)
+fig.subplots_adjust(hspace=0.3)
+
+for i in range(len(samples["f_err_in_mod"][0])):
+    sns.distplot(
+        samples["f_err_in_mod"][:, i],
+        hist=False,
+        norm_hist=True,
+        kde_kws={"alpha": 0.7, "lw": 1},
+        ax=ax[0],
+    )
+for i in range(len(samples["f_err_in_mod"][0])):
+    sns.distplot(
+        samples["f_err_eg_mod"][:, i],
+        hist=False,
+        norm_hist=True,
+        kde_kws={"alpha": 0.7, "lw": 1},
+        ax=ax[1],
+    )
+
+ax[0].set_xlabel("Ingress errorbars [GW/um/sr]")
+ax[1].set_xlabel("Egress errorbars [GW/um/sr]")
+fig.text(0.07, 0.5, "Posterior probability", va="center", rotation="vertical")
+
+for a in ax:
+    a.grid()
+    a.set_xlim(-0.1, 2.0)
+    a.set_ylabel("")
+
+fig.savefig("irtf_1998_errorbars.pdf", bbox_inches="tight", dpi=500)
